### 2017-04-12 paper/paper.tex
Initial paper commit

\documentclass{article}
\usepackage{amsmath, amsthm, amssymb}
\newtheorem{theorem}{Theorem}

\title{Differential invariant signatures for planar Lie group transformations of
images}
\date{\today}
\author{Huey, Duey, and Louey}

\begin{document}
\maketitle

\section{Introduction}
\subsection{Invariants, hey!}
literature (Cartan, Olver, Russians, Draisma), motivation, etc,

\subsection{Invariants for images}
Colour and the lack of independence. Fractal dimension

Calculating derivatives (discussion on desirability thereof).
Euclidean-invariant smoothing is a thing, other groups not so much.

\subsection{Introducing the cast}
Define each group, mesh image of what transformations can look like

\subsection{Technical wank}
Completeness, degeneracy, moving frames as concept, table of numbers of
derivatives, all that jazz, maybe scaling technique
for dealing with invariants of non-unit weight

\section{The invariants}
One subsection for each group. Mathematical details/theorem/derivation, no
examples
\subsection{SA(2), E(2), SE(2), and Sim(2), or some better title}
\begin{theorem}
  SA(2) invariants up to second order are:
  I0, I1, I2 from Jupyter document
\end{theorem}

Corollary for E(2), SE(2), R2 and Sim(2)

Commentary on geometric interpretation of these things.
\subsection{A(2)}
\begin{theorem}
  General affine invariants using transvectants
\end{theorem}
Relative invariants and weights go here? probably

\subsection{M\"obius and Projective (finite dimensional)}
\begin{theorem}
  Moving frame invariants for M\"obius
\end{theorem}
\begin{theorem}
  Moving frame invariants for Projective
\end{theorem}

\subsection{Infinite dimensional diff groups (diff con, diff vol, diff)}

\section{Computational examples}
General idea of what we've done. Experiment to compare e.g. SA(2) and
Sim(2). Contrast between intuitive notion of complexity (described by
number of parameters in group) versus reality.

\subsection{Examples of all of 'em}
Big matrix of pictures for comparison purposes

\subsection{Hat tip to practicality: smoothing for E(2) and subgroups thereof}
Allows these groups to be used on real (i.e. not particularly
differentiable) images

\subsection{colour}

\section{Discussion and Conclusion or whatever}
Why are we using invariants? 
This idea is extremely local, can global information be better utilised?
Relation to using more computationally
tractable e.g. SA(2) not E(2)
Comparison with other invariant forms - e.g. Fourier, integral, etc.

\subsection{Future work}
Can we do better with the weights?
Can we do better with derivatives?
Projection onto Riemann sphere?
Noise. Ugh.

\end{document}

### 2017-05-03 main.tex
everything, pre-prune

\documentclass[11pt]{article}
% mathtools for \coloneqq
\usepackage{amsmath, amssymb, mathtools}

\title{Invariant signatures}
\date{\today}
\author{Huey, Duey, and Louey}

\begin{document}
\maketitle

\section{Introduction}
\subsection{Notation}
Let $G$ be a planar transformation group that acts on $k$-colour images $f
\colon \mathbb{R}^2 \rightarrow \mathbb{R}^k$ by $\varphi \cdot f \coloneqq
f \circ \varphi^{-1}$, where $\varphi \in G$.

When referring to coordinates, with $x \in \mathbb{R}^2$, we write $\hat{x}
= \varphi(x)$  and define the image post-transformation in the new
coordinates as
\begin{equation}
  \hat{f}(\hat{x}) = f(x).
\end{equation}
We derive relationships between the derivatives before and after
transformation by the chain rule:
\begin{equation*}
  f_{, i} = \hat{f}_{,k} \varphi_{k, i} 
\end{equation*}
etc.

\section{The Stamp Collection I: The Affine group and its subgroups}
In this section we consider all the groups whose transformation is of the
form. For these groups, the change of variables formulae are, in tensor,
and matrix notations,
\begin{align}
  f_{,i} &= \hat{f}_{, k} a_{ki} & \nabla f &= A^T \nabla \hat{f} \\
  f_{,ij} &= \hat{f}_{, kl} a_{ki} a_{lj} & 
  \nabla^2 f &= A^T \nabla^2 \hat{f} A
\end{align}
$\varphi(x) = Ax + b$ for some matrix $A$ and vector $b$.

\subsection{SE(2)}
In this case we have $A^TA = I$ and $\det A = 1$.

\end{document}

### 2017-05-03 ImageInvariant.m

@@ -1,0 +1,243 @@
+classdef ImageInvariant
+    properties
+        % Note: default values are in the "parseinputs" function below
+        h
+        f
+        xlim
+        ylim
+    end
+    methods
+        function self = ImageInvariant(f, varargin)
+            self.f = f;
+            params = parse_inputs(varargin{:});
+            fields = fieldnames(params);
+            for i = 1:numel(fields)
+                self.(fields{i}) = params.(fields{i});
+            end
+        end   
+        function [F, X, Y] = evaluate(self)
+            x = self.xlim(1):self.h:self.xlim(2);
+            y = self.ylim(1):self.h:self.ylim(2);
+            [X, Y] = meshgrid(x, y);
+            F = self.f(X, Y);
+        end
+        function varargout = SA2_signature(self)
+            F = self.evaluate();
+            [~, Fx, Fy, Fxx, Fxy, Fyy, Fxxx, Fxxy, Fxyy, Fyyy] = ...
+                compute_derivatives(F, 3, self.h);
+            I0 = F;
+            I1 = Fxx.*Fyy - Fxy.^2;
+            I2 = Fy.^2.*Fxx - 2*Fx.*Fy.*Fxy + Fx.^2.*Fyy;
+            I3 = Fyy.*Fxxy.^2 - Fyy.*Fxxx.*Fxyy - Fxy.*Fxxy.*Fxyy + ...
+                Fxx.*Fxyy.^2 + Fxy.*Fxxx.*Fyyy - Fxx.*Fxxy.*Fyyy;
+            I4 = Fy.*Fyy.*Fxxx - 2*Fy.*Fxy.*Fxxy - Fx.*Fyy.*Fxxy + ...
+                Fy.*Fxx.*Fxyy + 2*Fx.*Fxy.*Fxyy - Fx.*Fxx.*Fyyy;
+            varargout = {I0, I1, I2, I3, I4}; 
+        end
+        function varargout = SE2_signature(self)
+            F = self.evaluate();
+            [~, Fx, Fy, Fxx, ~, Fyy] = ...
+                compute_derivatives(F, 2, self.h);
+            I0 = F;
+            I1 = Fx*Fx + Fy*Fy;
+            I2 = Fxx + Fyy;
+            varargout = {I0, I1, I2};
+        end
+        function varargout = Sim2_signature(self)
+           F = self.evaluate();
[…]

### 2017-05-03 SA2sig.m

@@ -1,0 +1,19 @@
+function sig = SA2sig(h, F)
+[Fx, Fy] = gradient(F, h);
+[Fxx, Fxy] = gradient(Fx, h);
+[~, Fyy] = gradient(Fy, h);
+[Fxxx, Fxxy] = gradient(Fxx, h);
+[~, Fxyy] = gradient(Fxy, h);
+[~, Fyyy] = gradient(Fyy, h);
+
+I0 = F;
+I1 = Fxx.*Fyy - Fxy.^2;
+I2 = Fy.^2.*Fxx - 2*Fx.*Fy.*Fxy + Fx.^2.*Fyy;
+I3 = Fyy.*Fxxy.^2 - Fyy.*Fxxx.*Fxyy - Fxy.*Fxxy.*Fxyy + ...
+    Fxx.*Fxyy.^2 + Fxy.*Fxxx.*Fyyy - Fxx.*Fxxy.*Fyyy;
+I4 = Fy.*Fyy.*Fxxx - 2*Fy.*Fxy.*Fxxy - Fx.*Fyy.*Fxxy + Fy.*Fxx.*Fxyy + ...
+    2*Fx.*Fxy.*Fxyy - Fx.*Fxx.*Fyyy;
+
+sig = {I0, I1, I2, I3, I4};
+
+end

### 2017-05-03 SE2sig.m

@@ -1,0 +1,12 @@
+function sig = SE2sig(h, F)
+[Fx, Fy] = gradient(F, h);
+[Fxx, Fxy] = gradient(Fx, h);
+[~, Fyy] = gradient(Fy, h);
+
+I0 = F;
+I1 = 1/100*(Fx*Fx + Fy*Fy);
+I2 = 1/100*(Fxx + Fyy);
+
+sig = {I0, I1, I2};
+
+end

### 2017-05-03 compute_derivatives.m

@@ -1,0 +1,20 @@
+function varargout = compute_derivatives(F, N, h)
+% COMPUTE_DERIVATIVES compute derivatives up to order N, returned in order
+%     fx, fy, fxx, fxy, fyy, fxxx, fxxy, fxyy, fyyy, etc
+derivs = cell((N+1)*(N+2)/2, 1);
+derivs{1} = F;
+k = 2; % index where next derivative goes
+for i = 1:N % order
+    start = ((i - 1)*i)/2;
+    for j = 1:i
+        if j == 1
+            [derivs{k}, derivs{k+1}] = gradient(derivs{start+j}, h);
+            k = k + 1;
+        else
+            [~, derivs{k}] = gradient(derivs{start+j}, h);
+        end
+        k = k + 1;
+    end
+end
+
+end

### 2017-05-03 invariants.py

@@ -1,0 +1,138 @@
+import numpy as np
+
+# transformation group signatures
+def SA2signature(F, h=1):
+    """ All the degree three and lower transvectants"""
+    Fx, Fy = np.gradient(F, h)
+    Fxx, Fxy = np.gradient(Fx, h)
+    Fyx, Fyy = np.gradient(Fy, h)
+    Fxxx, Fxxy = np.gradient(Fxx, h)
+    Fxyx, Fxyy = np.gradient(Fxy, h)
+    Fyyx, Fyyy = np.gradient(Fyy, h)
+    
+    I0 = F
+    I1 = Fxx*Fyy - Fxy**2
+    I2 = Fy**2*Fxx - 2*Fx*Fy*Fxy + Fx**2*Fyy
+    I3 = (Fyy*Fxxy**2 - Fyy*Fxxx*Fxyy - Fxy*Fxxy*Fxyy + Fxx*Fxyy**2 +
+            Fxy*Fxxx*Fyyy - Fxx*Fxxy*Fyyy)
+    I4 = (Fy*Fyy*Fxxx - 2*Fy*Fxy*Fxxy - Fx*Fyy*Fxxy + Fy*Fxx*Fxyy +
+            2*Fx*Fxy*Fxyy - Fx*Fxx*Fyyy)
+    
+    return (I0, I1, I2, I3, I4)
+
+def SE2signature(F, h=1):
+    Fx, Fy = np.gradient(F, h)
+    Fxx, Fxy = np.gradient(Fx, h)
+    Fyx, Fyy = np.gradient(Fy, h)
+
+    I0 = F # function value
+    I1 = Fx*Fx + Fy*Fy
+    I2 = Fxx + Fyy
+    return (I0, I1, I2)
+
+def signed_area(ax, ay, bx, by, cx, cy):
+    """ Compute signed area of a triangle
+
+    Arguments:
+    ax, ay, bx, by, cx, cy -- the x and y coordinates of the (ordered)
+    vertices a, b, c of the triangle
+    """
+    return 0.5*(ax*by - ay*bx + bx*cy - by*cx + cx*ay - cy*ax)
+
+def triangle_areas(X, Y):
+    """ Compute signed area of triangulation of gridded mesh
+
+    Arguments:
+    X, Y -- 2D arrays of X, Y coordinates. Each grid square is split into
+    two triangles and the oriented area computed
+    """
+
[…]

### 2017-05-03 invariants_experiments.py

@@ -1,0 +1,43 @@
+# Create a test image
+from invariants import *
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Create a two test functions which produce similar looking images. These
+# will be used in a classification experiment
+def f(x, y):
+    return 0.5*(1 + np.sin(4*x) * np.cos(7*y)) * 2*np.exp(-10*((x - 0.1)**2
+        + (y+0.2)**2))
+
+def g(x, y):
+    return 0.5*(1 + np.sin(5*x) * np.cos(6*y)) * 2*np.exp(-12*((x - 0.1)**2
+        + (y+0.2)**2))
+
+def create_current(h, m, n, k):
+    X, Y = np.meshgrid(np.arange(-1.5, 1.5, h), np.arange(-1.5, 1.5, h))
+    F = f(X, Y)
+    sig = SA2signature(F, h)
+
+    surf = InvariantSurface(sig[0], sig[1], sig[2])
+    return surf.current(m, n, k)
+
+# Test convergence of current operation
+m, n, k = 2, 2, 2
+h = 0.05
+x0 = create_current(h, m, n, k)
+for i in range(6):
+    h = h/2
+    x1 = create_current(h, m, n, k)
+    print(np.abs(x1 - x0) / np.abs(x0))
+    x0 = x1
+
+
+
+
+
+
+
+
+
+
+

### 2017-05-03 matlab/R2_signature.m

@@ -1,0 +1,9 @@
+function [sig3, sig4] = R2_signature(F, varargin)
+[~, Fx, Fy, Fxx, Fxy, Fyy] = compute_derivatives(F, 2, varargin{:});
+I0 = F;
+I1 = Fx;
+I2 = Fy;
+I3 = Fxx;
+sig3 = {I0, I1, I2};
+sig4 = {I0, I1, I2, I3};
+end

### 2017-05-03 matlab/SA2_signature.m

@@ -1,0 +1,10 @@
+function [sig3, sig4] = SA2_signature(f, varargin)
+[~, Fx, Fy, Fxx, Fxy, Fyy, Fxxx, Fxxy, Fxyy, Fyyy] = ...
+    compute_derivatives(f, 3, varargin{:});
+C = Fxx.*Fyy - Fxy.^2;
+D = Fy.^2.*Fxx - 2*Fx.*Fy.*Fxy + Fx.^2.*Fyy;
+F = Fyy.*Fxxy.^2 + Fxx.*Fxyy.^2 + Fxyy.*Fxxx.*Fyyy - Fyy.*Fxxx.*Fxyy - ...
+    Fxyy.*Fxxy.*Fxyy - Fxx.*Fxxy.*Fyyy;
+sig3 = {f, C, D};
+sig4 = {f, C, D, F};
+end

### 2017-05-03 matlab/generate_images.m

@@ -1,0 +1,78 @@
+%% Signature visualisation script
+xlim = [-0.5 0.5];
+ylim = [-0.5, 0.5];
+n = 1000;
+x = linspace(xlim(1), xlim(2), n);
+y = linspace(ylim(1), ylim(2), n);
+hx = (xlim(2) - xlim(1)) / (n - 1);
+hy = (ylim(2) - ylim(1)) / (n - 1);
+[X, Y] = meshgrid(x, y);
+
+f = @(x, y) 0.05*x.^3 - 0.2*x.^2.*y + 0.1*x*y.^2 - 0.1*y.^3 + ...
+   0.3*x.^2 - 0.2*x.*y.^2 + 0.4*y.^2 + 0.1*x + 0.1*y + 1;
+%f = @(x, y) exp(-x.^2 -8*(y - 0.2*x - 0.8*x.^2).^2);
+syms x y
+F = f(x, y);
+F_num = f(X, Y);
+figure(1)
+surf(X, Y, F_num, 'edgecolor', 'none')
+print -r200 -dpng figures/f.png
+
+%%
+sym_to_numeric = @(sig) cellfun(@matlabFunction, sig, 'UniformOutput', false)
+eval_sig = @(sig, X, Y) cellfun(@(f) f(X, Y), sig, 'UniformOutput', false);
+eval_sym = @(sig, X, Y) eval_sig(sym_to_numeric(sig), X, Y);
+
+sig_R2   = eval_sym(R2_signature(F), X, Y);
+sig_SE2  = eval_sym(SE2_signature(F, hx, hy),X,Y);
+sig_E2   = eval_sym(E2_signature(F, hx, hy),X,Y);
+sig_Sim2 = eval_sym(Sim2_signature(F, hx, hy),X,Y);
+sig_SA2  = eval_sym(SA2_signature(F, hx, hy),X,Y);
+sig_A2   = eval_sym(A2_signature(F, hx, hy),X,Y);
+
+%%
+figure(2)
+subplot(2, 3, 1)
+sig_surface(sig_R2)
+title('R^2 signature')
+subplot(2, 3, 2)
+sig_surface(sig_SE2)
+title('SE(2) signature')
+subplot(2, 3, 3)
+sig_surface(sig_E2)
+title('E(2) signature')
+subplot(2, 3, 4)
+sig_surface(sig_Sim2)
+title('Sim(2) signature')
+subplot(2, 3, 5)
[…]

### 2017-05-03 matlab/sig_contour.m

@@ -1,0 +1,32 @@
+function sig_contour(sig, varargin)
+% SIG_CONTOUR: Produce a contour plot of a 3D or 4D signature
+%    
+%     Contours are taken with respect to the first variable in the
+%     signature, colours with respect to the fourth (if present)
+%
+%     
+params = parse_inputs(varargin{:});
+J1 = sig{1}; % contour levels with respect to this one
+J2 = sig{2};
+J3 = sig{3};
+
+levels = params.levels;
+if isempty(levels)
+    levels = linspace(min(J1(:)), max(J1(:)), params.n_contours);
+end
+
+if numel(sig) == 3;
+    contour(J2, J3, J1, levels)
+else
+    % ?
+end
+
+function params = parse_inputs(varargin)
+p = inputParser();
+p.addParameter('levels', []);
+p.addParameter('n_contours', 10);
+p.parse(varargin{:});
+params = p.Results;
+end
+
+end

### 2017-05-03 matlab/sig_surface.m

@@ -1,0 +1,29 @@
+function sig_surface(sig, varargin)
+% SIG_SURFACE: Produce a surface plot of a 3D or 4D signature
+%    
+%     The first variable is the z coordinate (as it is usually the 
+%     function value), the fourth is the colour (if present)
+%
+%     
+params = parse_inputs(varargin{:});
+J1 = sig{1}; % contour levels with respect to this one
+J2 = sig{2};
+J3 = sig{3};
+if numel(sig) == 4;
+    J4 = sig{4};
+end
+surf_opts = {'edgecolor', 'none', 'facealpha', 0.9};
+if numel(sig) == 3
+    surf(J2, J3, J1, surf_opts{:})
+else
+    surf(J2, J3, J1, J4, surf_opts{:}) 
+end
+camlight()
+function params = parse_inputs(varargin)
+p = inputParser();
+p.addParameter('color', 'b');
+p.parse(varargin{:});
+params = p.Results;
+
+end
+end

### 2017-05-03 matlab/something.m

@@ -1,0 +1,63 @@
+%% Signature visualisation stuff
+
+% Create some transformations
+
+t_E2 = E2Transform(1.1, -1, 0.1, 0.2);
+t_Sim2 = Sim2Transform(1.1, 0.1, 0.2, 0.8);
+A = rand(2); 
+A(1, :) = sign(det(A)) * A(1, :);
+A = A / sqrt(det(A));
+t_SA2 = A2Transform(A, [0.2; 0.1]);
+t_PSL3R = PSL3RTransform(1, 0.1, 0.05, 0.8, 0.2, 0.3);
+A = rand(2);
+t_A2 = A2Transform(A, [0.2; 0.1]);
+
+% Define our image function
+%f = @(x, y) cos(exp(-((x + 0.2).^2 + (y + 0.6).^2)/(2*(0.6^2)))) + ...
+%     exp(-((x - 0.4).^2 + (y - 0.8).^2)/(2*(0.6)^2));
+f = @(x, y) exp(1*(-4*x.^2 - 8*(y - 0.2*x - 0.8*x.^2).^2));
+
+%% Choose which one to use
+
+tform = t_PSL3R;
+sig_fun = @PSL3R_signature;
+
+%% Plot the image, before and after transform
+n = 1000;
+x = linspace(-1, 1, n);
+y = linspace(-1, 1, n);
+h = 2 / (n - 1);
+[X, Y] = meshgrid(x, y);
+
+fp = tform.forward(f);
+
+F = f(X, Y);
+Fp = fp(X, Y);
+figure(1);
+clf
+subplot(1,2,1)
+imagesc(f(X, Y))
+axis image
+colormap(gray(65536));
+subplot(1,2,2)
+imagesc(fp(X, Y))
+colormap(gray(65536));
+axis image
+
+%% Compute signatures and plot surface and contour maps
+sig = sig_fun(F, h);
+sigp = sig_fun(Fp, h);
+
+figure(2)
+clf
+surf(sig{1}, sig{2}, sig{3}, 'facecolor', 'red', 'facealpha', 0.5, 'edgecolor', 'none')
+hold on
+surf(sigp{1}, sigp{2}, sigp{3}, 'facecolor', 'blue', 'facealpha', 0.5, 'edgecolor', 'none')
+camlight()
+
+figure(3)
+levels = linspace(0, 1, 11);
+clf
+contour(sig{2}, sig{3}, sig{1}, 'k')
+hold on
+contour(sigp{2}, sigp{3}, sigp{1}, 'r:')

### 2017-05-03 nzms_figures.m

@@ -1,0 +1,121 @@
+%% Figures for the NZMS colloquium talk
+% First we need to define our function
+h = 0.005;
+f = @(x, y) 0.5 + 0.5*(sin(4*x).*cos(7*y)) .* exp(-10*((x - 0.1).^2 + (y+0.2).^2));
+
+% Second colour channel
+f1 = @(x, y) 0.5 + 0.5*(sin(5*x).*cos(3*y)) .* exp(-10*((x - 0.1).^2 + (y+0.1).^2));
+[X, Y] = meshgrid(-1.5:h:1.5, -1.5:h:1.5);
+
+G = f(X, Y);
+B = f1(X, Y);
+R = zeros(size(X));
+Im = zeros(size(X, 1), size(X, 2), 3);
+Im(:, :, 1) = R; Im(:, :, 2) = G; Im(:, :, 3) = B;
+
+
+sigfun = @SA2sig;
+%% Generate a random equiaffine mapping
+% Or in this case, load one from file, just contains A, b and Ainv, binv
+% for the forward and backward transformations
+load SA2tform.mat
+
+%% Perform forward mapping
+% By remapping coordinates
+z = A\([X(:), Y(:)]' - repmat(b, 1, numel(X)));
+Xn = reshape(z(1, :), size(X));
+Yn = reshape(z(2, :), size(Y));
+
+%% Compute various signature derivatives
+sig1 = sigfun(h, f(X, Y));
+sig2 = sigfun(h, f(Xn, Yn));
+
+%% Compute the colour images
+G = f(X, Y); B = f1(X, Y); R = zeros(size(X));
+Im = zeros(size(X, 1), size(X, 2), 3);
+Im(:, :, 1) = R; Im(:, :, 2) = G; Im(:, :, 3) = B;
+
+G1 = f(Xn, Yn); B1 = f1(Xn, Yn); R1 = zeros(size(X));
+Im1 = zeros(size(X, 1), size(X, 2), 3);
+Im1(:, :, 1) = R1; Im1(:, :, 2) = G1; Im1(:, :, 3) = B1;
+
+
+%% Plot surfaces
+cm = gray(16384);
+figure(1)
+surf(X, Y, f(X, Y), 'edgecolor', 'none')
+colormap(cm)
+shading('interp')
+camlight()
+axis off
+%print -r200 -dpng 'surf_before.png'
+
+figure(2)
+surf(X, Y, f(Xn, Yn), 'edgecolor', 'none')
+colormap(cm)
+shading('interp')
[…]

### 2017-05-03 nzms_figures_conformal.m

@@ -1,0 +1,110 @@
+%% Figures for the NZMS colloquium talk
+% First we need to define our function
+h = 0.005;
+f = @(x, y) 0.5 + 0.5*(sin(4*x).*cos(7*y)) .* exp(-10*((x - 0.1).^2 + (y+0.2).^2));
+
+% Second colour channel
+f1 = @(x, y) 0.5 + 0.5*(sin(5*x).*cos(3*y)) .* exp(-10*((x - 0.1).^2 + (y+0.1).^2));
+[X, Y] = meshgrid(-1.5:h:1.5, -1.5:h:1.5);
+
+G = f(X, Y);
+B = f1(X, Y);
+R = zeros(size(X));
+Im = zeros(size(X, 1), size(X, 2), 3);
+Im(:, :, 1) = R; Im(:, :, 2) = G; Im(:, :, 3) = B;
+image(Im)
+
+%% Generate a random conformal mapping
+f_forward = random_mobius();
+[Xn, Yn] = f_forward(X, Y);
+
+%% Compute various signature derivatives
+sig1 = SA2sig(h, f(X, Y));
+sig2 = SA2sig(h, f(Xn, Yn));
+
+%% Compute the colour images
+G = f(X, Y); B = f1(X, Y); R = zeros(size(X));
+Im = zeros(size(X, 1), size(X, 2), 3);
+Im(:, :, 1) = R; Im(:, :, 2) = G; Im(:, :, 3) = B;
+
+G1 = f(Xn, Yn); B1 = f1(Xn, Yn); R1 = zeros(size(X));
+Im1 = zeros(size(X, 1), size(X, 2), 3);
+Im1(:, :, 1) = R1; Im1(:, :, 2) = G1; Im1(:, :, 3) = B1;
+
+
+%% Plot surfaces
+cm = gray(16384);
+figure(1)
+surf(X, Y, f(X, Y), 'edgecolor', 'none')
+colormap(cm)
+shading('interp')
+camlight()
+axis off
+%print -r200 -dpng 'surf_before.png'
+
+figure(2)
+surf(X, Y, f(Xn, Yn), 'edgecolor', 'none')
+colormap(cm)
+shading('interp')
+camlight()
+axis off
+%print -r200 -dpng 'surf_after.png'
+
+%% Plot grayscale images
+figure(3)
+imagesc(f(X, Y))
+colormap(cm)
+axis off
+print -r200 -dpng 'image_before.png'
+figure(4)
+imagesc(f(Xn, Yn))
+colormap(cm)
[…]

### 2017-05-03 paper/code/A2_signature.m

@@ -1,0 +1,10 @@
+function sig = A2_signature(f, varargin)
+[~, Fx, Fy, Fxx, Fxy, Fyy, Fxxx, Fxxy, Fxyy, Fyyy] = ...
+    compute_derivatives(f, 3, varargin{:});
+C = Fxx.*Fyy - Fxy.^2;
+D = Fy.^2.*Fxx - 2*Fx.*Fy.*Fxy + Fx.^2.*Fyy;
+E = Fxxx.*Fy.^3 - 3*Fxxy.*Fx.*Fy.^2 + 3*Fxyy.*Fx.^2.*Fy - Fyyy.*Fx.^3;
+
+denom = sqrt(C.^6 + D.^6 + E.^4);
+sig = {f.*C.^3./denom, f.*D.^3./denom, f.*E.^2./denom};
+end

### 2017-05-03 paper/code/PSL3R_signature.m

@@ -1,0 +1,5 @@
+function varargout = PSL3R_signature(f, varargin)
+[~, Fx, Fy, Fxx, Fxy, Fyy, Fxxx, Fxxy, Fxyy, Fyyy] = ...
+    compute_derivatives(f, 3, varargin{:});
+D = Fy.^2.*Fxx - 2*Fx.*Fy.*Fxy + Fx.^2.*Fyy;
+E = Fxxx.*Fy.^3 - 3*Fxxy.*Fx.*Fy.^2 + 3*Fxyy.*Fx.^2.*Fy - Fyyy.*Fx.^3;

### 2017-05-03 paper/code/SA2_signature.m

@@ -1,0 +1,11 @@
+function [sig3, sig4] = SA2_signature(f, varargin)
+[~, Fx, Fy, Fxx, Fxy, Fyy, Fxxx, Fxxy, Fxyy, Fyyy] = ...
+    compute_derivatives(f, 3, varargin{:});
+C = Fxx.*Fyy - Fxy.^2;
+D = Fy.^2.*Fxx - 2*Fx.*Fy.*Fxy + Fx.^2.*Fyy;
+E = Fxxx.*Fy.^3 - 3*Fxxy.*Fx.*Fy.^2 + 3*Fxyy.*Fx.^2.*Fy - Fyyy.*Fx.^3;
+F = Fyy.*Fxxy.^2 + Fxx.*Fxyy.^2 + Fxyy.*Fxxx.*Fyyy - Fyy.*Fxxx.*Fxyy - ...
+    Fxyy.*Fxxy.*Fxyy - Fxx.*Fxxy.*Fyyy;
+sig3 = {f, C, D};
+sig4 = {f, C, D, F};
+end

### 2017-05-03 paper/code/draw_image.m

@@ -1,0 +1,22 @@
+function draw_image(f, varargin)
+params = parse_inputs(varargin{:});
+[X, Y, x, y] = regular_grid(...
+    params.xlim(1), params.xlim(2), params.nx, ...
+    params.ylim(1), params.ylim(2), params.ny);
+f_numeric = matlabFunction(f);
+imagesc(x, y, f_numeric(X, Y), params.clim)
+axis image
+colormap(params.cmap);
+end
+
+function params = parse_inputs(varargin)
+p = inputParser();
+p.addParameter('nx', 1000);
+p.addParameter('ny', 1000);
+p.addParameter('xlim', [-1, 1]);
+p.addParameter('ylim', [-1, 1]);
+p.addParameter('clim', [0 1]);
+p.addParameter('cmap', gray(65536));
+p.parse(varargin{:});
+params = p.Results;
+end

### 2017-05-03 paper/code/draw_signature.m

@@ -1,0 +1,28 @@
+function draw_signature(sig, varargin)
+params = parse_inputs(varargin{:});
+[X, Y] = regular_grid(...
+    params.xlim(1), params.xlim(2), params.nx, ...
+    params.ylim(1), params.ylim(2), params.ny);
+S = cell(1, 3);
+for i = 1:3
+    f_num = matlabFunction(sig{i});
+    S{i} = f_num(X, Y);
+end
+surf(S{2}, S{3}, S{1}, 'facecolor', params.color, 'edgecolor', 'none')
+camlight()
+
+
+
+
+end
+
+function params = parse_inputs(varargin)
+p = inputParser();
+p.addParameter('nx', 1000);
+p.addParameter('ny', 1000);
+p.addParameter('xlim', [-1, 1]);
+p.addParameter('ylim', [-1, 1]);
+p.addParameter('color', 'blue')
+p.parse(varargin{:})
+params = p.Results;
+end

### 2017-05-03 paper/code/make_figures.m

@@ -1,0 +1,24 @@
+%% Signature surface generation script
+syms x y
+f = exp(-x.^2 - sin(y).^2);
+draw_image(f)
+
+%% E(2)
+sig = E2_signature(f);
+draw_signature(sig)
+
+%% SE(2)
+sig = SE2_signature(f);
+draw_signature(sig)
+
+%% SA(2)
+sig = SA2_signature(f);
+draw_signature(sig)
+
+%% A(2)
+sig = A2_signature(f);
+draw_signature(sig)
+
+%% PSL(3, R)
+sig = PSL3R_signature(f);
+draw_signature(sig)

### 2017-05-03 paper/code/regular_grid.m

@@ -1,0 +1,4 @@
+function [X, Y, x, y] = regular_grid(xmin, xmax, nx, ymin, ymax, ny)
+x = linspace(xmin, xmax, nx);
+y = linspace(ymin, ymax, ny);
+[X, Y] = meshgrid(x, y);

### 2017-05-03 random_SA2.m

@@ -1,0 +1,22 @@
+function [f_forward, A, b] = random_SA2()
+theta = 2*pi*rand();
+gamma = 0.5;
+R = [cos(theta), -sin(theta); sin(theta), cos(theta)];
+A = gamma*R + rand(2);
+if det(A) < 0
+    A(1, :) = -A(1, :);
+end
+A = 1 / sqrt(det(A)) * A;
+b = 0.2 * randn(2, 1);
+f_forward = @forward_tform;
+
+    function [Xn, Yn] = forward_tform(X, Y)
+        z = A\([X(:), Y(:)]' - repmat(b, 1, numel(X)));
+        Xn = reshape(z(1, :), size(X));
+        Yn = reshape(z(2, :), size(Y));
+    end
+end
+
+
+
+

### 2017-05-03 random_conformal.m

@@ -1,0 +1,17 @@
+function f_forward = random_conformal()
+% Generate the first 10 Taylor coefficients
+order = 100;
+a = (randn(1, order+1) + 1i*randn(1, order+1)) ./ (factorial(0:order));
+a(1) = a(1) / 10;
+f_forward = @forward;
+    function [Xn, Yn] = forward(X, Y)
+       Z = X + 1i*Y;
+       Zn = zeros(size(Z));
+       for k = 0:order
+           Zn = Zn + a(k+1)*Z.^k;
+       end
+       Xn = real(Zn);
+       Yn = imag(Zn);
+        
+    end
+end

### 2017-05-03 random_mobius.m

@@ -1,0 +1,13 @@
+function f_forward = random_mobius()
+coeffs = randn(1, 4) + 1i * randn(1, 4);
+a = coeffs(1); b = 0.1*coeffs(2); c = coeffs(3); d = coeffs(4);
+f_forward = @forward;
+
+    function [Xn, Yn] = forward(X, Y)
+        Z = X + 1i * Y;
+        Zn = (a*Z + b) ./ (c*Z + d);
+        Xn = real(Zn);
+        Yn = imag(Zn);
+    end
+
+end

### 2017-05-03 sig_pics.m

@@ -1,0 +1,104 @@
+%% Signature surface pictures
+% Script file to create nice signature surface pictures
+%
+
+%% Test function
+% Same function as in the Mobius  paper
+f = @(x, y) exp(-4*x.^2 -8*(y-0.2*x - 0.8*x.^2).^2);
+
+%%
+% Set the colormap for all figures
+cmap = hot(65536);
+
+%% Construct the invariant object
+% This is an object that stores the function and step size, and has methods
+% to compute all of the things that we are interested in (signatures etc).
+% The image is depicted below. Note you can modify 'h' later
+foo = ImageInvariant(f, 'h', 0.001);
+imshow(foo.evaluate())
+colormap(cmap)
+
+%% SE2 signature surface
+% Just computes the signature using function value S0, $f_x + f_x$ (S1), and
+% $f_{xx} + f_{yy}$ (S2)
+figure(1)
+clf
+foo.h = 0.005;
+[S0, S1, S2] = foo.SE2_signature();
+surf(S1, S2, S0, 'edgecolor', 'none', 'facealpha', 0.9)
+%axis off
+colormap('default')
+camlight
+lighting('phong')
+shading('interp')
+
+%% Sim2 signature surface
+% Just computes the signature using function value S0, $f_x + f_x$ (S1), and
+% $f_{xx} + f_{yy}$ (S2)
+figure(1)
+clf
+foo.h = 0.005;
+[S0, S1, S2] = foo.Sim2_signature();
+surf(S1, S2, S0, 'edgecolor', 'none', 'facealpha', 0.9)
+axis('equal')
+colormap('default')
+camlight
+lighting('phong')
+shading('interp')
+
+%% SA2 signature surface
+figure(2)
+clf
+foo.h = 0.005;
+[S0, S1, S2] = foo.SA2_signature();
+surf(S1, S2, S0, 'edgecolor', 'none', 'facealpha', 0.9)
+%axis off
+colormap(cmap)
+camlight
+lighting('phong')
+shading('interp')
+
+%% Mobius signature surface
+% S0 is the function value, S1, S2 are the two polar coordinate angles of
+% the invariants projected to the unit sphere (as in dis.pdf), S3 and S4
+% are the ones involving curl and divergence
+figure(3)
+clf
+foo.h = 0.005;
+tol = 0;
[…]

### 2017-05-03 visualise_signature_points.m

@@ -1,0 +1,59 @@
+function visualise_signature_points(I, S0, S1, S2)
+
+% Richard Brown, 2015
+
+% Create the figure
+hF = figure( ...
+       'Name',        'Signature Visualisation'...
+       );
+
+hA_im = subplot(1,2,1);
+imshow(I)
+axis('image')
+colormap('hot')
+hold on
+
+hA_surf = subplot(1,2,2);
+surf(S0, S1, S2, 'edgecolor', 'none', 'facealpha', 0.5);
+colormap('hot')
+hold on
+
+
+% Initialise points and lines
+[m, n] = size(I);
+markerSize = 40;
+axesLimits = [0.5, n+0.5, 0.5, m+0.5];
+
+hold on
+hx = plot(hA_im, 1, 1, 'b.', 'markersize', markerSize);
+set(hA_im, 'xlim', axesLimits(1:2), 'ylim', axesLimits(3:4))
+hs = plot3(hA_surf, 0, 0, 0, 'b.', 'markersize', markerSize);
+
+% Set Axes Properties
+grid on
+%set(hA_surf, 'DataAspectRatio', [1 1 1])
+
+% Associate the callback with mouse click
+set(hF, 'WindowButtonMotionFcn', @foo)
+
+% Callback nested function
+    function foo(varargin)
+        % Get the x point from the axes
+        cp = get(hA_im, 'CurrentPoint');
+        if cp(1,1) < axesLimits(1) || cp(1,1) > axesLimits(2) || ...
+                cp(1,2) < axesLimits(3) || cp(1,2) > axesLimits(4)
+            return
+        end
+        x = round(cp(1, 1:2));
+        
+        % Transform it
+
+        
+        % Modify the points and lines
+        set(hx, 'XData', x(1), 'YData', x(2));
+        set(hs, 'XData', S0(x(2), x(1)), ...
+            'YData', S1(x(2), x(1)), ...
+            'ZData', S2(x(2), x(1)));
+    end % foo
+
+end % EIGENDEMO

### 2017-05-09 paper/code/PSL3R_signature.m
tidying ...

@@ -3,3 +3,4 @@ function varargout = PSL3R_signature(f, varargin)
     compute_derivatives(f, 3, varargin{:});
 D = Fy.^2.*Fxx - 2*Fx.*Fy.*Fxy + Fx.^2.*Fyy;
 E = Fxxx.*Fy.^3 - 3*Fxxy.*Fx.*Fy.^2 + 3*Fxyy.*Fx.^2.*Fy - Fyyy.*Fx.^3;
+

### 2017-05-09 paper/code/make_figures.m

@@ -20,5 +20,5 @@ sig = A2_signature(f);
 draw_signature(sig)
 
 %% PSL(3, R)
-sig = PSL3R_signature(f);
-draw_signature(sig)
+%sig = PSL3R_signature(f);
+%draw_signature(sig)

### 2017-05-09 paper/paper.tex
tidying ...
Get the repo all up to date before culling

@@
 \documentclass{article}
-\usepackage{amsmath, amsthm, amssymb}
+\usepackage{amsmath, amsthm, amssymb, mathtools}
 \newtheorem{theorem}{Theorem}
@@
 
+% TODO
+%   SRM: Kiwi picture to Richard, paste text from disappear.tex
+%   RGB: Images for mesh, and for signatures
+
 \section{Introduction}
+\subsection{Notation}
+Let $G$ be a planar transformation group that acts on $k$-colour images $f
+\colon \mathbb{R}^2 \rightarrow \mathbb{R}^k$ by $\varphi \cdot f \coloneqq
+f \circ \varphi^{-1}$, where $\varphi \in G$.
+
+When referring to coordinates, with $x \in \mathbb{R}^2$, we write $\hat{x}
+= \varphi(x)$  and define the image post-transformation in the new
+coordinates as
+\begin{equation}
+  \hat{f}(\hat{x}) = f(x).
+\end{equation}
+We derive relationships between the derivatives before and after
+transformation by the chain rule:
+\begin{equation*}
+  f_{, i} = \hat{f}_{,k} \varphi_{k, i} 
+\end{equation*}
+etc.
+
+\section{The Stamp Collection I: The Affine group and its subgroups}
+In this section we consider all the groups whose transformation is of the
+form. For these groups, the change of variables formulae are, in tensor,
+and matrix notations,
+\begin{align}
+  f_{,i} &= \hat{f}_{, k} a_{ki} & \nabla f &= A^T \nabla \hat{f} \\
+  f_{,ij} &= \hat{f}_{, kl} a_{ki} a_{lj} & 
+  \nabla^2 f &= A^T \nabla^2 \hat{f} A
+\end{align}
+$\varphi(x) = Ax + b$ for some matrix $A$ and vector $b$.
+
+\subsection{SE(2)}
+In this case we have $A^TA = I$ and $\det A = 1$.
+
 \subsection{Invariants, hey!}

### 2017-05-09 matlab/E2_real_image.m

@@ -6,7 +6,10 @@
 
 
 %% Load test image and set up coordinates
-F = double(imread('images/lena.jpg')) / 255;
+F = double(imread('images/kiwi.jpg')) / 255;
+if size(F, 3) == 3
+    F = rgb2gray(F);
+end
 nx = size(F, 2);
 ny = size(F, 1);
 x = linspace(-1, 1, nx);

### 2017-05-09 ImageInvariant.m
phew, that's better

@@ -1,243 +1,0 @@
-classdef ImageInvariant
-    properties
-        % Note: default values are in the "parseinputs" function below
-        h
-        f
-        xlim
-        ylim
-    end
-    methods
-        function self = ImageInvariant(f, varargin)
-            self.f = f;
-            params = parse_inputs(varargin{:});
-            fields = fieldnames(params);
-            for i = 1:numel(fields)
-                self.(fields{i}) = params.(fields{i});
-            end
-        end   
-        function [F, X, Y] = evaluate(self)
-            x = self.xlim(1):self.h:self.xlim(2);
-            y = self.ylim(1):self.h:self.ylim(2);
-            [X, Y] = meshgrid(x, y);
-            F = self.f(X, Y);
-        end
-        function varargout = SA2_signature(self)
-            F = self.evaluate();
-            [~, Fx, Fy, Fxx, Fxy, Fyy, Fxxx, Fxxy, Fxyy, Fyyy] = ...
-                compute_derivatives(F, 3, self.h);
-            I0 = F;
-            I1 = Fxx.*Fyy - Fxy.^2;
-            I2 = Fy.^2.*Fxx - 2*Fx.*Fy.*Fxy + Fx.^2.*Fyy;
-            I3 = Fyy.*Fxxy.^2 - Fyy.*Fxxx.*Fxyy - Fxy.*Fxxy.*Fxyy + ...
-                Fxx.*Fxyy.^2 + Fxy.*Fxxx.*Fyyy - Fxx.*Fxxy.*Fyyy;
-            I4 = Fy.*Fyy.*Fxxx - 2*Fy.*Fxy.*Fxxy - Fx.*Fyy.*Fxxy + ...
-                Fy.*Fxx.*Fxyy + 2*Fx.*Fxy.*Fxyy - Fx.*Fxx.*Fyyy;
-            varargout = {I0, I1, I2, I3, I4}; 
-        end
-        function varargout = SE2_signature(self)
-            F = self.evaluate();
-            [~, Fx, Fy, Fxx, ~, Fyy] = ...
-                compute_derivatives(F, 2, self.h);
-            I0 = F;
-            I1 = Fx*Fx + Fy*Fy;
-            I2 = Fxx + Fyy;
-            varargout = {I0, I1, I2};
-        end
-        function varargout = Sim2_signature(self)
-           F = self.evaluate();
[…]

### 2017-05-09 SA2sig.m

@@ -1,19 +1,0 @@
-function sig = SA2sig(h, F)
-[Fx, Fy] = gradient(F, h);
-[Fxx, Fxy] = gradient(Fx, h);
-[~, Fyy] = gradient(Fy, h);
-[Fxxx, Fxxy] = gradient(Fxx, h);
-[~, Fxyy] = gradient(Fxy, h);
-[~, Fyyy] = gradient(Fyy, h);
-
-I0 = F;
-I1 = Fxx.*Fyy - Fxy.^2;
-I2 = Fy.^2.*Fxx - 2*Fx.*Fy.*Fxy + Fx.^2.*Fyy;
-I3 = Fyy.*Fxxy.^2 - Fyy.*Fxxx.*Fxyy - Fxy.*Fxxy.*Fxyy + ...
-    Fxx.*Fxyy.^2 + Fxy.*Fxxx.*Fyyy - Fxx.*Fxxy.*Fyyy;
-I4 = Fy.*Fyy.*Fxxx - 2*Fy.*Fxy.*Fxxy - Fx.*Fyy.*Fxxy + Fy.*Fxx.*Fxyy + ...
-    2*Fx.*Fxy.*Fxyy - Fx.*Fxx.*Fyyy;
-
-sig = {I0, I1, I2, I3, I4};
-
-end

### 2017-05-09 SE2Transform.m

@@ -1,29 +1,0 @@
-classdef SE2Transform < SpatialTransform2D
-    properties
-        theta
-        tx % translation vector
-        ty %
-        c % sine theta
-        s % cos theta
-    end
-    methods
-        function obj = SE2Transform(theta, tx, ty) 
-            obj.theta = theta;
-            obj.tx = tx;
-            obj.ty = ty;
-            obj.c = cos(theta);
-            obj.s = sin(theta);
-        end
-        
-        function [xnew, ynew] = forward(obj, x, y)
-            xnew = obj.c*x - obj.s*y + obj.tx;
-            ynew = obj.s*x + obj.c*y + obj.ty;
-        end
-        
-        function [xnew, ynew] = reverse(obj, x, y)
-            xnew = obj.c*(x - obj.tx) + obj.s*(y - obj.ty);
-            ynew = -obj.s*(x - obj.tx) + obj.c*(y - obj.ty);
-        end
-    end
-        
-end

### 2017-05-09 SE2sig.m

@@ -1,12 +1,0 @@
-function sig = SE2sig(h, F)
-[Fx, Fy] = gradient(F, h);
-[Fxx, Fxy] = gradient(Fx, h);
-[~, Fyy] = gradient(Fy, h);
-
-I0 = F;
-I1 = 1/100*(Fx*Fx + Fy*Fy);
-I2 = 1/100*(Fxx + Fyy);
-
-sig = {I0, I1, I2};
-
-end

### 2017-05-09 SpatialTransform2D.m

@@ -1,6 +1,0 @@
-classdef (Abstract) SpatialTransform2D
-    methods (Abstract)
-        forward(obj, x, y)
-        reverse(obj, x, y)
-    end
-end

### 2017-05-09 compute_derivatives.m

@@ -1,20 +1,0 @@
-function varargout = compute_derivatives(F, N, h)
-% COMPUTE_DERIVATIVES compute derivatives up to order N, returned in order
-%     fx, fy, fxx, fxy, fyy, fxxx, fxxy, fxyy, fyyy, etc
-derivs = cell((N+1)*(N+2)/2, 1);
-derivs{1} = F;
-k = 2; % index where next derivative goes
-for i = 1:N % order
-    start = ((i - 1)*i)/2;
-    for j = 1:i
-        if j == 1
-            [derivs{k}, derivs{k+1}] = gradient(derivs{start+j}, h);
-            k = k + 1;
-        else
-            [~, derivs{k}] = gradient(derivs{start+j}, h);
-        end
-        k = k + 1;
-    end
-end
-
-end

### 2017-05-09 invariants.py

@@ -1,138 +1,0 @@
-import numpy as np
-
-# transformation group signatures
-def SA2signature(F, h=1):
-    """ All the degree three and lower transvectants"""
-    Fx, Fy = np.gradient(F, h)
-    Fxx, Fxy = np.gradient(Fx, h)
-    Fyx, Fyy = np.gradient(Fy, h)
-    Fxxx, Fxxy = np.gradient(Fxx, h)
-    Fxyx, Fxyy = np.gradient(Fxy, h)
-    Fyyx, Fyyy = np.gradient(Fyy, h)
-    
-    I0 = F
-    I1 = Fxx*Fyy - Fxy**2
-    I2 = Fy**2*Fxx - 2*Fx*Fy*Fxy + Fx**2*Fyy
-    I3 = (Fyy*Fxxy**2 - Fyy*Fxxx*Fxyy - Fxy*Fxxy*Fxyy + Fxx*Fxyy**2 +
-            Fxy*Fxxx*Fyyy - Fxx*Fxxy*Fyyy)
-    I4 = (Fy*Fyy*Fxxx - 2*Fy*Fxy*Fxxy - Fx*Fyy*Fxxy + Fy*Fxx*Fxyy +
-            2*Fx*Fxy*Fxyy - Fx*Fxx*Fyyy)
-    
-    return (I0, I1, I2, I3, I4)
-
-def SE2signature(F, h=1):
-    Fx, Fy = np.gradient(F, h)
-    Fxx, Fxy = np.gradient(Fx, h)
-    Fyx, Fyy = np.gradient(Fy, h)
-
-    I0 = F # function value
-    I1 = Fx*Fx + Fy*Fy
-    I2 = Fxx + Fyy
-    return (I0, I1, I2)
-
-def signed_area(ax, ay, bx, by, cx, cy):
-    """ Compute signed area of a triangle
-
-    Arguments:
-    ax, ay, bx, by, cx, cy -- the x and y coordinates of the (ordered)
-    vertices a, b, c of the triangle
-    """
-    return 0.5*(ax*by - ay*bx + bx*cy - by*cx + cx*ay - cy*ax)
-
-def triangle_areas(X, Y):
-    """ Compute signed area of triangulation of gridded mesh
-
-    Arguments:
-    X, Y -- 2D arrays of X, Y coordinates. Each grid square is split into
-    two triangles and the oriented area computed
-    """
-
[…]

### 2017-05-09 invariants_experiments.py

@@ -1,43 +1,0 @@
-# Create a test image
-from invariants import *
-import numpy as np
-import matplotlib.pyplot as plt
-
-# Create a two test functions which produce similar looking images. These
-# will be used in a classification experiment
-def f(x, y):
-    return 0.5*(1 + np.sin(4*x) * np.cos(7*y)) * 2*np.exp(-10*((x - 0.1)**2
-        + (y+0.2)**2))
-
-def g(x, y):
-    return 0.5*(1 + np.sin(5*x) * np.cos(6*y)) * 2*np.exp(-12*((x - 0.1)**2
-        + (y+0.2)**2))
-
-def create_current(h, m, n, k):
-    X, Y = np.meshgrid(np.arange(-1.5, 1.5, h), np.arange(-1.5, 1.5, h))
-    F = f(X, Y)
-    sig = SA2signature(F, h)
-
-    surf = InvariantSurface(sig[0], sig[1], sig[2])
-    return surf.current(m, n, k)
-
-# Test convergence of current operation
-m, n, k = 2, 2, 2
-h = 0.05
-x0 = create_current(h, m, n, k)
-for i in range(6):
-    h = h/2
-    x1 = create_current(h, m, n, k)
-    print(np.abs(x1 - x0) / np.abs(x0))
-    x0 = x1
-
-
-
-
-
-
-
-
-
-
-

### 2017-05-09 matlab/A2Transform.m

@@ -1,29 +1,0 @@
-classdef A2Transform < SpatialTransform2D
-    properties
-        theta
-        tx % translation vector
-        ty %
-        c % sine theta
-        s % cos theta
-    end
-    methods
-        function obj = SE2Transform(theta, tx, ty) 
-            obj.theta = theta;
-            obj.tx = tx;
-            obj.ty = ty;
-            obj.c = cos(theta);
-            obj.s = sin(theta);
-        end
-        
-        function [xnew, ynew] = forward_coords(obj, x, y)
-            xnew = obj.c*x - obj.s*y + obj.tx;
-            ynew = obj.s*x + obj.c*y + obj.ty;
-        end
-        
-        function [xnew, ynew] = reverse_coordsFp(obj, x, y)
-            xnew = obj.c*(x - obj.tx) + obj.s*(y - obj.ty);
-            ynew = -obj.s*(x - obj.tx) + obj.c*(y - obj.ty);
-        end
-    end
-        
-end

### 2017-05-09 matlab/A2_signature.m

@@ -1,8 +1,0 @@
-function sig = A2_signature(F, varargin)
-[~, Fx, Fy, Fxx, Fxy, Fyy] = compute_derivatives(F, 2, varargin{:});
-I0 = F;
-I1 = Fx.*Fx + Fy.*Fy;
-v = {Fxx.*Fx + Fxy.*Fy, Fxy.*Fx + Fyy.*Fy};
-I2 = Fx.*v{2} - Fy.*v{1};
-sig = {I0, I1, I2};
-end

### 2017-05-09 matlab/E2Transform.m

@@ -1,31 +1,0 @@
-classdef E2Transform < SpatialTransform2D
-    properties
-        determinant
-        theta
-        tx % translation vector
-        ty %
-        c % sine theta
-        s % cos theta
-    end
-    methods
-        function obj = E2Transform(theta, determinant, tx, ty) 
-            obj.theta = theta;
-            obj.determinant = sign(determinant);
-            obj.tx = tx;
-            obj.ty = ty;
-            obj.c = cos(theta);
-            obj.s = sin(theta);
-        end
-        
-        function [xnew, ynew] = forward_coords(obj, x, y)
-            xnew = obj.determinant*(obj.c*x - obj.s*y) + obj.tx;
-            ynew = obj.s*x + obj.c*y + obj.ty;
-        end
-        
-        function [xnew, ynew] = reverse_coords(obj, x, y)
-            xnew = obj.determinant*obj.c*(x - obj.tx) + obj.s*(y - obj.ty);
-            ynew = -obj.determinant*obj.s*(x - obj.tx) + obj.c*(y - obj.ty);
-        end
-    end
-        
-end

### 2017-05-09 matlab/E2_colour_signature.m

@@ -1,10 +1,0 @@
-function out = E2_signature_colour(F1, F2, varargin)
-[~, F1x, F1y] = compute_derivatives(F1, 1, varargin{:});
-[~, F2x, F2y] = compute_derivatives(F2, 1, varargin{:});
-
-I0 = F1 + F2;
-I1 = F1x.*F1x + F1y.*F1y + F2x.*F2x + F2y.*F2y;
-I2 = F1x.*F2x + F1y.*F2y;
-out = {I0, I1, I2};
-
-end

### 2017-05-09 matlab/E2_greyscale_reconstruction.m

@@ -1,168 +1,0 @@
-%% E(2) Section
-%
-
-%% Real image
-% Load image
-F = imread('images/lena.jpg');
-F = double(F) / 255;
-
-%% Blur and transform 
-x = linspace(-1, 1, size(F, 2));
-y = linspace(-1, 1, size(F, 1));
-[X, Y] = meshgrid(x, y);
-dx = mean(diff(x));
-tform = E2Transform(1.1, -1, -0.1, .2);
-[X_irreg, Y_irreg] = tform.reverse(X, Y);
-
-% Transform image
-Fp = interp2(X, Y, F, X_irreg, Y_irreg,'cubic');  
-Fp(isnan(Fp)) = 0;
-
-SIGMA = [10:10:100];
-n = numel(SIGMA);
-dx = 2 / size(F, 2);
-nk = 200;
-for i = 1:n
-    sigma = SIGMA(i);
-    K = gaussian_filter(sigma, nk);
-    
-    F_filtered = conv2(F, K, 'same');
-    Fp_filtered = conv2(Fp, K, 'same');
-    
-    sig{i} = E2_signature(F_filtered, dx);
-    sigp{i} = E2_signature(Fp_filtered, dx);
-    
-    s = sig{i};
-    sp = sigp{i};
-    
-    clf()
-    surf(s{1}, s{2}, s{3}, 'facecolor', 'red', 'edgecolor', 'none', 'facealpha', 0.5)
-    camlight()
-    
-    print('-dpng', '-r200', sprintf('figures/siglenaE2%02d.png', i));
-    clf()
-    surf(sp{1}, sp{2}, sp{3}, 'facecolor', 'red', 'edgecolor', 'none', 'facealpha', 0.5)
-    camlight()
-    print('-dpng', '-r200', sprintf('figures/sigplenaE2%02.png', i));
-    
-end
-
-%% Create E(2) signatures of all images
-myimread = @(name) double(imread(name)) / 255;
-
-
-for i = 1:1
-    dx = 2/size(F,2);
-    sig{i} = E2_signature(F, dx);
-    sigp{i} = E2_signature(Fp, dx);
-    s = sig{i};
-    sp = sigp{i};
-    clf()
-    surf(s{1}, s{2}, s{3}, 'facecolor', 'red', 'edgecolor', 'none', 'facealpha', 0.5)
[…]

### 2017-05-09 matlab/E2_real_image.m

@@ -1,238 +1,0 @@
-%% E2 Real Image
-% In this script, we show how the E(2) signature can be applied to real
-% images by first using presmoothing by a Gaussian filter, a process which
-% is itself Euclidean-invariant
-
-
-
-%% Load test image and set up coordinates
-F = double(imread('images/kiwi.jpg')) / 255;
-if size(F, 3) == 3
-    F = rgb2gray(F);
-end
-nx = size(F, 2);
-ny = size(F, 1);
-x = linspace(-1, 1, nx);
-y = linspace(-1, 1, ny);
-dx = 2 / (nx - 1);
-dy = 2 / (ny - 1);
-imshow(F)
-
-%% Define a Euclidean transformation
-theta = 1.1; 
-determinant = -1; 
-tx = -0.1; 
-ty = 0.2;
-tform = E2Transform(theta, determinant, tx, ty);
-
-%% Transform our image
-Fp = tform.forward_image(F, x, y);
-Fp(isnan(Fp)) = 0;
-imshow(Fp);
-
-%% Set up the truncated Gaussian filter machinery
-[X_filter, Y_filter] = meshgrid(x, y);
-normalise = @(x) x / sum(x(:));
-makefilter = @(sigma) normalise(exp(-(X_filter.^2 + Y_filter.^2) ./ (2*sigma^2)));
-
-K = makefilter(0.01);
-F_smooth = conv_fft2(F, K, 'same');
-imshow(F_smooth)
-
-%% Now perform the experiments
-sigma_vals = linspace(0.01, 0.1, 9);
-n = numel(sigma_vals);
-sig = cell(1, n);
-sigp = cell(1, n);
-fprintf('progress (%d):', n);
-for i = 1:n
-    fprintf('%d ', i);
-    sigma = sigma_vals(i);
-    K = makefilter(sigma);
-    F_smooth = conv_fft2(F, K, 'same');
-    Fp_smooth = conv_fft2(Fp, K, 'same');
-    sig{i} = E2_signature(F_smooth, dx);
-    sigp{i} = E2_signature(Fp_smooth, dx);
-    figure(1)
-    subplot(3, 3, i);
-    imshow(F_smooth)
-    figure(2)
-    subplot(3, 3, i);
[…]

### 2017-05-09 matlab/E2_reconstruction.m

@@ -1,50 +1,0 @@
-%% E(2) Reconstruction
-
-%% Greyscale
-% signature (f, f_i f_i, f_ii)
-
-
-%% Colour
-% signature (f1 + f2, f1_i^2 + f2_i^2, f1_i f2_i)
-
-%% Three colour image
-syms x y
-f_sym(x, y) = exp(-4*x.^2 -8*(y - 0.2*x - 0.8*x.^2).^2);
-g_sym(x, y) = exp(-5*(x.^2 + y.^2)).*sin(2*pi*(x+y));
-h_sym(x, y) = 0.1*sign(x).^2;
-f = matlabFunction(f_sym);
-g = matlabFunction(g_sym);
-h = matlabFunction(h_sym);
-
-npts = 500;
-x = linspace(-1, 1, npts);
-dx = 2 / (npts - 1);
-y = x;
-[X, Y] = meshgrid(x, y);
-
-I = cat(3, f(X, Y), g(X, Y), h(X, Y));
-figure(1)
-imshow(I)
-%% Construct the ****ing images
-F = f(X, Y);
-G = g(X, Y);
-H = h(X, Y);
-
-tform = E2Transform(1.1, -1, -0.1, 0.2);
-[Xp, Yp] = tform.reverse(X, Y);
-
-Fp = f(Xp, Yp);
-Gp = g(Xp, Yp);
-Hp = h(Xp, Yp);
-%%
-sig = E2_colour_signature(F, G, dx);
-sig1 = E2_colour_signature(Fp, Gp, dx);
-levels = linspace(0, 1, 3);
-contour(sig{2}, sig{3}, sig{1}, levels, 'linewidth', 2, 'linecolor', 'blue')
-hold on
-contour(sig1{2}, sig1{3}, sig1{1}, levels, 'linewidth', 2, 'linecolor', 'red')
-
-%%
-surf(sig{1}, sig{2}, sig{3}, 'edgecolor', 'none', 'facecolor', 'red', 'facealpha', 0.5);
-hold on
-surf(sig1{1}, sig1{2}, sig1{3}, 'edgecolor', 'none', 'facecolor', 'blue', 'facealpha', 0.5);

### 2017-05-09 matlab/E2_signature.m

@@ -1,7 +1,0 @@
-function sig = E2_signature(F, varargin)
-[~, Fx, Fy, Fxx, ~, Fyy] = compute_derivatives(F, 2, varargin{:});
-I0 = F;
-I1 = Fx.*Fx + Fy.*Fy;
-I2 = Fxx + Fyy;
-sig = {I0, I1, I2};
-end

### 2017-05-09 matlab/Experiments.m

@@ -1,94 +1,0 @@
-f = @(x, y) exp(-4*x.^2 -8*(y - 0.2*x - 0.8*x.^2).^2);
-tx = SE2Transform(pi/4, 0.1, -0.2);
-visualise_signatures(f, @SE2_signature, tx);
-
-
-
-%tx = Sim2Transform(pi/4, 0.1, -0.2, 0.8);
-
-%% PSL3R experiment
-tx = PSL3RTransform(1, 0.1, 0.05, 0.8, 0.2, 0.3);
-f = @(x, y) exp(-4*x.^2 -8*(y - 0.2*x - 0.8*x.^2).^2);
-visualise_signatures(f, @PSL3R_signature, tx)
-
-%%
-figure(1) 
-npts = 10000;
-xmin = -1;
-xmax = 1;
-x = linspace(xmin, xmax, npts);
-y = linspace(xmin, xmax, npts);
-dx = (xmax - xmin) / (npts - 1);
-[X, Y] = meshgrid(x, y);
-[Xp, Yp] = tx.reverse(X, Y);
-F = f(X, Y);
-G = f(Xp, Yp);
-
-figure(1)
-subplot(1, 2, 1)
-imagesc(F)
-axis image
-subplot(1, 2, 2)
-imagesc(G)
-axis image
-
-[I0, I1, I2] = PSL3R_signature(F, dx);
-[J0, J1, J2] = PSL3R_signature(G, dx);
-
-levels = linspace(0.2, 0.8, 5);
-figure(2)
-
-contour(I0, I1, I2, levels, 'k')
-hold on
-contour(J0, J1, J2, levels, 'r')
-hold off
-
-
-%% Three colour image
-syms x y
-fs(x, y) = exp(-4*x.^2 -8*(y - 0.2*x - 0.8*x.^2).^2);
-gs(x, y) = exp(-5*(x.^2 + y.^2)).*sin(2*pi*(x+y));
-hs(x, y) = 0.5 + 0.25*x - 0.25*y;
-f = matlabFunction(fs);
-g = matlabFunction(gs);
-h = matlabFunction(hs);
-%%
-
-npts = 500;
-x = linspace(-1, 1, npts);
-dx = 2 / (npts - 1);
-y = x;
-[X, Y] = meshgrid(x, y);
-
-I = cat(3, f(X, Y), g(X, Y), h(X, Y));
-figure(1)
-imshow(I)
-
-F = f(X, Y);
[…]

### 2017-05-09 matlab/PSL3RTransform.m

@@ -1,36 +1,0 @@
-classdef PSL3RTransform < SpatialTransform2D
-    properties
-        a
-        b
-        c
-        d
-        g
-        h
-    end
-    methods
-        function obj = PSL3RTransform(a, b, c, d, g, h) 
-            obj.a = a;
-            obj.b = b;
-            obj.c = c;
-            obj.d = d;
-            obj.g = g;
-            obj.h = h;
-        end
-        
-        function [xnew, ynew] = forward(obj, x, y)
-            denom = 1 + obj.g*x + obj.h*y;
-            xnew = (obj.a*x + obj.b*y) ./ denom;
-            ynew = (obj.c*x + obj.d*y) ./ denom;
-        end
-        
-        function [xnew, ynew] = reverse(obj, x, y)
-            denom = (obj.c*obj.h - obj.d*obj.g) * x + ...
-                (obj.b*obj.g - obj.a*obj.h) * y + ...
-                obj.a*obj.d - obj.b*obj.c;
-            
-            xnew = (obj.d*x - obj.b*y) ./ denom;
-            ynew = (-obj.c*x + obj.a*y) ./ denom;
-        end
-    end
-        
-end

### 2017-05-09 matlab/PSL3R_signature.m

@@ -1,91 +1,0 @@
-function varargout = PSL3R_signature(F, varargin)
-[~, Fx, Fy, Fxx, Fxy, Fyy, Fxxx, Fxxy, Fxyy, Fyyy] = ...
-    compute_derivatives(F, 3, varargin{:});
-
-D = Fx.^2.*Fyy + Fy.^2.*Fxx - 2*Fx.*Fy.*Fxy;
-
-% choice of frame depends on sign of D (which is itself an
-% invariant)
-i_dge0 = D >= 0;
-b = zeros(size(Fx));
-d = zeros(size(Fx));
-d(i_dge0) = Fx(i_dge0) ./ sqrt(D(i_dge0));
-b(i_dge0) = -Fy(i_dge0) ./ sqrt(D(i_dge0));
-d(~i_dge0) = Fx(~i_dge0) ./ sqrt(-D(~i_dge0));
-b(~i_dge0) = -Fy(~i_dge0) ./ sqrt(-D(~i_dge0));
-%b = -d * Fy ./ Fx;
-
-% what is this? which moving frame variable was set to zero -
-% It was Fbar222
-h = d./(6*D.*Fx) .* (-Fxxx.*Fy.^3 + 3*Fxxy.*Fy.^2.*Fx + ...
-    -3*Fxyy.*Fx.^2.*Fy + Fyyy.*Fx.^3);
-
-c = h.*Fx.^2./(d.*D) - (Fx.*Fxy - Fy.*Fxx) ./ D;
-
-a = (1 - c.*Fy) ./ Fx;
-
-% checked g
-g = 1 ./ (2*Fx.^2) .* (Fxx + 2*c.*(Fx.*Fxy - Fy.*Fxx) + c.^2.*D);
-
-% G is Fbar
-Gx = a.*Fx + c.*Fy;
-Gy = b.*Fx + d.*Fy;
-Gxx = -2*a.*g.*Fx - 2*c.*g.*Fy + ...
-    a.^2.*Fxx + 2*a.*c.*Fxy + c.^2.*Fyy;
-Gxy = (-b.*g - a.*h).*Fx + (-d.*g - c.*h).*Fy + ...
-    a.*b.*Fxx + (b.*c + a.*d).*Fxy + c.*d.*Fyy;
-Gyy = -2*b.*h.*Fx - 2.*d.*h.*Fy + ...
[…]

### 2017-05-09 matlab/R2_signature.m

@@ -1,9 +1,0 @@
-function [sig3, sig4] = R2_signature(F, varargin)
-[~, Fx, Fy, Fxx, Fxy, Fyy] = compute_derivatives(F, 2, varargin{:});
-I0 = F;
-I1 = Fx;
-I2 = Fy;
-I3 = Fxx;
-sig3 = {I0, I1, I2};
-sig4 = {I0, I1, I2, I3};
-end

### 2017-05-09 matlab/SA2_signature.m

@@ -1,10 +1,0 @@
-function [sig3, sig4] = SA2_signature(f, varargin)
-[~, Fx, Fy, Fxx, Fxy, Fyy, Fxxx, Fxxy, Fxyy, Fyyy] = ...
-    compute_derivatives(f, 3, varargin{:});
-C = Fxx.*Fyy - Fxy.^2;
-D = Fy.^2.*Fxx - 2*Fx.*Fy.*Fxy + Fx.^2.*Fyy;
-F = Fyy.*Fxxy.^2 + Fxx.*Fxyy.^2 + Fxyy.*Fxxx.*Fyyy - Fyy.*Fxxx.*Fxyy - ...
-    Fxyy.*Fxxy.*Fxyy - Fxx.*Fxxy.*Fyyy;
-sig3 = {f, C, D};
-sig4 = {f, C, D, F};
-end

### 2017-05-09 matlab/SE2Transform.m

@@ -1,29 +1,0 @@
-classdef SE2Transform < SpatialTransform2D
-    properties
-        theta
-        tx % translation vector
-        ty %
-        c % sine theta
-        s % cos theta
-    end
-    methods
-        function obj = SE2Transform(theta, tx, ty) 
-            obj.theta = theta;
-            obj.tx = tx;
-            obj.ty = ty;
-            obj.c = cos(theta);
-            obj.s = sin(theta);
-        end
-        
-        function [xnew, ynew] = forward_coords(obj, x, y)
-            xnew = obj.c*x - obj.s*y + obj.tx;
-            ynew = obj.s*x + obj.c*y + obj.ty;
-        end
-        
-        function [xnew, ynew] = reverse_coordsFp(obj, x, y)
-            xnew = obj.c*(x - obj.tx) + obj.s*(y - obj.ty);
-            ynew = -obj.s*(x - obj.tx) + obj.c*(y - obj.ty);
-        end
-    end
-        
-end

### 2017-05-09 matlab/SE2_2col_signature.m

@@ -1,9 +1,0 @@
-function out = SE2_2col_signature(F, G, varargin)
-[~, Fx, Fy] = compute_derivatives(F, 1, varargin{:});
-[~, Gx, Gy] = compute_derivatives(G, 1, varargin{:});
-
-I0 = F;
-I1 = Fx.*Fx + Fy.*Fy;
-I2 = Fx.*Gy - Fy.*Gx;
-out = {I0, I1, I2};
-end

### 2017-05-09 matlab/SE2_experiment.m

@@ -1,62 +1,0 @@
-function SE2_experiment(f)
-n = 400;
-xlim = [-1 1];
-ylim = [-1 1];
-x = linspace(xlim(1), xlim(2), n);
-y = linspace(xlim(1), xlim(2), n);
-[X, Y] = meshgrid(x, y);
-f1 = figure();
-
-% initialise image part of the gui
-h_image_axes = subplot(1,2,1);
-ncolors = 65536;
-colormap(bone(ncolors));
-F = f(X, Y);
-him = image(x, y, ncolors*F, 'parent', h_image_axes);
-
-% initialise signature part of the GUI
-h_signature_axes = subplot(1,2,2);
-hx = (xlim(2) - xlim(1)) / n;
-hy = (ylim(2) - ylim(1)) / n;
-[S0, S1, S2] = SE2_signature(F, hx, hy);
-hs = surf(S1(2:end-1, 2:end-1), S2(2:end-1, 2:end-1), S0(2:end-1, 2:end-1),...
-    'edgecolor', 'none');
-camlight
-shading interp
-
-
-
-% set up callbacks
-hz = zoom(f1);
-hp = pan(f1);
-hz.ActionPostCallback = @motion_callback;
-hp.ActionPostCallback = @motion_callback;
-
-
-    function motion_callback(obj, event_obj)
-        hax = event_obj.Axes;
-        if hax ~= h_image_axes
-            return
-        end
-        
-        % process zoomed image
-        xlim = get(hax, 'xlim');
-        ylim = get(hax, 'ylim');
-        x = linspace(xlim(1), xlim(2), n);
-        y = linspace(ylim(1), ylim(2), n);
-        [X, Y] = meshgrid(x, y);
-        F = f(X, Y);
-        set(him, 'xdata', x, 'ydata', y, 'CData', ncolors*F);
-        
-        % process signature
-        hx = (xlim(2) - xlim(1)) / n;
-        hy = (ylim(2) - ylim(1)) / n;
-        [S0, S1, S2] = SE2_signature(F, hx, hy);
-        set(hs, 'XData', S1(2:end-1, 2:end-1), 'YData', ...
-            S2(2:end-1, 2:end-1), ...
-            'ZData', S0(2:end-1, 2:end-1))
-    end
-
-
-
-end

### 2017-05-09 matlab/SE2_signature.m

@@ -1,8 +1,0 @@
-function sig = SE2_signature(F, varargin)
-[~, Fx, Fy, Fxx, Fxy, Fyy] = compute_derivatives(F, 2, varargin{:});
-I0 = F;
-I1 = Fx.*Fx + Fy.*Fy;
-v = {Fxx.*Fx + Fxy.*Fy, Fxy.*Fx + Fyy.*Fy};
-I2 = Fx.*v{2} - Fy.*v{1};
-sig = {I0, I1, I2};
-end

### 2017-05-09 matlab/Sim2Transform.m

@@ -1,31 +1,0 @@
-classdef Sim2Transform < SpatialTransform2D
-    properties
-        theta
-        tx % translation vector
-        ty %
-        lambda
-        c % sine theta
-        s % cos theta
-    end
-    methods
-        function obj = Sim2Transform(theta, tx, ty, lambda) 
-            obj.theta = theta;
-            obj.tx = tx;
-            obj.ty = ty;
-            obj.lambda = lambda;
-            obj.c = cos(theta);
-            obj.s = sin(theta);
-        end
-        
-        function [xnew, ynew] = forward_coords(obj, x, y)
-            xnew = obj.lambda*(obj.c*x - obj.s*y) + obj.tx;
-            ynew = obj.lambda*(obj.s*x + obj.c*y) + obj.ty;
-        end
-        
-        function [xnew, ynew] = reverse_coords(obj, x, y)
-            xnew = 1/obj.lambda*(obj.c*(x - obj.tx) + obj.s*(y - obj.ty));
-            ynew = 1/obj.lambda*(-obj.s*(x - obj.tx) + obj.c*(y - obj.ty));
-        end
-    end
-        
-end

### 2017-05-09 matlab/Sim2_signature.m

@@ -1,14 +1,0 @@
-function sig = Sim2_signature(F, varargin)
-[~, Fx, Fy, Fxx, Fxy, Fyy] = compute_derivatives(F, 2, varargin{:});
-J1 = Fx.*Fx + Fy.*Fy;
-J2 = Fxx + Fyy;
-J3 = sqrt(Fxx.*Fxx + 2*Fxy.*Fxy + Fyy.*Fyy);
-denom = sqrt(J1.*J1 + J2.*J2 + J3.*J3);
-J1 = J1 ./ denom;
-J2 = J2 ./ denom;
-J3 = J3 ./ denom;
-
-I1 = acos(J3);
-I2 = atan2(J2, J1);
-
-sig = {F, I1, I2};

### 2017-05-09 matlab/SpatialTransform2D.m

@@ -1,75 +1,0 @@
-classdef (Abstract) SpatialTransform2D
-    methods (Abstract)
-        forward_coords(obj, x, y)
-        reverse_coords(obj, x, y)
-    end
-    methods
-        function varargout = forward(obj, varargin)
-            if nargin == 3
-                [Xp, Yp] = obj.forward_coords(varargin{:});
-                varargout = {Xp, Yp};
-            elseif nargin == 2 % function handle
-                fp = obj.forward_fun(varargin{:});
-                varargout = {fp};
-            elseif nargin == 4 % image with x y limits
-                Fp = obj.forward_image(varargin{:});
-                varargout = {Fp};
-            end
-        end
-        function varargout = reverse(obj, varargin)
-            if nargin == 3
-                [Xp, Yp] = obj.reverse_coords(varargin{:});
-                varargout = {Xp, Yp};
-            elseif nargin == 2 % function handle
-                fp = obj.reverse_fun(varargin{:});
-                varargout = {fp};
-            elseif nargin == 4 % image with x y limits
-                Fp = obj.reverse_image(varargin{:});
-                varargout = {Fp};
-            end
-        end
-                
-        function Fp = forward_image(obj, F, x, y)
-            nx = size(F, 2);
-            ny = size(F, 1);
-            x = check_xlim(x, nx);
-            y = check_xlim(y, ny);
-            [X, Y] = meshgrid(x, y);
-            [X_irreg, Y_irreg] = obj.reverse(X, Y);
-            Fp = interp2(X, Y, F, X_irreg, Y_irreg, 'cubic');
-        end
-        function Fp = reverse_image(obj, F, x, y)
-            nx = size(F, 2);
-            ny = size(F, 1);
-            x = check_xlim(x, nx);
-            y = check_xlim(y, ny);
-            [X, Y] = meshgrid(x, y);
-            [X_irreg, Y_irreg] = obj.forward(X, Y);
-            Fp = interp2(X, Y, F, X_irreg, Y_irreg, 'cubic');
-        end
-        function fp = forward_fun(obj, f)
-            fp = @out_fun;
-            function z = out_fun(x, y)
-                [xp, yp] = obj.reverse(x, y);
-                z = f(xp, yp);
-            end
-        end
-        function fp = reverse_fun(obj, f)
-            fp = @out_fun;
-            function z = out_fun(x, y)
-                [xp, yp] = obj.forward(x, y);
[…]

### 2017-05-09 matlab/compute_derivatives.m

@@ -1,64 +1,0 @@
-function varargout = compute_derivatives(F, N, varargin)
-if isa(F, 'symfun') || isa(F, 'sym')
-    derivs = compute_derivatives_symbolic(F, N, varargin{:});
-else
-    derivs = compute_derivatives_numeric(F, N, varargin{:});
-end
-varargout = derivs;
-end
-
-function derivs = compute_derivatives_symbolic(F, N, varargin)
-syms x y
-derivs = cell((N+1)*(N+2)/2, 1);
-derivs{1} = F;
-k = 2;
-for i = 1:N % order
-    start = ((i - 1)*i)/2;
-    for j = 1:i
-        if j == 1
-            derivs{k} = simplify(diff(derivs{start + j}, x));
-            derivs{k+1} = simplify(diff(derivs{start + j}, y));
-            k = k + 1;
-        else
-            derivs{k} = simplify(diff(derivs{start + j}, y));
-        end
-        k = k + 1;
-    end
-end
-end
-
-
-function derivs = compute_derivatives_numeric(F, N, varargin)
-% COMPUTE_DERIVATIVES compute derivatives up to order N, returned in order
-%     fx, fy, fxx, fxy, fyy, fxxx, fxxy, fxyy, fyyy, etc
-%
-% put function signature description here
-%
-%
-% Example:
-%     [f, fx, fy, fxx, fxy, fyy] = compute_derivatives(F, 2, 0.01)
-
-if nargin == 3
-    hx = varargin{1};
-    hy = hx;
-else
-    hx = varargin{1};
-    hy = varargin{2};
-end
-
-derivs = cell((N+1)*(N+2)/2, 1);
-derivs{1} = F;
-k = 2; % index where next derivative goes
-for i = 1:N % order
-    start = ((i - 1)*i)/2;
-    for j = 1:i
-        if j == 1
-            [derivs{k}, derivs{k+1}] = gradient(derivs{start+j}, hx, hy);
-            k = k + 1;
-        else
-            [~, derivs{k}] = gradient(derivs{start+j}, hx, hy);
-        end
-        k = k + 1;
-    end
-end
-end

### 2017-05-09 matlab/conv_fft2.m

@@ -1,120 +1,0 @@
-function y = conv_fft2(x, m, shape)
-%CONV_FFT2 Two dimensional convolution via the FFT.
-%   Y = CONV_FFT2(X, M) performs the 2-D convolution of matrices X and M.
-%   If [mx,nx] = size(X) and [mm,nm] = size(M), then size(Y) =
-%   [mx+mm-1,nx+nm-1]. Values near the boundaries of the output array are
-%   calculated as if X was surrounded by a border of zero values.
-%
-%   Y = CONV_FFT2(X, M, SHAPE) where SHAPE is a string returns a
-%   subsection of the 2-D convolution with size specified by SHAPE:
-%
-%       'full'    - (default) returns the full 2-D convolution,
-%       'same'    - returns the central part of the convolution
-%                   that is the same size as X (using zero padding),
-%       'valid'   - returns only those parts of the convolution
-%                   that are computed without the zero-padded
-%                   edges, size(Y) = [mx-mm+1,nx-nm+1] when
-%                   size(X) > size(M),
-%       'wrap'    - as for 'same' except that instead of using
-%                   zero-padding the input X is taken to wrap round as
-%                   on a toroid.
-%       'reflect' - as for 'same' except that instead of using
-%                   zero-padding the input X is taken to be reflected
-%                   at its boundaries.
-%
-%   For shape options 'full', 'same' and 'valid' this function should
-%   return the same result as CONV2, to within a small tolerance. For all
-%   shape options, this function should return the same result as CONVOLVE2
-%   (available via the MATLAB Central File Exchange), with no TOL argument,
-%   to within a small tolerance.
-%
-%   CONV_FFT2 uses multiplication in the frequency domain to compute the
-%   convolution. It may be faster than CONV2 and CONVOLVE2 for masks above
-%   a certain size. This should be checked experimentally for any given
-%   application and system.
-%
-%   See also CONV2, CONVOLVE2, FILTER2.
-
-% Copyright David Young, April 2011
-
-narginchk(2,3);
-if nargin < 3
-    shape = 'full';    % shape default as for CONV2
-end;
-
-[x, m, fsize] = padarrays(x, m, shape);
-
[…]

### 2017-05-09 matlab/generate_images.m

@@ -1,78 +1,0 @@
-%% Signature visualisation script
-xlim = [-0.5 0.5];
-ylim = [-0.5, 0.5];
-n = 1000;
-x = linspace(xlim(1), xlim(2), n);
-y = linspace(ylim(1), ylim(2), n);
-hx = (xlim(2) - xlim(1)) / (n - 1);
-hy = (ylim(2) - ylim(1)) / (n - 1);
-[X, Y] = meshgrid(x, y);
-
-f = @(x, y) 0.05*x.^3 - 0.2*x.^2.*y + 0.1*x*y.^2 - 0.1*y.^3 + ...
-   0.3*x.^2 - 0.2*x.*y.^2 + 0.4*y.^2 + 0.1*x + 0.1*y + 1;
-%f = @(x, y) exp(-x.^2 -8*(y - 0.2*x - 0.8*x.^2).^2);
-syms x y
-F = f(x, y);
-F_num = f(X, Y);
-figure(1)
-surf(X, Y, F_num, 'edgecolor', 'none')
-print -r200 -dpng figures/f.png
-
-%%
-sym_to_numeric = @(sig) cellfun(@matlabFunction, sig, 'UniformOutput', false)
-eval_sig = @(sig, X, Y) cellfun(@(f) f(X, Y), sig, 'UniformOutput', false);
-eval_sym = @(sig, X, Y) eval_sig(sym_to_numeric(sig), X, Y);
-
-sig_R2   = eval_sym(R2_signature(F), X, Y);
-sig_SE2  = eval_sym(SE2_signature(F, hx, hy),X,Y);
-sig_E2   = eval_sym(E2_signature(F, hx, hy),X,Y);
-sig_Sim2 = eval_sym(Sim2_signature(F, hx, hy),X,Y);
-sig_SA2  = eval_sym(SA2_signature(F, hx, hy),X,Y);
-sig_A2   = eval_sym(A2_signature(F, hx, hy),X,Y);
-
-%%
-figure(2)
-subplot(2, 3, 1)
-sig_surface(sig_R2)
-title('R^2 signature')
-subplot(2, 3, 2)
-sig_surface(sig_SE2)
-title('SE(2) signature')
-subplot(2, 3, 3)
-sig_surface(sig_E2)
-title('E(2) signature')
-subplot(2, 3, 4)
-sig_surface(sig_Sim2)
-title('Sim(2) signature')
-subplot(2, 3, 5)
[…]

### 2017-05-09 matlab/sig_contour.m

@@ -1,32 +1,0 @@
-function sig_contour(sig, varargin)
-% SIG_CONTOUR: Produce a contour plot of a 3D or 4D signature
-%    
-%     Contours are taken with respect to the first variable in the
-%     signature, colours with respect to the fourth (if present)
-%
-%     
-params = parse_inputs(varargin{:});
-J1 = sig{1}; % contour levels with respect to this one
-J2 = sig{2};
-J3 = sig{3};
-
-levels = params.levels;
-if isempty(levels)
-    levels = linspace(min(J1(:)), max(J1(:)), params.n_contours);
-end
-
-if numel(sig) == 3;
-    contour(J2, J3, J1, levels)
-else
-    % ?
-end
-
-function params = parse_inputs(varargin)
-p = inputParser();
-p.addParameter('levels', []);
-p.addParameter('n_contours', 10);
-p.parse(varargin{:});
-params = p.Results;
-end
-
-end

### 2017-05-09 matlab/sig_surface.m

@@ -1,29 +1,0 @@
-function sig_surface(sig, varargin)
-% SIG_SURFACE: Produce a surface plot of a 3D or 4D signature
-%    
-%     The first variable is the z coordinate (as it is usually the 
-%     function value), the fourth is the colour (if present)
-%
-%     
-params = parse_inputs(varargin{:});
-J1 = sig{1}; % contour levels with respect to this one
-J2 = sig{2};
-J3 = sig{3};
-if numel(sig) == 4;
-    J4 = sig{4};
-end
-surf_opts = {'edgecolor', 'none', 'facealpha', 0.9};
-if numel(sig) == 3
-    surf(J2, J3, J1, surf_opts{:})
-else
-    surf(J2, J3, J1, J4, surf_opts{:}) 
-end
-camlight()
-function params = parse_inputs(varargin)
-p = inputParser();
-p.addParameter('color', 'b');
-p.parse(varargin{:});
-params = p.Results;
-
-end
-end

### 2017-05-09 matlab/something.m

@@ -1,63 +1,0 @@
-%% Signature visualisation stuff
-
-% Create some transformations
-
-t_E2 = E2Transform(1.1, -1, 0.1, 0.2);
-t_Sim2 = Sim2Transform(1.1, 0.1, 0.2, 0.8);
-A = rand(2); 
-A(1, :) = sign(det(A)) * A(1, :);
-A = A / sqrt(det(A));
-t_SA2 = A2Transform(A, [0.2; 0.1]);
-t_PSL3R = PSL3RTransform(1, 0.1, 0.05, 0.8, 0.2, 0.3);
-A = rand(2);
-t_A2 = A2Transform(A, [0.2; 0.1]);
-
-% Define our image function
-%f = @(x, y) cos(exp(-((x + 0.2).^2 + (y + 0.6).^2)/(2*(0.6^2)))) + ...
-%     exp(-((x - 0.4).^2 + (y - 0.8).^2)/(2*(0.6)^2));
-f = @(x, y) exp(1*(-4*x.^2 - 8*(y - 0.2*x - 0.8*x.^2).^2));
-
-%% Choose which one to use
-
-tform = t_PSL3R;
-sig_fun = @PSL3R_signature;
-
-%% Plot the image, before and after transform
-n = 1000;
-x = linspace(-1, 1, n);
-y = linspace(-1, 1, n);
-h = 2 / (n - 1);
-[X, Y] = meshgrid(x, y);
-
-fp = tform.forward(f);
-
-F = f(X, Y);
-Fp = fp(X, Y);
-figure(1);
-clf
-subplot(1,2,1)
-imagesc(f(X, Y))
-axis image
-colormap(gray(65536));
-subplot(1,2,2)
-imagesc(fp(X, Y))
-colormap(gray(65536));
-axis image
-
-%% Compute signatures and plot surface and contour maps
-sig = sig_fun(F, h);
-sigp = sig_fun(Fp, h);
-
-figure(2)
-clf
-surf(sig{1}, sig{2}, sig{3}, 'facecolor', 'red', 'facealpha', 0.5, 'edgecolor', 'none')
-hold on
-surf(sigp{1}, sigp{2}, sigp{3}, 'facecolor', 'blue', 'facealpha', 0.5, 'edgecolor', 'none')
-camlight()
-
-figure(3)
-levels = linspace(0, 1, 11);
-clf
-contour(sig{2}, sig{3}, sig{1}, 'k')
-hold on
-contour(sigp{2}, sigp{3}, sigp{1}, 'r:')

### 2017-05-09 matlab/testzoomcallback.m

@@ -1,4 +1,0 @@
-function testzoomcallback(obj, event_obj)
-display(get(event_obj.Axes, 'xlim'))
-display(get(event_obj.Axes, 'ylim'))
-end

### 2017-05-09 matlab/visualise_signatures.m

@@ -1,117 +1,0 @@
-function visualise_signatures(fn, sig_fn, varargin)
-% Create a simple GUI to visualise the signature surfaces of two different
-% images related by a transformation
-
-
-% Initialise the GUI
-handles.fig = figure();
-if (nargin == 2)
-    handles.image_axes_1 = subplot(1, 2, 1);
-    handles.image_axes_2 = 0;
-    handles.signature_axes = subplot(1, 2, 2);
-else
-    handles.image_axes_1 = subplot(2, 2, 1);
-    handles.image_axes_2 = subplot(2, 2, 3);
-    handles.signature_axes = subplot(2, 2, [2, 4]);
-    xlim2 = [-1, 1];
-    ylim2 = [-1, 1];
-    tform = varargin{1};
-end
-handles.zoom = zoom(handles.fig);
-handles.pan = pan(handles.fig);
-
-xlim1 = [-1, 1];
-ylim1 = [-1, 1];
-
-npts = 300;
-ncolors = 65536;
-colormap(parula(ncolors));
-
-clip = 3;
-
-x1 = linspace(xlim1(1), xlim1(2), npts);
-y1 = linspace(ylim1(1), ylim1(2), npts);
-[X, Y] = meshgrid(x1, y1);
-F1 = fn(X, Y);
-handles.image_1 = image(x1, y1, ncolors*F1, 'parent', handles.image_axes_1);
-set(handles.image_axes_1, 'DataAspectRatio', [1 1 1])
-
-if nargin == 3
-    x2 = linspace(xlim2(1), xlim2(2), npts);
-    y2 = linspace(ylim2(1), ylim2(2), npts);
-    [X, Y] = meshgrid(x2, y2);
-    [X, Y] = tform.reverse(X, Y);
-    F2 = fn(X, Y);
-    handles.image_2 = image(x1, y1, ncolors*F2, 'parent', handles.image_axes_2);
-    set(handles.image_axes_2, 'DataAspectRatio', [1 1 1])
-    hx2 = diff(xlim2) / npts;
-    hy2 = diff(ylim2) / npts;
-    [S2z, S2x, S2y] = sig_fn(F2, hx2, hy2);
-end
-% Initialise the signature plots
-hx1 = diff(xlim1) / npts;
-hy1 = diff(ylim1) / npts;
-[S1z, S1x, S1y] = sig_fn(F1, hx1, hy1);
-
-
[…]

### 2017-05-09 nzms_figures.m

@@ -1,121 +1,0 @@
-%% Figures for the NZMS colloquium talk
-% First we need to define our function
-h = 0.005;
-f = @(x, y) 0.5 + 0.5*(sin(4*x).*cos(7*y)) .* exp(-10*((x - 0.1).^2 + (y+0.2).^2));
-
-% Second colour channel
-f1 = @(x, y) 0.5 + 0.5*(sin(5*x).*cos(3*y)) .* exp(-10*((x - 0.1).^2 + (y+0.1).^2));
-[X, Y] = meshgrid(-1.5:h:1.5, -1.5:h:1.5);
-
-G = f(X, Y);
-B = f1(X, Y);
-R = zeros(size(X));
-Im = zeros(size(X, 1), size(X, 2), 3);
-Im(:, :, 1) = R; Im(:, :, 2) = G; Im(:, :, 3) = B;
-
-
-sigfun = @SA2sig;
-%% Generate a random equiaffine mapping
-% Or in this case, load one from file, just contains A, b and Ainv, binv
-% for the forward and backward transformations
-load SA2tform.mat
-
-%% Perform forward mapping
-% By remapping coordinates
-z = A\([X(:), Y(:)]' - repmat(b, 1, numel(X)));
-Xn = reshape(z(1, :), size(X));
-Yn = reshape(z(2, :), size(Y));
-
-%% Compute various signature derivatives
-sig1 = sigfun(h, f(X, Y));
-sig2 = sigfun(h, f(Xn, Yn));
-
-%% Compute the colour images
-G = f(X, Y); B = f1(X, Y); R = zeros(size(X));
-Im = zeros(size(X, 1), size(X, 2), 3);
-Im(:, :, 1) = R; Im(:, :, 2) = G; Im(:, :, 3) = B;
-
-G1 = f(Xn, Yn); B1 = f1(Xn, Yn); R1 = zeros(size(X));
-Im1 = zeros(size(X, 1), size(X, 2), 3);
-Im1(:, :, 1) = R1; Im1(:, :, 2) = G1; Im1(:, :, 3) = B1;
-
-
-%% Plot surfaces
-cm = gray(16384);
-figure(1)
-surf(X, Y, f(X, Y), 'edgecolor', 'none')
-colormap(cm)
-shading('interp')
-camlight()
-axis off
-%print -r200 -dpng 'surf_before.png'
-
-figure(2)
-surf(X, Y, f(Xn, Yn), 'edgecolor', 'none')
-colormap(cm)
-shading('interp')
[…]

### 2017-05-09 nzms_figures_conformal.m

@@ -1,110 +1,0 @@
-%% Figures for the NZMS colloquium talk
-% First we need to define our function
-h = 0.005;
-f = @(x, y) 0.5 + 0.5*(sin(4*x).*cos(7*y)) .* exp(-10*((x - 0.1).^2 + (y+0.2).^2));
-
-% Second colour channel
-f1 = @(x, y) 0.5 + 0.5*(sin(5*x).*cos(3*y)) .* exp(-10*((x - 0.1).^2 + (y+0.1).^2));
-[X, Y] = meshgrid(-1.5:h:1.5, -1.5:h:1.5);
-
-G = f(X, Y);
-B = f1(X, Y);
-R = zeros(size(X));
-Im = zeros(size(X, 1), size(X, 2), 3);
-Im(:, :, 1) = R; Im(:, :, 2) = G; Im(:, :, 3) = B;
-image(Im)
-
-%% Generate a random conformal mapping
-f_forward = random_mobius();
-[Xn, Yn] = f_forward(X, Y);
-
-%% Compute various signature derivatives
-sig1 = SA2sig(h, f(X, Y));
-sig2 = SA2sig(h, f(Xn, Yn));
-
-%% Compute the colour images
-G = f(X, Y); B = f1(X, Y); R = zeros(size(X));
-Im = zeros(size(X, 1), size(X, 2), 3);
-Im(:, :, 1) = R; Im(:, :, 2) = G; Im(:, :, 3) = B;
-
-G1 = f(Xn, Yn); B1 = f1(Xn, Yn); R1 = zeros(size(X));
-Im1 = zeros(size(X, 1), size(X, 2), 3);
-Im1(:, :, 1) = R1; Im1(:, :, 2) = G1; Im1(:, :, 3) = B1;
-
-
-%% Plot surfaces
-cm = gray(16384);
-figure(1)
-surf(X, Y, f(X, Y), 'edgecolor', 'none')
-colormap(cm)
-shading('interp')
-camlight()
-axis off
-%print -r200 -dpng 'surf_before.png'
-
-figure(2)
-surf(X, Y, f(Xn, Yn), 'edgecolor', 'none')
-colormap(cm)
-shading('interp')
-camlight()
-axis off
-%print -r200 -dpng 'surf_after.png'
-
-%% Plot grayscale images
-figure(3)
-imagesc(f(X, Y))
-colormap(cm)
-axis off
-print -r200 -dpng 'image_before.png'
-figure(4)
-imagesc(f(Xn, Yn))
-colormap(cm)
[…]

### 2017-05-09 random_SA2.m

@@ -1,22 +1,0 @@
-function [f_forward, A, b] = random_SA2()
-theta = 2*pi*rand();
-gamma = 0.5;
-R = [cos(theta), -sin(theta); sin(theta), cos(theta)];
-A = gamma*R + rand(2);
-if det(A) < 0
-    A(1, :) = -A(1, :);
-end
-A = 1 / sqrt(det(A)) * A;
-b = 0.2 * randn(2, 1);
-f_forward = @forward_tform;
-
-    function [Xn, Yn] = forward_tform(X, Y)
-        z = A\([X(:), Y(:)]' - repmat(b, 1, numel(X)));
-        Xn = reshape(z(1, :), size(X));
-        Yn = reshape(z(2, :), size(Y));
-    end
-end
-
-
-
-

### 2017-05-09 random_conformal.m

@@ -1,17 +1,0 @@
-function f_forward = random_conformal()
-% Generate the first 10 Taylor coefficients
-order = 100;
-a = (randn(1, order+1) + 1i*randn(1, order+1)) ./ (factorial(0:order));
-a(1) = a(1) / 10;
-f_forward = @forward;
-    function [Xn, Yn] = forward(X, Y)
-       Z = X + 1i*Y;
-       Zn = zeros(size(Z));
-       for k = 0:order
-           Zn = Zn + a(k+1)*Z.^k;
-       end
-       Xn = real(Zn);
-       Yn = imag(Zn);
-        
-    end
-end

### 2017-05-09 random_mobius.m

@@ -1,13 +1,0 @@
-function f_forward = random_mobius()
-coeffs = randn(1, 4) + 1i * randn(1, 4);
-a = coeffs(1); b = 0.1*coeffs(2); c = coeffs(3); d = coeffs(4);
-f_forward = @forward;
-
-    function [Xn, Yn] = forward(X, Y)
-        Z = X + 1i * Y;
-        Zn = (a*Z + b) ./ (c*Z + d);
-        Xn = real(Zn);
-        Yn = imag(Zn);
-    end
-
-end

### 2017-05-09 sig_pics.m

@@ -1,104 +1,0 @@
-%% Signature surface pictures
-% Script file to create nice signature surface pictures
-%
-
-%% Test function
-% Same function as in the Mobius  paper
-f = @(x, y) exp(-4*x.^2 -8*(y-0.2*x - 0.8*x.^2).^2);
-
-%%
-% Set the colormap for all figures
-cmap = hot(65536);
-
-%% Construct the invariant object
-% This is an object that stores the function and step size, and has methods
-% to compute all of the things that we are interested in (signatures etc).
-% The image is depicted below. Note you can modify 'h' later
-foo = ImageInvariant(f, 'h', 0.001);
-imshow(foo.evaluate())
-colormap(cmap)
-
-%% SE2 signature surface
-% Just computes the signature using function value S0, $f_x + f_x$ (S1), and
-% $f_{xx} + f_{yy}$ (S2)
-figure(1)
-clf
-foo.h = 0.005;
-[S0, S1, S2] = foo.SE2_signature();
-surf(S1, S2, S0, 'edgecolor', 'none', 'facealpha', 0.9)
-%axis off
-colormap('default')
-camlight
-lighting('phong')
-shading('interp')
-
-%% Sim2 signature surface
-% Just computes the signature using function value S0, $f_x + f_x$ (S1), and
-% $f_{xx} + f_{yy}$ (S2)
-figure(1)
-clf
-foo.h = 0.005;
-[S0, S1, S2] = foo.Sim2_signature();
-surf(S1, S2, S0, 'edgecolor', 'none', 'facealpha', 0.9)
-axis('equal')
-colormap('default')
-camlight
-lighting('phong')
-shading('interp')
-
-%% SA2 signature surface
-figure(2)
-clf
-foo.h = 0.005;
-[S0, S1, S2] = foo.SA2_signature();
-surf(S1, S2, S0, 'edgecolor', 'none', 'facealpha', 0.9)
-%axis off
-colormap(cmap)
-camlight
-lighting('phong')
-shading('interp')
-
-%% Mobius signature surface
-% S0 is the function value, S1, S2 are the two polar coordinate angles of
-% the invariants projected to the unit sphere (as in dis.pdf), S3 and S4
-% are the ones involving curl and divergence
-figure(3)
-clf
-foo.h = 0.005;
-tol = 0;
[…]

### 2017-05-09 visualise_signature_points.m

@@ -1,59 +1,0 @@
-function visualise_signature_points(I, S0, S1, S2)
-
-% Richard Brown, 2015
-
-% Create the figure
-hF = figure( ...
-       'Name',        'Signature Visualisation'...
-       );
-
-hA_im = subplot(1,2,1);
-imshow(I)
-axis('image')
-colormap('hot')
-hold on
-
-hA_surf = subplot(1,2,2);
-surf(S0, S1, S2, 'edgecolor', 'none', 'facealpha', 0.5);
-colormap('hot')
-hold on
-
-
-% Initialise points and lines
-[m, n] = size(I);
-markerSize = 40;
-axesLimits = [0.5, n+0.5, 0.5, m+0.5];
-
-hold on
-hx = plot(hA_im, 1, 1, 'b.', 'markersize', markerSize);
-set(hA_im, 'xlim', axesLimits(1:2), 'ylim', axesLimits(3:4))
-hs = plot3(hA_surf, 0, 0, 0, 'b.', 'markersize', markerSize);
-
-% Set Axes Properties
-grid on
-%set(hA_surf, 'DataAspectRatio', [1 1 1])
-
-% Associate the callback with mouse click
-set(hF, 'WindowButtonMotionFcn', @foo)
-
-% Callback nested function
-    function foo(varargin)
-        % Get the x point from the axes
-        cp = get(hA_im, 'CurrentPoint');
-        if cp(1,1) < axesLimits(1) || cp(1,1) > axesLimits(2) || ...
-                cp(1,2) < axesLimits(3) || cp(1,2) > axesLimits(4)
-            return
-        end
-        x = round(cp(1, 1:2));
-        
-        % Transform it
-
-        
-        % Modify the points and lines
-        set(hx, 'XData', x(1), 'YData', x(2));
-        set(hs, 'XData', S0(x(2), x(1)), ...
-            'YData', S1(x(2), x(1)), ...
-            'ZData', S2(x(2), x(1)));
-    end % foo
-
-end % EIGENDEMO

### 2017-06-16 code/MobiusTransform.m
Fix bug in Mobius transformation

@@ -26,7 +26,7 @@ classdef MobiusTransform < SpatialTransform2D
         
         function [xnew, ynew] = reverse_coords(obj, x, y)
             z = x + 1i*y;
-            w = -z ./(obj.gamma*y - obj.alpha);
+            w = -z ./(obj.gamma*z - obj.alpha);
             xnew = real(w);
             ynew = imag(w);
         end

### 2017-06-16 code/Mobius_signature.m

@@ -3,12 +3,17 @@ derivative_order = 3;
 out = signature_switch(f, @evaluate, derivative_order, varargin{:});
     function sig = evaluate(derivs)
         [f, fx, fy, fxx, fxy, fyy, fxxx, fxxy, fxyy, fyyy] = derivs{:};
+        
         J1 = fx.*fx + fy.*fy;
+        
         J2 = fxx + fyy;
+        
         J3 = J1.*(fx.*(fxxx + fxyy) + fy.*(fxxy + fyyy)) + ...
             2*J2.*(fx.^2.*fxx + 2*fx.*fy.*fxy + fy.^2.*fyy);
+        
         J4 = J1.*(fx.*(fxxy + fyyy) - fy.*(fxxx + fxyy)) + ...
             2*J2.*(fx.^2.*fxy + fx.*fy.*fyy - fx.*fy.*fxx - fy.^2.*fxy);
+        
         K1 = fy.^5.*fyyy + 9/2*fy.^2.*fyy.^2.*fx.^2 + fy.^3.*fyyy.*fx.^2 + ...
             3/2*fyy.^2.*fx.^4 -9*fy.^3.*fyy.*fx.*fxy + 3.*fy.*fyy.*fx.^3.*fxy + ...
             3/2*fy.^4.*fxy.^2 - 9*fy.^2.*fx.^2.*fxy.^2 + ...
@@ -17,6 +22,7 @@ out = signature_switch(f, @evaluate, derivative_order, varargin{:});
             9*fy.*fx.^3.*fxy.*fxx + 3/2*fy.^4.*fxx.^2 + 9/2*fy.^2.*fx.^2.*fxx.^2 + ...
             3*fy.^3.*fx.^2.*fxxy + 3*fy.*fx.^4.*fxxy + fy.^2.*fx.^3.*fxxx + ...
             fx.^5.*fxxx;
+        
         K4 = -3*fy.*fyy.^2.*fx.^3 + fy.^2.*fyyy.*fx.^3 + fyyy.*fx.^5 + 9*fy.^2.*fyy.*fx.^2.*fxy ...
             - 3*fyy.*fx.^4.*fxy - 6*fy.^3.*fx.*fxy.^2 + 6*fy.*fx.^3.*fxy.^2 - ...
             3*fy.^3.*fx.^2.*fxyy - 3*fy.*fx.^4.*fxyy - 3*fy.^3.*fyy.*fx.*fxx + ...
[…]

### 2017-06-16 paper/paper.tex
Updates

@@
 \usepackage{amsmath, amsthm, amssymb, mathtools}
+\usepackage{graphicx}
 \newtheorem{theorem}{Theorem}
@@
 \subsection{Technical wank}
-Completeness, degeneracy, moving frames as concept, table of numbers of
+Completeness, degeneracy, moving frames as concept table of numbers of
 derivatives, all that jazz, maybe scaling technique
@@
 
+\begin{figure}
+	\includegraphics[width=12cm]{../images/SE2Transform_signature}
+	\caption{SE(2) signature}
+\end{figure}
+\begin{figure}
+	\includegraphics[width=12cm]{../images/E2Transform_signature}
+	\caption{E(2) signature}
+\end{figure}
+\begin{figure}
+	\includegraphics[width=12cm]{../images/SA2Transform_signature}
+	\caption{SA(2) signature}
+\end{figure}
+\begin{figure}
+	\includegraphics[width=12cm]{../images/A2Transform_signature}
+	\caption{A(2) signature}
+\end{figure}
+
 \subsection{Hat tip to practicality: smoothing for E(2) and subgroups thereof}

### 2017-06-16 code/make_figures.m

@@ -1,13 +1,33 @@
 %% Signature surface generation script
 syms x y
-f(x, y) = exp(-2*x.^2 - 4.*sin(y + x).^2);
+%f(x, y) = exp(-2*x.^2 - 4.*sin((y + 0.5*x.^2)).^2);
+f(x, y) = 0.6*(exp(-2*x.^2 - 0.5*x.*y - 4*y.^2) + 0.5 + 0.5*sin(2*(x + y)));
 f_numeric = matlabFunction(f);
 
-xlim = [-1, 1];
-ylim = [-1, 1];
+% Mesh for plotting surfaces
+xlim = [-0.2, 0.2];
+ylim = [-0.2, 0.2];
 ngrid = 500;
+ny = 480;
 [X, Y, xvec, yvec] = regular_grid(xlim(1), xlim(2), ngrid, ...
-    ylim(1), ylim(2), ngrid);
+    ylim(1), ylim(2), ny);
+
+%% Write image 
+n_image = 2000;
+[Xim, Yim, ximvec, yimvec] = regular_grid(xlim(1), xlim(2), n_image, ...
+    ylim(1), ylim(2), n_image);
+F = f_numeric(Xim, Yim);
+draw_image(F, 'xlim', xlim, 'ylim', ylim);
+%imwrite(F, 'images/image.jpg')
+
+%% Write transformed image
+[Xpi, Ypi] = tform.reverse(Xim, Yim);
+imwrite(f_numeric(Xpi, Ypi), strcat('images/', class(tform), '_image.jpg'));
+
+%% Write signature picture
+% Manually position the signature and lighting first, then run this:
+axis off
+print('-r200', '-dpng', strcat('images/', class(tform), '_signature.png'))
 
 %% E(2)
 tform = E2Transform(1, -1, 0.1, -0.2);
@@ -15,44 +35,57 @@ tform = E2Transform(1, -1, 0.1, -0.2);
 [Xp, Yp] = tform.reverse(X, Y); % arrays
 [xp, yp] = tform.reverse(x, y); %symbolic
 
-
 sig = E2_signature(f);
 sigp = E2_signature(f(xp, yp));
 
 figure(1)
+clf
 subplot(1,2,1)
 draw_image(f_numeric(X, Y), 'xlim', xlim, 'ylim', ylim)
 subplot(1,2,2)
[…]

### 2017-08-11 paper/paper.tex
Most just pasting

--- 2017-05-09 paper/paper.tex
@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{proposition}{Proposition}
+\def\R{\mathbb{R}}
+\usepackage{xcolor}
 
@@
 \section{Introduction}
+
+A classic problem in image processing is to recognise the similarity or planar objects (point sets, curves, or images) up to transformations from a local planar group such as the Euclidean, similarity, and projective groups.
+Building on Cartan's solution to the equivalence problem, an influential new paradigm for this problem was introduced by Calabi et al.
+\cite{calabi98}, the differential invariant signature.
+The general theory has been developed extensively \cite{} and many examples computed for planar curves \cite{}, including the Euclidean, equi-affine, and projective groups.
+In this paper we develop and apply differential invariant signatures for planar images.
+Beyond merely computing the invariants, we emphasize the following.
+\begin{enumerate}
+\item We consider a very wide range of planar groups; the lattice structure of the set of groups influences
+the relationship between the sets of invariants for the different groups.
+\item We consider both finite-dimensional local Lie transformation groups and infinite-dimensional pseudogroups.
+\item The signature must vary continuously with respect to the image, either for all smooth images or for all except
+a set of sufficiently high codimension. This is essential if the signature is to be used to detect similarity of images, but it fails for the rational invariants found in the literature.
+\item We do not insist that the signature is complete, i.e., that it  determines the image up to a transformation; for many applications an incomplete signature is sufficient.
+This may allow comparison of less smooth images.
+\item We consider $k$-colour images for $k=1,2,\dots$. 
+\item Putting these ingredients together, we arrive at a crucial ``meta-invariant'': the number of derivatives
+of the image required as a function of the parameters (group, completeness, and number of colours).
+\end{enumerate}
+
+Let $G$ be a (finite or infinite-dimensional) local planar transformation group. 
+A {\em $k$-colour image} is a triple $(f,\Omega,k)$ where $\Omega\subset\R^2$, $1\le k\in\mathbb{Z}$,
+and $f\colon\Omega\to\R^k$. The function $f$ will be taken to be as smooth as necessary.
+A transformation $\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) = (f\circ\varphi^{-1},\varphi(\Omega),k)$.
+(As we work locally, we will usually omit the domain $\Omega$; if the number of colours $k$ is not given, we assume $k=1$.)  A differential invariant is an invariant of the prolonged action of $G$ on the derivatives of $f$, i.e., a function $I$ of the values of $f$ and its derivatives at a point such that $I(f)(x,y) = I(\varphi\cdot f)(\varphi(x,y))$.
+An {\em $m$-dimensional signature set} is the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e.
+the
+set $\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$. 
+A signature set is complete for $f$ if it determines $f$ up to transformations from $G$, i.e.
+if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies there exists a transformation $\varphi\in G$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
+
+An algorithm to compute invariants and determine complete signature sets is described in \cite{olver2001}. First, the
+entire set of invariants is computed using the method of moving frames.
+Second, determine the differential invariant order $s$ of $f$.
+Then the signature set of a maximal set of functionally independent invariants of order $s+1$ is complete.
+A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
+
+While we follow this approach in general, in specific cases we have computed invariants using other techniques
+including the invariant tensor theorem and classical invariant theory.
+We shall see that this yields insights into the relationships between the different groups.
+We develop our approach through examples of progressively more complicated groups.
+
 \subsection{Notation}
@@
 
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{| l | c c c |}
+\hline
+\# derivs. & $k=1$ & $k=2$ & $k=3$ \\
+\hline
+SE(2) & 2 &1 & 1 \\
+E(2) & 2 & 1 & 1 \\
+Sim(2) & 2 & 1 & 1 \\
+SA(2) & 2 & 2 & 2 \\
+A(2) & 3 & 2 & 2 \\
+$\mathrm{PSL}(2,\mathbb{C})$ & 3 & 3 & 3 \\
+$\mathrm{PSL}(3,\R)$ & 3 & 2 & 2 \\
+$\mathrm{Diff}_{\mathrm{vol}}$ & -- & 1 & 1 \\
+$\mathrm{Diff}_{\mathrm{con}}$ & 3 & 1 & 1 \\
+$\mathrm{Diff}$ & -- & -- & 0 \\
+\hline
+\end{tabular}
+\caption{Number of derivatives of $f$ needed to construct a differential invariant signature of $f$ as a function of the group $G$ and the number of colours $k$ of $f$.
+The entry `--' indicates that there is no differential invariant signature in that case.}
+\end{center}
+\end{table}
+
 \section{The Stamp Collection I: The Affine group and its subgroups}
@@
 In this case we have $A^TA = I$ and $\det A = 1$.
+
+$E(2)$ is the Euclidean group of planar translations, rotations, and reflections.
+We write $f_1 = \partial f/\partial x$ and $f_2 = \partial f/\partial y$ and use the summation convention, so that two well-known Euclidean invariants $\|\nabla f\|^2$ and $\nabla^2 f$ can be written as $f_i f_i$ and $f_{ii}$, respectively.
+
+By the invariant tensor theorem (???ref???), all polynomial invariants of $f$ and its derivatives are the complete contractions. Up to order 2 there are 5 of these:
+$ (f, f_i f_i, f_{ii}, f_{ij}f_i f_j, f_{ij}f_{ij})$
+Any relation (syzygy) between 3 of these involves 2nd derivatives; so any derived relation involves 3rd derivatives and
+cannot be used to determine a second order invariant. In this paper we shall focus on the signature sets
+$ (f,f_i f_i,f_{ii})$
+in $\mathbb{R}^3$
+and
+$(f, f_i f_i, f_{ii}, f_{ij}f_{ij})$
+in $\mathbb{R}^4$. 
+Although the first is not complete (we shall give an example of a parameterized family $(f_c,\Omega_c)$
+of images, not related by Euclidean transformations, with the same signature sets), it can still
+be used to distinguish {\em most} images.
+
+\medskip
+
+{\narrower\small
+
+{\bf Aside 1. Testing the 3-dim signature.} Let $c$ be a parameter in the range $0<c<\pi/4$. Let $a = \sin(c)\cos(c)$ and $b=1/a$.
+Consider the image $ f = a x y$ on domain $\Omega$ the sector  given in polar
+coordinates by $\{(r,\theta)\colon 0 \le r \le b,\ 0 \le \theta \le c\}$.
+Then in polar coordinates, the 3-dimensional signature set is
+$$ (f, f_i f_i, f_{ii})(\Omega) = \{(ar^2 \sin\theta\cos\theta, a^2 r^2, 0)\colon 0 \le r \le b,\ 0 \le \theta \le c\}$$
+which is the  triangle with vertices $(0,0,0)$, $(0,1,0)$, and $(1,1,0)$.
+That is, all of these images (with different values of $c$) have the same signature set, but they are
+not related by a Euclidean transformation.
+
+}
+
+\medskip
+
+{\narrower\small 
+{\bf Aside 2. Testing the 4-dim signature.} 
+Now the 4-dimensional signature is checked. Let $(f,\Omega)$ be an image with
+signature $\Sigma := \mathcal{I}(f)(\Omega) = (f,f_if_i,f_{ii},f_{ij}f_{ij})(\Omega)$. Let $(g,\widetilde\Omega)$ be
+an image with the same signature set $\Sigma$. We need to determine coordinates 
+$(\tilde x,\tilde y)$ on $\Sigma$ such that $\mathcal{I}(g)(x,y) = \mathcal{I}(f)(\tilde x,\tilde y)$.
+The first component is $g(x,y)=f(\tilde x,\tilde y)$. That is, $g$ must be {\em some} coordinate
+transformation of $f$. 
+We seek the generators of solutions, setting $\tilde x = x + \varepsilon v^1(x,y)$,
+$\tilde y = y + \varepsilon v^2(x,y)$. The first component yields $g_j = f_j + 2\varepsilon (f_i v^i v_j + 
+f_{ij}v^i) + \dots$. This can be used to eliminate $g$ from the remaining equations, yielding
+
+\begin{equation}
+\begin{aligned}
+f_i f_j v^{i}_j &= 0 \\
+f_i v^i{jj} + 2 f_{ij}v^i_j&= 0\\
+f_{jk}f_i v^i_{jk} + 2 f_{jk}f_{ik}v^i_j &= 0\\
+\end{aligned}
+\end{equation}
+
+This is a set of 3 linear PDEs in $v^1$, $v^2$. Note that Euclidean
+transformations have $v^i_j = -v^j_i$ and do satisfy all 3 equations. We can test
+if the equations are locally overdetermined by differentiating and seeking compatibility 
+conditions. We do this in Mathematica and find that differentiating the first equation 
+3 times in $x$ and $y$, and the second two equations twice, yields a system
+of 22 linear equations for the derivatives of $v^i$ at a point that,
+for generic $f$, imply $v^i_{jk}=0$ at that point for all $i$, $j$, $k$. Since the point is arbitrary,
+we conclude that the $v^i$ must be linear functions and that the transformation
+is Euclidean.
+
+}
+
+\medskip
+
+{\narrower\small 
+{\bf Aside 3. Role of the invariants} 
+All of the 2nd order differential invariants play known roles in geometric analysis:
+\begin{enumerate}
+\item $f_if_i=\|\nabla f\|^2$ is the Lagrangian density for the Laplacian;
+\item $f_{ii}$ is the Laplacian, which plays a key role in Euclidean and conformal geometry;
+\item $f_{ij}f_i f_j$ is the `infinity-Laplacian'; critical points of $\|\nabla f\|_{L^\infty}$ obey the PDE $f_{ij}f_i f_j=0$;
+\item
+$f_{ij}f_i f_j$ is also a Lagrangian density for $-2\det f_{ij}$, which arises in Monge--Amp\`ere equations and
+which can be written in terms of the final 2nd order invariant as $-2 \det f_{ij} = f_{ij}f_{ij}-f_{ii}^2$.
+\end{enumerate}
+In addition, we shall see in later sections that functions of these invariants are invariants or
+relative invariants for many groups that contain $E(2)$, namely $Sim(2)$, $SA(2)$, $A(2)$, $PSL(3,\mathbb{R})$, $PSL(2,\mathbb{C})$, and the conformal group.
+}
+
+\medskip
+
+For $k$ colours, signature sets of dimension up to $k + k(k+1)/2$ can be 
+chosen from the invariants $f^i$ and $f^i_m f^j_m$ for $i,j=1,\dots, k$.
+For $k\ge 2$, first derivatives suffice. However, note that for
+$k\ge 3$ the 3-dimensional signature $(f^1,f^2,f^3)$ 
+is invariant under all local planar diffeomorphisms; a higher-dimensional
+signature, involving first derivatives, is required.
+
+The similarity group is the direct product of $E(2)$ with the positive scalings.
+All invariants of $Sim(2)$ must be functions of invariants of its subgroup $E(2)$. We therefore
+determine how the scalings $(x,y) \mapsto (\lambda x,\lambda y)$ transform the Euclidean invariants:
+$$ (f, f_i f_i, f_{ii}, f_{ij}f_if_j, f_{ij}f_{ij}) \mapsto (f, \lambda^2 f_i f_i, \lambda^2 f_{ii}, \lambda^4 f_{ij}f_i f_j, 
+\lambda^4 f_{ij}f_{ij}).$$
+A standard approach in such a situation is to form rational invariants. One possibility is
+$$\left(f, \frac{f_{ii}}{f_i f_i}, \frac{f_{ij}f_i f_j}{(f_i f_i)^2}, \frac{f_{ij}f_{ij}}{(f_i f_i)^2}\right).$$
+However, this is singular at critical points of $f$. Critical points are a generic phenomenon of real
+functions, so this invariant is not continuous for generic $f$.
+
+Another possibility is
+$$\left(f, \frac{(f_i f_i)^2}{f_{ij}f_{ij}}, \frac{(f_{ii})^2}{f_{ij}f_{ij}}, \frac{f_{ij}f_i f_j}{f_{ij}f_{ij}}\right).$$
+This is singular only when $f_{ij}=0$ for all $i$ and $j$, a codimension 1 phenomenon for images.
+
+However, an even better solution is possible, which also leads to a general technique for
+dealing with rational invariants that we shall use throughout our study. 
+Let $I_1=(f_i f_i)^2$, $I_2=(f_{ii})^2$, and $I_3=f_{ij}f_{ij}$. Then $I\mapsto \lambda^4 I$ under scalings.
+Thus, positive rays in $I$ are similarity invariants. This leads to the invariant $I/\|I\|$ which
+takes values in the unit sphere in $\mathbb{R}^3$. That is, it is an $S^2$-valued invariant.
+It is singular only when $I=0$, i.e., when $f_i = f_{ij}=0$ for all $i$ and $j$, a codimension
+3 phenomenon for images. Overall, we have the 3-dimensional Sim(2) signature set
+$$(f,I/\|I\|)(\Omega)\subset \mathbb{R}\times S^2.$$
+As any function of an invariant is also invariant, we can map the invariant into Euclidean space for convenience.
+We can use, for example, the signature set $F(f)I/\|I\|(\Omega)\subset\mathbb{R}^3$ for some $F$.
+
+Including $I_4=f_{ij}f_if_j$ in the set leads to an $\mathbb{R}\times S^3$-valued 4-dimensional signature set.
+
+\medskip
+
+{\narrower\small
+
+{\bf Aside. Signatures with removable singularities.} As remarked above, at points
+where $f_i=f_{ij}=0$ for all $i$, $j$, the $S^2$-valued signature () is not defined. However,
+it is possible that for some images and some signatures, such singularities are removable.
+Let $f$ be a cubic polynomial in $x$ and $y$ so that $f_i=f_{ij}=0$ at $(x,y)=(0,0)$.
+Then the components of $((f_if_i)^2,(f_{ii})^2, f_{ij}f_{ij})$ are polynomials
+of degree 8, 2, and 2 respectively. Therefore as $(x,y)\to(0,0)$ along a ray,
+the $S^2$-valued signature $I/\|I\|$ tends to a point on the great circle with $I_1=0$. Along
+different rays, it tends to different points. Thus the singularity at $(x,y)=(0,0)$ is not removable.
+
+Now consider the slightly different signature set formed from 
+$\tilde I = ((f_if_i)^2, f_{ij}f_{ij}, f_{ij}f_i f_j)$. 
+Its components are polynomials of degree 8, 2, and 5, respectively, when $f$ is a cubic. Thus
+as $(x,y)\to(0,0)$, the $S^2$-valued signature $\tilde I/\|\tilde I\|$ tends to
+$(0,1,0)$ provided $f_{11}$, $f_{122}$, and $f_{22}$ are not simultaneously equal
+to zero on a ray. But this happens if and only if the cubic $f$ is identically zero.
+Therefore, this signature is continuous for arbitrary smooth functions
+{\em except} those which obey $f_i = f_{ij}=f_{ijk}=0$ for some $(x,y)$,
+which is a codimension 6 phenomenon for images.
+
+}
+
+\medskip
+
+Although extremely simple and apparently tied to scaling symmetries, this trick has
+wide applicability. As is well known, for many group actions orbits cannot be separated by continuous
+invariants. In contrast, generic orbits of rational algebraic groups are always separated by
+a finite set of rational invariants \cite{hubert}. Suppose we have found some rational
+invariants of images for some group that can be written in the form
+$$ \left( \frac{N_1}{D},\dots,\frac{N_r}{D}\right)$$
+where the $N_i$ are continuous rational functions (not necessarily polynomials), and $D$ is a polynomial.
+Then we have
+$$ \varphi \cdot \left(D,N_1,\dots,N_r\right) \mapsto \psi(\varphi)(D,N_1,\dots,N_r)$$
+---that is, essentially a scaling. There are now two cases.
+
+Case 1. $\psi(\varphi)>0$ for all $\varphi\in G$. In this case we have an $S^r$-valued invariant that
+is continuous except where $D=N_1=\dots N_r=0$. When $r\ge 2$, this is typically a codimension
+1 condition for images. That is,  $r$ rational invariants with the same denominator yield $r$ continuous
+invariants.
+
+Case 2. $\psi(\varphi)$ takes on both signs. (As the action is continuous, this case is only
+possible if $G$ is not connected.) In this case we have an invariant on the projective space $\mathbb{R}P^r$.
+The options are to work directly on this space or to map it into a Euclidean space, by an embedding or immersion
+(e.g. $\mathbb{R}P^2$ can be embedded in $\mathbb{R}^4$ or immersed in $\mathbb{R}^3$).
+
+The crucial requirement is that at least two invariants share the same denominator. In all
+of the examples in this paper, only one denominator arises.
+
+If $r$ is large enough it is possible to increase the codimension of the bad set of images without
+increasing the dimension of the signature. For example, if $r=3$ we can project
+$ (D, N_1, N_2^2+N_3^2)$
+to $S^2$; this is only singular when $D=N_1=N_2=N_3=0$, which is typically a codimension-2 situation for images.
+
+\section{Equi-affine and affine planar curves}
+
+We illustrate the usefulness of this technique by reconsidering the example of equi-affine signature curves
+of planar curves studied in Calabi et al. \cite{calabi}. Here $r\colon S^1\to\R^2$ is a planar curve, on 
+which the equi-affine group acts by $(A,b)\cdot r = A r + b$, $\det A = 1$. The signature curve
+of \cite{calabi} is $(\kappa,\kappa_s)$ where $\kappa$ is equi-affine curvature and $\kappa_s$
+is derivative with respect to equi-affine arclength. It is sufficient for our purposes to record
+this in local coordinates in which the curve is written $y=u(x)$:
+$$\kappa = \frac{3 u_2 u_4 - 5 u_3^2}{9 u_2^{8/3}}$$
+$$\kappa_s  \frac{9 u_2^2 u_5 - 45 u_2 u_3 u_4 + 40 u_3^3}{27 u_2^4}$$
+Here $u_n = d^n u/dx^n$.
+It is remarked in \cite{calabi}  that ``affine geometry requires the (unfortunate) restriction to convex curves'',
+as the curvature and its derivatives are not defined when $u_{xx}=0$, e.g. at inflection points; in \cite{calabi} 
+it is suggested to deal with this by studying the asymptotic behaviour of the signature curve as it blows
+up near inflection points.
+
+We now show that using a spherical instead of a planar signature curve, with singularities removed,
+yields a signature curve that is continuous for all planar curves with inflection points of any finite order.
+
+Let
+$$ I = (u_2^8, u_2^8(9\kappa)^3, u_2^4 (27\kappa_s)^2) = (u_2^8, (-5 u_3^2 + 3 u_2 u_4)^3,(9 u_2^2 u_5 - 45 u_2 u_3 u_4 + 40 u_3^3)^2).$$
+The equiaffine group acts on $I$ as $(A,b)\cdot I = A_{11}^{-24}I$, so projection 
+to the sphere yields an equiaffine signature curve. If $u\sim x^n$ as $x\to 0$ with $n\ge 3$, then
+$I\sim(x^{8(n-2)}, x^{6(n-3)},x^{6(n-3)})$ as $x\to 0$. Therefore the signature curve
+tends to a well-defined point on $I_1=0$ as $x\to 0$ for an inflection point
+of any order $n$, and the signature is continuous except for a set of 
+curves of infinite codimension.
+
+(Note that the precise behaviour of the signature near singularities is important. A signature
+that behaved like $(x^3, x^3, x)$ as $x\to 0$ would not yield a continuous $S^2$-valued signature,
+as it tends to $(0,0,1)$ as $x\to 0^+$ and to $(0,0,-1)$ as $x\to 0^-$; removing the sign requires an extra step.)
+
+In this example, the projection technique is more or less equivalent to
+Calabi et al.'s suggestion of analyzing the blowup of the planar signature.
+
+The same technique provides a continuous affine signature. The next equi-affine invariant is
+$$ \kappa_{ss} = \frac{-160 u_{3}^4 + 255 u_2 u_3^2 u_4 - 45 u_2^2 u_4^2 - 63 u_2^2 u_3 u_5 + 9 u_2^3 u_6}{27 u_2^({16/3}}.$$
+Under the action of the affine group, we
+have
+$$(\kappa,\kappa_s,\kappa_{ss})\mapsto (\lambda^{-4/3},\lambda^{-2},\lambda^{-8/3})$$
+where $\lambda = \det A$. Therefore we form the rational relative invariant of weight $-8$
+$$\tilde I = (\kappa^6,\kappa_s^4,\kappa_{ss}^3).$$
+Projection to the sphere provides an $S^2$-valued 4th order affine signature curve.
+The denominator of each term is $u_{xx}^{16}$. If $u\sim x^n$ as $x\to 0$ with 
+$n\ge 3$, then $\tilde I \sim (x^{-4(n+1)},x^{-4(n+1)},x^{-4(n+1)})$.
+Therefore the signature curve tends to a well-defined point on $S^2$ as $x\to 0$ 
+for an inflection point of any order $n$, and, as for the equiaffine case, the signature is continuous except for
+a set of curves of infinite codimension.
+
+\section{Special affine group {\bf SA(2)}}
+
+The special or equi-affine group $SA(2)$ is the group of transformations $\mathbf{x}\mapsto A\mathbf{x}+\mathbf{b}$
+where $\det A =1$.  This case leads to an intriguing connection with classical invariant theory \cite{olverclassical}.
+This is because the derivatives of $f$ transform as
+\begin{equation}
+\begin{aligned}
+f_i & \mapsto A_{ij} f_j \\
+f_{ij} & \mapsto A_{il} A_{jm} f_{lm}\\
+f_{ijk} & \mapsto A_{il}A_{jm}A_{kn}f_{lmn}\\
+\end{aligned}
+\end{equation}
+and so on. These are the same transformation rules obey by a linear, quadratic, and cubic binary forms.
+The Taylor series of $f$ {\em is} the sum of a constant, a linear binary form, a quadratic binary form, and so on.
+ In this case we have a vector
+space $V=\R^2$, the space $V_n$ of binary forms of degree $n$ ($\cong Sym(V^{\otimes n})$), and seek
+joint invariants of $V_1\oplus V_2\oplus V_3\oplus\dots$ under the action of $SL(V)$. The ones we need,
+the joint invariants of $V_1\oplus V_2\oplus V_3$, 
+were found first by Alexander Bessel in 1869 \cite{bessel}. (See page 108 of \cite{draisma}.)
+
+The invariants can all be written as ``transvectants''. 
+Given forms $g$ and $h$, their $p$th transvectant $(g,h)_p$ is given by (up to a constant)
+$$ (g,h)_p = \sum_{i=0}^p (-1)^p {p \choose i} 
+\frac{\partial^p g}{\partial x^{p-i}\partial y^{i}}
+\frac{\partial^p h}{\partial x^{i}\partial y^{p-i}}
+$$
+If $g$ is degree $m$ and $h$ is degree $n$ then $(g,h)_p$ is degree $m+n-2p$; transvectants of degree 0 are invariants.
+The general method to find them is to first compute how many invariants there are of each degree (this can be done independently), form the available invariants from transvectants, and then finding an independent set -- this is done by evaluating the derivatives of a candidate set on random forms and checking if they have full rank.
+
+Let $\ell$ be the linear form $f_i x_i$ and $q$ be the quadratic form $f_{ij} x_i x_j$.
+For derivatives up to 2nd order, we need the invariants of $V_1\oplus V_2$. 
+The polynomial invariants are generated by
+$$(q,q)_2 = \det f'' =: C$$
+and
+$$(q,\ell^2)_2 = f_{22}f_1^2 + f_{11}f_2^2 - 2 f_{122} f_1 f_2 =: D.$$
+The group orbits on $V_1\oplus V_2$ are codimension 2 and generic orbits are separated by these invariants.
+
+In fact, it is easy to see directly that these two quantities are invariant. Switching to matrix notation, we 
+have $f'' \mapsto A f'' A^T$ so that $\det f'' \mapsto \det(A)\det(f'')\det(A^T) = \det(f'')$,
+and $(f')^T (f'')^{-1} f' \mapsto (A f')^T A^{-T} (f'')^{-1} A^{-1}  (A f') = (f')^T (f'')^{-1} f'$. 
+The product of these two invariants is $(f')^T \mathrm{adj}(f'') f' = D$.
+
+This quantity $D$ turns out to be of interest in its own right; we discuss aspects and interpretations of it here.
+\begin{enumerate}
+\item $D$ can of course be written as a function
+of the invariants of its Euclidean subgroup, namely
+$$D = f_{ii} f_j f_j - f_{ij}f_i f_j.$$
+\item
+$D$ has a more directly Euclidean interpretation in terms of the curvature $\kappa$ of the level sets of $f$:
+$$ D = \kappa (f_i f_i)^{3/2}$$
+(This follows from the expression $\kappa = \nabla\cdot n$, where $n=\nabla f/\|\nabla f\|$ is the 
+unit normal to the level sets of $f$; see Section \ref{sec:}.)
+\item
+$D$ is directly related to the equiaffine arclength. This is $d\mu = \kappa^{1/3}ds$, where
+$\kappa$ is Euclidean curvature and $ds$ is Euclidean arclength. Therefore,
+$$ D = \kappa \|\nabla f\|^3 = \left(\frac{d\mu}{ds}\|\nabla f\|\right)^3.$$
+The normal and tangent directions to the level sets of $f$ are at right angles
+to each other. If, under an equiaffine transformation, the distance
+between level sets scales by $\lambda$, then $\nabla f$ scales by $1/\lambda$, 
+and $ds$ also scales by $1/\lambda$ as the transformation is area preserving.
+Thus the right hand side of () is equiaffine invariant.
+\item We shall show in Section \ref{sec:proj} that $D$ is also relative invariant of the projective group.
+\item The 2nd order invariants () imply that any equiaffine-invariant 2nd order PDE can be written in the form
+$\mathcal{F}(f, C, D)=0$.
+The special case of equations of the form $\mathcal{F}(f,C)=0$, namely Monge--Amp\`ere equations, is well known.
+Naturally occurring examples of $\mathcal{F}(f,C,D)=0$ would be of great interest.
+\item $D$ is an $SA(2)$-invariant Lagrangian density for $C$:
+$$ \delta\int \left(f_{22}f_1^2 + f_{11}f_2^2 - 2 f_{122} f_1 f_2\right) \, dx\, dy = - 6\det f_{ij}.$$
+\end{enumerate}
+
+For derivatives up to 3rd order, we need the invariants of $V_1\oplus V_2\oplus V_3$, which are
+given by those given above together with new ones containing 3rd derivatives. As there are 4 independent
+entries in $f'''$, and the group parameters have already all been taken out, there should be at least 4 new invariants.
+It turns out that to generate all the polynomial invariants requires not 4 but 13 new polynomial invariants.
+Of these, 2, 4, 4, 2, and 1 have degree 3, 4, 5, 6, and 7 respectively \cite{draisma}.
+A set of generating invariants for $V_1\oplus V_2\oplus V_3$ is given in Table \ref{tab:sl2},
+where  $c$ is the cubic form $f_{ijk}x_i x_j x_k$.
+
+To summarize, for 1-colour images, the 3-dimensional signature $(f,C,D)$ requires 2 derivatives;
+a 4-dimensional signature requires 3 derivatives. Such a signature is given by 
+$(f,C,D)$ together with one of the invariants containing $c$ in Table \ref{tab:sl2}, 
+such as $I_6$ (which is linear in $f'''$) or $I_3$ (which does not contain $\ell$, so it
+does not vanish at critical points.)
+
+\begin{table}
+\label{tab:sl2}
+\begin{center}
+\begin{tabular}{| l | l | l | l |}
+\hline
+name & deg & weight & invariant \\
+\hline
+$I_1$ & 2 & 4 & $(q,q)_2$\\
+& & & $\quad \propto C := \det f_{ij}$ \\
+$I_2$ & 3 & 4 & $(q,\ell^2)_2$\\
+& & & $\quad  \propto D := f_{11}f_2^2 + f_{22} f_1^2 - 2 f_{12} f_1 f_2$ \\
+$I_3$ & 3 & 8 & $(q,(c,c)_2)_2$\\
+& & & $\quad  \propto  f_{22} f_{112}^2 + f_{11} f_{122}^2 + f_{12} f_{111}f_{222} $ \\
+& & & $\qquad- f_{22}f_{111}f_{122}
+- f_{12} f_{112}f_{122} -f_{11} f_{112} f_{222}$\\
+$I_4$ & 3 & 6 & $(c,q\ell)_3$\\
+& & & $\quad   \propto f_2 f_{22} f_{111} - 2 f_2 f_{122} f_{112} - f_1 f_{22} f_{112} $\\
+& & & $\qquad + f_2 f_{11} f_{122}
++ 2 f_1 f_{122} f_{122} - f_1 f_{11} f_{222}$\\
+$I_5$ & 4 & 12 & $((c,c)_2,(c,c)_2)_2$ \\
+$I_{6}$ & 4& 6 &  $(c,\ell^3)_3$\\
+& & & $\quad \propto E := f_{111} f_2^3 - 3 f_{112}f_1 f_2^2  + 3f_{122} f_1^2 f_2  - f_{222}f_1^3 $\\
+$I_{7}$ &4 & 8 &  $((c,c)_2,\ell^2)_2$\\
+$I_{8}$ & 4& 8 &  $(c \ell,q^2)_4$\\
+$I_{9}$ & 5& 12 &  $(c^2,q^3)_6$\\
+$I_{10}$ &5 &8  &  $(((c,\ell)_1,q)_1,\ell^2)_2$\\
+$I_{11}$ &5 &12 &  $(q,(((c,c)_2,c)_1,\ell)_1)_2$\\
+$I_{12}$ &5 & 10 &  $(((c,c)_2,q)_1,\ell^2)_2$\\
+$I_{13}$ & 6& 12&  $(\ell c,(\ell c,\ell c)_2)_4$\\
+$I_{14}$ & 6& 14&  $(((c,c)_2,q)_1,(q \ell,c)_2)_2$\\
+$I_{15}$ & 7& 18 &  $(q^3,c((c,c)_2,c)_1)_6$\\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
+For more colours,  we are seeking invariants of $k V_1 \oplus k V_2 \oplus \dots$. One can take transvectants of any components of $f$ to get invariants.
+
+For $k=2$ colours, there is only one  invariant formed from 1st derivatives, namely $((f^1)',(f^2)')_1 = f^1_1 f^2_2 - f^1_2 f^2_1$ (the Poisson bracket $\{f^1,f^2\}$).
+So again two derivatives are necessary, even for
+a 3-dimensional signature.
+
+ For $k\ge 3$ colours, a new phenomenon enters.  There are plenty of invariants
+formed from 1st derivatives, namely $\nabla f^i \times \nabla f^j$ for $i<j$.
+But these are all invariant under the bigger group $\mathrm{Diff}_{\mathrm{vol}}$ of local volume preserving diffeomorphisms.
+So the Poisson brackets
+cannot form a complete invariant for $SA(2)$. Two derivatives are always needed no matter how many
+colours we have. The relation $SA(2)\subset \mathrm{Diff}_{\mathrm{vol}}$ acts an obstruction
+to $SA(2)$, an instance of the phenomenon of hidden symmetry.
 
@@
 
+The affine group of transformations  $\mathbf{x}\mapsto A\mathbf{x}+\mathbf{b}$, $\det A\ne 0$,
+is common in image processing. It is the product of $SA(2)$ with the positive scalings, thus
+we can use the same method as for $Sim(2)$ to construct invariants. Each $SA(2)$ invariant
+becomes a relative invariant of $A(2)$ of a certain weight, given in Table \ref{tab:sl2}.
+ As $C$ and $D$ have weight 4 and
+$E$ has weight 6, a simple 3-dimensional signature set is formed from $f$ together with
+the weight-12 relative invariant
+$$(C^3,D^3,E^2)$$
+projected to $S^2$. This signature is continuous except at points where $C=D=E=0$, which 
+is a codimension 1 phenomenon for images; the bad points include $f_1=f_2=\det f_{ij}=0$.
+
+As for $Sim(2)$, signature sets which are continuous on sets of higher codimension can be
+formed by including more (relative) invariants.
+
+First consider including {\em all 15} invariants of Table \ref{tab:sl2}. They define
+a map $I\colon \mathbb{R}^9\to \mathbb{R}^{15}$ where 
+$(f_i,f_{ij},f_{ijk})$ are the 9 coordinates on the domain. As $\dim SL(2,\mathbb{R})=3$, 
+the rank of this map is at most 6. Indeed, the rank is 6 at generic points, and
+most level sets of $I$ are 3-dimensional.
+However, $I^{-1}(0)$ is not 3-, but 5-dimensional. 
+Despite the high degree of the equations $I=0$ (the product of the individual
+degrees, more than 2 billion), the equations can be reduced to a single quadratic.
+One component of $I^{-1}(0)$ can be written
+$$ \begin{pmatrix}f_1 \\f_2 \\f_{11} \\f_{12} \\f_{22} \\f_{111} \\f_{112} \\f_{122} \\f_{222}\end{pmatrix}=
+\alpha_3^{-2}\begin{pmatrix}\alpha_1\alpha_3\\
+ \alpha_1\alpha_3(\alpha_2-\beta)\\ 
+ \alpha_3\alpha_4\\
+\alpha_3\alpha_4(\alpha_2-\beta)\\
+\alpha_4(2\alpha_2^2-2\alpha_2\beta - \alpha_3\alpha_5)\\
+\alpha_3\\
+\alpha_2\\
+\alpha_5\\
+2\beta^3 + \alpha_2(3\alpha_3\alpha_5 - 2\alpha_2^2)
+\end{pmatrix}$$
+where $\beta=\sqrt{\alpha_2^2-\alpha_3\alpha_5}$ and
+$\alpha_1,\dots,\alpha_5$ are parameters.
+That is, the level set $I^{-1}(0)$ contains a union of several orbits of $SA(2)$ and these
+cannot be distinguished using the entire set of relative invariants.
+
+Likewise, we can consider the reduced set $\widetilde I := (I_1,I_2,I_3,I_4)$. 
+We find that the highest dimensional component of $\widetilde{I}^{-1}(0)$ 
+again has dimension 5. (It includes, but is not idential to, $I^{-1}(0)$.) 
+So the 4-dimensional signature formed from $f$ and $\widetilde I$
+is continuous except on a set of images of codimension $5-2=3$, the same 
+as  the 15-dimensional signature formed from $f$ and $I$. 
+Many other reduced sets (maps from $\widetilde{I}$ to $\R^4$ have the same property
+and can be used instead.
+
+The root cause of the obstruction to finding a signature that is continuous on a set of images
+of codimension greater than 3 is that rational invariants are only guaranteed
+to separate generic orbits, not all orbits. Characterizing the orbits
+that can be separated by rational invariants a question that
+has to be tackled separately in each case.
+
+Thus for 1-colour images, an affine signature set or 3 or 4 dimensions requires three derivatives.
+
+With $k\ge 2$ colours, there are plenty of available invariants formed from  two derivatives, already 9 when $k=2$. 
+However, as with $SA(2)$, we can never get away with one derivative because all the 1-derivative invariants,
+such as $\{f^1,f^2\}/\{f^1,f^3\}$ 
+are also invariant
+under $\mathrm{Diff}_{\mathrm{vol}}$ (even though $A(2)$ is not even a subgroup of $\mathrm{Diff}_{\mathrm{vo}l}$).
+
 \subsection{M\"obius and Projective (finite dimensional)}
@@
 \end{theorem}
+
+The M\"obius group $\mathrm{PSL}(2,\mathbb{C})$ acts on the Riemann sphere
+$\overline{\mathbb{C}} = \mathbb{C}\cup\infty$ by 
+$$ \phi\colon \overline{\mathbb{C}} \to \overline{\mathbb{C}},\quad \phi(z) = \frac{\alpha z + \beta}{\gamma z + \delta},\quad \alpha,\beta,\gamma,\delta\in\mathbb{C}, \quad
+\alpha\delta-\beta\gamma\ne 0.$$
+Identifying $\R^2$ with $\mathbb{C}$, the M\"obius group is a real 6-dimensional local Lie group acting on $\mathbb{R}^2$.
+It is the smallest nonlinear planar group that contains $SE(2)$, and it is the set of biholomorphic maps of the Riemann sphere; it also has direct applications in image processing since it arises in the {\em conformal camera} model of vision, in which scenes are projected radially onto a sphere \cite{lenz1990group,turski2004geometric,turski2005geometric}.
+Different shapes may be related by M\"obius transformations, as is explored by
+Petukhov \cite{petukhov1989non} for biological objects: in one example, the human skull grows approximately by M\"obius transformations.
+Note also that Thompson \cite{thompson1942growth} famously deformed images of one species to match those of another, many of his examples using conformal mappings, and thus may be approximated (or even determined by) M\"obius transformations.
+Discussing this work, Milnor \cite{milnor2010growth}  argued that ``The geometrically simplest way to change the relative size of different body parts would be by a conformal transformation.
+It seems plausible that this simplest solution will often be the most efficient, so that natural selection tend to choose it.'' (Milnor was thinking of 3D conformal transformations, whose restriction to 2D is the M\"obius transformations.)
+
+The M\"obius action is locally identical to the full conformal group up to and including second order.
+Therefore, there are no new M\"obius invariants, apart from the conformal invariants, up to second order.
+At third order, there are no new group parameters
+to be eliminated; we therefore expect four independent invariants, of which two are the conformal invariants found in the previous section.
+We find the two remaining independent invariants using the moving frame method.
+
+The 0th order moving frame translates $z$ to
+$\beta$. We can therefore take $\beta=0$; we are also free to take $\delta=1$. This leaves 4 group parameters $a,b,c,d$, where $\alpha = a + i b$, $\gamma = c + i d$,
+to be determined as follows. First we prolong the action to 3rd derivatives of $f$. There are 9 derivatives of
+$f$ of order 1, 2, and 3, so there must be at least 5 invariants.
+
+The prolonged action is
+\begin{equation}
+\small
+\arraycolsep=1.4pt
+\left(
+\begin{array}{c}
+  \bar f_1 \\ \bar f_2 \\ \bar f_{11} \\ \bar f_{122} \\ \bar f_{22} \\ \bar f_{111} \\ \bar f_{112} \\ \bar f_{122} \\ \bar f_{222} 
+ \end{array}
+ \right)
+ = 
+\left(
+\begin{array}{ccccccccc}
+ a & b & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ -b & a & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ 2\mu & -2 \rho & a^2 & 2 a b & b^2 & 0 & 0 & 0 & 0 \\
+ 2 \rho & 2\mu & -a b & a^2\!-b^2 & a b & 0 & 0 & 0 & 0 \\
+ -2\mu & 2 \rho & b^2 & -2 a b & a^2 & 0 & 0 & 0 & 0 \\
+ -6 (2 b c d+a \lambda) & 6 (2 a c d-b\lambda) & 6 a \mu &
+  M_{64}  & -6 b \rho & a^3 & 3 a^2 b & 3 a b^2 & b^3 \\
+ -6 (2 a c d-b\lambda) & -6 (2 b c d+a \lambda) & M_{73}& M_{74} & 
+ M_{75} & -a^2 b & a^3\!-2 a b^2 & 2
+   a^2 b\!-b^3 & a b^2 \\
+ 6 (2 b c d+a \lambda) & -6 (2 a c d-b\lambda) & M_{83} & M_{84} & M_{85} & a b^2 & b^3\!-2
+   a^2 b & a^3\!-2 a b^2 & a^2 b \\
+ 6 (2 a c d-b\lambda) & 6 (2 b c d+a \lambda) & 6 b \mu & 
+  M_{94} & 6 a \rho & -b^3 & 3 a b^2 & -3 a^2 b & a^3 \\
+\end{array}
+\right)\left(
+\begin{array}{c}
+f_1 \\ f_2 \\ f_{11} \\ f_{122} \\ f_{22} \\ f_{111} \\ f_{112} \\ f_{122} \\ f_{222} 
+ \end{array}
+ \right).
+ \end{equation}
+ where
+ \begin{equation*}
+ \small
+ \begin{array}{lll}
+M_{64}=-12abc+6d(a^2-b^2), & 
+M_{73}=4 d a^2+6 b c a-2 b^2 d, & 
+M_{74}=-6 c a^2+12 b d a+6 b^2 c, \\
+ M_{75}=-2 d a^2-6 b c a+4 b^2 d, &
+ M_{83}=2 c a^2-6 b d a-4 b^2 c, &
+ M_{84}=6 (d a^2+2 b c a-b^2 d),\\
+ M_{85}=-4 c a^2+6 b d a+2 b^2 c,& 
+ M_{94}= -12a b d + 6c(a^2-b^2),\\
+\lambda=d^2-c^2, & 
+\mu = b d - a c, & 
+\rho = b c + a d.
+\end{array}
+\end{equation*}
+
+The moving frame calculation now proceeds as follows.
+\begin{enumerate}
+\item The frame $\bar f_1=1$, $\bar f_2=0$ determines the group parameters
+$$ a = f_1/(f_i f_i),\quad b = f_2/(f_i f_i).$$
+
+\item The frame $\bar f_{122}=\bar f_{22}=0$ determines the group parameters
+$$ c = (2 f_1f_2f_{122} - f_{11}f_2^2 - f_{22}f_1^2)/(2 f_i f_i)^2$$
+$$ d = (f_{122}f_1^2 - f_1 f_2 f_{11} - f_{122}f_2^2 - f_{22} f_1 f_2)/(2 f_i f_i)^2.$$
+
+\item The 2nd order invariant is then given by $\bar f_{11}$ using (); it is 
+$$\bar f_{11} = \frac{f_ii}{f_i f_i},$$
+which we have already determined as the conformal invariant $J_2/J_1$.
+
+\item The four 3rd order invariants are then given by $\bar f_{111},\dots,f_{222}$ using (). They are
+rational functions with numerators of degree 6 and denominators $(f_i f_i)^4$. We call
+the numerators $K_1,\dots, K_4$; they are relative invariants of weight 8.
+\end{enumerate}
+
+It is clear that there must be 2 syzygies between the relative invariants $J_1,\dots,J_4,K_1,\dots,K_4$.
+They are easily found algebraically to be
+$$K_2 = -K_4 + J_1 J_4$$
+and
+$$K_3=-K_1 +J_1 J_3 + 2 J_1^2 J_2^2.$$
+Therefore we can take $K_1$ and $K_4$ as two independent M\"obius invariants. They are
+$K_1=
+f_2 ^5 f_{222} + \frac{9}{2} f_2 ^2 f_{22}^2 f_1 ^2 + 
+ f_2 ^3 f_{222} f_1 ^2 + \frac{3}{2} f_{22}^2 f_1 ^4 - 
+ 9 f_2 ^3 f_{22} f_1  f_{12} + 
+ 3 f_2  f_{22} f_1 ^3 f_{12} + \frac{3}{2} f_2 ^4 f_{12}^2 - 
+ 9 f_2 ^2 f_1 ^2 f_{12}^2 + \frac{3}{2} f_1 ^4 f_{12}^2 + 
+ 3 f_2 ^4 f_1  f_{122} + 3 f_2 ^2 f_1 ^3 f_{122} + 
+ 3 f_2 ^4 f_{22} f_{11} + 3 f_{22} f_1 ^4 f_{11} + 
+ 3 f_2 ^3 f_1  f_{12} f_{11} - 
+ 9 f_2  f_1 ^3 f_{12} f_{11} + \frac{3}{2} f_2 ^4 f_{11}^2 + 
+ \frac{9}{2} f_2 ^2 f_1 ^2 f_{11}^2 + 3 f_2 ^3 f_1 ^2 f_{112} + 
+ 3 f_2  f_1 ^4 f_{112} + f_2 ^2 f_1 ^3 f_{111} + 
+ f_1 ^5 f_{111}, 
+ $
+
+ $K_4=-3 f_2  f_{22}^2 f_1 ^3 + 
+ f_2 ^2 f_{222} f_1 ^3 + f_{222} f_1 ^5 + 
+ 9 f_2 ^2 f_{22} f_1 ^2 f_{12} - 
+ 3 f_{22} f_1 ^4 f_{12} - 6 f_2 ^3 f_1  f_{12}^2 + 
+ 6 f_2  f_1 ^3 f_{12}^2 - 3 f_2 ^3 f_1 ^2 f_{122} - 
+ 3 f_2  f_1 ^4 f_{122} - 3 f_2 ^3 f_{22} f_1  f_{11} + 
+ 3 f_2  f_{22} f_1 ^3 f_{11} + 3 f_2 ^4 f_{12} f_{11} - 
+ 9 f_2 ^2 f_1 ^2 f_{12} f_{11} + 
+ 3 f_2 ^3 f_1  f_{11}^2 + 3 f_2 ^4 f_1  f_{112} + 
+ 3 f_2 ^2 f_1 ^3 f_{112} - f_2 ^5 f_{111} - 
+ f_2 ^3 f_1 ^2 f_{111}
+$
+
+In previous work \cite{mobius}, two independent 3rd order M\"obius invariants were calculated
+from the classical M\"obius geometry of curves. Namely, the M\"obius arclength 
+of a curve is $\sqrt{|\kappa_s|}ds$, were $ds$ is Euclidean arclength. Under any conformal map $\phi$,
+both $ds$ and $1/\|\nabla f\|$ scale by $|\phi'|$. The sign of $\kappa_s$ is also  invariant,
+hence $\kappa_s/\|\nabla f\|^2$ is  invariant for any invariant curve. Calculating this invariant
+for the level sets of $f$ and for their orthogonal curves yields two invariants of $f$ that
+we call $\lambda_t$ and $\lambda_n$, respectively. Writing 
+them out in full and comparing to the invariants founds above shows that they are related very simply, by
+
+$$ \frac{K_2}{\|\nabla f\|^8} = \lambda_t$$
+$$\frac{K_4}{\|\nabla f\|^8} =\lambda_n$$
+
+We do not know of any equivalent characterization of the invariants $K_1$, $K_3$ in
+terms of classical M\"obius geometry.
+
+We now have that
+$$ (J_1^4, J_2^4, J_1 J_3, J_1 J_4, K_1, K_4)$$
+are 6 relative invariants of weight 8. Projecting any subset to a sphere provides a M\"obius signature.
+For example, the image $f$ together with the projection of $(J_1^4, J_2^4, K_1)$ provides a 3-dimensional signature.
+Any such signature that includes $J_1$ and $J_2$ is singular when $f_1=f_2=f_{ii}=0$, a codimension 1
+phenomenon for images.
+
+For images with $k\ge 2$ colours, recall that M\"obius and conformal transformations cannot be distinguished
+by their action on second derivatives. Therefore at least 3 derivatives are needed, no matter how many 
+colours we have. We can use, for example, the invariants arising from the curvature of the level sets of
+each colour. Replacing the first relative invariant $\|\nabla f\|^2$ by $\sum_{j=1}^k \|\nabla f^j\|^2$,
+and the second relative invariant $f_{ii}$ by $\sum_{j=1}^k (f^j_{ii})^2$, increases
+the codimension of the singular images from 1 to $3k-2$.
+
+\section{{\bf $\mathbf{PSL}({\bf 3},\R)$}}
+
+We consider the 8-dimensional group $\mathrm{PSL}(3,\R)$ acting on $\R^2$ by projective transformations, i.e.,
+$$(x,y) \mapsto \left(\frac{a x + b y + j}{l + g x + h y}, \frac{c x + d y + k}{l+ g x + h y}\right).$$
+We will construct invariants using the moving frame method. The 0th order moving frame translates $(x,y)$ to
+$(0,0)$. We can therefore take $j=k=0$; we will also take $l=1$. This leaves 6 group parameters $(a,b,c,d,g,h)$
+to be determined as follows. First we prolong the action to 3rd derivatives of $f$. There are 9 derivatives of
+$f$ of order 1, 2, and 3, so there must be at least 3 invariants.
+
+The prolonged action is
+\begin{equation}
+\tiny
+\arraycolsep=1.4pt
+\label{eq:prolong}
+\left(
+\begin{array}{c}
+  \bar f_1 \\ \bar f_2 \\ \bar f_{11} \\ \bar f_{122} \\ \bar f_{22} \\ \bar f_{111} \\ \bar f_{112} \\ \bar f_{122} \\ \bar f_{222} 
+ \end{array}
+ \right)
+ = 
+\left(
+\begin{array}{ccccccccc}
+ a & c & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ b & d & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ -2 a g & -2 c g & a^2 & 2 a c & c^2 & 0 & 0 & 0 & 0 \\
+ -b g-a h & -d g-c h & a b & b c+a d & c d & 0 & 0 & 0 & 0 \\
+ -2 b h & -2 d h & b^2 & 2 b d & d^2 & 0 & 0 & 0 & 0 \\
+ 6 a g^2 & 6 c g^2 & -6 a^2 g & -12 a c g & -6 c^2 g & a^3 & 3 a^2 c & 3 a c^2 & c^3 \\
+ 2 g (b g+2 a h) & 2 g (d g+2 c h) & -2 a (2 b g+a h) & -4 (b c g+a d g+a c h) & -2 c (2 d
+   g+c h) & a^2 b & a (2 b c+a d) & c (b c+2 a d) & c^2 d \\
+ 2 h (2 b g+a h) & 2 h (2 d g+c h) & -2 b (b g+2 a h) & -4 (b d g+b c h+a d h) & -2 d (d g+2
+   c h) & a b^2 & b (b c+2 a d) & d (2 b c+a d) & c d^2 \\
+ 6 b h^2 & 6 d h^2 & -6 b^2 h & -12 b d h & -6 d^2 h & b^3 & 3 b^2 d & 3 b d^2 & d^3 \\
+\end{array}
+\right)\left(
+\begin{array}{c}
+f_1 \\ f_2 \\ f_{11} \\ f_{122} \\ f_{22} \\ f_{111} \\ f_{112} \\ f_{122} \\ f_{222} 
+ \end{array}
+ \right).
+ \end{equation}
+
+First, recall from the analysis of the subgroup $A(2)$ that under $f\mapsto f\circ \phi$, $\phi\in A(2)$, we have 
+\begin{equation}
+\label{eq:D}
+D \mapsto (\det \phi')^2 D\circ \phi
+\end{equation}
+where $D = f_{1}^2 f_{22} + f_2^2 f_{11} - 2 f_1 f_2 f_{122}$. 
+A direct calculation using (\ref{eq:prolong}) shows that the same transformation rule (\ref{eq:D}) holds for $\phi\in\mathrm{PSL}(3,\R)$.
+That is, $D$ is a relative invariant of weight 2 of this action. From (\ref{eq:D}), the sign of $D$ is invariant and therefore
+the choice of moving frame must depend on the sign of $D$.
+
+\begin{enumerate}
+\item The frame $\bar f_1 = 1$  determines the group parameter $$a = (1-c f_2)/f_1.$$
+\item The frame $\bar f_2=  0$ determines the group parameter $$b = -d f_2/f_1.$$
+\item Substituting this choice of $a$ and $b$ and examining the dependencies of $f_{11}$, $f_{122}$, $f_{22}$, and $f_{222}$ on the remaining group parameters allows them to be solved sequentially, as follows.
+\item We have $\bar f_{22} = d^2 D/f_1^2$; therefore if $D>0$ we choose the frame
+$\bar f_{22} = 1$ and $$d = f_1/D^{1/2}.$$
+\item The frame $\bar f_{222} = 0$ determines the group parameter
+$$ h = \frac{d(f_{222}f_1^3 - 3 f_1^2 f_2 f_{122} + 3 f_1 f_2^2 f_{112} - f_2^3 f_{111})}{6 f_1 D}.$$
+\item The frame $\bar f_{122}=0$ determines the group parameter
+$$ c = \frac{h f_1^2}{d D} - \frac{f_1 f_{12} - f_2 f_{11}}{D}.$$
+\item The frame $\bar f_{11}=0$ determines the group parameter
+$$ g = \frac{1}{2 f_1^2}(f_{11} + 2 c ( f_1 f_{12} - f_2 f_{11} ) + c^2 D).$$
+\end{enumerate}
+
+Having determined the frame, any function of the remaining derivatives $\bar f_{111}$, $\bar f_{112}$, and $\bar f_{222}$,
+as given in (\ref{eq:prolong}),
+provides invariants. We choose
+$$ (f_{111}, f_{112}^2, f_{122})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right)$$
+because these all have denominators given by integer powers  of $D$, resolving the issue caused
+by the sign of $D$. Therefore,
+$$ (D^{18}, J_1^3, J_2^2, J_3^6)$$
+are all relative invariants of weight 36; so projecting any subset of them of them to a sphere
+yields a 3rd order invariant signature.
+
+However, these signatures can be simplified and made more robust, as follows.
+
+The components of $J$ are polynomials of degree 16, 24, and 8, respectively, and are extremely complicated when written out explicitly.
+More seriously, $J$ vanishes on generic images.
+This can be seen as follows.
+Recall the $SA(2)$ invariant $E$ defined in (\ref{eq:E}).
+%Let
+%$$ E := f_{222}f_1^3 - 3 f_{122}f_1 f_2^2 + 3 f_{112}f_1^2 f_2 - f_{111}f_2^3$$
+Then the components of $J$ have the structure
+$$ J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5$$
+where the $P_n$ are polynomials of degree $n$. Therefore $J=0$ when $D=E=0$, which 
+is a codimension 0 phenomenon for images. In particular, $D=E=0$ at critical points.
+
+The structure of () suggests considering the combination $J_1 - J_3^2$ which turns out to obey
+$$J_1 - J_3^2 = 144 D^4 P_4.$$
+Therefore, as $J_1/D^6$ and $J_3/D^3$ are invariant, so is $P_4/D^2$. 
+Moreover, {\em the numerator of this new invariant does not vanish at critical points.} 
+It has the structure
+$$P_4 = -4(\det f_{ij})^2 + Q_4,$$
+where $Q_4$ is a polynomial of degree 4 that vanishes when $f_1=f_2=0$. In conclusion, the
+relative invariant of weight 12
+$$ (D^6, P_4^3, (E^2-12D P_5)^2)$$
+can be projected to $S^2$ yielding a projective invariant of images that
+is singular only when $D=E=P_4=0$, which is a codimension 1 phenomenon for images.
+(One can check that $D=E=0\nRightarrow P_4=0$.) In particular, at critical points it tends to
+$$ (0, (2\det f_{ij})^6, 0)$$
+and hence critical points with $\det f_{ij}\ne 0$ have signature $(0,1,0)$.
+
+For completeness we write out the invariants explicitly:
+
+$Q_4=4 f_1  f_{12} ^2 f_{122}  - 
+f_1 ^2 f_{122} ^2 - 
+ 2 f_{222}  f_1  f_{12}  f_{11}  + 
+ 2 f_{22}  f_1  f_{122}  f_{11}  - 
+ 6 f_{2}  f_{12}  f_{122}  f_{11}  + 
+ 2 f_{2}  f_{222}  f_{11} ^2 + 
+ f_{222}  f_1 ^2 f_{112}  - 
+ 6 f_{22}  f_1  f_{12}  f_{112}  + 
+ 4 f_{2}  f_{12} ^2 f_{112}  + 
+ f_{2}  f_1  f_{122}  f_{112}  + 
+ 2 f_{2}  f_{22}  f_{11}  f_{112}  - 
+ f_{2} ^2 f_{112} ^2 + 
+ 2 f_{22} ^2 f_1  f_{111}  - 
+ f_{2}  f_{222}  f_1  f_{111}  - 
+ 2 f_{2}  f_{22}  f_{12}  f_{111}  + f_{2} ^2 f_{122}  f_{111} $
+
+$P_5=f_{222}  f_{1} ^3 f_{12}  - 
+f_{22}  f_{1} ^2 f_{12} ^2 + 
+ 2 f_{2}  f_{1}  f_{12} ^3 - 
+ f_{22}  f_{1} ^3 f_{122}  - 
+ f_{2}  f_{1} ^2 f_{12}  f_{122}  + 
+ f_{22} ^2 f_{1} ^2 f_{11}  - 
+ f_{2}  f_{222}  f_{1} ^2 f_{11}  - 
+ 2 f_{2}  f_{22}  f_{1}  f_{12}  f_{11}  - 
+ f_{2} ^2 f_{12} ^2 f_{11}  + 
+ 2 f_{2} ^2 f_{1}  f_{122}  f_{11}  + 
+ f_{2} ^2 f_{22}  f_{11} ^2 + 
+ 2 f_{2}  f_{22}  f_{1} ^2 f_{112}  - 
+ f_{2} ^2 f_{1}  f_{12}  f_{112}  - 
+ f_{2} ^3 f_{11}  f_{112}  - 
+ f_{2} ^2 f_{22}  f_{1}  f_{111}  + 
+ f_{2} ^3 f_{12}  f_{111} $
+
+ Including $J_2$ in addition provides a 4-dimensional signature set, but does not increase
+ the codimension of the set of bad images.
+
+Further invariants can be found by noting that, for any planar transformation group and any two invariants
+$I^1$ and $I^2$, $\nabla I^1 \times \nabla I^2$ is a relative invariant of weight 1; that is,
+$$\nabla I^1 \times \nabla I^2\mapsto (\det \phi')(\nabla I^1 \times \nabla I^2).$$
+Applying this operation to $f$ and the 4 3rd order invariants yields $5\cdot4/2=1$0  4th order invariants.
+
+{\color{red}Following needs work:}
+
+For $2$-colour images, there are 3  second order relative invariants of weight 2,
+namely $(D_1,D_2,(\nabla f^1\times \nabla f^2)^2)$. Together with $(f^1,f^2)$, these yield
+a 4-dimensional $\mathbb{R}^2\times S^2$-valued signature using only 2nd derivatives.
+With $k>2$ colours there are many more 2nd order invariants; however, as the action
+of the projective group on 1st derivatives is indistinguishable from that of the full
+diffeomorphism group, it is not possible to have a 1st order signature that distinguishes
+projectively-related images from diffeomorphically-related ones.
+
 \begin{theorem}
@@
 \subsection{Infinite dimensional diff groups (diff con, diff vol, diff)}
+
+The conformal
+group is infinite-dimensional, but still small enough that images have local differential invariants.
+
+We first compute the invariants of the conformal group up to 3rd order. Instead of applying the method
+of moving frames, we perform a direct calculation using the defining geometric properties of the conformal
+group.
+
+The conformal transformations are defined to be those that preserve angles. At first order, the only
+available data are $(f,f_i)$, which do not create any angles. There are no first order invariants.
+
+At second order, we first consider the action of conformal maps on the Euclidean invariants
+$f_i f_i$ and $f_{ii}$.
+
+Let $\psi := \varphi^{-1}$. For any diffeomorphism, the derivatives of $f$ transform as
+$$f_i \mapsto f_j \psi^j_i$$
+and
+$$f_{ij} \mapsto f_{kl} \psi^k_i\psi^l_j + f_{k}\psi^k_{ij}.$$
+Therefore the Laplacian of $f$ transforms as
+$$ f_{ii} \mapsto f_{kl} \psi^k_i \psi^l_i + f_k \psi^k_{ii}.$$
+When $\psi=u + i v$ is conformal, $\psi_{k,ii}=0$ because the components of conformal maps are harmonic functions,
+and the Cauchy-Riemann equations give $\psi_{k,i}\psi_{l,i} = (u_x^2 + u_y^2)\delta_{kl}$. Therefore,
+$$ f_{ii} \mapsto f_{ii}(u_x^2+u_y^2).$$
+Here $u_x^2+u_y^2=\det\psi^k_i$ is the local scaling factor of the transformation.
+Note also that
+$$f_i f_i \mapsto f_k f_l \psi_{k,i} \psi_{l,i} = f_k f_k (u_x^2 + u_y^2).$$
+That is, $f_{ii}$ and $f_i f_i$ are both relative invariants of weight 2.
+
+Therefore, $f_{ii}/(f_i f_i)$ is a conformal invariant. By itself, it is not useful for images as it is singular at critical points of $f$.
+
+At higher order,  representing $\psi(z) = a_0 + a_1 z + a_2 z^2 + \dots$ where $z=x+iy$ and $a_i\in \mathbb{C}$ shows that
+2 real group parameters, $Re(a_n)$ and $Im(a_n)$, enter at order $n$. There are $n+1$ independent derivatives of $f$ of order $n$, 
+so there must be at least $n-1$ independent invariants of order $n$. For $n=2$, we have we have found the single invariant above.
+
+The transformation of 1st derivatives is more clearly written in complex variables as
+$$ f_x + i f_y \mapsto a_1 (f_x + i f_y).$$
+Given any two real invariants $g,h$, the real and imaginary parts of $(g_x+i g_y)(h_x-i h_y)$ are
+relative invariants of weight 2. This generates the required two invariants of order 3. (We have
+repeated and confirmed this calculation using the method of moving frames.)
+Specifically, let $J_1 = f_i f_i$ and  $J_2 = f_{ii}$, so that  $g = J_2/J_1$ is invariant.
+We want to work with polynomials, so we clear denominators and
+let $J_3+iJ_4 = J_1^2 (g_x + i g_y)  (f_x - i f_y)$. $J_3$ and $J_4$ are a differential polynomials of $f$
+of degree 4 and order 3, and are relative invariants of weight 6. They can be written explicitly as functions
+of the basic invariants of $SE(2)$ as
+$$J_3 = f_k f_k f_{iij}f_j - 2 f_{ii} f_{jk} f_j f_k$$
+and (writing $a_i\times b_i$ for $a_1 b_2 - b_2 a_1$)
+$$ J_4 = f_k f_k f_{iij}\times f_j - 2 f_{ii} f_{jk} f_k\times f_j.$$
+Under conformal maps we have
+$$ (J_1,J_2,J_3,J_4) \mapsto (|a_1|^2 J_1, |a_1|^2 J_2, |a_1|^6 J_3,|a_1|^6 J_4).$$
+
+Therefore, projecting $(J_1^3,J_2^3,J_3)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^2$. It is continuous at all $(x,y)$ such that
+$J_1$, $J_2$, and $J_3$ are not simultaneously equal to zero. 
+Now $J_1=0$ implies $f_1=f_2=0$, and $J_2=0$ implies $f_{ii}=0$, but these together
+imply $J_3=0$. Thus the signature set is discontinuous when 
+ $f_1=f_2=f_{ii}=0$, a codimension-1 phenomenon for images.
+
+Similarly,
+projecting $(J_1^3,J_2^3,J_3,J_4)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^3$. This is also singular when $f_1=f_2=f_{ii}=0$.
+
+Are these singularities removable? A typical image near a `bad' point takes
+the form $f = a(x^2-y^2) + b x y + c x^3 + d x^2 y + e x y^2 + g y^3$.
+For such an $f$, $(J_1^3,J_2^3,J_3,J_4)=\mathcal{O}(x^6,x^3,x^3,x^3)$.
+The cubic forms always change sign and do not generically lead to a well-defined direction
+as $(x,y)\to(0,0)$. Thus the singularities are not removable.
+
+{\color{red} So far I can't find a signature of codimension $>1$. The reason is that
+all relative invariants appear to vanish when $f_1=f_2=0$. Is there a geometric reason for this?
+It doesn't happen with $Sim(2)$ or $A(2)$. I checked invariants up to 4th order using moving frame, also the ones
+calculated by differentiation above. It seems that $f_1=f_2=0$ is special in some way. But note that
+on $f_1=f_2=0$, new invariants appear, such as $\det f_{ij}/(f_{ii}^2)$ (related to the ratio of eigenvalues
+of $f_{ij}$). These orbits can't be distinguished by globally defined functions. Another way to see this is to compute
+\begin{equation}
+\begin{aligned}
+f_i f_i & \mapsto |a_1|^2 f_i f_i \\
+f_{ii} & \mapsto |a_1|^2 f_{ii}\\
+\det f_{ij} & \mapsto |a_1|^4 \det f_{ij} - 4 |a_2|^2 f_i f_i\\
+\end{aligned}
+\end{equation}
+which shows how the new invariant appears on $f_if_i=0$ only, due to the lower-dimensional orbits.
+But the projective case, in which taking combinations of invariants changed things, is cautionary.
+}
+
+For $k\ge 2$ colours, first order signature sets are possible. They are formed from 
+the relative invariants $(f^j_1 + i f^j_2)(f^m_1 - i f^m_2)$ of weight 2. We illustrate this
+using the Hopf fibration for $k=2$. The weight 2 relative invariant
+$$J = (2(f^1_1 + i f^1_2)(f^2_1 - i f^2_2), ||\nabla f^1\|^2 - \|\nabla f^2\|^2)$$
+obeys $\|J\|^2 = \|\nabla f^1\|^2 + \|\nabla f^2\|^2$, hence projecting to the unit sphere
+shows that $(f^1,f^2,J/\|J\|)$ provides a 4-dimensional signature set that is singular
+only when $\nabla f^1 = \nabla f^2 = 0$, a codimension 2 phenomenon for images.
+
+\section{{\bf $\mathbf{Diff_{vol}}$}}
+
+Area preserving maps are defined by one function of two variables, the generating function $S$; one
+possibility is $S(x,y')$ where $(x,y)\mapsto(x',y')$ according to
+$$ x'=\frac{\partial S}{\partial y'},\quad y = \frac{\partial S}{\partial x}.$$
+Consider expanding $S$ in Taylor series. The linear terms in the map
+are determined from the quadratic terms in $S$, which contain 3 group parameters, and 
+act on 2 coordinates, $f_1$ and $f_2$. 
+The quadratic terms in the map are determined from the cubic terms in $S$, which contain 4 group parameters,
+and act on 3 coordinates, $f_{11}$, $f_{12}$, and $f_{22}$. At order $n$ we have
+$n+2$ new group parameters acting on $n+1$ coordinates. Thus, barring some exceptional behaviour
+in the action, we do not expect any invariants at generic points.
+
+This can be confirmed by considering a small image patch with $f(x,y)=x.$ Let $v=\psi_y\partial/\partial_x
+- \psi_x\partial/\partial_y$ be the generator of an area-preserving map. The image
+$f$ transforms to $x + \varepsilon \psi_y(x,y)$ which (by choosing $\psi$ appropriately) can
+be any function close to $x$.
+
+At nongeneric points, there can be invariants. For example, the area enclosed in any level
+set of $f$ is invariant. At minima or maxima of $f$, this will lead to invariants expressed in terms of the derivatives of $f$.
+
+When $k\ge 2$ there are $k(k-1)/2$ first-order invariants $ \nabla f^i \times \nabla f^j$. 
+We consider the case $k=2$ and the 3-dimensional signature
+$$ (f^1,f^2, \nabla f^1 \times \nabla f^2).$$
+This signature determines (generically and locally) the image up to an area-preserving map.
+For, we have seen that we can generically choose the area-preserving map so that $f^1=x$, and
+we assume that this has been done. The remaining freedom is that of the area-preserving
+maps that preserve $x$: these are the shears $y\mapsto y + g(x)$. The signature for each fixed $x$ now gives $(f^2,f^2_2)$. This is the standard signature curve for the group of translations in $y$.
+Thus, $f^2$ is determined by the signature up to a translation in $y$, i.e., an area-preserving map.
+
+\section{{\bf $\mathbf{Diff}$}}
+
+With 1 or 2 colours there are no differential invariants. With $k=2$, for example, for generic $f^1$, $f^2$ we
+can choose a diffeomorphism (i.e., choose local coordinates) so that $f^1=x$ and $f^2=y$.
+We therefore take $k\ge 3$. This provides the first order relative invariants of weight 1 $\nabla f^i\times \nabla f^j$,
+and hence a first order signature. However, a 0th order signature set is possible: $(f^1,\dots,f^k)$. This is
+the image of the image. It is (locally and generically) complete. For, we can choose
+coordinates so that $f^1=x$ and $f^2=y$; then the signature locally determines $f^3,\dots,f^k$ as
+functions of $f^1$ and $f^2$, i.e., the image.
 
@@
 
+\begin{thebibliography}{99}
+\bibitem{bessel} A. Bessel, Ueber die Invarianten der einfachsten Systeme simultaner bin\"arer Formen, Math. Ann. 1 (1869) 173--194.
+\bibitem{draisma} M. I. P. Draisma, {\em Invariants of binary forms}, PhD thesis, Basel, 2014.
+\end{thebibliography}
 \end{document}

### 2018-05-17 paper/figpaper.tex
new paper for figures

\documentclass[11pt]{article}
\usepackage{amsmath}

\begin{document}
In order to compare the invariants visually, we use the following
polynomial in two variables:
\begin{equation}
  \begin{split}
    f(x, y) &= 0.5 - 0.2x - 0.3y - 0.05x^2 + 0.03xy + 0.04y^2 \\ 
    &+ 0.03y^3 + 0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3.
  \end{split}
\end{equation}
The function was chosen to have no critical points, and to be predominantly
linear, so that the higher order derivatives were not too large.

\begin{figure}

\end{figure}

\end{document}

### 2018-05-17 code/Signature.m
Tweaking figure plotting

@@ -89,6 +89,10 @@ classdef Signature < handle
             imagesc(x, y, obj.fn_numeric(X, Y), params.clim);
             axis image
             colormap(params.cmap);
+            set(gca, 'fontsize', 16, 'TickLabelInterpreter', 'latex')
+            colorbar('TickLabelInterpreter', 'latex')
+            xlabel('$x$', 'interpreter', 'latex')
+            ylabel('$y$', 'interpreter', 'latex')
             if params.showscanlines
                 hold on
                 xscan = linspace(params.xlim(1), params.xlim(2), params.nlines);
@@ -108,6 +112,7 @@ classdef Signature < handle
                         t*params.ylim(1) + (1 - t)*params.ylim(2);
                 end 
                 plot(Xscan, Yscan, params.scanparams{:})
+             
             end
         end
         

### 2018-05-17 code/make_figures.m

@@ -13,7 +13,6 @@ write_images = false;
 f(x, y) = 0.5 - 0.2*x - 0.3*y - 0.05*x.^2 + 0.03*x.*y + 0.04*y.^2 + ...
     0.03*y.^3 +0.001*x.^3 - 0.0015*x.^2.*y + 0.002*x.*y.^2 - 0.0005*y.^3;
 
-
 %% Write signature picture
 groups = {'E2', 'SE2', 'A2', 'Mobius', 'PSL3R', 'SA2', 'Sim2'};
 for i = 1:numel(groups)

### 2018-05-17 code/Signature.m
Update plotting code

@@ -8,16 +8,25 @@ classdef Signature < handle
         derivatives
         derivatives_matlab
         camera_info
+        tform
     end
     methods
         function obj = Signature(fn, sig_fn, order, group, varargin)
+            params = parseinputs(varargin{:});
             syms x y
             assert(isa(fn, 'sym') || isa(fn, 'symfun'));
             obj.derivative_order = order;
             obj.signature_fn = sig_fn;
-            obj.fn = fn;
-            obj.fn_numeric = matlabFunction(fn, 'Vars', [x y]);
-            obj.derivatives = compute_derivatives(fn, order);  
+            if ~isempty(params.tform)
+                obj.tform = params.tform;
+                [xp, yp] = obj.tform.reverse(x, y);
+                obj.fn = fn(xp, yp);
+            else
+                obj.fn = fn;
+                obj.tform = [];
+            end
+            obj.fn_numeric = matlabFunction(obj.fn, 'Vars', [x y]);
+            obj.derivatives = compute_derivatives(obj.fn, order);  
             obj.derivatives_matlab = cellfun(@(f) ...
                 matlabFunction(f, 'Vars', [x y]), ...
                 obj.derivatives, 'UniformOutput', false);
@@ -111,9 +120,13 @@ classdef Signature < handle
                     Yscan(:, i + params.nlines) = ...
                         t*params.ylim(1) + (1 - t)*params.ylim(2);
                 end 
+                if ~isempty(obj.tform)
+                    [Xscan, Yscan] = obj.tform.forward(Xscan, Yscan);
+                end
                 plot(Xscan, Yscan, params.scanparams{:})
-             
             end
+            set(gca, 'xlim', params.xlim);
+            set(gca, 'ylim', params.ylim);
         end
         
         function save_camera(obj, varargin)
@@ -127,6 +140,13 @@ classdef Signature < handle
             obj.camera_info.loadFromAxes();
         end
     end
+end
+
+function params = parseinputs(varargin)
+p = inputParser();
+p.addParameter('tform', []);
+p.parse(varargin{:});
+params = p.Results;
 end
 
 function params = draw_parameters(varargin)

### 2018-05-17 code/group_experiment.m

@@ -21,17 +21,20 @@ visualise();
     function visualise()
         figure(1)
         clf
-        subplot(1,2,1)
+        sig.draw_image('showscanlines', fscan);
+        figure(2)
+        sigp.draw_image('showscanlines', false);
         draw_image(f_map, 'xlim', xlim, 'ylim', ylim);
         subplot(1,2,2)
         draw_image(fp_map, 'xlim', xlim, 'ylim', ylim);
         figure(2)
         clf
-        draw_signature(@sig.evaluate, 'xlim', xlim, 'ylim', ylim);
+        sig.draw();
         figure(3)
         clf
-        draw_signature(@sig.evaluate, 'xlim', xlim, 'ylim', ylim, 'facealpha', 0.5);
+        sig.draw('facealpha', 0.5);
         hold on
+        sigp.draw('facecolor', 'red', 'facealpha', 0.5);
         draw_signature(@sigp.evaluate, 'xlim', xlim, 'ylim', ylim, ...
             'facecolor', 'red', 'facealpha', 0.5);  
         axis off

### 2018-05-17 code/make_figures.m

@@ -13,6 +13,15 @@ write_images = false;
 f(x, y) = 0.5 - 0.2*x - 0.3*y - 0.05*x.^2 + 0.03*x.*y + 0.04*y.^2 + ...
     0.03*y.^3 +0.001*x.^3 - 0.0015*x.^2.*y + 0.002*x.*y.^2 - 0.0005*y.^3;
 
+%% Plot and write image
+clf
+sig = E2_signature(f);
+sig.draw_image('showscanlines', false)
+print('-dpng', '-r200', 'images/function.png')
+clf
+sig.draw_image()
+print('-dpng', '-r200', 'images/function_scanlines.png')
+
 %% Write signature picture
 groups = {'E2', 'SE2', 'A2', 'Mobius', 'PSL3R', 'SA2', 'Sim2'};
 for i = 1:numel(groups)
@@ -28,17 +37,28 @@ end
 sig.save_camera();
 save(strcat('images/', sig.group, '_signature.mat'), 'sig');
 
+%% Save transformed image to file
+clf
+sigp.draw_image()
+print('-dpng', '-r200', strcat('images/f_transformed_', sigp.group, '.png'));
 %% E(2)
 % Visualise transformation
 close all
 tform = E2Transform(1, -1, 0.1, -0.2);
 sig = E2_signature(f);
-sig.draw()
+[xp, yp] = tform.reverse(x, y);
+sigp = E2_signature(f, 'tform', tform);
+
+
+
+
 
 %% SE(2)
 close all
 tform = SE2Transform(1, 0.1, -0.2);
 sig = SE2_signature(f);
+[xp, yp] = tform.reverse(x, y);
+sigp = SE2_signature(f, 'tform', tform);
 sig.draw()
 % group_experiment(f, tform, @SE2_signature, 'scanlines', {Xscan, Yscan});
 
@@ -49,6 +69,8 @@ A = [0.7, 1.1;
 A = A / sqrt(det(A));
 tform = SA2Transform(A(1,1), A(1,2), A(2,1), A(2,2), 0.1, -0.2);
 sig = SA2_signature(f);
+[xp, yp] = tform.reverse(x, y);
+sigp = SA2_signature(f, 'tform', tform);
 sig.draw()
 %group_experiment(f, tform, @SA2_signature, 'scanlines', {Xscan, Yscan});
 
@@ -56,6 +78,8 @@ sig.draw()
 close all
[…]

### 2018-05-17 code/signature_switch.m

@@ -16,5 +16,5 @@ if isnumeric(f)
     derivatives = compute_derivatives(f, order, hx, hy);
     out = sig_fun(derivatives); 
 else
-    out = Signature(f, sig_fun, order, group);
+    out = Signature(f, sig_fun, order, group, varargin{:});
 end

### 2018-05-17 paper/figpaper.tex
Most of the pictures into separate paper

@@
 \documentclass[11pt]{article}
-\usepackage{amsmath}
+\usepackage{amsmath, amssymb}
+\usepackage{graphicx}
 
 \begin{document}
-In order to compare the invariants visually, we use the following
-polynomial in two variables:
-\begin{equation}
+
+\section{Introduction}
+We consider as our image, the following function, defined on $[-1, 1]
+\times:
+[-1, 1]$
+\begin{equation}\label{eq:function}
   \begin{split}
@@
 \end{equation}
-The function was chosen to have no critical points, and to be predominantly
-linear, so that the higher order derivatives were not too large.
+This function was chosen to have no critical points, and to be
+predominantly linear, so that the higher order derivatives were not too
+large. This was predominantly so the higher order terms in the signatures
+would not overwhelm the smaller terms. The function is depicted as a
+greyscale image in Figure~\ref{fig:function}
+\begin{figure}
+  \centering
+  \includegraphics[width=10cm]{figures/function}
+  \caption{The test function used in this document, from
+  Eq.~\eqref{eq:function}.}\label{fig:function}
+\end{figure}
+
+We consider the signatures of this function under various transformation
+groups, as detailed throughout the main body of the paper and illustrate
+the signature in three dimensions. A grid is overlaid on the image of the
+function itself, as shown in Fig~\ref{fig:function_scanlines}. This grid is
+mapped to the signature surface to help understand what the signature looks
+like locally.
+\begin{figure}
+  \centering
+  \includegraphics[width=10cm]{figures/function_scanlines}
+  \caption{The test function used in this document, from
+  Eq.~\eqref{eq:function} with a grid of lines
+overlaid.}\label{fig:function_scanlines}
+\end{figure}
+
+\section{The transformation groups}
+
+\subsection{Sim(2)}
+For $\text{Sim}(2)$, we use the signature $(I_0, I_1, I_2)$, defined by
+\begin{equation}\label{eq:sim2sig}
+  I_i = \frac{f}{\sqrt{J_1^2 + J_2^2 + J_3^2}} J_i,
+\end{equation}
+where
+\begin{equation*}
+  \begin{split} 
+    J_1 &= f_x^2 + f_y^2, \\
+    J_2 &= (f_{xx} + f_{xy})^2, \\
+    J_3 &= f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2.
+  \end{split}
+\end{equation*}
+The signature is visualised in Fig.~\ref{fig:sim2signature}
+\begin{figure}
+  \centering
+    \includegraphics[width=10cm]{figures/Sim2_signature}
+    \caption{$\text{Sim}(2)$ signature}
+    \label{fig:sim2signature}
+\end{figure}
+
+\subsection{SE(2)}
+For $SE(2)$, we use the signature
+\begin{equation}\label{eq:se2sig}
+  \begin{split}
+    I_1 &= f \\
+    I_2 &= f_x^2 + f_y^2 \\
+    I_3 &= f_x^2 f_{xy} + f_x f_y f_{yy} - f_x f_y f_{xx} - f_y^2 f_{xy}
+  \end{split}
+\end{equation}
+The signature is visualised below in Fig.~\ref{fig:se2signature}
+\begin{figure}
+  \centering
+    \includegraphics[width=10cm]{figures/SE2_signature}
+  \caption{$SE(2)$ signature}
+  \label{fig:se2signature}
+\end{figure}
+
+\subsection{E(2)}
+For $E(2)$, we use the signature
+\begin{equation}\label{eq:e2sig}
+  \begin{split}
+    I_1 &= f \\
+    I_2 &= f_x^2 + f_y^2 \\
+    I_3 &= f_{xx} + f_{yy}
+  \end{split}
+\end{equation}
+The signature is visualised in Fig.~\ref{fig:e2signature}
+\begin{figure}
+  \centering
+    \includegraphics[width=10cm]{figures/E2_signature}
+  \caption{$E(2)$ signature}
+  \label{fig:e2signature}
+\end{figure}
+
+\subsection{SA(2)}
+For $SA(2)$, we use the signature
+\begin{equation}\label{eq:sa2sig}
+  \begin{split}
+    I_1 &= f_{xx}f_{yy} - f_{xy}^2  \\
+    I_2 &= f_y^2f_{xx} - 2f_x f_y f_{xy} + f_x^2f_{yy} \\
+    I_3 &= f_{xxx}f_y^3 - 3*f_{xxy}f_x f_y^2 + 3f_{xyy}f_x^2f_y - f_{yyy}f_x^3
+  \end{split}
+\end{equation}
+The signature is visualised in Fig.~\ref{fig:sa2signature}
+\begin{figure}
+  \centering
+    \includegraphics[width=10cm]{figures/SA2_signature}
+  \caption{$SA(2)$ signature}
+  \label{fig:sa2signature}
+\end{figure}
+
+\subsection{A(2)}
+For $A(2)$, we use the signature
+\begin{equation}\label{eq:a2sig}
+  \begin{split}
+    I_1 &= \frac{fC^3}{\sqrt{C^6 + D^6 + E^4}} \\
+    I_2 &= \frac{fD^3}{\sqrt{C^6 + D^6 + E^4}} \\
+    I_3 &= \frac{fE^2}{\sqrt{C^6 + D^6 + E^4}} \\
+  \end{split}
+\end{equation}
+where
+\begin{equation*}
+  \begin{split}
+    C &= f_{xx}f_{yy} - f_{xy}^2 \\
+    D &= f_y^2f_{xx} - 2f_xf_y f_{xy} + f_x^2f_{yy} \\
+    E &= f_{xxx}f_y^3 - 3f_{xxy}f_x f_y^2 + 3f_{xyy}f_x^2 f_y - f_{yyy}f_x^3
+  \end{split}
+\end{equation*}
+The signature is visualised in Fig.~\ref{fig:a2signature}
+\begin{figure}
+  \centering
+    \includegraphics[width=10cm]{figures/A2_signature}
+  \caption{$A(2)$ signature}
+  \label{fig:a2signature}
+\end{figure}
+
+\subsection{M{\"o}bius}
+For $\text{M{\"o}bius}$, we use the signature
+\begin{equation}\label{eq:mobiussig}
+  \begin{split}
+    I_1 &= \frac{fJ_1^4}{\sqrt{J_1^8 + K_1^2 + K_4^2}} \\
+    I_2 &= \frac{fK_1}{\sqrt{J_1^8 + K_1^2 + K_4^2}} \\
+    I_3 &= \frac{fK_4}{\sqrt{J_1^8 + K_1^2 + K_4^2}}
+  \end{split}
+\end{equation}
+where
+\begin{equation*}
+  \begin{split}
+  J_1 &= f_xf_x + f_yf_y \\
+  J_2 &= f_{xx} + f_{yy} \\
+  J_3 &= J_1(f_x(f_{xxx} + f_{xyy}) + f_y(f_{xxy} + f_{yyy})) + 
+      2J_2(f_x^2f_{xx} + 2f_xf_yf_{xy} + f_y^2f_{yy}) \\
+  J_4 &= J_1(f_x(f_{xxy} + f_{yyy}) - f_y(f_{xxx} + f_{xyy})) + 
+      2J_2(f_x^2f_{xy} + f_xf_yf_{yy} - f_xf_yf_{xx} - f_y^2f_{xy}) \\
+  K_1 &= f_y^5f_{yyy} + 9/2f_y^2f_{yy}^2f_x^2 + f_y^3f_{yyy}f_x^2 + 
+      3/2f_{yy}^2f_x^4 -9f_y^3f_{yy}f_xf_{xy} + 3f_yf_{yy}f_x^3f_{xy} + \\
+      & 3/2f_y^4f_{xy}^2 - 9f_y^2f_x^2f_{xy}^2 + 
+      3/2f_x^4f_{xy}^2 + 3f_y^4f_xf_{xyy} + 3f_y^2f_x^3f_{xyy} + \\
+      & 3f_y^4f_{yy}f_{xx} + 3f_{yy}f_x^4f_{xx} + 3f_y^3f_xf_{xy}f_{xx} -
+      9f_yf_x^3f_{xy}f_{xx} + 3/2f_y^4f_{xx}^2 + 9/2f_y^2f_x^2f_{xx}^2 + \\
+      & 3f_y^3f_x^2f_{xxy} + 3f_yf_x^4f_{xxy} + f_y^2f_x^3f_{xxx} + 
+      f_x^5f_{xxx} \\
+  K_4 &= -3f_yf_{yy}^2f_x^3 + f_y^2f_{yyy}f_x^3 + f_{yyy}f_x^5 +
+  9f_y^2f_{yy}f_x^2f_{xy}   - 3f_{yy}f_x^4f_{xy} - 6f_y^3f_xf_{xy}^2 + \\
+  & 6f_yf_x^3f_{xy}^2 -   3f_y^3f_x^2f_{xyy} - 3f_yf_x^4f_{xyy} - 
+  3f_y^3f_{yy}f_xf_{xx} +   3f_yf_{yy}f_x^3f_{xx} + 3f_y^4f_{xy}f_{xx} -
+  \\
+  & 9f_y^2f_x^2f_{xy}f_{xx} + 3f_y^3f_xf_{xx}^2 + 3f_y^4f_xf_{xxy} +
+  3f_y^2f_x^3f_{xxy} - f_y^5f_{xxx} - f_y^3f_x^2f_{xxx} \\
+\end{split}
+\end{equation*}
+The signature is visualised in Fig.~\ref{fig:mobiussignature}
+\begin{figure}
+  \centering
+    \includegraphics[width=10cm]{figures/mobius_signature}
+    \caption{$\text{M{\"o}bius}$ signature}
+  \label{fig:mobiussignature}
+\end{figure}
 
 \begin{figure}
-
+  \centering
+    \includegraphics[width=10cm]{figures/PSL3R_signature}
+    \caption{$PSL(3, \mathbb{R})$ signature}
+  \label{fig:psl3rsignature}
 \end{figure}
-
 \end{document}

### 2018-05-17 paper/figpaper.tex
finished putting signatures in

@@
 \usepackage{amsmath, amssymb}
+\usepackage{geometry}
 \usepackage{graphicx}
-
 \begin{document}
@@
   \centering
-  \includegraphics[width=10cm]{figures/function}
+  \includegraphics[width=12cm]{figures/function}
   \caption{The test function used in this document, from
@@
   \centering
-  \includegraphics[width=10cm]{figures/function_scanlines}
+  \includegraphics[width=12cm]{figures/function_scanlines}
   \caption{The test function used in this document, from
@@
 \subsection{Sim(2)}
-For $\text{Sim}(2)$, we use the signature $(I_0, I_1, I_2)$, defined by
+For $\text{Sim}(2)$, we use the signature $(I_1, I_2, I_3)$, defined by
 \begin{equation}\label{eq:sim2sig}
-  I_i = \frac{f}{\sqrt{J_1^2 + J_2^2 + J_3^2}} J_i,
+    I_i = \frac{f}{\sqrt{J_1^2 + J_2^2 + J_3^2}} J_i, \qquad i \in \{1, 2,
+    3\}
 \end{equation}
@@
   \centering
-    \includegraphics[width=10cm]{figures/Sim2_signature}
+    \includegraphics[width=12cm]{figures/Sim2_signature}
     \caption{$\text{Sim}(2)$ signature}
@@
   \centering
-    \includegraphics[width=10cm]{figures/SE2_signature}
+    \includegraphics[width=12cm]{figures/SE2_signature}
   \caption{$SE(2)$ signature}
@@
   \centering
-    \includegraphics[width=10cm]{figures/E2_signature}
+    \includegraphics[width=12cm]{figures/E2_signature}
   \caption{$E(2)$ signature}
@@
   \centering
-    \includegraphics[width=10cm]{figures/SA2_signature}
+    \includegraphics[width=12cm]{figures/SA2_signature}
   \caption{$SA(2)$ signature}
@@
   \centering
-    \includegraphics[width=10cm]{figures/A2_signature}
+    \includegraphics[width=12cm]{figures/A2_signature}
   \caption{$A(2)$ signature}
@@
   \centering
-    \includegraphics[width=10cm]{figures/mobius_signature}
+    \includegraphics[width=12cm]{figures/mobius_signature}
     \caption{$\text{M{\"o}bius}$ signature}
@@
 
+\subsection{$PSL(3, \mathbb{R})$}
+For $PSL(3, \mathbb{R})$, we use the signature
+\begin{equation}\label{eq:psl3rsig}
+  \begin{split}
+    I_1 &= \frac{f}{\gamma}D^6 \\
+    I_2 &= \frac{f}{\gamma}P_4^3\\
+    I_3 &= \frac{f}{\gamma}(E^2- 12DP_5)^2
+  \end{split}
+\end{equation}
+where
+\begin{equation*}
+  \begin{split}
+    C &= f_{xx}f_{yy} - f_{xy}^2 \\
+    D &= f_y^2f_{xx} - 2f_xf_yf_{xy} + f_x^2f_{yy} \\
+    E &= f_{xxx}f_y^3 - 3f_{xxy}f_xf_y^2 + 3f_{xyy}f_x^2f_y - f_{yyy}f_x^3
+    \\
+    \gamma &= \sqrt{D^{12} + P_4^6 + (E^2 - 12DP_5)^4} \\
+    Q_4 &= 4f_xf_{xy}^2f_{xyy} - f_x^2f_{xyy}^2 - 2f_{yyy}f_xf_{xy}f_{xx} +
+    \\
+    & 2f_{yy}f_xf_{xyy}f_{xx} - 6f_yf_{xy}f_{xyy}f_{xx} + \\
+    & 2f_yf_{yyy}f_{xx}^2 + f_{yyy}f_x^2f_{xxy} - 6f_{yy}f_xf_{xy}f_{xxy} + \\ 
+    & 4f_yf_{xy}^2f_{xxy} + f_yf_xf_{xyy}f_{xxy} + 2f_yf_{yy}f_{xx}f_{xxy} - \\
+    & f_y^2f_{xxy}^2 + 2f_{yy}^2f_xf_{xxx} - f_yf_{yyy}f_xf_{xxx} \\
+    & -2f_yf_{yy}f_{xy}f_{xxx} + f_y^2f_{xyy}f_{xxx} \\
+    P_5 &= f_{yyy}f_x^3f_{xy} - f_{yy}f_x^2f_{xy}^2 + 2f_yf_xf_{xy}^3 - \\
+    & f_{yy}f_x^3f_{xyy} - f_yf_x^2f_{xy}f_{xyy} + f_{yy}^2f_x^2f_{xx} - \\
+    & f_yf_{yyy}f_x^2f_{xx} - 2f_yf_{yy}f_xf_{xy}f_{xx} - \\
+    & f_y^2f_{xy}^2f_{xx} + 2f_y^2f_xf_{xyy}f_{xx} + f_y^2f_{yy}f_{xx}^2 + \\
+    & 2f_yf_{yy}f_x^2f_{xxy} - f_y^2f_xf_{xy}f_{xxy} - f_y^3f_{xx}f_{xxy} - \\
+    & f_y^2f_{yy}f_xf_{xxx} + f_y^3f_{xy}f_{xxx} \\
+    P_4 &= -4C^2 + Q_4 
+  \end{split}
+\end{equation*}
+The signature is visualised in Fig.~\ref{fig:psl3rsignature}
 \begin{figure}
   \centering
-    \includegraphics[width=10cm]{figures/PSL3R_signature}
+    \includegraphics[width=12cm]{figures/PSL3R_signature}
     \caption{$PSL(3, \mathbb{R})$ signature}

### 2018-11-09 code/transvectant.m
Glory, honour, and transvectants

@@ -1,0 +1,10 @@
+function T = transvectant(Q, R, r)
+syms x_a y_a x_b y_b x y
+% Q, R come in as expressions, nothing we can do about this. This line
+% forces them back to being functions
+S(x_a, y_a, x_b, y_b) = Q(x_a, y_a)*R(x_b, y_b);
+for i = 1:r
+    S(x_a, y_a, x_b, y_b) = omega_process(S);
+end
+T(x, y) = S(x, y, x, y);
+end

### 2018-11-09 code/make_transvectants.m
Basic transvectant making

@@ -1,0 +1,21 @@
+%% Make ye olde transvectants
+max_order = 4;
+syms Q(x, y)
+m = floor(max_order/2);
+for i = 1:m
+    S{i} = transvectant(Q, Q, 2*i);
+end
+
+for i = 1:m
+    for j = 1:m
+        T{i, j} = transvectant(Q, S{i}, j);
+    end
+end
+
+for i = 1:m
+    for j = 1:m
+        for k = 1:m
+            V{i, j, k} = transvectant(S{i}, S{j}, k);
+        end
+    end
+end

### 2018-11-09 code/transvectant.m

@@ -1,4 +1,8 @@
 function T = transvectant(Q, R, r)
+%TRANSVECTANT(Q, R, r)
+%   Make r-th order transvectant (Q, R)^{(r)}
+%
+%   Q and R are symbolic functions of two variables
 syms x_a y_a x_b y_b x y
 % Q, R come in as expressions, nothing we can do about this. This line
 % forces them back to being functions

### 2018-11-09 code/make_transvectants.m
code mostly working, need to fix pretty printing

@@ -1,21 +1,37 @@
 %% Make ye olde transvectants
 max_order = 4;
 syms Q(x, y)
-m = floor(max_order/2);
+m = floor(max_order/2)+1;
+fd = fopen('foo.tex', 'w');
+fprintf(fd, '%s\n', '\documentclass{article}')
+fprintf(fd, '%s\n', '\usepackage{amsmath, breqn}')
+fprintf(fd, '%s\n', '\begin{document}')
+fprintf(fd, '%s\n', 'S: \begin{dgroup}')
 for i = 1:m
-    S{i} = transvectant(Q, Q, 2*i);
+    S{i} = simplify(transvectant(Q, Q, 2*(i-1)));
+    fprintf(fd, '%s\n%s\n%s\n', '\begin{dmath}', ...
+        latex(S{i}), '\end{dmath}');
 end
-
+fprintf(fd, '%s\n', '\end{dgroup}')
+fprintf(fd, '%s\n', 'T: \begin{dgroup}')
 for i = 1:m
     for j = 1:m
-        T{i, j} = transvectant(Q, S{i}, j);
+        T{i, j} = transvectant(Q, S{i}, j-1);
+        fprintf(fd, '%s\n%s\n%s\n', '\begin{dmath}', ...
+            latex(T{i, j}), '\end{dmath}');
     end
 end
-
-for i = 1:m
-    for j = 1:m
-        for k = 1:m
-            V{i, j, k} = transvectant(S{i}, S{j}, k);
-        end
-    end
-end
+fprintf(fd, '%s\n', '\end{dgroup}')
+% fprintf(fd, '%s\n', 'V: \begin{dgroup}')
+% for i = 1:m
+%     for j = 1:m
+%         for k = 1:m
+%             V{i, j, k} = transvectant(S{i}, S{j}, k-1);
+%             fprintf(fd, '%s\n%s\n%s\n', '\begin{dmath}', ...
+%                 latex(V{i, j, k}), '\end{dmath}');
+%         end
+%     end
+% end
+% fprintf(fd, '%s\n', '\end{dgroup}')
+fprintf(fd, '%s\n', '\end{document}')
+fclose(fd)

### 2018-11-09 paper/newpaper.tex
Add actual paper

\documentclass{article}
\date{\today}
\title{Working title}
\author{Not-working authors}

\begin{document}
\maketitle
\abstract{ }
\section{Introduction}
Shapes/objects/images can be acted on by simple transformations that change
their appearance. We want to recognise the objects or identify the set of
transformations. If the set is a group, then we can seek to either identify
the group or solve the equivalence problem by
\begin{enumerate}
    \item Registration, or
    \item Invariance.
\end{enumerate}
The first is commonly studied but is computationally expensive and prone to
local minima. If you're not interested in the actual transformation it is
therefore to be avoided. Here we'll consider invariance. There are many
choices of type e.g. Fourier, integral, or differential invariants. The
last set are cheap to compute and have nice theoretical properties but are
not robust to noise. However, we'll use them anyway. This paper is a
tutorial on differential invariants for planar Lie groups (e.g.
Euclidean, affine, projective) since they are relatively simple, useful,
and relevant to images. We'll use these to demonstrate the methods of
constructing and using differential invariant signatures. Note that this
reduces the recognition problem to recognising higher-dimensional
differential invariant signatures. We'll mention some approaches to this.
See the companion paper for an implementation.

\subsection{Tutorial on differential invariants / differential geometry}
\subsubsection{Differential geometry stuff}
\begin{description}
    \item[Completeness]
    \item[Invariant]
    \item[joint invariant and weight]
    \item[transvectant]
    \item[generic functions]
    \item[differential invariant order]
    \item[transitive]
    \item[free]
    \item[effective]
    \item[group prolongation]
\end{description}

\subsubsection{Construction of signatures}
Including dealing with projection to deal with scalings
Signatures are higher dimensional objects 
Completeness vs practicality

Will include Translation as basic example.

\section{Classical Invariant Theory}
\subsection{Description of method}
\subsection{Groups}
\begin{itemize}
    \item $SE(2)$
    \item $E(2)$
    \item $Sim(2)$
    \item $SA(2)$
    \item $A(2)$
\end{itemize}

\section{The Moving Frame Method}
\subsection{Description of method}
\subsection{Groups}
\begin{itemize}
    \item M\"obius
    \item Projective
\end{itemize}

\subsection{Diffeomorphism groups}
Diff then Diff vol and Diff conf. No invariants -> there are some.

\section{Experiments}
Effects of noise
\subsection{Example signatures}
\subsection{`Spot the group'}

\section{Discussion and Conclusions}
\subsection{Colour images}
\subsection{Number of invariants}
\end{document}

### 2019-07-08 paper/newpaper.tex
words

@@
-\documentclass{article}
+\documentclass[review,onefignum,onetabnum]{siamonline171218}
+\usepackage{amsfonts,graphicx}
+\def\R{\mathbb{R}}
+\usepackage{xcolor}
+
 \date{\today}
@@
 \maketitle
-\abstract{ }
+\begin{abstract}
+\end{abstract}
+
+% REQUIRED
+\begin{keywords}
+\end{keywords}
+
+% REQUIRED
+\begin{AMS}
+\end{AMS}
+
 \section{Introduction}
@@
 
-\subsection{Tutorial on differential invariants / differential geometry}
-\subsubsection{Differential geometry stuff}
-\begin{description}
-    \item[Completeness]
-    \item[Invariant]
-    \item[joint invariant and weight]
-    \item[transvectant]
-    \item[generic functions]
-    \item[differential invariant order]
-    \item[transitive]
-    \item[free]
-    \item[effective]
-    \item[group prolongation]
-\end{description}
+\section{Differential invariants through transvectants}
 
-\subsubsection{Construction of signatures}
-Including dealing with projection to deal with scalings
-Signatures are higher dimensional objects 
-Completeness vs practicality
+One way to compute invariants is to compare the action of group elements on separate copies of the underlying space.
+For images, this is typically $\mathbb{R}^2$; colour images in $\mathbb{R}^{2k}$ will be considered in Section~\ref{sec:aaah}.
 
-Will include Translation as basic example.
+Following the treatment in~\cite{OlverCIT}, this leads to Cayley's Omega Process~\cite{Cayley}. We will demonstrate this for the affine group $A(2)$ and its subgroup $SA(2)$.
 
-\section{Classical Invariant Theory}
-\subsection{Description of method}
-\subsection{Groups}
-\begin{itemize}
-    \item $SE(2)$
-    \item $E(2)$
-    \item $Sim(2)$
-    \item $SA(2)$
-    \item $A(2)$
-\end{itemize}
+Consider $\mathbf{x}_i \ in \mathbb{R}^2, i=1,2$, so that $mathbf{x}_i$ can be written in coordinates as $(x_i, y_i)$.
+Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$.
+Now consider applying an affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i_ \mapsto A \mathbf{x}_i + b$ where $A \in GL(2,\mathbb{R}$ and $b \in \mathbb{R}^2$.
+Then the Omega Process is a second-order differential operator defined by:
 
-\section{The Moving Frame Method}
-\subsection{Description of method}
-\subsection{Groups}
-\begin{itemize}
-    \item M\"obius
-    \item Projective
-\end{itemize}
+\begin{equation}
+\Omega_{ij} = \left| \begin{array}{cc} \frac{\partial}{\partial x_i} & \frac{\partial}{\partial y_i} \\ \frac{\partial}{\partial x_j} & \frac{\partial}{\partial y_j} & \right| = \frac{\partial^2}{\partial x_i \partial y_j} \frac{\partial^2}{\partial x_j \partial y_i}.
+\end{equation}
 
-\subsection{Diffeomorphism groups}
-Diff then Diff vol and Diff conf. No invariants -> there are some.
+Under the above affine transformation, $\Omega_{ij} \mapsto \det A^{-1} \Omega_{ij}$. Note that $\det A^{-1}$ has no dependence on the coordinates.
 
-\section{Experiments}
-Effects of noise
-\subsection{Example signatures}
-\subsection{`Spot the group'}
+The Omega Process can be applied to pairs of smooth functions as follows:
 
-\section{Discussion and Conclusions}
-\subsection{Colour images}
-\subsection{Number of invariants}
+\begin{equation}
+\Omega_{ij} f(x_i, y_i) g(x_j, y_j) = ...
+\end{equation}
+
+Identifying $x_i = x_j = x, y_i = y_j = y$ gives us functions of $x$ and $y$ that only vary by a scaling factor of $\det A^{-1}$ when $\mathbf{x}$ is mapped by an affine transformation.
+This matches the definition of a first-order partial transvectant of two functions:
+
+\begin{equation}
+\mbox{tr} \Omega_{ij} f(x_i, y_i) g(x_j, y_j),
+\end{equation}
+
+\noindent where $mbox{tr}$  is the operator that identifies the coordinates of each function $x_i = x_j = x, y_i = y_j = y$.
+
+This can be generalised to $n$ functions and $r-$th order~\cite{Olver} as:
+
+\begin{equation}
+\mbox{tr} \left( \Pi_{k=1}^r \Omega_{i_k j_k} \right) f_1(x_1, y_1) f_2(x_2, y_2), \ldots f_n (x_n, y_n)
+\end{equation}
+
+Under this formula we end with a factor $\det A^{-r}$ in place of $\det A^{-1}$ that we saw previously.
+$r$ is referred to as the weight of the partial transvectant.
+It can also be useful to consider the total number of derivatives computed, which we term degree, e.g., $f_{xy}^2 f_x f_y$ has degree 6.
+For the current case it is sufficient to consider $n$ copies of the same function $f$.
+
+This formula can be applied to generate partial transvectants, as we will now show for the action of two groups: $A(2)$ itself, and its subgroup $SA(2)$.
+
+Then computations.
+
+Then the graphs and the weights.
+
+Discussion of singularities.
+
+And then a list of explicit invariants by group.
+
+And the signatures.
+
+\section{Differential invariants through moving frames}
+
+Cartan developed the moving frame to compute invariants.
+
+Then computations.
+
+Then the graphs and the weights.
+
+And then a list of explicit invariants by group.
+
+And the signatures.
+
+\section{Extension to larger groups, role of colour, etc.}
+
+\section{Use in practice; noise, singularities}
+
 \end{document}

### 2019-07-08 paper/newpaper.tex
pics

@@
 \documentclass[review,onefignum,onetabnum]{siamonline171218}
-\usepackage{amsfonts,graphicx}
+\usepackage{amsmath,amsfonts,graphicx}
 \def\R{\mathbb{R}}
 \usepackage{xcolor}
+\usepackage{todonotes}
+\usepackage{tikz}
 
@@
 \section{Introduction}
+\todo[inline]{This is a start. To be completed later.}
+
 Shapes/objects/images can be acted on by simple transformations that change
@@
 Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$.
-Now consider applying an affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i_ \mapsto A \mathbf{x}_i + b$ where $A \in GL(2,\mathbb{R}$ and $b \in \mathbb{R}^2$.
+Now consider applying an affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + b$ where $A \in GL(2,\mathbb{R}$ and $b \in \mathbb{R}^2$.
 Then the Omega Process is a second-order differential operator defined by:
@@
 \begin{equation}
-\Omega_{ij} = \left| \begin{array}{cc} \frac{\partial}{\partial x_i} & \frac{\partial}{\partial y_i} \\ \frac{\partial}{\partial x_j} & \frac{\partial}{\partial y_j} & \right| = \frac{\partial^2}{\partial x_i \partial y_j} \frac{\partial^2}{\partial x_j \partial y_i}.
+\Omega_{ij} = \begin{vmatrix} \frac{\partial}{\partial x_i} & \frac{\partial}{\partial y_i} \\ \frac{\partial}{\partial x_j} & \frac{\partial}{\partial y_j} \end{vmatrix}  = \frac{\partial^2}{\partial x_i \partial y_j} - \frac{\partial^2}{\partial x_j \partial y_i}.
 \end{equation}
@@
 $r$ is referred to as the weight of the partial transvectant.
-It can also be useful to consider the total number of derivatives computed, which we term degree, e.g., $f_{xy}^2 f_x f_y$ has degree 6.
+It can also be useful to consider the maximum number of derivatives computed, which we term degree, e.g., $f_{xy}^2 f_x f_y$ has degree 2.
 For the current case it is sufficient to consider $n$ copies of the same function $f$.
@@
 
+\todo[inline]{Start here... write out some bits.}
+
 Then computations.
@@
 Then the graphs and the weights.
+
+\centering
+\begin{tabular}{cccc}
+Degree & Weight & Diagram & Invariant \\
+\hline
+2 & 2 &
+\begin{tikzpicture}
+    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
+    \draw[-] (1) to [out=30,in=150] (2);
+    \draw[-] (1) to [out=-30,in=-150] (2);
+\end{tikzpicture}
+& $fxx$ \\
+
+2 & 2 &
+\begin{tikzpicture}
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+\end{tikzpicture}
+& $fxx$ \\
+
+3 & 3 &
+\begin{tikzpicture}
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to (3);
+\end{tikzpicture}
+& $fxx$ \\
+
+3 & 4 &
+\begin{tikzpicture}
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to (3);
+    \draw[-] (2) to (3);
+\end{tikzpicture}
+& $fxx$ \\
+
+%=====
+3 & 3 &
+\begin{tikzpicture}
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+    \draw[-] (1) to (4);
+\end{tikzpicture}
+& $fxx$ \\
+
+3 & 4 &
+\begin{tikzpicture}
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to [out=-120,in=120] (2);
+    \draw[-] (1) to [out=-60,in=60] (2);
+    \draw[-] (2) to (3);
+    \draw[-] (3) to (4);
+\end{tikzpicture}
+& $fxx$ \\
+
+2 & 4 &
+\begin{tikzpicture}
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to (2);
+    \draw[-] (2) to (3);
+    \draw[-] (3) to (4);
+    \draw[-] (4) to (1);
+\end{tikzpicture}
+& $fxx$ \\
+
+3 & 4 &
+\begin{tikzpicture}
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to [out=-120,in=120] (2);
+    \draw[-] (1) to [out=-60,in=60] (2);
+    \draw[-] (2) to (3);
+    \draw[-] (1) to (4);
+\end{tikzpicture}
+& $fxx$ \\
+
+% =========
+2 & 4 &
+\begin{tikzpicture}
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
+    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
+    \draw[-] (1) to (2);
+    \draw[-] (2) to (3);
+    \draw[-] (3) to (4);
+    \draw[-] (4) to (5);
+\end{tikzpicture}
+& $fxx$ \\
+
+3 & 4 &
+\begin{tikzpicture}
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
+    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+    \draw[-] (1) to (4);
+    \draw[-] (4) to (5);
+\end{tikzpicture}
+& $fxx$ \\
+
+4 & 4 &
+\begin{tikzpicture}
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
+    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+    \draw[-] (1) to (4);
+    \draw[-] (1) to (5);
+\end{tikzpicture}
+& $fxx$ \\
+\end{tabular}
 
@@
 
+\todo[inline]{Intro to model bit above. Steal equations from dispaper. TBC}
 Cartan developed the moving frame to compute invariants.
@@
 
+\todo[inline]{Largely discursive? Except conformal.}
+
 \section{Use in practice; noise, singularities}
+ \todo[inline]{Experimental}
+
+\section{Algorithms}
+ This will go in paper 2, but let's start in here.
+
+\todo[inline]{Pseudocode for the matlab experimental code}
+\todo[inline]{Something about computing transvectants?}
+
+\section{Experiments}
+
+\todo[inline]{Signature examples}
+\todo[inline]{Noise}
+\todo[inline]{Spot the group}
+\todo[inline]{Example on bits of images}
 

### 2019-08-14 paper/newpaper.tex
With more, not necessarily better, words

@@
-\documentclass[review,onefignum,onetabnum]{siamonline171218}
+\documentclass[review,onefignum,onetabnum]{siamonline190516}
 \usepackage{amsmath,amsfonts,graphicx}
@@
 \date{\today}
-\title{Working title}
+\title{Differential invariant signatures for planar Lie group transformations of images}
 \author{Not-working authors}
@@
 
+The setting that we will consider is a transformation group $\mathcal{G}$ acting on a manifold $\mathcal{M}$ of dimension $n$.
+A $d$-th order differential invariant is a local scalar function $I: J^{d} (\mathbb{R}, \mathcal{M} ) \to \mathbb{R}$ that is invariant under the action of $\mathcal{G}$, i.e., $I(g(x,u^{(d)})) = I(x, u^{(d)}) \forall g \in \mathcal{G}$, where $J^{d}$ denotes the $d$-th order jet space.
+
+====
+Let $G$ be a (finite or infinite-dimensional) local planar transformation group. 
+A {\em $k$-colour image} is a triple $(f,\Omega,k)$ where $\Omega\subset\R^2$, $1\le k\in\mathbb{Z}$,
+and $f\colon\Omega\to\R^k$. The function $f$ will be taken to be as smooth as necessary.
+A transformation $\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) = (f\circ\varphi^{-1},\varphi(\Omega),k)$.
+(As we work locally, we will usually omit the domain $\Omega$; if the number of colours $k$ is not given, we assume $k=1$.)  A differential invariant is an invariant of the prolonged action of $G$ on the derivatives of $f$, i.e., a function $I$ of the values of $f$ and its derivatives at a point such that $I(f)(x,y) = I(\varphi\cdot f)(\varphi(x,y))$.
+An {\em $m$-dimensional signature set} is the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e.
+the
+set $\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$. 
+A signature set is complete for $f$ if it determines $f$ up to transformations from $G$, i.e.
+if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies there exists a transformation $\varphi\in G$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
+
+An algorithm to compute invariants and determine complete signature sets is described in \cite{olver2001}. First, the
+entire set of invariants is computed using the method of moving frames.
+Second, determine the differential invariant order $s$ of $f$.
+Then the signature set of a maximal set of functionally independent invariants of order $s+1$ is complete.
+A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
+
+While we follow this approach in general, in specific cases we have computed invariants using other techniques
+including the invariant tensor theorem and classical invariant theory.
+We shall see that this yields insights into the relationships between the different groups.
+We develop our approach through examples of progressively more complicated groups.
+===
+
+local invariants -> occlusions OK
+derivatives -> noise is not
+
+signatures, dimensions, orders
+
+Is this helpful? 
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}[node distance=1.5cm]
+\node(C1) [] {Diff};
+\node(C2) [below left of=C1] {$\mathrm{Diff}_{\mathrm{vol}}$};
+\node(C3) [below right of=C1] {$\mathrm{Diff}_{\mathrm{con}}$};
+\node(A1) [below right of=C3]                          {$PSL(2,\mathbb{C})$};
+\node(B1)    [below of=C2]    {$PSL(3,\mathbb{R})$};
+\node(B2)   [below of=B1]              {$A(2)$};
+\node(A2)       [below left of=A1]          {Sim$(2)$};
+\node(A3)      [right of=A2]              {$PSL(2,\mathbb{R})$};
+\node(B3)   [below of=B2]            {$SA(2)$};
+\node(A4)      [below of=A2]            {$E(2)$};
+\node(A5) [below right of=A4]{Translation};
+
+\draw[thick,->] (C1) to  (C2);
+\draw[thick,->] (C1) to  (C3);
+%\draw[thick,->] (C1) to  (A2);
+\draw[thick,->] (C3) to  (A1);
+\draw[thick,->] (A1)   to (A2);
+\draw[thick,->] (A1)    to (A3);
+\draw[thick,->] (B1) to  (B2);
+\draw[thick,->] (B2) to  (B3);
+\draw[thick,->] (A2) to  (A4);
+\draw[thick,->] (B3) to  (A4);
+\draw[thick,->] (A3) to  (A5);
+\draw[thick,->] (A4) to  (A5);
+\end{tikzpicture}
+\end{center}
+\caption{The lattice of groups considered in this paper. The edges identify subgroups.}
+\end{figure}
+
+%Groups we've done:
+
+%translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
+
+SE(2) is done via the moving frame by Olver in Ch 8 of CIT.
+
 \section{Differential invariants through transvectants}
@@
 
-Consider $\mathbf{x}_i \ in \mathbb{R}^2, i=1,2$, so that $mathbf{x}_i$ can be written in coordinates as $(x_i, y_i)$.
+Consider $\mathbf{x}_i \in \mathbb{R}^2, i=1,2$, so that $\mathbf{x}_i$ can be written in coordinates as $(x_i, y_i)$.
 Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$.
@@
 
+\begin{tabular}{cccc}
 \centering
-\begin{tabular}{cccc}
 Degree & Weight & Diagram & Invariant \\
@@
 
+E2:
+{\bf Aside 3. Role of the invariants} 
+All of the 2nd order differential invariants play known roles in geometric analysis:
+\begin{enumerate}
+\item $f_if_i=\|\nabla f\|^2$ is the Lagrangian density for the Laplacian;
+\item $f_{ii}$ is the Laplacian, which plays a key role in Euclidean and conformal geometry;
+\item $f_{ij}f_i f_j$ is the `infinity-Laplacian'; critical points of $\|\nabla f\|_{L^\infty}$ obey the PDE $f_{ij}f_i f_j=0$;
+\item
+$f_{ij}f_i f_j$ is also a Lagrangian density for $-2\det f_{ij}$, which arises in Monge--Amp\`ere equations and
+which can be written in terms of the final 2nd order invariant as $-2 \det f_{ij} = f_{ij}f_{ij}-f_{ii}^2$.
+\end{enumerate}
+In addition, we shall see in later sections that functions of these invariants are invariants or
+relative invariants for many groups that contain $E(2)$, namely $Sim(2)$, $SA(2)$, $A(2)$, $PSL(3,\mathbb{R})$, $PSL(2,\mathbb{C})$, and the conformal group.
+
 And the signatures.
+
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/SE2Transform_transform.png}
+\includegraphics[width=.45\textwidth]{Figs/SE2Transform_signature.png}
+\caption{A sample $SE(2)$ Transform and 3D signature.}
+\label{fig:SE2}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/E2Transform_transform.png}
+\includegraphics[width=.45\textwidth]{Figs/E2Transform_signature.png}
+\caption{A sample $E(2)$ Transform and 3D signature.}
+\label{fig:E2}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/SA2Transform_transform.png}
+\includegraphics[width=.45\textwidth]{Figs/SA2Transform_signature.png}
+\caption{A sample $SA(2)$ Transform and 3D signature.}
+\label{fig:SA2}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/A2Transform_transform.png}
+\includegraphics[width=.45\textwidth]{Figs/A2Transform_signature.png}
+\caption{A sample $A(2)$ Transform and 3D signature.}
+\label{fig:A2}
+\end{figure}
 
@@
 
-\todo[inline]{Intro to model bit above. Steal equations from dispaper. TBC}
-Cartan developed the moving frame to compute invariants.
+The method of moving frames enables one to identify invariants under the action of groups of transformations.
+It has a long history, as summarised in \cite{Olver14}; particularly noteworthy contributions are by Cartan~\cite{Cartan37} and Olver and co-authors; see~\cite{Olver14} for an overview, and note particularly for an application to~\cite{Calabi98}.
+The method is described in detail in~\cite{OlverCIT}r.
 
-Then computations.
+A right moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$.
 
-Then the graphs and the weights.
+In order to construct differential invariants to the action of Lie group $\mathcal{G}$ acting on manifold $\mathcal{M}$, the procedure can be summarised as follows:
 
-And then a list of explicit invariants by group.
+\begin{enumerate}
+\item Prolong the group action to the jet space of $n$-th order derivatives (using implicit differentiation): $F: J^n \to \mathbb{R}$. 
+\item Apply Cartan normalisation:
+    \begin{enumerate}
+    \item Choose a local cross-section to the group orbits, i.e., a ($n - \dim \mathcal{G}$)-dimensional submanifold $\mathcal{K}$ that intersects transversally at most once with each orbit
+    \item $\mathcal{K}$ is specified by $\dim \mathcal{G}$ independent equations $Z_i (z) = c_i$, for $z \in J^n$,  and $Z_i$ scalar-valued functions and $c_i$ constants.
+    \item The right moving frame $g = \rho(z)$ is found by solving the normalisation questions $Z_i (g \cdot z) = c_i$ for the group parameters $g$ (in terms of $z$).
+    \end{enumerate}
+\item The differential invariants are not affected by the action of the group: $I(g \cdot z) = I(z) \: \forall z \in \mathrm{dom} I$, or equivalently, if it is constant on the orbits. 
+\item Hence $F$ is made invariant by transforming it with a group action: $I(z) = F(g \cdot z) |_{g=\rho(z)}$.  
+\end{enumerate}
 
-And the signatures.
+Olver uses the group $SE(2)$ as an example~\cite{Olver}, recovering the Euclidean curvature as a second-order invariant.
+We demonstrate the method with two groups: the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).
+
+\subsection{The M\"{o}bius Group}
+
+The M\"obius group $\mathrm{PSL}(2,\mathbb{C})$ acts on the Riemann sphere
+$\overline{\mathbb{C}} = \mathbb{C}\cup\infty$ by 
+$$ \phi\colon \overline{\mathbb{C}} \to \overline{\mathbb{C}},\quad \phi(z) = \frac{\alpha z + \beta}{\gamma z + \delta},\quad \alpha,\beta,\gamma,\delta\in\mathbb{C}, \quad
+\alpha\delta-\beta\gamma\ne 0.$$
+
+Identifying $\R^2$ with $\mathbb{C}$, the M\"obius group is a real 6-dimensional local Lie group acting on $\mathbb{R}^2$.
+It is the smallest nonlinear planar group that contains $SE(2)$, and it is the set of biholomorphic maps of the Riemann sphere; it also has direct applications in image processing since it arises in the {\em conformal camera} model of vision, in which scenes are projected radially onto a sphere \cite{lenz1990group,turski2004geometric}.
+%Different shapes may be related by M\"obius transformations, as is explored by Petukhov \cite{petukhov1989non} for biological objects: in one example, the human skull grows approximately by M\"obius transformations.
+Note also that Thompson \cite{thompson1942growth} famously deformed images of one species to match those of another, many of his examples using conformal mappings, and thus may be approximated (or even determined by) M\"obius transformations.
+Discussing this work, Milnor \cite{milnor2010growth}  argued that ``The geometrically simplest way to change the relative size of different body parts would be by a conformal transformation.
+It seems plausible that this simplest solution will often be the most efficient, so that natural selection tend to choose it.'' (Milnor was thinking of 3D conformal transformations, whose restriction to 2D is the M\"obius transformations.)
+
+The 0th order moving frame translates $z$ to $\beta$.
+We can therefore take $\beta=0$; we are also free to take $\delta=1$.
+This leaves 4 group parameters $a,b,c,d$, where $\alpha = a + i b$, $\gamma = c + i d$, to be determined as follows.
+First we prolong the action to 3rd derivatives of $f$.
+There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 5 invariants.
+
+The prolonged action is:
+\begin{equation}
+\small
+\arraycolsep=1.4pt
+\left(
+\begin{array}{c}
+  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
+ \end{array}
+ \right)
+ = 
+\left(
+\begin{array}{ccccccccc}
+ a & b & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ -b & a & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ 2\mu & -2 \rho & a^2 & 2 a b & b^2 & 0 & 0 & 0 & 0 \\
+ 2 \rho & 2\mu & -a b & a^2\!-b^2 & a b & 0 & 0 & 0 & 0 \\
+ -2\mu & 2 \rho & b^2 & -2 a b & a^2 & 0 & 0 & 0 & 0 \\
+ -6 (2 b c d+a \lambda) & 6 (2 a c d-b\lambda) & 6 a \mu &
+  M_{64}  & -6 b \rho & a^3 & 3 a^2 b & 3 a b^2 & b^3 \\
+ -6 (2 a c d-b\lambda) & -6 (2 b c d+a \lambda) & M_{73}& M_{74} & 
+ M_{75} & -a^2 b & a^3\!-2 a b^2 & 2
+   a^2 b\!-b^3 & a b^2 \\
+ 6 (2 b c d+a \lambda) & -6 (2 a c d-b\lambda) & M_{83} & M_{84} & M_{85} & a b^2 & b^3\!-2
+   a^2 b & a^3\!-2 a b^2 & a^2 b \\
+ 6 (2 a c d-b\lambda) & 6 (2 b c d+a \lambda) & 6 b \mu & 
+  M_{94} & 6 a \rho & -b^3 & 3 a b^2 & -3 a^2 b & a^3 \\
+\end{array}
+\right)\left(
+\begin{array}{c}
+f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
+ \end{array}
+ \right).
+\label{eqn:mobius}
+ \end{equation}
+ where
+ \begin{equation*}
+ \small
+ \begin{array}{lll}
+M_{64}=-12abc+6d(a^2-b^2), & 
+M_{73}=4 d a^2+6 b c a-2 b^2 d, & 
+M_{74}=-6 c a^2+12 b d a+6 b^2 c, \\
+ M_{75}=-2 d a^2-6 b c a+4 b^2 d, &
+ M_{83}=2 c a^2-6 b d a-4 b^2 c, &
+ M_{84}=6 (d a^2+2 b c a-b^2 d),\\
+ M_{85}=-4 c a^2+6 b d a+2 b^2 c,& 
+ M_{94}= -12a b d + 6c(a^2-b^2),\\
+\lambda=d^2-c^2, & 
+\mu = b d - a c, & 
+\rho = b c + a d.
+\end{array}
+\end{equation*}
+
+The moving frame calculation now proceeds as follows.
+\begin{enumerate}
+\item The frame $\bar f_x=1$, $\bar f_y=0$ determines the group parameters
+$$ a = f_x/(f_i f_i),\quad b = f_y/(f_i f_i).$$
+
+\item The frame $\bar f_{xyy}=\bar f_{yy}=0$ determines the group parameters
+$$ c = (2 f_xf_yf_{xyy} - f_{xx}f_y^2 - f_{yy}f_x^2)/(2 f_i f_i)^2$$
+$$ d = (f_{xyy}f_x^2 - f_x f_y f_{xx} - f_{xyy}f_y^2 - f_{yy} f_x f_y)/(2 f_i f_i)^2.$$
+
+\item The 2nd order invariant is then given by $\bar f_{xx}$ using Equation~(\ref{eqn:mobius}); it is 
+$$\bar f_{xx} = \frac{f_{ii}}{f_i f_i}.$$
+
+\item The four 3rd order invariants are then given by $\bar f_{xxx},\dots, \barf_{yyy}$ using Equation~(\ref{eqn:mobius}). They are
+rational functions with numerators of degree 6 and denominators $(f_i f_i)^4$, and are relative invariants of weight 8.
+\end{enumerate}
+
+%It is clear that there must be 2 syzygies between the relative invariants $J_1,\dots,J_4,K_1,\dots,K_4$.
+%They are easily found algebraically to be
+%$$K_2 = -K_4 + J_1 J_4$$
+%and
+%$$K_3=-K_1 +J_1 J_3 + 2 J_1^2 J_2^2.$$
+
+We want to work with polynomials, and so clear denominators. We choose to use $M_1 = f^4_{ii}$ and two of the four 3rd order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where: 
+$M_2=
+f_y ^5 f_{yyy} + \frac{9}{2} f_y ^2 f_{yy}^2 f_x ^2 + 
+ f_y ^3 f_{yyy} f_x ^2 + \frac{3}{2} f_{yy}^2 f_x ^4 - 
+ 9 f_y ^3 f_{yy} f_x  f_{xy} + 
+ 3 f_y  f_{yy} f_x ^3 f_{xy} + \frac{3}{2} f_y ^4 f_{xy}^2 - 
+ 9 f_y ^2 f_x ^2 f_{xy}^2 + \frac{3}{2} f_z ^4 f_{xy}^2 + 
+ 3 f_y ^4 f_x  f_{xyy} + 3 f_y ^2 f_x ^3 f_{xyy} + 
+ 3 f_y ^4 f_{yy} f_{xx} + 3 f_{yy} f_x ^4 f_{xx} + 
+ 3 f_y ^3 f_x  f_{xy} f_{xx} - 
+ 9 f_y  f_x ^3 f_{xy} f_{xx} + \frac{3}{2} f_y ^4 f_{xx}^2 + 
+ \frac{9}{2} f_y ^2 f_x ^2 f_{xx}^2 + 3 f_y ^3 f_x ^2 f_{xxy} + 
+ 3 f_y  f_x ^4 f_{xxy} + f_y ^2 f_x ^3 f_{xxx} + 
+ f_x ^5 f_{xxx}, 
+ $
+
+ $M_3=-3 f_y  f_{yy}^2 f_x ^3 + 
+ f_y ^2 f_{yyy} f_x ^3 + f_{yyy} f_x ^5 + 
+ 9 f_y ^2 f_{yy} f_x ^2 f_{xy} - 
+ 3 f_{yy} f_x ^4 f_{xy} - 6 f_y ^3 f_x  f_{xy}^2 + 
+ 6 f_y  f_x ^3 f_{xy}^2 - 3 f_y ^3 f_x ^2 f_{xyy} - 
+ 3 f_y  f_x ^4 f_{xyy} - 3 f_y ^3 f_{yy} f_x  f_{xx} + 
+ 3 f_y  f_{yy} f_x ^3 f_{xx} + 3 f_y ^4 f_{xy} f_{xx} - 
+ 9 f_y ^2 f_x ^2 f_{xy} f_{xx} + 
+ 3 f_y ^3 f_x  f_{xx}^2 + 3 f_y ^4 f_x  f_{xxy} + 
+ 3 f_y ^2 f_x ^3 f_{xxy} - f_y ^5 f_{xxx} - 
+ f_y ^3 f_x ^2 f_{xxx}
+$
+
+The image $f$ and these 3 relative invariants of weight 8 provide a 3-dimensional signature; an example is shown in Figure~\ref{fig:mobius}, although note that it is singular when $f_x=f_y=f_{ii}=0$, a codimension 1 phenomenon for images.
+
+%In previous work \cite{mobius}, two independent 3rd order M\"obius invariants were calculated
+%from the classical M\"obius geometry of curves. Namely, the M\"obius arclength 
+%of a curve is $\sqrt{|\kappa_s|}ds$, were $ds$ is Euclidean arclength. Under any conformal map $\phi$,
+%both $ds$ and $1/\|\nabla f\|$ scale by $|\phi'|$. The sign of $\kappa_s$ is also  invariant,
+%hence $\kappa_s/\|\nabla f\|^2$ is  invariant for any invariant curve. Calculating this invariant
+%for the level sets of $f$ and for their orthogonal curves yields two invariants of $f$ that
+%we call $\lambda_t$ and $\lambda_n$, respectively. Writing 
+%them out in full and comparing to the invariants founds above shows that they are related very simply, by
+
+%$$ \frac{K_2}{\|\nabla f\|^8} = \lambda_t$$
+%$$\frac{K_4}{\|\nabla f\|^8} =\lambda_n$$
+
+%We do not know of any equivalent characterization of the invariants $K_1$, $K_3$ in
+%terms of classical M\"obius geometry.
+
+%We now have that
+%$$ (J_1^4, J_2^4, J_1 J_3, J_1 J_4, K_1, K_4)$$
+%are 6 relative invariants of weight 8. Projecting any subset to a sphere provides a M\"obius signature.
+%For example, the image $f$ together with the projection of $(J_1^4, J_2^4, K_1)$ provides a 3-dimensional signature.
+%Any such signature that includes $J_1$ and $J_2$ is
+
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/MobiusTransform_transform.png}
+\includegraphics[width=.45\textwidth]{Figs/MobiusTransform_signature.png}
+\caption{A sample M\"obius Transform and 3D signature.}
+\label{fig:mobius}
+\end{figure}
+
+\subsection{The Projective Group}
+
+We consider the 8-dimensional group $\mathrm{PSL}(3,\R)$ acting on $\R^2$ by projective transformations, i.e., $$(x,y) \mapsto \left(\frac{a x + b y + j}{l + g x + h y}, \frac{c x + d y + k}{l+ g x + h y}\right).$$
+
+The 0th order moving frame translates $(x,y)$ to $(0,0)$.
+We can therefore take $j=k=0$; we will also take $l=1$.
+This leaves 6 group parameters $(a,b,c,d,g,h)$ to be determined.
+First we prolong the action to 3rd derivatives of $f$.
+There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 3 invariants.
+
+The prolonged action is:
+\begin{equation}
+\tiny
+\arraycolsep=1.4pt
+\label{eq:prolong}
+\left(
+\begin{array}{c}
+  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
+ \end{array}
+ \right)
+ = 
+\left(
+\begin{array}{ccccccccc}
+ a & c & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ b & d & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ -2 a g & -2 c g & a^2 & 2 a c & c^2 & 0 & 0 & 0 & 0 \\
+ -b g-a h & -d g-c h & a b & b c+a d & c d & 0 & 0 & 0 & 0 \\
+ -2 b h & -2 d h & b^2 & 2 b d & d^2 & 0 & 0 & 0 & 0 \\
+ 6 a g^2 & 6 c g^2 & -6 a^2 g & -12 a c g & -6 c^2 g & a^3 & 3 a^2 c & 3 a c^2 & c^3 \\
+ 2 g (b g+2 a h) & 2 g (d g+2 c h) & -2 a (2 b g+a h) & -4 (b c g+a d g+a c h) & -2 c (2 d
+   g+c h) & a^2 b & a (2 b c+a d) & c (b c+2 a d) & c^2 d \\
+ 2 h (2 b g+a h) & 2 h (2 d g+c h) & -2 b (b g+2 a h) & -4 (b d g+b c h+a d h) & -2 d (d g+2
+   c h) & a b^2 & b (b c+2 a d) & d (2 b c+a d) & c d^2 \\
+ 6 b h^2 & 6 d h^2 & -6 b^2 h & -12 b d h & -6 d^2 h & b^3 & 3 b^2 d & 3 b d^2 & d^3 \\
+\end{array}
+\right)\left(
+\begin{array}{c}
+f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
+ \end{array}
+ \right).
+ \end{equation}
+
+First, recall from the analysis of the subgroup $A(2)$ that under $f\mapsto f\circ \phi$, $\phi\in A(2)$, we have 
+\begin{equation}
+\label{eq:D}
+D \mapsto (\det \phi')^2 D\circ \phi
+\end{equation}
+where $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$.
+
+A direct calculation using (\ref{eq:prolong}) shows that the same transformation rule (\ref{eq:D}) holds for $\phi\in\mathrm{PSL}(3,\R)$.
+That is, $D$ is a relative invariant of weight 2 of this action.
+From (\ref{eq:D}), the sign of $D$ is invariant and therefore the choice of moving frame must depend on the sign of $D$.
+
+\begin{enumerate}
+\item The frame $\bar f_x = 1$  determines the group parameter $$a = (1-c f_y)/f_x.$$
+\item The frame $\bar f_y=  0$ determines the group parameter $$b = -d f_y/f_x.$$
+\item Substituting this choice of $a$ and $b$ and examining the dependencies of $f_{xx}$, $f_{xy}$, $f_{yy}$, and $f_{yyy}$ on the remaining group parameters allows them to be solved sequentially, as follows.
+\item We have $\bar f_{yy} = d^2 D/f_x^2$; therefore if $D>0$ we choose the frame
+$\bar f_{yy} = 1$ and $$d = f_x/D^{1/2}.$$
+\item The frame $\bar f_{yyy} = 0$ determines the group parameter
+$$ h = \frac{d(f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2 f_{xxy} - f_y^3 f_{xxx})}{6 f_x D}.$$
+\item The frame $\bar f_{xyy}=0$ determines the group parameter
+$$ c = \frac{h f_x^2}{d D} - \frac{f_x f_{xy} - f_y f_{xx}}{D}.$$
+\item The frame $\bar f_{xx}=0$ determines the group parameter
+$$ g = \frac{1}{2 f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$$
+\end{enumerate}
+
+\todo[inline]{Need to get the Js from somewhere...}
+Having determined the frame, any function of the remaining derivatives $\bar f_{xxx}$, $\bar f_{xxy}$, and $\bar f_{yyy}$, as given in Equation~(\ref{eq:prolong}), provides invariants.
+We choose $$ (f_{xxx}, f_{xxy}^2, f_{xyy})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right)$$
+because these all have denominators given by integer powers  of $D$, resolving the issue caused
+by the sign of $D$. Therefore,
+$$ (D^{18}, J_1^3, J_2^2, J_3^6)$$
+are all relative invariants of weight 36; so projecting any subset of them of them to a sphere
+yields a 3rd order invariant signature.
+
+However, these signatures can be simplified and made more robust, as follows.
+
+The components of $J$ are polynomials of degree 16, 24, and 8, respectively, and are extremely complicated when written out explicitly.
+More seriously, $J$ vanishes on generic images.
+This can be seen as follows.
+Recall the $SA(2)$ invariant $E$ defined in (\ref{eq:E}).
+%Let
+%$$ E := f_{222}f_1^3 - 3 f_{122}f_1 f_2^2 + 3 f_{112}f_1^2 f_2 - f_{111}f_2^3$$
+Then the components of $J$ have the structure
+$$ J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5$$
+where the $P_n$ are polynomials of degree $n$. Therefore $J=0$ when $D=E=0$, which 
+is a codimension 0 phenomenon for images. In particular, $D=E=0$ at critical points.
+
+The structure of () suggests considering the combination $J_1 - J_3^2$ which turns out to obey
+$$J_1 - J_3^2 = 144 D^4 P_4.$$
+Therefore, as $J_1/D^6$ and $J_3/D^3$ are invariant, so is $P_4/D^2$. 
+Moreover, {\em the numerator of this new invariant does not vanish at critical points.} 
+It has the structure
+$$P_4 = -4(\det f_{ij})^2 + Q_4,$$
+where $Q_4$ is a polynomial of degree 4 that vanishes when $f_x=f_y=0$. In conclusion, the
+relative invariant of weight 12
+$$ (D^6, P_4^3, (E^2-12D P_5)^2)$$
+can be projected to $S^2$ yielding a projective invariant of images that
+is singular only when $D=E=P_4=0$, which is a codimension 1 phenomenon for images.
+(One can check that $D=E=0\Rightarrow P_4=0$.) In particular, at critical points it tends to
+$$ (0, (2\det f_{ij})^6, 0)$$
+and hence critical points with $\det f_{ij}\ne 0$ have signature $(0,1,0)$.
+
+For completeness we write out the invariants explicitly:
+
+$Q_4=4 f_x  f_{xy} ^2 f_{xyy}  - 
+f_x ^2 f_{xyy} ^2 - 
+ 2 f_{yyy}  f_x  f_{xy}  f_{xx}  + 
+ 2 f_{yy}  f_x  f_{xyy}  f_{xx}  - 
+ 6 f_{y}  f_{xy}  f_{xyy}  f_{xx}  + 
+ 2 f_{y}  f_{yyy}  f_{xx} ^2 + 
+ f_{yyy}  f_x ^2 f_{xxy}  - 
+ 6 f_{yy}  f_x  f_{xy}  f_{xxy}  + 
+ 4 f_{y}  f_{xy} ^2 f_{xxy}  + 
+ f_{y}  f_x  f_{xyy}  f_{xxy}  + 
+ 2 f_{y}  f_{yy}  f_{xx}  f_{xxy}  - 
+ f_{y} ^2 f_{xxy} ^2 + 
+ 2 f_{yy} ^2 f_x  f_{xxx}  - 
+ f_{y}  f_{yyy}  f_x  f_{xxx}  - 
+ 2 f_{y}  f_{yy}  f_{xy}  f_{xxx}  + f_{y} ^2 f_{xyy}  f_{xxx} $
+
+$P_5=f_{yyy}  f_{x} ^3 f_{xy}  - 
+f_{yy}  f_{x} ^2 f_{xy} ^2 + 
+ 2 f_{y}  f_{x}  f_{xy} ^3 - 
+ f_{yy}  f_{x} ^3 f_{xyy}  - 
+ f_{y}  f_{x} ^2 f_{xy}  f_{xyy}  + 
+ f_{yy} ^2 f_{x} ^2 f_{xx}  - 
+ f_{y}  f_{yyy}  f_{x} ^2 f_{xx}  - 
+ 2 f_{y}  f_{yy}  f_{x}  f_{xy}  f_{xx}  - 
+ f_{y} ^2 f_{xy} ^2 f_{xx}  + 
+ 2 f_{y} ^2 f_{x}  f_{xyy}  f_{xx}  + 
+ f_{y} ^2 f_{yy}  f_{xx} ^2 + 
+ 2 f_{y}  f_{yy}  f_{x} ^2 f_{xxy}  - 
+ f_{y} ^2 f_{x}  f_{xy}  f_{xxy}  - 
+ f_{y} ^3 f_{xx}  f_{xxy}  - 
+ f_{y} ^2 f_{yy}  f_{x}  f_{xxx}  + 
+ f_{y} ^3 f_{xy}  f_{xxx} $
+
+Including $J_2$ in addition provides a 4-dimensional signature set, but does not increase the codimension of the set of bad images.
+
+Further invariants can be found by noting that, for any planar transformation group and any two invariants
+$I^1$ and $I^2$, $\nabla I^1 \times \nabla I^2$ is a relative invariant of weight 1; that is,
+$$\nabla I^1 \times \nabla I^2\mapsto (\det \phi')(\nabla I^1 \times \nabla I^2).$$
+Applying this operation to $f$ and the 4 3rd order invariants yields $5\cdot4/2=1$0  4th order invariants.
+
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/PSL3RTransform_transform.png}
+\includegraphics[width=.45\textwidth]{Figs/PSL3RTransform_signature.png}
+\caption{A sample $PSL(3,\mathbb{R})$ Transform and 3D signature.}
+\label{fig:PSL3R}
+\end{figure}
 
@@
 
-\todo[inline]{Largely discursive? Except conformal.}
+Define diffeo here
+
+\subsection{Conformal Diffeomorphisms $\mathbf{Diff}_{\mathbf{con}}$}
+
+The group of conformal diffeomorphisms is the subgroup of diffeomorphisms that are angle-preserving, i.e.,
+
+\begin{equation}
+\angle (u,v) = \angle (D \phi(x) . u, D \phi(x).v)
+\end{equation}
+
+\noindent where $\angle(u, v)$ denotes the angle between tangent vectors $u$ and $v$ based at $x \in \mathbb{R}^2$, $\phi \in \Diff$ and $D$ represents the Jacobian.
+The group is infinite-dimensional, but still small enough that images have local differential invariants.
+
+The M\"obius action is locally identical to the full conformal group up to and including second order.
+Therefore, there are no new conformal invariants, apart from the M\"obius ones, up to second order.
+Rather than applying the method of moving frames (which has been extended to Lie pseduo-groups in~\cite{}), we perform a direct calculation using the defining geometric properties of the conformal group.
+
+At second order, we first consider the action of conformal maps on the Euclidean invariants $f_i f_i$ and $f_{ii}$.
+
+Let $\psi := \varphi^{-1}$. For any diffeomorphism, the derivatives of $f$ transform as
+$$f_i \mapsto f_j \psi^j_i$$
+and
+$$f_{ij} \mapsto f_{kl} \psi^k_i\psi^l_j + f_{k}\psi^k_{ij}.$$
+Therefore the Laplacian of $f$ transforms as
+$$ f_{ii} \mapsto f_{kl} \psi^k_i \psi^l_i + f_k \psi^k_{ii}.$$
+When $\psi=u + i v$ is conformal, $\psi_{k,ii}=0$ because the components of conformal maps are harmonic functions,
+and the Cauchy-Riemann equations give $\psi_{k,i}\psi_{l,i} = (u_x^2 + u_y^2)\delta_{kl}$. Therefore,
+$$ f_{ii} \mapsto f_{ii}(u_x^2+u_y^2).$$
+Here $u_x^2+u_y^2=\det\psi^k_i$ is the local scaling factor of the transformation.
+Note also that
+$$f_i f_i \mapsto f_k f_l \psi_{k,i} \psi_{l,i} = f_k f_k (u_x^2 + u_y^2).$$
+That is, $f_{ii}$ and $f_i f_i$ are both relative invariants of weight 2, while $f_{ii}/(f_i f_i)$ is a conformal invariant, as we saw for the M\"obius group.
+By itself, it is not useful for images as it is singular at critical points of $f$.
+
+At higher order,  representing $\psi(z) = a_0 + a_1 z + a_2 z^2 + \dots$ where $z=x+iy$ and $a_i\in \mathbb{C}$ shows that 2 real group parameters, $Re(a_n)$ and $Im(a_n)$, enter at order $n$.
+There are $n+1$ independent derivatives of $f$ of order $n$, so there must be at least $n-1$ independent invariants of order $n$.
+(For $n=2$, we have we have found the single invariant above.)
+
+The transformation of 1st derivatives is more clearly written in complex variables as $$ f_x + i f_y \mapsto a_1 (f_x + i f_y).$$ Given any two real invariants $g,h$, the real and imaginary parts of $(g_x+i g_y)(h_x-i h_y)$ are relative invariants of weight 2.
+This generates the required two invariants of order 3.
+(We have repeated and confirmed this calculation using the method of moving frames.) Specifically, let $J_1 = f_i f_i$ and  $J_2 = f_{ii}$, so that  $g = J_2/J_1$ is invariant.
+We want to work with polynomials, so we clear denominators and let $J_3+iJ_4 = J_1^2 (g_x + i g_y)  (f_x - i f_y)$.
+$J_3$ and $J_4$ are a differential polynomials of $f$ of degree 4 and order 3, and are relative invariants of weight 6.
+They can be written explicitly as functions of the basic invariants of $SE(2)$ as
+$$J_3 = f_k f_k f_{iij}f_j - 2 f_{ii} f_{jk} f_j f_k$$
+and (writing $a_i\times b_i$ for $a_1 b_2 - b_2 a_1$)
+$$ J_4 = f_k f_k f_{iij}\times f_j - 2 f_{ii} f_{jk} f_k\times f_j.$$
+Under conformal maps we have
+$$ (J_1,J_2,J_3,J_4) \mapsto (|a_1|^2 J_1, |a_1|^2 J_2, |a_1|^6 J_3,|a_1|^6 J_4).$$
+
+Therefore, projecting $(J_1^3,J_2^3,J_3)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^2$.
+It is continuous at all $(x,y)$ such that $J_1$, $J_2$, and $J_3$ are not simultaneously equal to zero.
+Now $J_1=0$ implies $f_1=f_2=0$, and $J_2=0$ implies $f_{ii}=0$, but these together imply $J_3=0$.
+Thus the signature set is discontinuous when $f_1=f_2=f_{ii}=0$, a codimension-1 phenomenon for images.
+
+Similarly, projecting $(J_1^3,J_2^3,J_3,J_4)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^3$.
+This is also singular when $f_1=f_2=f_{ii}=0$.
+These singularities are not removable.
+A typical image near a `bad' point takes the form $f = a(x^2-y^2) + b x y + c x^3 + d x^2 y + e x y^2 + g y^3$.
+For such an $f$, $(J_1^3,J_2^3,J_3,J_4)=\mathcal{O}(x^6,x^3,x^3,x^3)$.
+The cubic forms always change sign and do not generically lead to a well-defined direction as $(x,y)\to(0,0)$.
+
+\subsection{Volume-Preserving Diffeomorphisms $\mathbf{Diff_{vol}}$}
+
+The subgroup of volume-preserving diffeomorphisms are those diffeomorphisms that preserve the volume form, which in 2D is actually the area form.
+They can be defined by one function of two variables, the generating function $S$; one possibility is $S(x,y')$ where $(x,y)\mapsto(x',y')$ according to
+$$ x'=\frac{\partial S}{\partial y'},\quad y = \frac{\partial S}{\partial x}.$$
+
+Consider expanding $S$ in Taylor series.
+The linear terms in the map are determined from the quadratic terms in $S$, which contain 3 group parameters, and act on 2 coordinates, $f_x$ and $f_y$.
+The quadratic terms in the map are determined from the cubic terms in $S$, which contain 4 group parameters, and act on 3 coordinates, $f_{xx}$, $f_{xy}$, and $f_{yy}$.
+At order $n$ we have $n+2$ new group parameters acting on $n+1$ coordinates.
+Thus, barring some exceptional behaviour in the action, we do not expect any invariants at generic points.
+
+This can be confirmed by considering a small image patch with $f(x,y)=x.$ Let $v=\psi_y\partial/\partial_x - \psi_x\partial/\partial_y$ be the generator of an area-preserving map.
+The image $f$ transforms to $x + \varepsilon \psi_y(x,y)$ which (by choosing $\psi$ appropriately) can be any function close to $x$.
+
+At nongeneric points, there can be invariants.
+For example, the area enclosed in any level set of $f$ is invariant.
+At minima or maxima of $f$, this will lead to invariants expressed in terms of the derivatives of $f$.
+
+\subsection{Colour}
+
+Thus far we have only considered greyscale images.
+However, most images are three-channel colour (typically represented as RBG values), and multi-spectral images can have hundreds of channels of measurement.
+It then becomes natural to consider how to use this information in the computation of invariants.
+The hope is that by constructing invariants using different colour channels, fewer derivatives need to be computed.
+For $k$ colours, signature sets of dimension up to $k + k(k+1)/2$ can be chosen from the invariants $f^i$ and $f^i_m f^j_m$ for $i,j=1,\dots, k$.
+
+Note that for $k\ge 3$ the 3-dimensional signature $(f^1,f^2,f^3)$ is invariant under all local planar diffeomorphisms; a higher-dimensional signature, involving at least first derivatives, is therefore required.
+
+However, there is a complication, which is that the information in the channels is not independent: colour is built by the intensities in the three channels, and so it there is correlation between them.
+This means that the invariant signature identified next are na\"ive, and should be viewed as best-case scenarios.
+We briefly sketch some possibilities for some of the groups that we have considered earlier.
+
+Considering $E(2)$, for $k\ge 2$, first derivatives suffice. 
+For $SA(2)$,  we are seeking invariants of $k V_1 \oplus k V_2 \oplus \dots$.
+One can take transvectants of any components of $f$ to get invariants.
+For $k=2$ colours, there is only one  invariant formed from 1st derivatives, namely $((f^1)',(f^2)')_x = f^1_x f^2_y - f^1_y f^2_x$ (the Poisson bracket $\{f^1,f^2\}$).
+So again two derivatives are necessary, even for a 3-dimensional signature.
+
+For $k\ge 3$ colours, a new phenomenon enters.
+There are plenty of invariants formed from 1st derivatives, namely $\nabla f^i \times \nabla f^j$ for $i<j$.
+But these are all invariant under the bigger group $\mathrm{Diff}_{\mathrm{vol}}$ of local volume-preserving diffeomorphisms.
+So the Poisson brackets cannot form a complete invariant for $SA(2)$.
+Two derivatives are always needed no matter how many colours we have.
+The relation $SA(2)\subset \mathrm{Diff}_{\mathrm{vol}}$ acts an obstruction to $SA(2)$, an instance of the phenomenon of hidden symmetry.
+
+The same problem occurs with $A(2)$.
+There are plenty of invariants formed from two derivatives: already 9 when $k=2$.
+However, as with $SA(2)$, we can never get away with one derivative because all the 1-derivative invariants,such as $\{f^1,f^2\}/\{f^1,f^3\}$ are also invariant under $\mathrm{Diff}_{\mathrm{vol}}$ (even though $A(2)$ is not even a subgroup of $\mathrm{Diff}_{\mathrm{vo}l}$).
+
+Recall that M\"obius and conformal transformations cannot be distinguished by their action on second derivatives.
+Therefore at least 3 derivatives are needed, no matter how many colours we have.
+We can use, for example, the invariants arising from the curvature of the level sets of each colour.
+Replacing the relative invariant $\|\nabla f\|^2$ by $\sum_{j=1}^k \|\nabla f^j\|^2$, and $f_{ii}$ by $\sum_{j=1}^k (f^j_{ii})^2$, increases the codimension of the singular images from 1 to $3k-2$.
+
+In $PSL(3, \mathbb{R})$ for $2$-colour images, there are 3 second order relative invariants of weight 2, namely $(D_1,D_2,(\nabla f^1\times \nabla f^2)^2)$.
+Together with $(f^1,f^2)$, these yield a 4-dimensional $\mathbb{R}^2\times S^2$-valued signature using only 2nd derivatives.
+With $k>2$ colours there are many more 2nd order invariants; however, as the action of the projective group on 1st derivatives is indistinguishable from that of the full diffeomorphism group, it is not possible to have a 1st order signature that distinguishes projectively-related images from diffeomorphically-related ones.
+
+For the infinite-dimensional group $\Diff_{\mathrm{con}}$, first order signature sets are possible for $k \ge 2$ colours.
+They are formed from the relative invariants $(f^j_1 + i f^j_2)(f^m_1 - i f^m_2)$ of weight 2.
+We illustrate this using the Hopf fibration for $k=2$.
+The weight 2 relative invariant $$J = (2(f^1_1 + i f^1_2)(f^2_1 - i f^2_2), ||\nabla f^1\|^2 - \|\nabla f^2\|^2)$$ obeys $\|J\|^2 = \|\nabla f^1\|^2 + \|\nabla f^2\|^2$, hence projecting to the unit sphere shows that $(f^1,f^2,J/\|J\|)$ provides a 4-dimensional signature set that is singular only when $\nabla f^1 = \nabla f^2 = 0$, a codimension 2 phenomenon for images.
+
+When $k\ge 2$ in $\Diff_{\mathrm{vol}}$ there are $k(k-1)/2$ first-order invariants $ \nabla f^i \times \nabla f^j$.
+We consider the case $k=2$ and the 3-dimensional signature $$ (f^1,f^2, \nabla f^1 \times \nabla f^2).$$ This signature determines (generically and locally) the image up to an area-preserving map.
+We have seen that we can generically choose the area-preserving map so that $f^1=x$, and we assume that this has been done.
+The remaining freedom is that of the area-preserving maps that preserve $x$: these are the shears $y\mapsto y + g(x)$.
+The signature for each fixed $x$ now gives $(f^2,f^2_y)$.
+This is the standard signature curve for the group of translations in $y$.
+Thus, $f^2$ is determined by the signature up to a translation in $y$, i.e., an area-preserving map.
+
+In the full diffeomorphism group there are no differential invariants using 1 or 2 colours.
+For example, with $k=2$, for generic $f^1$, $f^2$ we can choose a diffeomorphism (i.e., choose local coordinates) so that $f^1=x$ and $f^2=y$.
+We therefore take $k\ge 3$.
+This provides the first order relative invariants of weight 1 $\nabla f^i\times \nabla f^j$, and hence a first order signature.
+However, a 0th order signature set is possible: $(f^1,\dots,f^k)$.
+This is the image of the image.
+It is (locally and generically) complete.
+We can choose coordinates so that $f^1=x$ and $f^2=y$; then the signature locally determines $f^3,\dots,f^k$ as functions of $f^1$ and $f^2$, i.e., the image.
 
@@
 
+\section{Discussion}
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{| l | c c c |}
+\hline
+\# derivs. & $k=1$ & $k=2$ & $k=3$ \\
+\hline
+SE(2) & 2 &1 & 1 \\
+E(2) & 2 & 1 & 1 \\
+Sim(2) & 2 & 1 & 1 \\
+SA(2) & 2 & 2 & 2 \\
+A(2) & 3 & 2 & 2 \\
+$\mathrm{PSL}(2,\mathbb{C})$ & 3 & 3 & 3 \\
+$\mathrm{PSL}(3,\R)$ & 3 & 2 & 2 \\
+$\mathrm{Diff}_{\mathrm{vol}}$ & -- & 1 & 1 \\
+$\mathrm{Diff}_{\mathrm{con}}$ & 3 & 1 & 1 \\
+$\mathrm{Diff}$ & -- & -- & 0 \\
+\hline
+\end{tabular}
+\caption{Number of derivatives of $f$ needed to construct a differential invariant signature of $f$ as a function of the group $G$ and the number of colours $k$ of $f$.
+The entry `--' indicates that there is no differential invariant signature in that case.}
+\end{center}
+\end{table}
+
 \end{document}

### 2019-08-22 paper/newpaper.tex
newpaper.tex

@@
 
-An algorithm to compute invariants and determine complete signature sets is described in \cite{olver2001}. First, the
-entire set of invariants is computed using the method of moving frames.
-Second, determine the differential invariant order $s$ of $f$.
-Then the signature set of a maximal set of functionally independent invariants of order $s+1$ is complete.
-A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
+An algorithm to compute invariants and determine complete signature sets is
+described in \cite{olver2001}. First, the entire set of invariants is
+computed using the method of moving frames. Second, determine the
+differential invariant order $s$ of $f$ \todo[inline]{we need to define the differential invariant order}. Then the signature set of a maximal
+set of functionally independent invariants of order $s+1$ is complete. A
+third step is possible, in which the dimension of the signature set is
+reduced by eliminating those invariants whose values can be computed from the
+values of derivatives of some subset of the invariants.
 
@@
 Is this helpful? 
+\todo[inline]{Yes, this is helpful but not quite correct yet - $SE(2)$ is missing, and we need edges from $\text{Diff}_{\text{vol}}$ to the special affine and Euclidean groups}
+\todo[inline]{Other notes: should our projective group be $PGL(3, \mathbb{R})$ rather than $PSL(3, \mathbb{R})$? or am I confused?}
 \begin{figure}

### 2019-09-03 paper/newpaper.tex
Included affine invariants in table

@@
 \usepackage{tikz}
+\usepackage{array}
 
@@
 
-The setting that we will consider is a transformation group $\mathcal{G}$ acting on a manifold $\mathcal{M}$ of dimension $n$.
-A $d$-th order differential invariant is a local scalar function $I: J^{d} (\mathbb{R}, \mathcal{M} ) \to \mathbb{R}$ that is invariant under the action of $\mathcal{G}$, i.e., $I(g(x,u^{(d)})) = I(x, u^{(d)}) \forall g \in \mathcal{G}$, where $J^{d}$ denotes the $d$-th order jet space.
+The setting that we will consider is a transformation group $\mathcal{G}$
+acting on a manifold $\mathcal{M}$ of dimension $n$. A $d$-th order
+differential invariant is a local scalar function $I: J^{d} (\mathbb{R},
+\mathcal{M} ) \to \mathbb{R}$ that is invariant under the action of
+$\mathcal{G}$, i.e., $I(g(x,u^{(d)})) = I(x, u^{(d)}) \forall g \in
+\mathcal{G}$, where $J^{d}$ denotes the $d$-th order jet space.
 
 ====
-Let $G$ be a (finite or infinite-dimensional) local planar transformation group. 
-A {\em $k$-colour image} is a triple $(f,\Omega,k)$ where $\Omega\subset\R^2$, $1\le k\in\mathbb{Z}$,
-and $f\colon\Omega\to\R^k$. The function $f$ will be taken to be as smooth as necessary.
-A transformation $\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) = (f\circ\varphi^{-1},\varphi(\Omega),k)$.
-(As we work locally, we will usually omit the domain $\Omega$; if the number of colours $k$ is not given, we assume $k=1$.)  A differential invariant is an invariant of the prolonged action of $G$ on the derivatives of $f$, i.e., a function $I$ of the values of $f$ and its derivatives at a point such that $I(f)(x,y) = I(\varphi\cdot f)(\varphi(x,y))$.
-An {\em $m$-dimensional signature set} is the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e.
-the
-set $\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$. 
-A signature set is complete for $f$ if it determines $f$ up to transformations from $G$, i.e.
-if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies there exists a transformation $\varphi\in G$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
+Let $G$ be a (finite or infinite-dimensional) local planar transformation
+group.  A {\em $k$-colour image} is a triple $(f,\Omega,k)$ where
+$\Omega\subset\R^2$, $1\le k\in\mathbb{Z}$, and $f\colon\Omega\to\R^k$. The
+function $f$ will be taken to be as smooth as necessary.  A transformation
+$\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) =
+(f\circ\varphi^{-1},\varphi(\Omega),k)$.  (As we work locally, we will
+usually omit the domain $\Omega$; if the number of colours $k$ is not
+given, we assume $k=1$.)  A differential invariant is an invariant of the
+prolonged action of $G$ on the derivatives of $f$, i.e., a function $I$ of
+the values of $f$ and its derivatives at a point such that $I(f)(x,y) =
+I(\varphi\cdot f)(\varphi(x,y))$. An {\em $m$-dimensional signature set} is
+the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e. the set
+$\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$.  A signature set is complete
+for $f$ if it determines $f$ up to transformations from $G$, i.e. if
+$\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies
+there exists a transformation $\varphi\in G$ such that $\tilde f =
+\varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
 
@@
 
-\begin{tabular}{cccc}
+\begin{tabular}{cm{1cm}cm{10cm}}
 \centering
@@
 2 & 2 &
-\begin{tikzpicture}
+\begin{tikzpicture}[baseline=0]
     \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
@@
 \end{tikzpicture}
-& $fxx$ \\
+& $2 f_{xx} f_{yy} - 2 \left(f_{xy}\right)^{2}$ \\
 
 2 & 2 &
-\begin{tikzpicture}
+\begin{tikzpicture}[baseline=0]
     \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
@@
 \end{tikzpicture}
-& $fxx$ \\
+& $\left(f_{x}\right)^{2} f_{yy} - 2 f_{x} f_{y} f_{xy} + f_{xx}
+\left(f_{y}\right)^{2}$ \\
 
 3 & 3 &
-\begin{tikzpicture}
+\begin{tikzpicture}[baseline=0]
     \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
@@
 \end{tikzpicture}
-& $fxx$ \\
+& $- f_{x} f_{xx} f_{yyy} - f_{x} f_{yy} f_{xxy} + 2 f_{x} f_{xy} f_{xyy} +
+f_{xx} f_{y} f_{xyy} + f_{xxx} f_{y} f_{yy} - 2 f_{y} f_{xy} f_{xxy}$ \\
+
+3 & 3 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+    \draw[-] (1) to (4);
+\end{tikzpicture}
+& $- \left(f_{x}\right)^{3} f_{yyy} + 3 \left(f_{x}\right)^{2} f_{y} f_{xyy} - 3 f_{x} \left(f_{y}\right)^{2} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3}$  \\
 
 3 & 4 &
-\begin{tikzpicture}
+\begin{tikzpicture}[baseline=0]
     \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
@@
 \end{tikzpicture}
-& $fxx$ \\
+& $2 f_{xx} f_{yyy} f_{xxy} - 2 f_{xx} \left(f_{xyy}\right)^{2} + 2 f_{xxx}
+f_{yy} f_{xyy} - 2 f_{xxx} f_{yyy} f_{xy} - 2 f_{yy}
+\left(f_{xxy}\right)^{2} + 2 f_{xy} f_{xyy} f_{xxy}$ \\
 
 %=====
-3 & 3 &
-\begin{tikzpicture}
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
-    \draw[-] (1) to (2);
-    \draw[-] (1) to (3);
-    \draw[-] (1) to (4);
-\end{tikzpicture}
-& $fxx$ \\
 
 3 & 4 &
-\begin{tikzpicture}
+\begin{tikzpicture}[baseline=0]
     \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
@@
 \end{tikzpicture}
-& $fxx$ \\
+& $- f_{x} f_{xx} f_{yy} f_{xyy} + f_{x} f_{xx} f_{yyy} f_{xy} - f_{x} f_{xxx} \left(f_{yy}\right)^{2} + 3 f_{x} f_{yy} f_{xy} f_{xxy} - 2 f_{x} \left(f_{xy}\right)^{2} f_{xyy} - \left(f_{xx}\right)^{2} f_{y} f_{yyy} - f_{xx} f_{y} f_{yy} f_{xxy} + 3 f_{xx} f_{y} f_{xy} f_{xyy} + f_{xxx} f_{y} f_{yy} f_{xy} - 2 f_{y} \left(f_{xy}\right)^{2} f_{xxy}$ \\
 
 2 & 4 &
-\begin{tikzpicture}
+\begin{tikzpicture}[baseline=0]
     \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
@@
 \end{tikzpicture}
-& $fxx$ \\
+& $2 \left(f_{xx}\right)^{2} \left(f_{yy}\right)^{2} - 4 f_{xx} f_{yy} \left(f_{xy}\right)^{2} + 2 \left(f_{xy}\right)^{4}$ \\
 
 3 & 4 &
-\begin{tikzpicture}
+\begin{tikzpicture}[baseline=0]
     \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
@@
 \end{tikzpicture}
-& $fxx$ \\
+& $2 \left(f_{x}\right)^{2} f_{yyy} f_{xxy} - 2 \left(f_{x}\right)^{2} \left(f_{xyy}\right)^{2} - 2 f_{x} f_{xxx} f_{y} f_{yyy} + 2 f_{x} f_{y} f_{xyy} f_{xxy} + 2 f_{xxx} \left(f_{y}\right)^{2} f_{xyy} - 2 \left(f_{y}\right)^{2} \left(f_{xxy}\right)^{2}$ \\
 
@@
 2 & 4 &
-\begin{tikzpicture}
+\begin{tikzpicture}[baseline=0]
     \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
@@
 \end{tikzpicture}
-& $fxx$ \\
+& $\left(f_{x}\right)^{2} f_{xx} \left(f_{yy}\right)^{2} - \left(f_{x}\right)^{2} f_{yy} \left(f_{xy}\right)^{2} - 2 f_{x} f_{xx} f_{y} f_{yy} f_{xy} + 2 f_{x} f_{y} \left(f_{xy}\right)^{3} + \left(f_{xx}\right)^{2} \left(f_{y}\right)^{2} f_{yy} - f_{xx} \left(f_{y}\right)^{2} \left(f_{xy}\right)^{2}$ \\
 
 3 & 4 &
-\begin{tikzpicture}
+\begin{tikzpicture}[baseline=0]
     \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
@@
 \end{tikzpicture}
-& $fxx$ \\
+& $- \left(f_{x}\right)^{3} f_{yy} f_{xyy} + \left(f_{x}\right)^{3} f_{yyy} f_{xy} - \left(f_{x}\right)^{2} f_{xx} f_{y} f_{yyy} + 2 \left(f_{x}\right)^{2} f_{y} f_{yy} f_{xxy} - \left(f_{x}\right)^{2} f_{y} f_{xy} f_{xyy} + 2 f_{x} f_{xx} \left(f_{y}\right)^{2} f_{xyy} - f_{x} f_{xxx} \left(f_{y}\right)^{2} f_{yy} - f_{x} \left(f_{y}\right)^{2} f_{xy} f_{xxy} - f_{xx} \left(f_{y}\right)^{3} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3} f_{xy}$ \\
 
 4 & 4 &
-\begin{tikzpicture}
+\begin{tikzpicture}[baseline=0]
     \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
@@
 \end{tikzpicture}
-& $fxx$ \\
+& $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\
 \end{tabular}
@@
 \centering
-\includegraphics[width=.45\textwidth]{Figs/SE2Transform_transform.png}
-\includegraphics[width=.45\textwidth]{Figs/SE2Transform_signature.png}
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_SE2.png}
+\includegraphics[width=.45\textwidth]{Figs/SE2_signature.png}
 \caption{A sample $SE(2)$ Transform and 3D signature.}
@@
 \centering
-\includegraphics[width=.45\textwidth]{Figs/E2Transform_transform.png}
-\includegraphics[width=.45\textwidth]{Figs/E2Transform_signature.png}
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_E2.png}
+\includegraphics[width=.45\textwidth]{Figs/E2_signature.png}
 \caption{A sample $E(2)$ Transform and 3D signature.}
@@
 \centering
-\includegraphics[width=.45\textwidth]{Figs/SA2Transform_transform.png}
-\includegraphics[width=.45\textwidth]{Figs/SA2Transform_signature.png}
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_SA2.png}
+\includegraphics[width=.45\textwidth]{Figs/SA2_signature.png}
 \caption{A sample $SA(2)$ Transform and 3D signature.}
@@
 \centering
-\includegraphics[width=.45\textwidth]{Figs/A2Transform_transform.png}
-\includegraphics[width=.45\textwidth]{Figs/A2Transform_signature.png}
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_A2.png}
+\includegraphics[width=.45\textwidth]{Figs/A2_signature.png}
 \caption{A sample $A(2)$ Transform and 3D signature.}
@@
 \begin{equation}
-\small
 \arraycolsep=1.4pt
@@
  \begin{equation*}
- \small
  \begin{array}{lll}
@@
 
-\item The four 3rd order invariants are then given by $\bar f_{xxx},\dots, \barf_{yyy}$ using Equation~(\ref{eqn:mobius}). They are
+\item The four 3rd order invariants are then given by $\bar f_{xxx},\dots, \bar f_{yyy}$ using Equation~(\ref{eqn:mobius}). They are
 rational functions with numerators of degree 6 and denominators $(f_i f_i)^4$, and are relative invariants of weight 8.
@@
 \centering
-\includegraphics[width=.45\textwidth]{Figs/MobiusTransform_transform.png}
-\includegraphics[width=.45\textwidth]{Figs/MobiusTransform_signature.png}
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_Mobius.png}
+\includegraphics[width=.45\textwidth]{Figs/Mobius_signature.png}
 \caption{A sample M\"obius Transform and 3D signature.}
@@
 \begin{equation}
-\tiny
 \arraycolsep=1.4pt
@@
 This can be seen as follows.
-Recall the $SA(2)$ invariant $E$ defined in (\ref{eq:E}).
+Recall the $SA(2)$ invariant $E$ defined in \todo[inline]{somewhere}
+
 %Let
@@
 \centering
-\includegraphics[width=.45\textwidth]{Figs/PSL3RTransform_transform.png}
-\includegraphics[width=.45\textwidth]{Figs/PSL3RTransform_signature.png}
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_PSL3R.png}
+\includegraphics[width=.45\textwidth]{Figs/PSL3R_signature.png}
 \caption{A sample $PSL(3,\mathbb{R})$ Transform and 3D signature.}
@@
 \section{Extension to larger groups, role of colour, etc.}
+\label{sec:aaah}
 
@@
 
-\noindent where $\angle(u, v)$ denotes the angle between tangent vectors $u$ and $v$ based at $x \in \mathbb{R}^2$, $\phi \in \Diff$ and $D$ represents the Jacobian.
-The group is infinite-dimensional, but still small enough that images have local differential invariants.
+\noindent where $\angle(u, v)$ denotes the angle between tangent vectors
+$u$ and $v$ based at $x \in \mathbb{R}^2$, $\phi \in \textrm{Diff}$ and $D$
+represents the Jacobian. The group is infinite-dimensional, but still small
+enough that images have local differential invariants.
 
@@
 
-For the infinite-dimensional group $\Diff_{\mathrm{con}}$, first order signature sets are possible for $k \ge 2$ colours.
+For the infinite-dimensional group $\mathrm{Diff}_{\mathrm{con}}$, first order signature sets are possible for $k \ge 2$ colours.
 They are formed from the relative invariants $(f^j_1 + i f^j_2)(f^m_1 - i f^m_2)$ of weight 2.
@@
 
-When $k\ge 2$ in $\Diff_{\mathrm{vol}}$ there are $k(k-1)/2$ first-order invariants $ \nabla f^i \times \nabla f^j$.
+When $k\ge 2$ in $\mathrm{Diff}_{\mathrm{vol}}$ there are $k(k-1)/2$ first-order invariants $ \nabla f^i \times \nabla f^j$.
 We consider the case $k=2$ and the 3-dimensional signature $$ (f^1,f^2, \nabla f^1 \times \nabla f^2).$$ This signature determines (generically and locally) the image up to an area-preserving map.

### 2019-09-05 paper/newpaper.tex
Minor improvements...

@@
 
-Is this helpful? 
-\todo[inline]{Yes, this is helpful but not quite correct yet - $SE(2)$ is missing, and we need edges from $\text{Diff}_{\text{vol}}$ to the special affine and Euclidean groups}
-\todo[inline]{Other notes: should our projective group be $PGL(3, \mathbb{R})$ rather than $PSL(3, \mathbb{R})$? or am I confused?}
 \begin{figure}
 \begin{center}
-\begin{tikzpicture}[node distance=1.5cm]
+\begin{tikzpicture}[node distance=2cm]
 \node(C1) [] {Diff};
@@
 \node(C3) [below right of=C1] {$\mathrm{Diff}_{\mathrm{con}}$};
-\node(A1) [below right of=C3]                          {$PSL(2,\mathbb{C})$};
-\node(B1)    [below of=C2]    {$PSL(3,\mathbb{R})$};
+\node(B1)    [below of=C1]    {$PSL(3,\mathbb{R})$};
+\node(A1) [below of=C3]                          {$PSL(2,\mathbb{C})$};
 \node(B2)   [below of=B1]              {$A(2)$};
-\node(A2)       [below left of=A1]          {Sim$(2)$};
-\node(A3)      [right of=A2]              {$PSL(2,\mathbb{R})$};
-\node(B3)   [below of=B2]            {$SA(2)$};
+\node(A2)       [below right of=B2]          {Sim$(2)$};
+%\node(A3)      [right of=A2]              {$PSL(2,\mathbb{R})$};
+\node(B3)   [below left of=B2]            {$SA(2)$};
 \node(A4)      [below of=A2]            {$E(2)$};
-\node(A5) [below right of=A4]{Translation};
+\node(A6)      [below left of=A4]            {$SE(2)$};
+\node(A5) [below of=A6]{$T(2)$};
 
@@
 \draw[thick,->] (C1) to  (C3);
+\draw[thick,->] (C1) to  (B1);
+\draw[thick,->] (C2) to  (B3);
 %\draw[thick,->] (C1) to  (A2);
@@
 \draw[thick,->] (A1)   to (A2);
-\draw[thick,->] (A1)    to (A3);
 \draw[thick,->] (B1) to  (B2);
 \draw[thick,->] (B2) to  (B3);
+\draw[thick,->] (B2) to  (A2);
 \draw[thick,->] (A2) to  (A4);
-\draw[thick,->] (B3) to  (A4);
-\draw[thick,->] (A3) to  (A5);
-\draw[thick,->] (A4) to  (A5);
+\draw[thick,->] (B3) to  (A6);
+\draw[thick,->] (A4) to  (A6);
+\draw[thick,->] (A6) to  (A5);
 \end{tikzpicture}
@@
 \begin{enumerate}
-\item $f_if_i=\|\nabla f\|^2$ is the Lagrangian density for the Laplacian;
-\item $f_{ii}$ is the Laplacian, which plays a key role in Euclidean and conformal geometry;
-\item $f_{ij}f_i f_j$ is the `infinity-Laplacian'; critical points of $\|\nabla f\|_{L^\infty}$ obey the PDE $f_{ij}f_i f_j=0$;
-\item
-$f_{ij}f_i f_j$ is also a Lagrangian density for $-2\det f_{ij}$, which arises in Monge--Amp\`ere equations and
-which can be written in terms of the final 2nd order invariant as $-2 \det f_{ij} = f_{ij}f_{ij}-f_{ii}^2$.
+\item $f_x^2 + f_y^2=\|\nabla f\|^2$ is the Lagrangian density for the Laplacian;
+\item $f_{xx} + f_{yy}$ is the Laplacian, which plays a key role in Euclidean and conformal geometry;
+\item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is the `infinity-Laplacian'; 
+\item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is also a Lagrangian density for $-2(f_{xx} f_{yy} - f_{xy}^2)$, which arises in the Monge--Amp\`ere equations and
+can be written in terms of the final 2nd order invariant as $-2 (f_{xx} f_{yy} - f_{xy}^2) = 2 f_{xy}^2 - f_{xx}^2 - f_{yy}^2$
 \end{enumerate}
@@
 
-Olver uses the group $SE(2)$ as an example~\cite{Olver}, recovering the Euclidean curvature as a second-order invariant.
+Olver uses the group $SE(2)$ on curves as an example~\cite{Olver}, recovering the Euclidean curvature as a second-order invariant.
 We demonstrate the method with two groups: the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).
@@
 There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 5 invariants.
+\todo[inline]{General thm for this earlier...}
 
@@
 \item The frame $\bar f_x=1$, $\bar f_y=0$ determines the group parameters
-$$ a = f_x/(f_i f_i),\quad b = f_y/(f_i f_i).$$
+$$ a = f_x/(f_x^2 + f_y^2),\quad b = f_y/(f_x^2 f_y^2).$$
 
-\item The frame $\bar f_{xyy}=\bar f_{yy}=0$ determines the group parameters
-$$ c = (2 f_xf_yf_{xyy} - f_{xx}f_y^2 - f_{yy}f_x^2)/(2 f_i f_i)^2$$
-$$ d = (f_{xyy}f_x^2 - f_x f_y f_{xx} - f_{xyy}f_y^2 - f_{yy} f_x f_y)/(2 f_i f_i)^2.$$
+\item The frame $\bar f_{xy}=\bar f_{yy}=0$ determines the group parameters
+$$ c = (2 f_xf_yf_{xyy} - f_{xx}f_y^2 - f_{yy}f_x^2)/(2 f_x^2 + f_y^2)^2$$
+$$ d = (f_{xy}f_x^2 - f_x f_y f_{xx} - f_{xy}f_y^2 - f_{yy} f_x f_y)/(2 f_x^2 + f_y^2)^2.$$
 
 \item The 2nd order invariant is then given by $\bar f_{xx}$ using Equation~(\ref{eqn:mobius}); it is 
-$$\bar f_{xx} = \frac{f_{ii}}{f_i f_i}.$$
+$$\bar f_{xx} = \frac{f_{xx}+f_{yy}}{f_x^2 + f_y^2}.$$
 
 \item The four 3rd order invariants are then given by $\bar f_{xxx},\dots, \bar f_{yyy}$ using Equation~(\ref{eqn:mobius}). They are
-rational functions with numerators of degree 6 and denominators $(f_i f_i)^4$, and are relative invariants of weight 8.
+rational functions with numerators of degree 6 and denominators $(f_x^2 + f_y^2)^4$, and are relative invariants of weight 8.
 \end{enumerate}

### 2019-09-11 paper/newpaper.tex
minor

@@
 It has a long history, as summarised in \cite{Olver14}; particularly noteworthy contributions are by Cartan~\cite{Cartan37} and Olver and co-authors; see~\cite{Olver14} for an overview, and note particularly for an application to~\cite{Calabi98}.
-The method is described in detail in~\cite{OlverCIT}r.
+The method is described in detail in~\cite{OlverCIT}.
 
@@
 Olver uses the group $SE(2)$ on curves as an example~\cite{Olver}, recovering the Euclidean curvature as a second-order invariant.
-We demonstrate the method with two groups: the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).
+As an example, we use it to compute invariants to $SE(2)$ on the plane, before moving on to two other planar Lie group examples: the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).
+
+\subsection{$SE(2)$}
+
+Ignoring translation, the action of $SE(2)$ is simply rotation by some angle $\theta$, i.e.,
+
+\begin{equation}
+\left( \begin{array}f_x \\ f_y \end{array} \right) = \left( \begin{array} \cos \theta & \sin \theta \\ - \sin \theta & \cos \theta \end{array} \right) \left( \begin{array} \bar f_{\bar x} \\ \bar f_{\bar y} \end{array} \right).
+\end{equation}
+
+Using $c$ for $\cos \theta$ and $s$ for $\sin \theta$ and prolonging the group to second order via the chain rule gives:
+
+\begin{equation}
+\arraycolsep=1.4pt
+\left(
+\begin{array}{c}
+  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} 
+ \end{array}
+ \right)
+ = 
+\left(
+\begin{array}{ccccc}
+ c & -s & 0 & 0 & 0 \\
+ s & c & 0 & 0 & 0 \\
+0 & 0 & c^2 & -2cs & s^2 \\
+0 & 0 & cs & c^2 - s^2 & -cs \\
+0 & 0 & s^2 & 2cs & c^2 \\
+\end{array}
+\right)\left(
+\begin{array}{c}
+f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} 
+ \end{array}
+ \right).
+\label{eqn:SE2}
+ \end{equation}
+
+As $SE(2)$ does not include scaling, lengths stay the same, and so an appropriate choice for first-order normalisation is $\bar f_x = \sqrt(f_x^2 + f_y^2),\:\: \bar f_y = 0$, which sets $c = f_x / \| \nabla f \|$, $s = - f_y / \| \nabla f \|$.
+This provides the invariant $I_1 = \nabla f$.
+As there are no more free parameters, the expressions for the second-order terms can be read off as:
+
+\begin{align}
+I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} \\
+I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) \\
+I_4 &= f_x^2 f_{xx} - 2 f_x f_y f_{xy} + f_y^2 f_{yy} \\
+\end{align}
+
+However, summing $I_2$ and $I_4$ we can write the expression as $f_x^2 f_{xx} + f_y^2 f_{yy}$.
+Which is the product of 2 invariants in Einstein summation, but a pain in the arse any other way.
+But I can't see how else to get $f_{ii}$!
 

### 2019-09-11 paper/newpaper.tex
now with compilation

@@
 \begin{equation}
-\left( \begin{array}f_x \\ f_y \end{array} \right) = \left( \begin{array} \cos \theta & \sin \theta \\ - \sin \theta & \cos \theta \end{array} \right) \left( \begin{array} \bar f_{\bar x} \\ \bar f_{\bar y} \end{array} \right).
+\left( \begin{array}{c} f_x \\ f_y \end{array} \right) = \left( \begin{array}{cc} \cos \theta & \sin \theta \\ - \sin \theta & \cos \theta \end{array} \right) \left( \begin{array}{c} \bar f_{\bar x} \\ \bar f_{\bar y} \end{array} \right).
 \end{equation}

### 2019-11-06 paper/newpaper.tex
Morning's work

@@
 \title{Differential invariant signatures for planar Lie group transformations of images}
-\author{Not-working authors}
+\author{Not-working authors }
 
@@
 \section{Introduction}
+\todo[inline]{Examples to be numbered like theorems}
 \todo[inline]{This is a start. To be completed later.}
@@
 
-Following the treatment in~\cite{OlverCIT}, this leads to Cayley's Omega Process~\cite{Cayley}. We will demonstrate this for the affine group $A(2)$ and its subgroup $SA(2)$.
+We will demonstrate this for the affine group $A(2)$ and its subgroup
+$SA(2)$ where, following the treatment in~\cite{OlverCIT}, this leads to
+Cayley's Omega Process~\cite{Cayley}.
 
-Consider $\mathbf{x}_i \in \mathbb{R}^2, i=1,2$, so that $\mathbf{x}_i$ can be written in coordinates as $(x_i, y_i)$.
+Consider $\mathbf{x}_i \in \mathbb{R}^2, i=1,2$, so that $\mathbf{x}_i$ can
+be written in coordinates as $(x_i, y_i)$.
 Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$.
-Now consider applying an affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + b$ where $A \in GL(2,\mathbb{R}$ and $b \in \mathbb{R}^2$.
+Now consider applying the same affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + b$ where $A \in GL(2,\mathbb{R}$ and $b \in \mathbb{R}^2$.
 Then the Omega Process is a second-order differential operator defined by:
-
 \begin{equation}
-\Omega_{ij} = \begin{vmatrix} \frac{\partial}{\partial x_i} & \frac{\partial}{\partial y_i} \\ \frac{\partial}{\partial x_j} & \frac{\partial}{\partial y_j} \end{vmatrix}  = \frac{\partial^2}{\partial x_i \partial y_j} - \frac{\partial^2}{\partial x_j \partial y_i}.
+\Omega_{ij} = \begin{vmatrix} \frac{\partial}{\partial x_i} &
+\frac{\partial}{\partial y_i} \\ \frac{\partial}{\partial x_j} &
+\frac{\partial}{\partial y_j} \end{vmatrix} = 
+\frac{\partial^2}{\partial x_i
+\partial y_j} - \frac{\partial^2}{\partial x_j \partial y_i}.
 \end{equation}
@@
 Under the above affine transformation, $\Omega_{ij} \mapsto \det A^{-1} \Omega_{ij}$. Note that $\det A^{-1}$ has no dependence on the coordinates. 
-
-The Omega Process can be applied to pairs of smooth functions as follows:
+The Omega Process can be applied to pairs of smooth functions as follows, writing $\frac{\partial f}{\partial x}$ as $f_x$:
 
 \begin{equation}
-\Omega_{ij} f(x_i, y_i) g(x_j, y_j) = ...
+\Omega_{ij} f(x_i, y_i) g(x_j, y_j) = f_{x_i}g_{y_j} - f_{y_i}g_{x_j}
 \end{equation}
@@
 
-\noindent where $mbox{tr}$  is the operator that identifies the coordinates of each function $x_i = x_j = x, y_i = y_j = y$.
+\noindent where $\mbox{tr}$  is the operator that identifies the coordinates of each function $x_i = x_j = x, y_i = y_j = y$.
 
-This can be generalised to $n$ functions and $r-$th order~\cite{Olver} as:
+This can be generalised to $n$ functions $f^{(1)}(x_1, y_1), \ldots, f^{(n)}(x_n, y_n)$ and $r$-th order~\cite{Olver} to define a partial transvectant as:
 
 \begin{equation}
-\mbox{tr} \left( \Pi_{k=1}^r \Omega_{i_k j_k} \right) f_1(x_1, y_1) f_2(x_2, y_2), \ldots f_n (x_n, y_n)
+\mbox{tr} \left[\left( \Pi_{k=1}^r \Omega_{i_k j_k} \right) f^{(1)}(x_1, y_1)
+f^{(2)}(x_2, y_2), \ldots f^{(n)} (x_n, y_n)\right]
 \end{equation}
+where $i_k \neq j_k \in \{1, \ldots, n\}$.
 
-Under this formula we end with a factor $\det A^{-r}$ in place of $\det A^{-1}$ that we saw previously.
-$r$ is referred to as the weight of the partial transvectant.
-It can also be useful to consider the maximum number of derivatives computed, which we term degree, e.g., $f_{xy}^2 f_x f_y$ has degree 2.
-For the current case it is sufficient to consider $n$ copies of the same function $f$.
+Under this formula we end with a factor $\det A^{-r}$ in place of $\det
+A^{-1}$ that we saw previously, when all $n$ copies of $\mathbb{R}^2$ are
+transformed by the same affine function $\mathbf{x} \mapsto A\mathbf{x} +
+\mathbf{b}$. $r$ is referred to as the weight of the partial
+transvectant. It can also be useful to consider the maximum order of
+derivative in the transvectant, which we term degree, e.g., $f_{xy}^2 f_x
+f_y$ has degree 2. Note also that the individual pairwise Omega processes commute.
 
-This formula can be applied to generate partial transvectants, as we will now show for the action of two groups: $A(2)$ itself, and its subgroup $SA(2)$.
+For the current case it is sufficient to consider $n$ copies of the same
+function $f$. If we represent each copy (of $\mathbb{R}^2$) as a node on a
+undirected graph, and each Omega process $\Omega_{ij}$ as an edge joining
+nodes $i$ and $j$, a partial transvectant can be compactly represented in a
+graphical form.
 
-\todo[inline]{Start here... write out some bits.}
-
-Then computations.
-
-Then the graphs and the weights.
-
-\begin{tabular}{cm{1cm}cm{10cm}}
+For example, consider a weight $2$ transvectant defined as
+\begin{align*}
+    \mbox{tr} &\left[(\Omega_{12}\Omega_{12}) f(x_1, y_1)f(x_2, y_2)\right] \\
+    &= \mbox{tr}\left[(\partial_{x_1 y_2} - \partial_{x_2y_1})(\partial_{x_1 y_2} -
+    \partial_{x_2y_1})f(x_1, y_1)f(x_2, y_2)\right]\\
+    &= \mbox{tr}\left[\left(\partial_{x_1 y_2} - \partial_{x_2 y_1}\right)\left(f_x(x_1, y_1)f_y(x_2, y_2) - f_y(x_1, y_1)f_x(x_2, y_2)\right)\right] \\
+    &= \mbox{tr}\left[f_{xx}(x_1, y_1)f_{yy}(x_2, y_2) - f_{xy}(x_1, y_1)f_{xy}(x_2, y_2)\right] \\
+    &= f_{xx}(x, y) f_{yy}(x, y) - f_{xy}(x, y)^2
+\end{align*}
+This is a degree $2$ partial transvectant as it involves derivatives of $f$
+up to second order, and can be represented graphically by the following
+diagram,
+\begin{center}
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
+    \draw[-] (1) to [out=30,in=150] (2);
+    \draw[-] (1) to [out=-30,in=-150] (2);
+\end{tikzpicture}
+\end{center}
+where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$.
+Table~\ref{tab:transvectants} shows all possible nonzero partial
+transvectants of $A_2$ up to weight $4$ that can be generated in this way.
+Note that the weight is the number of edges in the graph.
+\begin{table}
 \centering
-Degree & Weight & Diagram & Invariant \\
+\begin{tabular}{cccp{11cm}}
+Degree & Weight & Diagram & Partial transvectant\\
 \hline
@@
 \end{tabular}
+\caption{Details and graphical representations of all partial transvectants up to weight $4$ of copies of a function $f$ under a transformation in $A(2)$.}
+\label{tab:transvectants}
+\end{table}
+
+\subsection{Signatures of $SA(2)$ and $A(2)$}
+Recall that invariants of a supergroup are automatically invariants of any of
+its subgroups.
+For example, invariants of $A(2)$ are automatically invariants of $SA(2)$, but not necessarily vice versa.
+Any of the partial transvectants found in Table~\ref{tab:transvectants} are invariants of $SA(2)$ (as the determinant is $1$) but only up to scale factor ($\det A^{-r}$) of $A(2)$.
+
+Hence, we can form a signature for $SA(2)$ by choosing any combination of
+partial transvectants. We'll choose a signature with three components so that
+it can be visualised as a three-dimensional surface; note that this will not
+be complete and may well have a \emph{very large bad set}. For example, we can choose the function value together with the first two partial transvectants to form the signature
+\begin{equation*}
+    \left(f, f_{xx}f_{yy}-f_{xy}^2, f_x^2f_{yy} - 2f_xf_yf_{xy} + f_{xx}f_y^2\right)
+\end{equation*}
+
+\subsubsection{Example}
+Consider as our image, the function $f(x, y) = 0.5 - 0.2x - 0.3y - 0.05x^2 +
+0.03xy + 0.04y^2 + 0.03y^3 +0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3$
+defined on $[0, 1]\times[0, 1]$.
+\todo[inline]{remake figure with modified matrix. Also modify function so it has some features like a critical point}
+We'll subject our image to a special affine transformation:
+\begin{equation*}
+\mathbf{x} \mapsto \frac{1}{1.1}\begin{bmatrix} 0.6875 & 1.1 \\ -0.6 & 0.8 \end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
+\end{equation*}
+Fig.~\ref{fig:SA2} shows the function as a greyscale image, the transformed
+function, and the signatures of both the untransformed and transformed
+images.
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_SA2.png}
+\includegraphics[width=.45\textwidth]{Figs/SA2_signature.png}
+\caption{\todo[inline]{add extra crap} A sample $SA(2)$ Transform and 3D signature. Mention what's going on with the grid.}
+\label{fig:SA2}
+\end{figure}
+
+\subsubsection{Moving on to $A(2)$, \ldots}
+Using the same function as an example, 
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_A2.png}
+\includegraphics[width=.45\textwidth]{Figs/A2_signature.png}
+\caption{A sample $A(2)$ Transform and 3D signature.}
+\label{fig:A2}
+\end{figure}
+
+\todo[inline]{visual obstruction}
 
@@
 \label{fig:E2}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.45\textwidth]{Figs/f_transformed_SA2.png}
-\includegraphics[width=.45\textwidth]{Figs/SA2_signature.png}
-\caption{A sample $SA(2)$ Transform and 3D signature.}
-\label{fig:SA2}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.45\textwidth]{Figs/f_transformed_A2.png}
-\includegraphics[width=.45\textwidth]{Figs/A2_signature.png}
-\caption{A sample $A(2)$ Transform and 3D signature.}
-\label{fig:A2}
 \end{figure}

### 2019-11-06 paper/tmp.tex
clipboard

Using the same function as our image.

For $A(2)$ the weight of the partial transvectants prevents them from being invariants. They can be normalised by choosing only those where all components have the same weight and projecting them onto a unit hypersphere. Instead, we select ratios of partial transvectants. It is beneficial to choose the numerator and denominator so that they have different critical points, which can be achieved by adding together partial transvectants of the same weight as appropriate.

### 2019-11-06 paper/newpaper.tex
Now with some real words...

@@
 & $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\
+
+4 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
+    \draw[-] (1) to [out=30,in=150] (2);
+    \draw[-] (1) to [out=-30,in=-150] (2);
+    \draw[-] (1) to [out=10,in=170] (2);
+    \draw[-] (1) to [out=-10,in=-170] (2);
+\end{tikzpicture}
+& $f_{xxxx} f_{yyyy} - 4 f_{xyyy} f_{xxxy} + 3 f_{xxyy}^2$ \\
+
+4 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to [out=-90,in=150] (3);
+    \draw[-] (1) to [out=-30,in=90] (3);
+\end{tikzpicture}
+& $ f_{xx}^2 f_{yyyy} + 2 f_{xx} f_{yy} f_{xxyy} - 4 f_{xx} f_{xy} f_{xyyy} - 4 f_{yy} f_{xy} f_{xxxy} + 4 f_{xy}^2 f_{xxyy} + f_{xxxx} f_{yy}^2$ \\
+
+4 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+\end{tikzpicture} 
+& $ f_{x} f_{xxx} f_{yyyy} - f_x f_{yyy} f_{xxxy} + 3 f_{x} f_{xyy} f_{xxyy} - 3 f_x f_{xyyy} f_{xxy} - f_{xxx} f_y f_{xyyy} + f_{xxxx} f_y f_{yyy} - 3 f_y f_{xyy} f_{xxxy} + 3 f_y f_{xxy} f_{xxyy}$ \\
 \end{tabular}
@@
 \end{table}
+
+\todo[inline]{Put into 2 tables: order 2 + products, order 3, rest order 4. Then explain a little bit.}
 
@@
 
+For $A(2)$ the weight of the partial transvectants prevents them from being invariants.
+They can be normalised by choosing only those where all components have the same weight and projecting them onto a unit hypersphere.
+Instead, we select ratios of partial transvectants.
+It is beneficial to choose the numerator and denominator so that they have different critical points, which can be achieved by adding together partial transvectants of the same weight as appropriate.
+
+====
+
+We consider as our image, the following function, defined on $[-1, 1]
+\times:
+[-1, 1]$
+\begin{equation}\label{eq:function}
+  \begin{split}
+    f(x, y) &= 0.5 - 0.2x - 0.3y - 0.05x^2 + 0.03xy + 0.04y^2 \\ 
+    &+ 0.03y^3 + 0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3.
+  \end{split}
+\end{equation}
+This function was chosen to have no critical points, and to be
+predominantly linear, so that the higher order derivatives were not too
+large. This was predominantly so the higher order terms in the signatures
+would not overwhelm the smaller terms. The function is depicted as a
+greyscale image in Figure~\ref{fig:function}
+\begin{figure}
+  \centering
+  \includegraphics[width=12cm]{figures/function}
+  \caption{The test function used in this document, from
+  Eq.~\eqref{eq:function}.}\label{fig:function}
+\end{figure}
+
+We consider the signatures of this function under various transformation
+groups, as detailed throughout the main body of the paper and illustrate
+the signature in three dimensions. A grid is overlaid on the image of the
+function itself, as shown in Fig~\ref{fig:function_scanlines}. This grid is
+mapped to the signature surface to help understand what the signature looks
+like locally.
+\begin{figure}
+  \centering
+  \includegraphics[width=12cm]{figures/function_scanlines}
+  \caption{The test function used in this document, from
+  Eq.~\eqref{eq:function} with a grid of lines
+overlaid.}\label{fig:function_scanlines}
+\end{figure}
+
 \todo[inline]{visual obstruction}
@@
 And then a list of explicit invariants by group.
-
-E2:
-{\bf Aside 3. Role of the invariants} 
-All of the 2nd order differential invariants play known roles in geometric analysis:
-\begin{enumerate}
-\item $f_x^2 + f_y^2=\|\nabla f\|^2$ is the Lagrangian density for the Laplacian;
-\item $f_{xx} + f_{yy}$ is the Laplacian, which plays a key role in Euclidean and conformal geometry;
-\item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is the `infinity-Laplacian'; 
-\item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is also a Lagrangian density for $-2(f_{xx} f_{yy} - f_{xy}^2)$, which arises in the Monge--Amp\`ere equations and
-can be written in terms of the final 2nd order invariant as $-2 (f_{xx} f_{yy} - f_{xy}^2) = 2 f_{xy}^2 - f_{xx}^2 - f_{yy}^2$
-\end{enumerate}
-In addition, we shall see in later sections that functions of these invariants are invariants or
-relative invariants for many groups that contain $E(2)$, namely $Sim(2)$, $SA(2)$, $A(2)$, $PSL(3,\mathbb{R})$, $PSL(2,\mathbb{C})$, and the conformal group.
 
@@
 
-Ignoring translation, the action of $SE(2)$ is simply rotation by some angle $\theta$, i.e.,
+\todo[inline]{Make precise!}
+Ignoring translation, the action of $SE(2)$ on the first derivatives is simply rotation by some angle $\theta$, i.e.,
 
@@
 I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) \\
-I_4 &= f_x^2 f_{xx} - 2 f_x f_y f_{xy} + f_y^2 f_{yy} \\
+I_4 &= f_x^2 f_{xx} - 2 f_x f_y f_{xy} + f_y^2 f_{yy} 
 \end{align}
 
-However, summing $I_2$ and $I_4$ we can write the expression as $f_x^2 f_{xx} + f_y^2 f_{yy}$.
+\todo[inline]{Richard: Check if the summation and negation (!) of I2 and I4 are actually invariants.} Then we can write this bit. 
+I3 is Robert's one.}
+%However, summing $I_2$ and $I_4$ we can write the expression as $f_x^2 f_{xx} + f_y^2 f_{yy}$.
 Which is the product of 2 invariants in Einstein summation, but a pain in the arse any other way.
 But I can't see how else to get $f_{ii}$!
+
+\todo[inline]{E(2) is confusing.
+Robert did it by contraction, and got nice invariants.
+For the moving frame, the issue is that you have to consider one of the branches, since there is a reflection ambiguity.
+This is hacked in the PSL(3,R) case.
+Even then, it isn't clear that you can get the nice ones.
+The same issue stands for trying to extend SE(2) to E(2).
+
+Question: is there an extension of transvectants (change of operator) that lets you get to it that way?
+
+However... we should do Sim(2) by adding a scaling to E(2), so we need it :(
+}
 
@@
 
+\todo[inline]{Richard to find the moving frame version!}
+
 The group of conformal diffeomorphisms is the subgroup of diffeomorphisms that are angle-preserving, i.e.,
@@
 
+E2:
+{\bf Aside 3. Role of the invariants} 
+All of the 2nd order differential invariants play known roles in geometric analysis:
+\begin{enumerate}
+\item $f_x^2 + f_y^2=\|\nabla f\|^2$ is the Lagrangian density for the Laplacian;
+\item $f_{xx} + f_{yy}$ is the Laplacian, which plays a key role in Euclidean and conformal geometry;
+\item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is the `infinity-Laplacian'; 
+\item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is also a Lagrangian density for $-2(f_{xx} f_{yy} - f_{xy}^2)$, which arises in the Monge--Amp\`ere equations and
+can be written in terms of the final 2nd order invariant as $-2 (f_{xx} f_{yy} - f_{xy}^2) = 2 f_{xy}^2 - f_{xx}^2 - f_{yy}^2$
+\end{enumerate}
+In addition, we shall see in later sections that functions of these invariants are invariants or
+relative invariants for many groups that contain $E(2)$, namely $Sim(2)$, $SA(2)$, $A(2)$, $PSL(3,\mathbb{R})$, $PSL(2,\mathbb{C})$, and the conformal group.
+
 \end{document}

### 2019-12-17 paper/newpaper.tex
Tidying up repository

@@
 Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$.
-Now consider applying the same affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + b$ where $A \in GL(2,\mathbb{R}$ and $b \in \mathbb{R}^2$.
+Now consider applying the same affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + \mathbf{b}$ where $A \in GL(2,\mathbb{R}$) and $\mathbf{b} \in \mathbb{R}^2$.
 Then the Omega Process is a second-order differential operator defined by:
@@
 
-Under the above affine transformation, $\Omega_{ij} \mapsto \det A^{-1} \Omega_{ij}$. Note that $\det A^{-1}$ has no dependence on the coordinates. 
-The Omega Process can be applied to pairs of smooth functions as follows, writing $\frac{\partial f}{\partial x}$ as $f_x$:
+Under the above affine transformation, $\Omega_{ij} \mapsto (\det A)^{-1}
+\Omega_{ij}$. Note that $(\det A)^{-1}$ has no dependence on the coordinates.
+The Omega Process can be applied to pairs of smooth functions as follows,
+writing $\frac{\partial f}{\partial x}$ as $f_x$:
 
 \begin{equation}
-\Omega_{ij} f(x_i, y_i) g(x_j, y_j) = f_{x_i}g_{y_j} - f_{y_i}g_{x_j}
+\Omega_{ij} \left(f(x_i, y_i) g(x_j, y_j)\right) = f_{x_i}g_{y_j} - f_{y_i}g_{x_j}
 \end{equation}
 
-Identifying $x_i = x_j = x, y_i = y_j = y$ gives us functions of $x$ and $y$ that only vary by a scaling factor of $\det A^{-1}$ when $\mathbf{x}$ is mapped by an affine transformation.
-This matches the definition of a first-order partial transvectant of two functions:
+Identifying $x_i = x_j = x, y_i = y_j = y$ gives us functions of $x$ and $y$
+that only vary by a scaling factor of $(\det A)^{-1}$ when $\mathbf{x}$ is
+mapped by an affine transformation. This matches the definition of a
+first-order partial transvectant of two functions:
 
@@
 
-Under this formula we end with a factor $\det A^{-r}$ in place of $\det
-A^{-1}$ that we saw previously, when all $n$ copies of $\mathbb{R}^2$ are
+Under this formula we end with a factor $(\det A)^{-r}$ in place of $(\det
+A)^{-1}$ that we saw previously, when all $n$ copies of $\mathbb{R}^2$ are
 transformed by the same affine function $\mathbf{x} \mapsto A\mathbf{x} +
@@
   \centering
-  \includegraphics[width=12cm]{figures/function}
+  \includegraphics[width=12cm]{Figs/function}
   \caption{The test function used in this document, from
@@
   \centering
-  \includegraphics[width=12cm]{figures/function_scanlines}
+  \includegraphics[width=12cm]{Figs/function_scanlines}
   \caption{The test function used in this document, from
@@
 
-\todo[inline]{Richard: Check if the summation and negation (!) of I2 and I4 are actually invariants.} Then we can write this bit. 
-I3 is Robert's one.}
+\todo[inline]{Richard: Check if the summation and negation (!) of I2 and I4
+are actually invariants. Then we can write this bit. I3 is Robert's one.}
 %However, summing $I_2$ and $I_4$ we can write the expression as $f_x^2 f_{xx} + f_y^2 f_{yy}$.

### 2019-12-17 code/Signature.m

@@ -1,9 +1,9 @@
 classdef Signature < handle
     properties
-        fn
-        fn_numeric
-        group
-        signature_fn
+        fn                 % image function (symbolic)
+        fn_numeric         % image function (numeric)
+        group              % string: name of the group
+        signature_fn       % 
         derivative_order
         derivatives
         derivatives_matlab

### 2019-12-17 code/make_figures.m

@@ -10,17 +10,29 @@ write_images = false;
  %   0.03*(x - 1.5)*(y + 1).^2 - 0.015*(y + 1).^3 + 0.9;
 %f(x, y) = exp(-2*x.^2 - 4.*sin((y + 0.5*x.^2)).^2);
 %f(x, y) = 0.6*(exp(-2*x.^2 - 0.5*x.*y - 4*y.^2) + 0.5 + 0.5*sin(2*(x + y)));
-f(x, y) = 0.5 - 0.2*x - 0.3*y - 0.05*x.^2 + 0.03*x.*y + 0.04*y.^2 + ...
-    0.03*y.^3 +0.001*x.^3 - 0.0015*x.^2.*y + 0.002*x.*y.^2 - 0.0005*y.^3;
+c = [0.5, -0.2, -0.3, -0.5, 0.03, -0.4, 0.001, -0.0015, 0.002, 0.03];
+foo = @(x, y, c) c(1) + c(2)*x + c(3)*y + ...
+    c(4)*x.^2 + c(5)*x.*y + c(6)*y.^2 + ...
+    c(7)*x.^3 + c(8)*x.^2.*y + c(9)*x.*y.^2 + c(10)*y.^3;
+
+f(x, y) = foo(x, y, c);
+f_numeric = matlabFunction(f);
 
 %% Plot and write image
-clf
 sig = E2_signature(f);
+
+figure(1)
+clf
 sig.draw_image('showscanlines', false)
-print('-dpng', '-r200', 'images/function.png')
+if write_images
+    print('-dpng', '-r200', 'images/function.png')
+end
+figure(2)
 clf
 sig.draw_image()
-print('-dpng', '-r200', 'images/function_scanlines.png')
+if write_images
+    print('-dpng', '-r200', 'images/function_scanlines.png')
+end
 
 %% Write signature picture
 groups = {'E2', 'SE2', 'A2', 'Mobius', 'PSL3R', 'SA2', 'Sim2'};
@@ -48,7 +60,7 @@ tform = E2Transform(1, -1, 0.1, -0.2);
 sig = E2_signature(f);
 [xp, yp] = tform.reverse(x, y);
 sigp = E2_signature(f, 'tform', tform);
-
+sig.draw()
 
 
 
@@ -71,7 +83,7 @@ tform = SA2Transform(A(1,1), A(1,2), A(2,1), A(2,2), 0.1, -0.2);
 sig = SA2_signature(f);
[…]

### 2019-12-18 paper/newpaper.tex
words

@@
 \section{Introduction}
+\todo[inline]{
+Richard:
+
+Stephen:
+
+}
+
 \todo[inline]{Examples to be numbered like theorems}
@@
 
-local invariants -> occlusions OK
-derivatives -> noise is not
+\todo[inline]{Use T(2) as an example}
+
+local invariants: occlusions OK
+derivatives: noise is not
 
 signatures, dimensions, orders
+Bad set, completeness
 
@@
 SE(2) is done via the moving frame by Olver in Ch 8 of CIT.
+
+\section{The Invariant Tensor Theorem}
+
+The new contraction mapping computation.
+
+E(2), Sim(2)
+
+Since this will be the first example, put the details of the image here. And remove one of the repeats below.
+
+3D and 4D signatures.
 
@@
 \section{Differential invariants through moving frames}
+
+\todo[inline]{This needs a friendly introduction, or at least a pointer to the notebooks}
 
@@
 
-\todo[inline]{E(2) is confusing.
-Robert did it by contraction, and got nice invariants.
-For the moving frame, the issue is that you have to consider one of the branches, since there is a reflection ambiguity.
-This is hacked in the PSL(3,R) case.
-Even then, it isn't clear that you can get the nice ones.
-The same issue stands for trying to extend SE(2) to E(2).
-
-Question: is there an extension of transvectants (change of operator) that lets you get to it that way?
-
-However... we should do Sim(2) by adding a scaling to E(2), so we need it :(
+\todo[inline]{ Two things to note: (1) SE(2) has similar invars, (2) there is an issue in E(2) with the moving frame: reflection ambiguity. That's why we did it by contraction.
 }
@@
 
-\todo[inline]{Richard to find the moving frame version!}
+\todo[inline]{Put the moving frame version here}
 
@@
 
-\section{Algorithms}
- This will go in paper 2, but let's start in here.
-
-\todo[inline]{Pseudocode for the matlab experimental code}
-\todo[inline]{Something about computing transvectants?}
-
-\section{Experiments}
+Some calculation detail
 
 \todo[inline]{Signature examples}
-\todo[inline]{Noise}
-\todo[inline]{Spot the group}
-\todo[inline]{Example on bits of images}
-
-\section{Discussion}
+\todo[inline]{Alien: Smoothing, noise}
+\todo[inline]{Spot the group?}
+
+\section{Conclusions}
+
+\todo[inline]{Number of derivatives}
+\item[inline]{Noise; integral invariants, Fourier}
+\todo[inline]{Is there a general theory - syzygy??}
 

### 2019-12-18 code/transvectants.py
Abomination of transvectants

@@ -63,6 +63,16 @@ class MyLatexPrinter(LatexPrinter):
             self._print(Symbol(function.func.__name__)),
                         ''.join(''.join(self._print(a[0]) for i in
                             range(a[1])) for a in vars))
+   
+    # This is an abomination
+    def _print_Subs(self, subs):
+        expr, old, new = subs.args
+        latex_expr = self._print(expr)
+        latex_old = (self._print(e) for e in old)
+        latex_new = (self._print(e) for e in new)
+        latex_subs = r'\\ '.join(
+            e[0] + '=' + e[1] for e in zip(latex_old, latex_new))
+        return r'%s' % (latex_expr)
 
 
 def print_my_latex(expr):
@@ -71,6 +81,7 @@ def print_my_latex(expr):
     any settings.
     """
     print(MyLatexPrinter().doprint(expr))
+   
     
 def my_latex(expr):
     return MyLatexPrinter().doprint(expr)

### 2019-12-18 paper/newpaper.tex
todo list

@@
 Richard: 
+Start on invariant tensor theorem
+Generate new pictures, add function details
+SE(2) jobs inline
+Mobius, Conformal -- finish code, tidy writing
+First bash at experimental section
 
 Stephen:
-
+Rearrange examples text to IVT section, write about signatures here
+Fix up tables, check bib
+Examples for SA(2), A(2) -- need to think about sig here
+Moving frame intro
+Projective -- tidy writing, especially the names of the invariants
+Colour
+First bash at conclusion
+
+Later:
+Introduction
+Count of derivatives and what to say
 }

### 2020-07-28 paper/newpaper.tex
Changes from July Kapiti meetup

@@
 \begin{AMS}
+
 \end{AMS}
@@
 I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) \\
-I_4 &= f_x^2 f_{xx} - 2 f_x f_y f_{xy} + f_y^2 f_{yy} 
+I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} 
 \end{align}
-
-\todo[inline]{Richard: Check if the summation and negation (!) of I2 and I4
-are actually invariants. Then we can write this bit. I3 is Robert's one.}
-%However, summing $I_2$ and $I_4$ we can write the expression as $f_x^2 f_{xx} + f_y^2 f_{yy}$.
-Which is the product of 2 invariants in Einstein summation, but a pain in the arse any other way.
-But I can't see how else to get $f_{ii}$!
 
@@
 \todo[inline]{Number of derivatives}
-\item[inline]{Noise; integral invariants, Fourier}
+\todo[inline]{Noise; integral invariants, Fourier}
 \todo[inline]{Is there a general theory - syzygy??}

### 2020-07-28 code/make_figures.m

@@ -7,15 +7,15 @@ write_images = false;
 % We create a symbolic and a numeric version of the function, for future
 % reference.
 %f(x, y) = 0.01*(x - 1.5).^3 -0.02*(x - 1.5).^2.*(y + 1) + ...
- %   0.03*(x - 1.5)*(y + 1).^2 - 0.015*(y + 1).^3 + 0.9;
-%f(x, y) = exp(-2*x.^2 - 4.*sin((y + 0.5*x.^2)).^2);
+%    0.03*(x - 1.5)*(y + 1).^2 - 0.015*(y + 1).^3 + 0.9;
+f(x, y) = exp(-2*x.^2 - 4.*sin((y + 0.5*x.^2)).^2);
 %f(x, y) = 0.6*(exp(-2*x.^2 - 0.5*x.*y - 4*y.^2) + 0.5 + 0.5*sin(2*(x + y)));
-c = [0.5, -0.2, -0.3, -0.5, 0.03, -0.4, 0.001, -0.0015, 0.002, 0.03];
-foo = @(x, y, c) c(1) + c(2)*x + c(3)*y + ...
-    c(4)*x.^2 + c(5)*x.*y + c(6)*y.^2 + ...
-    c(7)*x.^3 + c(8)*x.^2.*y + c(9)*x.*y.^2 + c(10)*y.^3;
+%c = [0.5, -0.2, -0.3, -0.5, 0.03, -0.4, 0.001, -0.0015, 0.002, 0.03];
+%foo = @(x, y, c) c(1) + c(2)*x + c(3)*y + ...
+%    c(4)*x.^2 + c(5)*x.*y + c(6)*y.^2 + ...
+%    c(7)*x.^3 + c(8)*x.^2.*y + c(9)*x.*y.^2 + c(10)*y.^3;
 
-f(x, y) = foo(x, y, c);
+%f(x, y) = foo(x, y, c);
 f_numeric = matlabFunction(f);
 
 %% Plot and write image
@@ -60,18 +60,21 @@ tform = E2Transform(1, -1, 0.1, -0.2);
 sig = E2_signature(f);
 [xp, yp] = tform.reverse(x, y);
 sigp = E2_signature(f, 'tform', tform);
-sig.draw()
-
+sig.draw('facecolor', 'blue', 'facealpha', 0.3, 'nx', 200, 'ny', 200, 'showscanlines', false)
+hold on
[…]

### 2020-07-28 code/signatures/E2_signature.m

@@ -7,9 +7,9 @@ out = signature_switch(f, @evaluate, derivative_order, group, varargin{:});
         I0 = f;
         I1 = fx.*fx + fy.*fy;
         I2 = fxx + fyy;
-        I3 = fx.^2.*fxx +2*fx.*fy.*fxy + fy.^2.*fyy;
-        I4 = fy.^2.*fxx -2*fx.*fy.*fxy + fx.^2.*fyy;
-        I5 = -fx.*fy.*(fxx - fyy) + (fx.^2 - fy.^2).*fxy;
+        I3 = fx.^2.*fxx +2*fx.*fy.*fxy + fy.^2.*fyy; % SE2
+        I4 = fy.^2.*fxx -2*fx.*fy.*fxy + fx.^2.*fyy; % SE2
+        I5 = (-fx.*fy.*(fxx - fyy) + (fx.^2 - fy.^2).*fxy); %SE2
         I6 = fxx.^2 + fyy.^2 + 2*fxy.^2;
         sig = {I0, I1, I5};
        

### 2020-07-28 code/signatures/SE2_signature_new.m

@@ -6,7 +6,7 @@ out = signature_switch(f, @evaluate, derivative_order, group, varargin{:});
         [f, fx, fy, fxx, fxy, fyy] = derivs{:};
         I0 = f;
         I1 = fx.*fx + fy.*fy;
-        I2 = fx.^2.*fxx + fy.^2.*fyy;
+        I2 = fy.^2.*fxx - 2*fx.*fy.*fxy + fx.^2.*fyy;
         I3 = fx.*fy.*fxy;
         sig = {I0, I1, I2};
     end

### 2020-07-29 paper/newpaper.tex
edits

@@
 \end{abstract}
+
+h
 
@@
 
+/subsection{Transformation notation}
+Most of the time we will work on grey-scale transformations of two-dimensional images.
+In this setting, we define the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$
+\begin{equation}\label{eq:transformation}
+  \mathbf{x} \mapsto \bar{\mathbf{x}} = \varphi(\mathbf{x})
+\end{equation}
+The transformed image is then defined to be
+\begin{equation}\label{eq:fbarequalsf}
+  \bar{f}(\bar{\mathbf{x}}) = (f\circ\varphi^{-1})(\bar{\mathbf{x}}) = f(\mathbf{x}).
+\end{equation}
+Derivatives of $\bar{f}$ and $f$ can be related by the chain rule, for example the first order derivatives are given by:
+\begin{equation}\label{eq:prolongation}
+  \begin{aligned}
+    f_x &= \bar{f}_{\bar{x}} \bar{x}_x + \bar{f}_{\bar{y}}\bar{y}_x \\
+    f_y &= \bar{f}_{\bar{x}} \bar{x}_y + \bar{f}_{\bar{y}}\bar{y}_y \\
+  \end{aligned}
+\end{equation}
+where $\bar{x}_x = \frac{\partial \varphi_1}{\partial x}(x, y)$, et cetera. It is often convenient to work with $\varphi^{-1}$ instead, which we will do in \S\ref{sec:movingframes}.
+
 ====
@@
 
-\section{Differential invariants through moving frames}
+\section{Differential invariants through moving frames}\label{sec:movingframes}
 
@@
 \subsection{$SE(2)$}
-
-\todo[inline]{Make precise!}
-Ignoring translation, the action of $SE(2)$ on the first derivatives is simply rotation by some angle $\theta$, i.e.,
-
+An element of the transformation group $SE(2)$ acts on an element $(x, y)$ of $\mathbb{R}^2$ to produce $(\bar{x}, \bar{y})$ as
+\begin{equation*}
+  \begin{aligned}
+    \bar{x} &= x\cos\theta  - y\sin\theta + t_x \\
+    \bar{y} &= x\sin\theta  + y\cos\theta + t_y.
+  \end{aligned}
+\end{equation*}
+Prolonging the group action up to second derivatives via the chain rule computations gives
 \begin{equation}
-\left( \begin{array}{c} f_x \\ f_y \end{array} \right) = \left( \begin{array}{cc} \cos \theta & \sin \theta \\ - \sin \theta & \cos \theta \end{array} \right) \left( \begin{array}{c} \bar f_{\bar x} \\ \bar f_{\bar y} \end{array} \right).
-\end{equation}
-
-Using $c$ for $\cos \theta$ and $s$ for $\sin \theta$ and prolonging the group to second order via the chain rule gives:
-
-\begin{equation}
-\arraycolsep=1.4pt
-\left(
-\begin{array}{c}
-  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} 
- \end{array}
- \right)
- = 
-\left(
-\begin{array}{ccccc}
+  \begin{bmatrix}
+  \bar f_{\bar x} \\ \bar f_{\bar y} \\ \bar f_{\bar{x}\bar{x}} \\ \bar f_{\bar{x}\bar{y}} \\ \bar f_{\bar{y}\bar{y}}
+  \end{bmatrix}
+  \begin{bmatrix}
  c & -s & 0 & 0 & 0 \\
@@
 0 & 0 & s^2 & 2cs & c^2 \\
-\end{array}
-\right)\left(
-\begin{array}{c}
+  \end{bmatrix}
+  \begin{bmatrix}
 f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} 
- \end{array}
- \right).
+  \end{bmatrix}
 \label{eqn:SE2}
  \end{equation}
-
-As $SE(2)$ does not include scaling, lengths stay the same, and so an appropriate choice for first-order normalisation is $\bar f_x = \sqrt(f_x^2 + f_y^2),\:\: \bar f_y = 0$, which sets $c = f_x / \| \nabla f \|$, $s = - f_y / \| \nabla f \|$.
-This provides the invariant $I_1 = \nabla f$.
-As there are no more free parameters, the expressions for the second-order terms can be read off as:
-
+where $c = \cos \theta$ and $s = \sin \theta$.
+
+We normalise in two stages.
+First, we set $\bar{f}_{\bar{y}} = 0$.
+This determines $\theta$, giving $\cos\theta = f_x/\lVert \nabla f \rVert$ and $\sin\theta = -f_y / \lVert \nabla f \rVert$.
+We then choose $t_x = -x\cos\theta + y\sin\theta$ and $t_y = -x\sin\theta - y \cos\theta$ to make $\bar{x} = 0$ and $\bar{y} = 0$.
+These three normalisations fully specify the moving frame, and so the remaining transformed derivatives are invariants.
+Apart from squaring $I_1$, these can be read off as:
 \begin{align}
+  I_0 &= f \\
+  I_1 &= f_x^2 + f_y^2 \\
   I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} \\
@@
 
-\todo[inline]{ Two things to note: (1) SE(2) has similar invars, (2) there is an issue in E(2) with the moving frame: reflection ambiguity. That's why we did it by contraction.
-}
+\todo[inline]{c.f. transvectant formulae}
+
+\subsection{The Euclidean Group E(2)}
+An element of the Euclidean group $E(2)$ maps an element $(x, y)$ of $\mathbb{R}^2$ to $(\bar{x}, \bar{y}$ as 
+\begin{equation*}
+  \begin{aligned}
+    \bar{x} &=  x\varepsilon\cos\theta  - y\varepsilon\sin\theta + t_x \\
+    \bar{y} &= x\sin\theta  + y\cos\theta + t_y.
+  \end{aligned}
+\end{equation*}
+where $\varepsilon \in \{-1, 1\}$ and the remaining parameters are the same as for $SE(2)$. If $\varepsilon = 1$ it is a rigid transformation, and if $\varepsilon = -1$ it contains a reflection.
+
+This time, the group action is not free on $J^1$ (with elements of the form $(x, y, f, f_x, f_y)$) because there are two possible transformations that map to the normalised coordinates $(0, 0, \bar{f}, \bar{f}_{\bar{x}}, 0)$ where $\bar{f}_{\bar{x}} \ge 0$, one that reflects the gradient, and one that rotates.
+And first derivatives give no information about $\varepsilon$.
+
+So, we prolong to second derivatives, giving
+\begin{equation}
+  \begin{bmatrix}
+  \bar f_{\bar x} \\ \bar f_{\bar y} \\ \bar f_{\bar{x}\bar{x}} \\ \bar f_{\bar{x}\bar{y}} \\ \bar f_{\bar{y}\bar{y}}
+  \end{bmatrix}
+  \begin{bmatrix}
+ \varepsilon c & -\varepsilon s & 0 & 0 & 0 \\
+ s & c & 0 & 0 & 0 \\
+0 & 0 & c^2 & -2cs & s^2 \\
+0 & 0 & \varepsilon cs & \varepsilon(c^2 - s^2) & -\varepsilon cs \\
+0 & 0 & s^2 & 2cs & c^2 \\
+  \end{bmatrix}
+  \begin{bmatrix}
+f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} 
+  \end{bmatrix}
+\label{eqn:E2prolongation}
+ \end{equation}
 

### 2020-08-04 paper/newpaper.tex
J hunting

--- 2020-07-28 paper/newpaper.tex
@@
 This leaves 6 group parameters $(a,b,c,d,g,h)$ to be determined.
-First we prolong the action to 3rd derivatives of $f$.
-There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 3 invariants.
+First we prolong the group action to 3rd derivatives of $f$.
+Since there are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 3 invariants.
 
@@
 
-First, recall from the analysis of the subgroup $A(2)$ that under $f\mapsto f\circ \phi$, $\phi\in A(2)$, we have 
+The affine group $A(2)$ is a subgroup of $\mathrm{PSL}(3,\R)$.
+In the analysis of that group, in Section~\ref{}, the invariant $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$ was identified.
+Under a general action of $\phi \in \mathrm{PSL}(3,\R)$, $D$ is a relative invariant (that is, the value is multiplied by a certain factor under group transformations):
 \begin{equation}
 \label{eq:D}
-D \mapsto (\det \phi')^2 D\circ \phi
+D \mapsto (\det \phi')^2 D\circ \phi.
 \end{equation}
-where $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$.
-
-A direct calculation using (\ref{eq:prolong}) shows that the same transformation rule (\ref{eq:D}) holds for $\phi\in\mathrm{PSL}(3,\R)$.
+
+Another invariant of $A(2)$ was
+
+\begin{equation}
+E := f_{yyy}f_x^3 - 3 f_{xyy}f_x f_y^2 + 3 f_{xxy}f_x^2 f_y - f_{xxx}f_y^3.
+\end{equation}
+
+%A direct calculation using (\ref{eq:prolong}) shows that the same transformation rule (\ref{eq:D}) holds for $\phi\in\mathrm{PSL}(3,\R)$.
 That is, $D$ is a relative invariant of weight 2 of this action.
-From (\ref{eq:D}), the sign of $D$ is invariant and therefore the choice of moving frame must depend on the sign of $D$.
-
-\begin{enumerate}
-\item The frame $\bar f_x = 1$  determines the group parameter $$a = (1-c f_y)/f_x.$$
-\item The frame $\bar f_y=  0$ determines the group parameter $$b = -d f_y/f_x.$$
-\item Substituting this choice of $a$ and $b$ and examining the dependencies of $f_{xx}$, $f_{xy}$, $f_{yy}$, and $f_{yyy}$ on the remaining group parameters allows them to be solved sequentially, as follows.
-\item We have $\bar f_{yy} = d^2 D/f_x^2$; therefore if $D>0$ we choose the frame
-$\bar f_{yy} = 1$ and $$d = f_x/D^{1/2}.$$
-\item The frame $\bar f_{yyy} = 0$ determines the group parameter
-$$ h = \frac{d(f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2 f_{xxy} - f_y^3 f_{xxx})}{6 f_x D}.$$
-\item The frame $\bar f_{xyy}=0$ determines the group parameter
-$$ c = \frac{h f_x^2}{d D} - \frac{f_x f_{xy} - f_y f_{xx}}{D}.$$
-\item The frame $\bar f_{xx}=0$ determines the group parameter
-$$ g = \frac{1}{2 f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$$
-\end{enumerate}
-
-\todo[inline]{Need to get the Js from somewhere...}
+Both $D$ and $E$ will be useful quantities shortly, but note that, from (\ref{eq:D}), the sign of $D$ is invariant and therefore the choice of moving frame must depend on its sign.
+We begin by choosing the frames $\bar f_x = 1$ and $\bar f_y=  0$, which determine the group parameters $a = (1-c f_y)/f_x.$ and $b = -d f_y/f_x$.
+Direction substition then shows that $\bar f_{yy} = d^2 D/f_x^2$.
+We assume that $D>0$ (if it is negative, relatively little changes in the following derivation) and choose the frame $\bar f_{yy} = 1$, so that $d = f_x/D^{1/2}.$
+
+The frame $\bar f_{yyy} = 0$ determines the group parameter $ h = \frac{d(f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2 f_{xxy} - f_y^3 f_{xxx})}{6 f_x D},$ while $\bar f_{xyy}=0$ provides $ c = \frac{h f_x^2}{d D} - \frac{f_x f_{xy} - f_y f_{xx}}{D}$, and $\bar f_{xx}=0$ gives $ g = \frac{1}{2 f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$
+
 Having determined the frame, any function of the remaining derivatives $\bar f_{xxx}$, $\bar f_{xxy}$, and $\bar f_{yyy}$, as given in Equation~(\ref{eq:prolong}), provides invariants.
-We choose $$ (f_{xxx}, f_{xxy}^2, f_{xyy})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right)$$
-because these all have denominators given by integer powers  of $D$, resolving the issue caused
-by the sign of $D$. Therefore,
-$$ (D^{18}, J_1^3, J_2^2, J_3^6)$$
-are all relative invariants of weight 36; so projecting any subset of them of them to a sphere
-yields a 3rd order invariant signature.
-
-However, these signatures can be simplified and made more robust, as follows.
-
-The components of $J$ are polynomials of degree 16, 24, and 8, respectively, and are extremely complicated when written out explicitly.
-More seriously, $J$ vanishes on generic images.
-This can be seen as follows.
-Recall the $SA(2)$ invariant $E$ defined in \todo[inline]{somewhere}
-
-%Let
-%$$ E := f_{222}f_1^3 - 3 f_{122}f_1 f_2^2 + 3 f_{112}f_1^2 f_2 - f_{111}f_2^3$$
-Then the components of $J$ have the structure
-$$ J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5$$
-where the $P_n$ are polynomials of degree $n$. Therefore $J=0$ when $D=E=0$, which 
-is a codimension 0 phenomenon for images. In particular, $D=E=0$ at critical points.
-
-The structure of () suggests considering the combination $J_1 - J_3^2$ which turns out to obey
+We choose: $$ (f_{xxx}, f_{xxy}^2, f_{xyy})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right)$$, where (with $P_n$ denoting a polynomial of degree $n$):
+$$ J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5.$$
+
+The $J_i$ are polynomials of degree 16, 24, and 8, respectively, and are extremely complicated when written out explicitly.
+They do have one benefit, though, which is that they  all have denominators given by integer powers of $D$, resolving the issue caused by the sign of $D$.
+Therefore, $$ (D^{18}, J_1^3, J_2^2, J_3^6)$$ are all relative invariants of weight 36; so projecting any subset of them of them to a sphere yields a 3rd order invariant signature.
+
+$J$ vanishes on generic images: $J=0$ when $D=E=0$, which is a codimension 0 phenomenon for images.
+In particular, $D=E=0$ at critical points.
+However, these signatures can be simplified and made more robust.
+Their structure suggests considering the combination $J_1 - J_3^2$, which turns out to obey
 $$J_1 - J_3^2 = 144 D^4 P_4.$$
-Therefore, as $J_1/D^6$ and $J_3/D^3$ are invariant, so is $P_4/D^2$. 
-Moreover, {\em the numerator of this new invariant does not vanish at critical points.} 
-It has the structure
+
+As $J_1/D^6$ and $J_3/D^3$ are invariant, so is $P_4/D^2$. 
+Moreover, the numerator of this new invariant does not vanish at critical points.  It has the structure
 $$P_4 = -4(\det f_{ij})^2 + Q_4,$$
-where $Q_4$ is a polynomial of degree 4 that vanishes when $f_x=f_y=0$. In conclusion, the
-relative invariant of weight 12
+where $Q_4$ is a polynomial of degree 4 that vanishes when $f_x=f_y=0$. Hence, the relative invariant of weight 12
 $$ (D^6, P_4^3, (E^2-12D P_5)^2)$$
-can be projected to $S^2$ yielding a projective invariant of images that
-is singular only when $D=E=P_4=0$, which is a codimension 1 phenomenon for images.
-(One can check that $D=E=0\Rightarrow P_4=0$.) In particular, at critical points it tends to
-$$ (0, (2\det f_{ij})^6, 0)$$
-and hence critical points with $\det f_{ij}\ne 0$ have signature $(0,1,0)$.
+can be projected to $S^2$, yielding a projective invariant of images that is singular only when $D=E=P_4=0$, which is a codimension 1 phenomenon, since  $D=E=0\Rightarrow P_4=0$.
+In particular, at critical points it tends to
+$(0, (2\det f_{ij})^6, 0),$ and hence critical points with $\det f_{ij}\ne 0$ have signature $(0,1,0)$.
 
@@
 $$\nabla I^1 \times \nabla I^2\mapsto (\det \phi')(\nabla I^1 \times \nabla I^2).$$
-Applying this operation to $f$ and the 4 3rd order invariants yields $5\cdot4/2=1$0  4th order invariants.
+Applying this operation to $f$ and the 4 3rd order invariants yields $5\cdot4/2=10$ 4th order invariants.
 

### 2020-08-05 paper/newpaper.tex
Minor updates

@@
 where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$.
-Table~\ref{tab:transvectants} shows all possible nonzero partial
+Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} shows all possible nonzero partial
 transvectants of $A_2$ up to weight $4$ that can be generated in this way.
@@
 & $- \left(f_{x}\right)^{3} f_{yy} f_{xyy} + \left(f_{x}\right)^{3} f_{yyy} f_{xy} - \left(f_{x}\right)^{2} f_{xx} f_{y} f_{yyy} + 2 \left(f_{x}\right)^{2} f_{y} f_{yy} f_{xxy} - \left(f_{x}\right)^{2} f_{y} f_{xy} f_{xyy} + 2 f_{x} f_{xx} \left(f_{y}\right)^{2} f_{xyy} - f_{x} f_{xxx} \left(f_{y}\right)^{2} f_{yy} - f_{x} \left(f_{y}\right)^{2} f_{xy} f_{xxy} - f_{xx} \left(f_{y}\right)^{3} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3} f_{xy}$ \\
-
+\end{tabular}
+\caption{Details and graphical representations of all partial transvectants up to degree $3$ of copies of a function $f$ under a transformation in $A(2)$.}
+\label{tab:transvectants1}
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{cccp{11cm}}
+Degree & Weight & Diagram & Partial transvectant\\
+\hline
 4 & 4 &
@@
 \end{tabular}
-\caption{Details and graphical representations of all partial transvectants up to weight $4$ of copies of a function $f$ under a transformation in $A(2)$.}
-\label{tab:transvectants}
+\caption{Details and graphical representations of all partial transvectants of weight $4$ of copies of a function $f$ under a transformation in $A(2)$.}
+\label{tab:transvectants2}
 \end{table}
 
-\todo[inline]{Put into 2 tables: order 2 + products, order 3, rest order 4. Then explain a little bit.}
+\todo{Explain}
 
@@
 For example, invariants of $A(2)$ are automatically invariants of $SA(2)$, but not necessarily vice versa.
-Any of the partial transvectants found in Table~\ref{tab:transvectants} are invariants of $SA(2)$ (as the determinant is $1$) but only up to scale factor ($\det A^{-r}$) of $A(2)$.
+Any of the partial transvectants found in Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} are invariants of $SA(2)$ (as the determinant is $1$) but only up to scale factor ($\det A^{-r}$) of $A(2)$.
 

### 2020-08-05 paper/newpaper.tex
edits

--- 2020-07-29 paper/newpaper.tex
@@
 \subsection{$SE(2)$}
-An element of the transformation group $SE(2)$ acts on an element $(x, y)$ of $\mathbb{R}^2$ to produce $(\bar{x}, \bar{y})$ as
+An element of the special Euclidean group $SE(2)$ acts on an element $(x, y)$ of $\mathbb{R}^2$ to produce $(\bar{x}, \bar{y})$ as 
 \begin{equation*}
@@
 \end{equation*}
-Prolonging the group action up to second derivatives via the chain rule computations gives
+Note that once $\theta$ has been fixed, it's always possible to choose $t_x$ and $t_y$ to ensure that $\bar{x} = \bar{y} = 0$.
+Prolonging the group action up to second derivatives via the chain rule gives
 \begin{equation}
@@
 f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} 
-  \end{bmatrix}
+  \end{bmatrix},
 \label{eqn:SE2}
  \end{equation}
-where $c = \cos \theta$ and $s = \sin \theta$.
-
-We normalise in two stages.
-First, we set $\bar{f}_{\bar{y}} = 0$.
-This determines $\theta$, giving $\cos\theta = f_x/\lVert \nabla f \rVert$ and $\sin\theta = -f_y / \lVert \nabla f \rVert$.
-We then choose $t_x = -x\cos\theta + y\sin\theta$ and $t_y = -x\sin\theta - y \cos\theta$ to make $\bar{x} = 0$ and $\bar{y} = 0$.
-These three normalisations fully specify the moving frame, and so the remaining transformed derivatives are invariants.
-Apart from squaring $I_1$, these can be read off as:
+where $c = \cos \theta$ and $s = \sin \theta$. We are going to choose the
+moving frame to project a point in the jet space onto the submanifold
+$\bar{x} = 0$, $\bar{y} = 0$, $\bar{f}_{\bar{y}} = 0$, $\bar{f}_{\bar{x}} \ge
+0$. This can be thought of as rotating the image about $(\bar{x}, \bar{y})$
+so that the gradient is pointing in the positive $\bar{x}$-direction, and
+then translating to the origin to put it in canonical position.
+
+This choice gives $\cos\theta = f_x / \lVert \nabla f \rVert$ and $\sin\theta = -f_y / \lVert \nabla f \rVert$, and then $t_x, t_y$ can be chosen as above.
+The remaining derivatives, transformed into canonical position, are therefore invariant and can be found by substituting in $c$ and $s$.
+Note we square $\bar{f}_{\bar{x}}$ for neatness.
 \begin{align}
   I_0 &= f \\
-  I_1 &= f_x^2 + f_y^2 \\
-  I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} \\
-  I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) \\
-  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} 
+  I_1 &= f_x^2 + f_y^2 & &(= \bar{f}_{\bar{x}}^2)\\
+  I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= \bar{f}_{\bar{x}\bar{x}}) \\
+  I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) &&(= \bar{f}_{\bar{x}\bar{y}})\\
+  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= \bar{f}_{\bar{y}\bar{y}})
 \end{align}

### 2020-08-13 paper/newpaper.tex
Derivation essentially there

@@
 
-\subsection{$SE(2)$}
+\subsection{The Special Euclidean Group $SE(2)$}
 An element of the special Euclidean group $SE(2)$ acts on an element $(x, y)$ of $\mathbb{R}^2$ to produce $(\bar{x}, \bar{y})$ as 
@@
 \end{equation*}
-Note that once $\theta$ has been fixed, it's always possible to choose $t_x$ and $t_y$ to ensure that $\bar{x} = \bar{y} = 0$.
-Prolonging the group action up to second derivatives via the chain rule gives
+We prolong the group action to form the jet space $J^2$ with coordinates $(x,
+y, f, f_x, f_y, f_{xx}, f_{xy}, f_{yy})$ via the chain rule. The
+transformation rule for the derivatives is given by
 \begin{equation}
@@
   \bar f_{\bar x} \\ \bar f_{\bar y} \\ \bar f_{\bar{x}\bar{x}} \\ \bar f_{\bar{x}\bar{y}} \\ \bar f_{\bar{y}\bar{y}}
-  \end{bmatrix}
+  \end{bmatrix} = 
   \begin{bmatrix}
@@
  \end{equation}
-where $c = \cos \theta$ and $s = \sin \theta$. We are going to choose the
-moving frame to project a point in the jet space onto the submanifold
-$\bar{x} = 0$, $\bar{y} = 0$, $\bar{f}_{\bar{y}} = 0$, $\bar{f}_{\bar{x}} \ge
-0$. This can be thought of as rotating the image about $(\bar{x}, \bar{y})$
-so that the gradient is pointing in the positive $\bar{x}$-direction, and
-then translating to the origin to put it in canonical position.
-
-This choice gives $\cos\theta = f_x / \lVert \nabla f \rVert$ and $\sin\theta = -f_y / \lVert \nabla f \rVert$, and then $t_x, t_y$ can be chosen as above.
-The remaining derivatives, transformed into canonical position, are therefore invariant and can be found by substituting in $c$ and $s$.
-Note we square $\bar{f}_{\bar{x}}$ for neatness.
-\begin{align}
+where $c = \cos \theta$ and $s = \sin \theta$. Because the group has three
+parameters, we choose the cross section of the group orbits to be $\bar{x}
+= 0, \bar{y} = 0, \bar{f}_{\bar{y}} = 0$. We also require that $\bar{f}_{x}
+> 0$ to uniquely define the moving frame. Note that the group action is
+locally free (away from critical points) when prolonged to $J^1$, however
+we prolonged to $J^2$ in order to compute invariants. points. The moving
+frame is then given by the prolonged Euclidean transformation that maps an
+element of  $J^2$ to this cross section. It can be thought of as rotating
+the image about that point so that its gradient is pointing in the positive
+$x$ direction, and then translating the image so the point is mapped to the
+origin.
+
+This choice of moving frame gives $\cos\theta = f_x/\lVert\nabla f\rVert$
+and $\sin\theta = -f_y/\lVert \nabla f \rVert$. The parameters $t_x, t_y$
+are then $t_x = -x\cos\theta + y\sin\theta$ and $t_y = -x\sin\theta -
+y\cos\theta$, however these have no effect on the derivatives, and will
+henceforth be ignored.
+
+The remaining elements not fixed by the cross section, $\bar{f}$,
+$\bar{f}_{\bar{x}}$, $\bar{f}_{\bar{x}\bar{x}}$,
+$\bar{f}_{\bar{x}\bar{y}}$, and $\bar{f}_{\bar{y}\bar{y}}$ are therefore
+all invariant. This gives the following set of invariants:
+\begin{equation}\label{eq:se2invariants}
+\begin{aligned}
   I_0 &= f \\
   I_1 &= f_x^2 + f_y^2 & &(= \bar{f}_{\bar{x}}^2)\\
-  I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= \bar{f}_{\bar{x}\bar{x}}) \\
-  I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) &&(= \bar{f}_{\bar{x}\bar{y}})\\
-  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= \bar{f}_{\bar{y}\bar{y}})
-\end{align}
+  I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= I_1\bar{f}_{\bar{x}\bar{x}}) \\
+  I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) &&(= I_1\bar{f}_{\bar{x}\bar{y}})\\
+  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}})
+\end{aligned}
+\end{equation}
+Note that we multiplied each of the second derivative invariants by $I_1$
+so that they would decay smoothly to zero at critical points.
 
@@
 \subsection{The Euclidean Group E(2)}
-An element of the Euclidean group $E(2)$ maps an element $(x, y)$ of $\mathbb{R}^2$ to $(\bar{x}, \bar{y}$ as 
+An element of the Euclidean group $E(2)$ maps an element $(x, y)$ of
+$\mathbb{R}^2$ to $(\bar{x}, \bar{y})$ as 
 \begin{equation*}
@@
 \end{equation*}
-where $\varepsilon \in \{-1, 1\}$ and the remaining parameters are the same as for $SE(2)$. If $\varepsilon = 1$ it is a rigid transformation, and if $\varepsilon = -1$ it contains a reflection.
-
-This time, the group action is not free on $J^1$ (with elements of the form $(x, y, f, f_x, f_y)$) because there are two possible transformations that map to the normalised coordinates $(0, 0, \bar{f}, \bar{f}_{\bar{x}}, 0)$ where $\bar{f}_{\bar{x}} \ge 0$, one that reflects the gradient, and one that rotates.
-And first derivatives give no information about $\varepsilon$.
-
-So, we prolong to second derivatives, giving
+where $\varepsilon \in \{-1, 1\}$ and the remaining parameters are the same
+as for $SE(2)$. If $\varepsilon = 1$ it is a rigid transformation, and if
+$\varepsilon = -1$ it contains a reflection.
+
+This time, the group action is not free on $J^1$ (with elements of the form
+$(x, y, f, f_x, f_y)$) away from critical points because there are two
+possible transformations that map to the cross section $(0, 0, \bar{f},
+\bar{f}_{\bar{x}}, 0)$ where $\bar{f}_{\bar{x}} > 0$, one that reflects the
+gradient into the positive $x$ direction, and one that rotates.
+
+We again prolong the group action to $J^2$, but this time we expect to need
+to use a second derivative term to determine $\varepsilon$ for the moving
+frame. The derivative transformations are given by
 \begin{equation}
@@
 f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} 
-  \end{bmatrix}
+  \end{bmatrix},
 \label{eqn:E2prolongation}
 \end{equation}
+where again $c = \cos\theta$ and $s = \sin\theta$.
+
+We begin by choosing the same cross section as for $SE(2)$, namely $\bar{x} = 0,
+\bar{y} = 0, \bar{f}_{\bar{y}} = 0, \bar{f}_{\bar{x}} > 0$. This gives
+$\cos\theta = \varepsilon f_x / \lVert \nabla f \rVert$ and $\sin\theta =
+-\varepsilon f_y / \lVert \nabla f \rVert$. Under this transformation,
+regardless of whether $\varepsilon = 1$ or $\varepsilon = -1$, the
+derivative $\bar{f}_{\bar{x}} = \lVert \nabla f \rVert$. We need a second
+derivative term to resolve the choice of $\varepsilon$ for the moving
+frame. The only second derivative term in which $\varepsilon$ appears is
+the $\bar{f}_{\bar{x}\bar{y}}$ term. Substituting in for $\cos\theta,
+\sin\theta$, we see that
+\begin{equation*}
+    \bar{f}_{\bar{x}\bar{y}} = \frac{\varepsilon(f_xf_y(f_{yy} - f_{xx}) + (f_x^2 -
+    f_y^2)f_{xy})}{f_x^2 + f_y^2}
+\end{equation*}
+This suggests choosing $\varepsilon$ to make $\bar{f}_{\bar{x}\bar{y}} \ge
+0$. We can then list the invariants:
+\begin{equation}\label{eq:e2invariants}
+\begin{aligned}
+  I_0 &= f \\
+  I_1 &= f_x^2 + f_y^2 & &(= \bar{f}_{\bar{x}}^2)\\
+  I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= I_1\bar{f}_{\bar{x}\bar{x}}) \\
+  I_3 &= \lvert f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2)\rvert
+  &&(= I_1\lvert \bar{f}_{\bar{x}\bar{y}}\rvert)\\
+  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}})
+\end{aligned}
+\end{equation}
+Notice that most, but not all of the $SE(2)$ invariants
+\eqref{eq:se2invariants} are also $E(2)$ invariants. We again multiply
+through the invariants by $I_1$ so that they decay smoothly at critical
+points.
 

### 2020-08-13 paper/newpaper.tex

--- 2020-08-05 paper/newpaper.tex
@@
 
-\subsection{$SE(2)$}
-
-\todo[inline]{Make precise!}
-Ignoring translation, the action of $SE(2)$ on the first derivatives is simply rotation by some angle $\theta$, i.e.,
-
+\subsection{The Special Euclidean Group $SE(2)$}
+An element of the special Euclidean group $SE(2)$ acts on an element $(x, y)$ of $\mathbb{R}^2$ to produce $(\bar{x}, \bar{y})$ as 
+\begin{equation*}
+  \begin{aligned}
+    \bar{x} &= x\cos\theta  - y\sin\theta + t_x \\
+    \bar{y} &= x\sin\theta  + y\cos\theta + t_y.
+  \end{aligned}
+\end{equation*}
+We prolong the group action to form the jet space $J^2$ with coordinates $(x,
+y, f, f_x, f_y, f_{xx}, f_{xy}, f_{yy})$ via the chain rule. The
+transformation rule for the derivatives is given by
 \begin{equation}
-\left( \begin{array}{c} f_x \\ f_y \end{array} \right) = \left( \begin{array}{cc} \cos \theta & \sin \theta \\ - \sin \theta & \cos \theta \end{array} \right) \left( \begin{array}{c} \bar f_{\bar x} \\ \bar f_{\bar y} \end{array} \right).
-\end{equation}
-
-Using $c$ for $\cos \theta$ and $s$ for $\sin \theta$ and prolonging the group to second order via the chain rule gives:
-
-\begin{equation}
-\arraycolsep=1.4pt
-\left(
-\begin{array}{c}
-  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} 
- \end{array}
- \right)
- = 
-\left(
-\begin{array}{ccccc}
+  \begin{bmatrix}
+  \bar f_{\bar x} \\ \bar f_{\bar y} \\ \bar f_{\bar{x}\bar{x}} \\ \bar f_{\bar{x}\bar{y}} \\ \bar f_{\bar{y}\bar{y}}
+  \end{bmatrix} = 
+  \begin{bmatrix}
  c & -s & 0 & 0 & 0 \\
@@
 0 & 0 & s^2 & 2cs & c^2 \\
-\end{array}
-\right)\left(
-\begin{array}{c}
+  \end{bmatrix}
+  \begin{bmatrix}
 f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} 
- \end{array}
- \right).
+  \end{bmatrix},
 \label{eqn:SE2}
  \end{equation}
-
-As $SE(2)$ does not include scaling, lengths stay the same, and so an appropriate choice for first-order normalisation is $\bar f_x = \sqrt(f_x^2 + f_y^2),\:\: \bar f_y = 0$, which sets $c = f_x / \| \nabla f \|$, $s = - f_y / \| \nabla f \|$.
-This provides the invariant $I_1 = \nabla f$.
-As there are no more free parameters, the expressions for the second-order terms can be read off as:
-
-\begin{align}
-I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} \\
-I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) \\
-I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} 
-\end{align}
-
-\todo[inline]{ Two things to note: (1) SE(2) has similar invars, (2) there is an issue in E(2) with the moving frame: reflection ambiguity. That's why we did it by contraction.
-}
+where $c = \cos \theta$ and $s = \sin \theta$. Because the group has three
+parameters, we choose the cross section of the group orbits to be $\bar{x}
+= 0, \bar{y} = 0, \bar{f}_{\bar{y}} = 0$. We also require that $\bar{f}_{x}
+> 0$ to uniquely define the moving frame. Note that the group action is
+locally free (away from critical points) when prolonged to $J^1$, however
+we prolonged to $J^2$ in order to compute invariants. points. The moving
+frame is then given by the prolonged Euclidean transformation that maps an
+element of  $J^2$ to this cross section. It can be thought of as rotating
+the image about that point so that its gradient is pointing in the positive
+$x$ direction, and then translating the image so the point is mapped to the
+origin.
+
+This choice of moving frame gives $\cos\theta = f_x/\lVert\nabla f\rVert$
+and $\sin\theta = -f_y/\lVert \nabla f \rVert$. The parameters $t_x, t_y$
+are then $t_x = -x\cos\theta + y\sin\theta$ and $t_y = -x\sin\theta -
+y\cos\theta$, however these have no effect on the derivatives, and will
+henceforth be ignored.
+
+The remaining elements not fixed by the cross section, $\bar{f}$,
+$\bar{f}_{\bar{x}}$, $\bar{f}_{\bar{x}\bar{x}}$,
+$\bar{f}_{\bar{x}\bar{y}}$, and $\bar{f}_{\bar{y}\bar{y}}$ are therefore
+all invariant. This gives the following set of invariants:
+\begin{equation}\label{eq:se2invariants}
+\begin{aligned}
+  I_0 &= f \\
+  I_1 &= f_x^2 + f_y^2 & &(= \bar{f}_{\bar{x}}^2)\\
+  I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= I_1\bar{f}_{\bar{x}\bar{x}}) \\
+  I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) &&(= I_1\bar{f}_{\bar{x}\bar{y}})\\
+  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}})
+\end{aligned}
+\end{equation}
+Note that we multiplied each of the second derivative invariants by $I_1$
+so that they would decay smoothly to zero at critical points.
+
+\todo[inline]{c.f. transvectant formulae}
+
+\subsection{The Euclidean Group E(2)}
+An element of the Euclidean group $E(2)$ maps an element $(x, y)$ of
+$\mathbb{R}^2$ to $(\bar{x}, \bar{y})$ as 
+\begin{equation*}
+  \begin{aligned}
+    \bar{x} &=  x\varepsilon\cos\theta  - y\varepsilon\sin\theta + t_x \\
+    \bar{y} &= x\sin\theta  + y\cos\theta + t_y.
+  \end{aligned}
+\end{equation*}
+where $\varepsilon \in \{-1, 1\}$ and the remaining parameters are the same
+as for $SE(2)$. If $\varepsilon = 1$ it is a rigid transformation, and if
+$\varepsilon = -1$ it contains a reflection.
+
+This time, the group action is not free on $J^1$ (with elements of the form
+$(x, y, f, f_x, f_y)$) away from critical points because there are two
+possible transformations that map to the cross section $(0, 0, \bar{f},
+\bar{f}_{\bar{x}}, 0)$ where $\bar{f}_{\bar{x}} > 0$, one that reflects the
+gradient into the positive $x$ direction, and one that rotates.
+
+We again prolong the group action to $J^2$, but this time we expect to need
+to use a second derivative term to determine $\varepsilon$ for the moving
+frame. The derivative transformations are given by
+\begin{equation}
+  \begin{bmatrix}
+  \bar f_{\bar x} \\ \bar f_{\bar y} \\ \bar f_{\bar{x}\bar{x}} \\ \bar f_{\bar{x}\bar{y}} \\ \bar f_{\bar{y}\bar{y}}
+  \end{bmatrix} = 
+  \begin{bmatrix}
+ \varepsilon c & -\varepsilon s & 0 & 0 & 0 \\
+ s & c & 0 & 0 & 0 \\
+0 & 0 & c^2 & -2cs & s^2 \\
+0 & 0 & \varepsilon cs & \varepsilon(c^2 - s^2) & -\varepsilon cs \\
+0 & 0 & s^2 & 2cs & c^2 \\
+  \end{bmatrix}
+  \begin{bmatrix}
+f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} 
+  \end{bmatrix},
+\label{eqn:E2prolongation}
+\end{equation}
+where again $c = \cos\theta$ and $s = \sin\theta$.
+
+We begin by choosing the same cross section as for $SE(2)$, namely $\bar{x} = 0,
+\bar{y} = 0, \bar{f}_{\bar{y}} = 0, \bar{f}_{\bar{x}} > 0$. This gives
+$\cos\theta = \varepsilon f_x / \lVert \nabla f \rVert$ and $\sin\theta =
+-\varepsilon f_y / \lVert \nabla f \rVert$. Under this transformation,
+regardless of whether $\varepsilon = 1$ or $\varepsilon = -1$, the
+derivative $\bar{f}_{\bar{x}} = \lVert \nabla f \rVert$. We need a second
+derivative term to resolve the choice of $\varepsilon$ for the moving
+frame. The only second derivative term in which $\varepsilon$ appears is
+the $\bar{f}_{\bar{x}\bar{y}}$ term. Substituting in for $\cos\theta,
+\sin\theta$, we see that
+\begin{equation*}
+    \bar{f}_{\bar{x}\bar{y}} = \frac{\varepsilon(f_xf_y(f_{yy} - f_{xx}) + (f_x^2 -
+    f_y^2)f_{xy})}{f_x^2 + f_y^2}
+\end{equation*}
+This suggests choosing $\varepsilon$ to make $\bar{f}_{\bar{x}\bar{y}} \ge
+0$. We can then list the invariants:
+\begin{equation}\label{eq:e2invariants}
+\begin{aligned}
+  I_0 &= f \\
+  I_1 &= f_x^2 + f_y^2 & &(= \bar{f}_{\bar{x}}^2)\\
+  I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= I_1\bar{f}_{\bar{x}\bar{x}}) \\
+  I_3 &= \lvert f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2)\rvert
+  &&(= I_1\lvert \bar{f}_{\bar{x}\bar{y}}\rvert)\\
+  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}})
+\end{aligned}
+\end{equation}
+Notice that most, but not all of the $SE(2)$ invariants
+\eqref{eq:se2invariants} are also $E(2)$ invariants. We again multiply
+through the invariants by $I_1$ so that they decay smoothly at critical
+points.
 

### 2020-08-21 paper/newpaper.tex
Draft of tensor contraction section

@@
 \end{abstract}
-
-h
 
@@
 
-/subsection{Transformation notation}
+\subsection{Transformation notation}
 Most of the time we will work on grey-scale transformations of two-dimensional images.
@@
 
+\subsection{Stuff from dispaper to tidy}
 ====
@@
 
-\section{The Invariant Tensor Theorem}
-
-The new contraction mapping computation.
-
-E(2), Sim(2)
-
-Since this will be the first example, put the details of the image here. And remove one of the repeats below.
-
-3D and 4D signatures.
+\section{Differential invariants of E(2) through tensor contraction}
+While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$.
+In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance, they are both the same thing.
+We use subscript indices exclusively, for this reason.
+
+In this setting, a Euclidean transformation acting on $\mathbb{R}^2$ is given
+by an expression of the form:
+\begin{equation*}
+  \bar{x}_i = a_{ij}x_j + b_j,
+\end{equation*}
+using the Einstein summation convention. The orthogonality condition is that $a_{ik}a_{jk} = a_{ki}a_{kj} = \delta_{ij}$.
+
+With respect to $\mathbb{R}^2$, a Cartesian tensor of rank $p$, or $p$-tensor is a $2^p$-tuple of real numbers $C_{i_1\ldots i_p}$ whose components transform under a Euclidean transformation as
+\begin{equation*}
+  \bar{C}_{i_1\ldots i_p} = a_{i_1j_1}\cdots a_{i_pj_p} C_{j_1\ldots j_p}
+\end{equation*}
+and a $0$-tensor is a scalar, or invariant.
+
+The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}} \cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor.
+\todo[inline]{Cite Florack et al, 1993} Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial f / \partial_{i_1} \cdots \partial_{i_p}$ will give a Euclidean invariant.
+
+For example, up to second derivatives, we have the following Euclidean invariants, expressed as tensor contractions:
+\begin{align*}
+  f &= f \\
+  f_if_i &= f_x^2 + f_y^2 \\
+  f_{ii} &= f_{xx}^2 + f_{yy}^2 \\
+  f_{ij} f_{ij} &= f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
+  f_i f_j f_{ij} &= f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}
+\end{align*}
+
+While we can construct any number of invariants this way, there is no guarantee of functional independence of the constructed invariants.
+We will address this issue in Section~\ref{sec:movingframes} when we construct invariants of $E(2)$ and other groups using the method of moving frames.
+
+\todo[inline]{Expand to Sim(2)}
+\todo[inline]{Introduce image that we are going to use in subsequenct examples}
+\todo[inline]{Introduce signatures - 3D and 4D perhaps?}
 

### 2020-08-21 paper/newpaper.tex
Relate MF and tensor invariants for E(2)

@@
 points.
+
+These invariants are a functionally independent, complete, set of polynomial differential invariants up to second derivatives.
+Note that the invariants found previously by tensor contraction can be expressed in terms of these:
+\begin{align*}
+  f = f &= I_0 \\
+  f_if_i = f_x^2 + f_y^2 &= I_1 \\
+  f_{ii} = f_{xx}^2 + f_{yy}^2 &= \frac{I_2 + I_4}{I_1} \\
+  f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 &= I_2\\
+  f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy} &= \frac{I_2^2 + I_4^2 + 2I_3^2}{I_1^2}.
+\end{align*}
 

### 2020-08-26 paper/newpaper.tex
Some additions, not enough

@@
 
+Some examples, plus mention Kendall shape.
+
 The setting that we will consider is a transformation group $\mathcal{G}$
@@
 Most of the time we will work on grey-scale transformations of two-dimensional images.
-In this setting, we define the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$
+In this setting, we define the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$:
 \begin{equation}\label{eq:transformation}
@@
 \end{equation}
-The transformed image is then defined to be
+The transformed image is then defined to be:
 \begin{equation}\label{eq:fbarequalsf}
@@
 \end{equation}
-where $\bar{x}_x = \frac{\partial \varphi_1}{\partial x}(x, y)$, et cetera. It is often convenient to work with $\varphi^{-1}$ instead, which we will do in \S\ref{sec:movingframes}.
+where $\bar{x}_x = \frac{\partial \varphi_1}{\partial x}(x, y)$, et cetera. It is often convenient to work with $\varphi^{-1}$ instead, as in \S\ref{sec:movingframes}.
+
+Mention colour here.
 
@@
 
+Signatures
+
+Idea, some notation, then completeness, bad set, have not removed the recognition problem, just removed the group variation.
+
+---
+TEXT FROM OUR MOBIUS PAPER
+Calabi et al. [9] propose the use of differential invariant signatures for shape analysis, and further
+argue that these should be approximated in a group-invariant way. For example, for the Euclidean
+group, the signature is the shape (; s) regarded as a subset of R2. The claimed advantages
+of the approach are that the signature determines the shape; that it does not depend on the
+choice of initial point on the curve or on parameterization by arclength, and that its G-invariance
+makes it robust; and that it is based on a general procedure for arbitrary objects and groups.
+See [2, 4, 9, 18, 30, 35, 36] for further developments and applications of the invariant signature.
+Although the signature at first sight appears to be complete (e.g., Theorem 5.2 in [9]),
+a more detailed treatment (e.g., [17, 28]) highlights the fact that it is not complete on shapes
+that contain singular parts { straight and circular segments in the Euclidean case. For these
+parts, the signature reduces to a point. Thus, for shapes that have nearly straight or nearly
+circular segments, the signature cannot be robust. In addition, while the signature does not
+depend on the starting point or the parameterization, it takes values in a very complicated set,
+namely, the planar shapes. To compare the invariants of two shapes requires comparing two
+shapes. Essentially, the parameterization-dependence has only been deferred to a later stage
+of the analysis (unless one is content to compare shapes visually). One approach to this is to
+weight the signature, see [32] for more details.
+---
+
 An algorithm to compute invariants and determine complete signature sets is
@@
 
-SE(2) is done via the moving frame by Olver in Ch 8 of CIT.
-
-\section{Differential invariants of E(2) through tensor contraction}
+\section{Differential invariants of $E(2)$ through tensor contraction}
 While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$.
-In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance, they are both the same thing.
-We use subscript indices exclusively, for this reason.
+In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance, as they are equivalent; we therefore use subscript indices exclusively.
 
@@
 
-With respect to $\mathbb{R}^2$, a Cartesian tensor of rank $p$, or $p$-tensor is a $2^p$-tuple of real numbers $C_{i_1\ldots i_p}$ whose components transform under a Euclidean transformation as
+With respect to $\mathbb{R}^2$, a Cartesian tensor of rank $p$, or $p$-tensor is a $2^p$-tuple of real numbers $C_{i_1\ldots i_p}$ whose components transform under a Euclidean transformation as:
 \begin{equation*}
@@
 \todo[inline]{Expand to Sim(2)}
-\todo[inline]{Introduce image that we are going to use in subsequenct examples}
+\todo[inline]{Introduce image that we are going to use in subsequent examples}
 \todo[inline]{Introduce signatures - 3D and 4D perhaps?}
@@
 Note that the weight is the number of edges in the graph.
+
 \begin{table}
@@
 \left(f_{y}\right)^{2}$ \\
-
-3 & 3 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
-    \draw[-] (1) to [out=-150,in=90] (2);
-    \draw[-] (1) to [out=-90,in=30] (2);
-    \draw[-] (1) to (3);
-\end{tikzpicture}
-& $- f_{x} f_{xx} f_{yyy} - f_{x} f_{yy} f_{xxy} + 2 f_{x} f_{xy} f_{xyy} +
-f_{xx} f_{y} f_{xyy} + f_{xxx} f_{y} f_{yy} - 2 f_{y} f_{xy} f_{xxy}$ \\
-
-3 & 3 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
-    \draw[-] (1) to (2);
-    \draw[-] (1) to (3);
-    \draw[-] (1) to (4);
-\end{tikzpicture}
-& $- \left(f_{x}\right)^{3} f_{yyy} + 3 \left(f_{x}\right)^{2} f_{y} f_{xyy} - 3 f_{x} \left(f_{y}\right)^{2} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3}$  \\
-
-3 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
-    \draw[-] (1) to [out=-150,in=90] (2);
-    \draw[-] (1) to [out=-90,in=30] (2);
-    \draw[-] (1) to (3);
-    \draw[-] (2) to (3);
-\end{tikzpicture}
-& $2 f_{xx} f_{yyy} f_{xxy} - 2 f_{xx} \left(f_{xyy}\right)^{2} + 2 f_{xxx}
-f_{yy} f_{xyy} - 2 f_{xxx} f_{yyy} f_{xy} - 2 f_{yy}
-\left(f_{xxy}\right)^{2} + 2 f_{xy} f_{xyy} f_{xxy}$ \\
-
-%=====
-
-3 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
-    \draw[-] (1) to [out=-120,in=120] (2);
-    \draw[-] (1) to [out=-60,in=60] (2);
-    \draw[-] (2) to (3);
-    \draw[-] (3) to (4);
-\end{tikzpicture}
-& $- f_{x} f_{xx} f_{yy} f_{xyy} + f_{x} f_{xx} f_{yyy} f_{xy} - f_{x} f_{xxx} \left(f_{yy}\right)^{2} + 3 f_{x} f_{yy} f_{xy} f_{xxy} - 2 f_{x} \left(f_{xy}\right)^{2} f_{xyy} - \left(f_{xx}\right)^{2} f_{y} f_{yyy} - f_{xx} f_{y} f_{yy} f_{xxy} + 3 f_{xx} f_{y} f_{xy} f_{xyy} + f_{xxx} f_{y} f_{yy} f_{xy} - 2 f_{y} \left(f_{xy}\right)^{2} f_{xxy}$ \\
 
@@
 
-3 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
-    \draw[-] (1) to [out=-120,in=120] (2);
-    \draw[-] (1) to [out=-60,in=60] (2);
-    \draw[-] (2) to (3);
-    \draw[-] (1) to (4);
-\end{tikzpicture}
-& $2 \left(f_{x}\right)^{2} f_{yyy} f_{xxy} - 2 \left(f_{x}\right)^{2} \left(f_{xyy}\right)^{2} - 2 f_{x} f_{xxx} f_{y} f_{yyy} + 2 f_{x} f_{y} f_{xyy} f_{xxy} + 2 f_{xxx} \left(f_{y}\right)^{2} f_{xyy} - 2 \left(f_{y}\right)^{2} \left(f_{xxy}\right)^{2}$ \\
-
-% =========
 2 & 4 &
@@
 
+3 & 3 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to (3);
+\end{tikzpicture}
+& $- f_{x} f_{xx} f_{yyy} - f_{x} f_{yy} f_{xxy} + 2 f_{x} f_{xy} f_{xyy} +
+f_{xx} f_{y} f_{xyy} + f_{xxx} f_{y} f_{yy} - 2 f_{y} f_{xy} f_{xxy}$ \\
+
+3 & 3 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+    \draw[-] (1) to (4);
+\end{tikzpicture}
+& $- \left(f_{x}\right)^{3} f_{yyy} + 3 \left(f_{x}\right)^{2} f_{y} f_{xyy} - 3 f_{x} \left(f_{y}\right)^{2} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3}$  \\
+
+3 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to (3);
+    \draw[-] (2) to (3);
+\end{tikzpicture}
+& $2 f_{xx} f_{yyy} f_{xxy} - 2 f_{xx} \left(f_{xyy}\right)^{2} + 2 f_{xxx}
+f_{yy} f_{xyy} - 2 f_{xxx} f_{yyy} f_{xy} - 2 f_{yy}
+\left(f_{xxy}\right)^{2} + 2 f_{xy} f_{xyy} f_{xxy}$ \\
+
+%=====
+
+3 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to [out=-120,in=120] (2);
+    \draw[-] (1) to [out=-60,in=60] (2);
+    \draw[-] (2) to (3);
+    \draw[-] (3) to (4);
+\end{tikzpicture}
+& $- f_{x} f_{xx} f_{yy} f_{xyy} + f_{x} f_{xx} f_{yyy} f_{xy} - f_{x} f_{xxx} \left(f_{yy}\right)^{2} + 3 f_{x} f_{yy} f_{xy} f_{xxy} - 2 f_{x} \left(f_{xy}\right)^{2} f_{xyy} - \left(f_{xx}\right)^{2} f_{y} f_{yyy} - f_{xx} f_{y} f_{yy} f_{xxy} + 3 f_{xx} f_{y} f_{xy} f_{xyy} + f_{xxx} f_{y} f_{yy} f_{xy} - 2 f_{y} \left(f_{xy}\right)^{2} f_{xxy}$ \\
+
+3 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to [out=-120,in=120] (2);
+    \draw[-] (1) to [out=-60,in=60] (2);
+    \draw[-] (2) to (3);
+    \draw[-] (1) to (4);
+\end{tikzpicture}
+& $2 \left(f_{x}\right)^{2} f_{yyy} f_{xxy} - 2 \left(f_{x}\right)^{2} \left(f_{xyy}\right)^{2} - 2 f_{x} f_{xxx} f_{y} f_{yyy} + 2 f_{x} f_{y} f_{xyy} f_{xxy} + 2 f_{xxx} \left(f_{y}\right)^{2} f_{xyy} - 2 \left(f_{y}\right)^{2} \left(f_{xxy}\right)^{2}$ \\
+
+% =========
 3 & 4 &
@@
 \begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
+    \draw[-] (1) to [out=30,in=150] (2);
+    \draw[-] (1) to [out=-30,in=-150] (2);
+    \draw[-] (1) to [out=10,in=170] (2);
+    \draw[-] (1) to [out=-10,in=-170] (2);
+\end{tikzpicture}
+& $f_{xxxx} f_{yyyy} - 4 f_{xyyy} f_{xxxy} + 3 f_{xxyy}^2$ \\
+
+4 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to [out=-90,in=150] (3);
+    \draw[-] (1) to [out=-30,in=90] (3);
+\end{tikzpicture}
+& $ f_{xx}^2 f_{yyyy} + 2 f_{xx} f_{yy} f_{xxyy} - 4 f_{xx} f_{xy} f_{xyyy} - 4 f_{yy} f_{xy} f_{xxxy} + 4 f_{xy}^2 f_{xxyy} + f_{xxxx} f_{yy}^2$ \\
+
+4 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+\end{tikzpicture} 
+& $ f_{x} f_{xxx} f_{yyyy} - f_x f_{yyy} f_{xxxy} + 3 f_{x} f_{xyy} f_{xxyy} - 3 f_x f_{xyyy} f_{xxy} - f_{xxx} f_y f_{xyyy} + f_{xxxx} f_y f_{yyy} - 3 f_y f_{xyy} f_{xxxy} + 3 f_y f_{xxy} f_{xxyy}$ \\
+
+4 & 4 &
+\begin{tikzpicture}[baseline=0]
     \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
@@
 & $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\
-
-4 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
-    \draw[-] (1) to [out=30,in=150] (2);
-    \draw[-] (1) to [out=-30,in=-150] (2);
-    \draw[-] (1) to [out=10,in=170] (2);
-    \draw[-] (1) to [out=-10,in=-170] (2);
-\end{tikzpicture}
-& $f_{xxxx} f_{yyyy} - 4 f_{xyyy} f_{xxxy} + 3 f_{xxyy}^2$ \\
-
-4 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
-    \draw[-] (1) to [out=-150,in=90] (2);
-    \draw[-] (1) to [out=-90,in=30] (2);
-    \draw[-] (1) to [out=-90,in=150] (3);
-    \draw[-] (1) to [out=-30,in=90] (3);
-\end{tikzpicture}
-& $ f_{xx}^2 f_{yyyy} + 2 f_{xx} f_{yy} f_{xxyy} - 4 f_{xx} f_{xy} f_{xyyy} - 4 f_{yy} f_{xy} f_{xxxy} + 4 f_{xy}^2 f_{xxyy} + f_{xxxx} f_{yy}^2$ \\
-
-4 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
-    \draw[-] (1) to [out=-150,in=90] (2);
-    \draw[-] (1) to [out=-90,in=30] (2);
-    \draw[-] (1) to (2);
-    \draw[-] (1) to (3);
-\end{tikzpicture} 
-& $ f_{x} f_{xxx} f_{yyyy} - f_x f_{yyy} f_{xxxy} + 3 f_{x} f_{xyy} f_{xxyy} - 3 f_x f_{xyyy} f_{xxy} - f_{xxx} f_y f_{xyyy} + f_{xxxx} f_y f_{yyy} - 3 f_y f_{xyy} f_{xxxy} + 3 f_y f_{xxy} f_{xxyy}$ \\
 \end{tabular}
@@
 it can be visualised as a three-dimensional surface; note that this will not
-be complete and may well have a \emph{very large bad set}. For example, we can choose the function value together with the first two partial transvectants to form the signature
+be complete and may well have a very large bad set. For example, we can choose the function value together with the first two partial transvectants to form the signature:
 \begin{equation*}
@@
 \end{equation*}
+
 Fig.~\ref{fig:SA2} shows the function as a greyscale image, the transformed
@@
 \todo[inline]{This needs a friendly introduction, or at least a pointer to the notebooks}
+
+Idea is that it is the transformation back to the cross-section.
 
@@
 Identifying $\R^2$ with $\mathbb{C}$, the M\"obius group is a real 6-dimensional local Lie group acting on $\mathbb{R}^2$.
-It is the smallest nonlinear planar group that contains $SE(2)$, and it is the set of biholomorphic maps of the Riemann sphere; it also has direct applications in image processing since it arises in the {\em conformal camera} model of vision, in which scenes are projected radially onto a sphere \cite{lenz1990group,turski2004geometric}.
+It is the smallest nonlinear planar group that contains $SE(2)$, and it also has direct applications in image processing since it arises in the {\em conformal camera} model of vision, in which scenes are projected radially onto a sphere \cite{lenz1990group,turski2004geometric}; it is also the set of biholomorphic maps of the Riemann sphere.
 %Different shapes may be related by M\"obius transformations, as is explored by Petukhov \cite{petukhov1989non} for biological objects: in one example, the human skull grows approximately by M\"obius transformations.
@@
 
-The 0th order moving frame translates $z$ to $\beta$.
-We can therefore take $\beta=0$; we are also free to take $\delta=1$.
+We are free to take $\delta=1$.
+Then $\bar f = f$ means that $z$ is translated to $\beta$; we can therefore take $\beta=0$.
 This leaves 4 group parameters $a,b,c,d$, where $\alpha = a + i b$, $\gamma = c + i d$, to be determined as follows.
-First we prolong the action to 3rd derivatives of $f$.
-There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 5 invariants.
+We prolong the action to 2nd derivatives of $f$, which is sufficient to allow the group to act freely.
+There are 5 derivatives of $f$ up to order 2, so there will be at least 1 invariant.
+In order to find further invariants the prolongation to 3rd derivatives is required, which will result in at least another four invariants.
+%There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 5 invariants.
 \todo[inline]{General thm for this earlier...}
@@
 \arraycolsep=1.4pt
-\left(
+\left[
 \begin{array}{c}
-  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
+  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} 
  \end{array}
- \right)
+ \right]
  = 
-\left(
-\begin{array}{ccccccccc}
- a & b & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
- -b & a & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
- 2\mu & -2 \rho & a^2 & 2 a b & b^2 & 0 & 0 & 0 & 0 \\
- 2 \rho & 2\mu & -a b & a^2\!-b^2 & a b & 0 & 0 & 0 & 0 \\
- -2\mu & 2 \rho & b^2 & -2 a b & a^2 & 0 & 0 & 0 & 0 \\
- -6 (2 b c d+a \lambda) & 6 (2 a c d-b\lambda) & 6 a \mu &
-  M_{64}  & -6 b \rho & a^3 & 3 a^2 b & 3 a b^2 & b^3 \\
- -6 (2 a c d-b\lambda) & -6 (2 b c d+a \lambda) & M_{73}& M_{74} & 
- M_{75} & -a^2 b & a^3\!-2 a b^2 & 2
-   a^2 b\!-b^3 & a b^2 \\
- 6 (2 b c d+a \lambda) & -6 (2 a c d-b\lambda) & M_{83} & M_{84} & M_{85} & a b^2 & b^3\!-2
-   a^2 b & a^3\!-2 a b^2 & a^2 b \\
- 6 (2 a c d-b\lambda) & 6 (2 b c d+a \lambda) & 6 b \mu & 
-  M_{94} & 6 a \rho & -b^3 & 3 a b^2 & -3 a^2 b & a^3 \\
+\left[
+\begin{array}{ccccc}
+ a & b & 0 & 0 & 0 \\
+ -b & a & 0 & 0 & 0 \\
+ 2\mu & -2 \rho & a^2 & 2 a b & b^2 \\
+ 2 \rho & 2\mu & -a b & a^2\!-b^2 & a b \\
+ -2\mu & 2 \rho & b^2 & -2 a b & a^2 \\
 \end{array}
-\right)\left(
+\right]\left[
 \begin{array}{c}
-f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
+f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\
  \end{array}
- \right).
+ \right].
 \label{eqn:mobius}
  \end{equation}
- where
- \begin{equation*}
- \begin{array}{lll}
-M_{64}=-12abc+6d(a^2-b^2), & 
-M_{73}=4 d a^2+6 b c a-2 b^2 d, & 
-M_{74}=-6 c a^2+12 b d a+6 b^2 c, \\
- M_{75}=-2 d a^2-6 b c a+4 b^2 d, &
- M_{83}=2 c a^2-6 b d a-4 b^2 c, &
- M_{84}=6 (d a^2+2 b c a-b^2 d),\\
- M_{85}=-4 c a^2+6 b d a+2 b^2 c,& 
- M_{94}= -12a b d + 6c(a^2-b^2),\\
-\lambda=d^2-c^2, & 
-\mu = b d - a c, & 
-\rho = b c + a d.
-\end{array}
-\end{equation*}
-
-The moving frame calculation now proceeds as follows.
+
+\noindent where $\mu = b d - a c$ and $\rho = b c + a d$.
+
+%\begin{equation}
+%\arraycolsep=1.4pt
+%\left(
+%\begin{array}{c}
+  %\bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
+ %\end{array}
+ %\right)
+ %= 
+%\left(
+%\begin{array}{ccccccccc}
+ %a & b & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ %-b & a & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ %2\mu & -2 \rho & a^2 & 2 a b & b^2 & 0 & 0 & 0 & 0 \\
+ %2 \rho & 2\mu & -a b & a^2\!-b^2 & a b & 0 & 0 & 0 & 0 \\
+ %-2\mu & 2 \rho & b^2 & -2 a b & a^2 & 0 & 0 & 0 & 0 \\
+ %-6 (2 b c d+a \lambda) & 6 (2 a c d-b\lambda) & 6 a \mu &
+  %M_{64}  & -6 b \rho & a^3 & 3 a^2 b & 3 a b^2 & b^3 \\
+ %-6 (2 a c d-b\lambda) & -6 (2 b c d+a \lambda) & M_{73}& M_{74} & 
+ %M_{75} & -a^2 b & a^3\!-2 a b^2 & 2
+   %a^2 b\!-b^3 & a b^2 \\
+ %6 (2 b c d+a \lambda) & -6 (2 a c d-b\lambda) & M_{83} & M_{84} & M_{85} & a b^2 & b^3\!-2
+   %a^2 b & a^3\!-2 a b^2 & a^2 b \\
+ %6 (2 a c d-b\lambda) & 6 (2 b c d+a \lambda) & 6 b \mu & 
+  %M_{94} & 6 a \rho & -b^3 & 3 a b^2 & -3 a^2 b & a^3 \\
+%\end{array}
+%\right)\left(
+%\begin{array}{c}
+%f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
+ %\end{array}
+ %\right).
+%\label{eqn:mobius}
+ %\end{equation}
+ %where
+ %\begin{equation*}
+ %\begin{array}{lll}
+%M_{64}=-12abc+6d(a^2-b^2), & 
+%M_{73}=4 d a^2+6 b c a-2 b^2 d, & 
+%M_{74}=-6 c a^2+12 b d a+6 b^2 c, \\
+ %M_{75}=-2 d a^2-6 b c a+4 b^2 d, &
+ %M_{83}=2 c a^2-6 b d a-4 b^2 c, &
+ %M_{84}=6 (d a^2+2 b c a-b^2 d),\\
+ %M_{85}=-4 c a^2+6 b d a+2 b^2 c,& 
+ %M_{94}= -12a b d + 6c(a^2-b^2),\\
+%\lambda=d^2-c^2, & 
+%\mu = b d - a c, & 
+%\rho = b c + a d.
+%\end{array}
+%\end{equation*}
+
+The moving frame calculation is then:
 \begin{enumerate}
@@
 $$\bar f_{xx} = \frac{f_{xx}+f_{yy}}{f_x^2 + f_y^2}.$$
-
-\item The four 3rd order invariants are then given by $\bar f_{xxx},\dots, \bar f_{yyy}$ using Equation~(\ref{eqn:mobius}). They are
-rational functions with numerators of degree 6 and denominators $(f_x^2 + f_y^2)^4$, and are relative invariants of weight 8.
 \end{enumerate}
@@
 
-We want to work with polynomials, and so clear denominators. We choose to use $M_1 = f^4_{ii}$ and two of the four 3rd order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where: 
+The four 3rd order invariants can be deduced from the moving frame.
+They are rational functions with numerators of degree 6 and denominators $(f_x^2 + f_y^2)^4$, and are relative invariants of weight 8.
+We want to work with polynomials, and so clear denominators.
+We choose to use $M_1 = (f_{xx} + f_{yy})^4$ and two of the four 3rd order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where:
 $M_2=
@@
 
-The image $f$ and these 3 relative invariants of weight 8 provide a 3-dimensional signature; an example is shown in Figure~\ref{fig:mobius}, although note that it is singular when $f_x=f_y=f_{ii}=0$, a codimension 1 phenomenon for images.
+The image $f$ and these 3 relative invariants of weight 8 provide a 3-dimensional signature; an example is shown in Figure~\ref{fig:mobius}, although note that it is singular when $f_x=f_y=f_{xx}+f_{yy}=0$, a codimension 1 phenomenon for images.
 
@@
 %both $ds$ and $1/\|\nabla f\|$ scale by $|\phi'|$. The sign of $\kappa_s$ is also  invariant,
-%hence $\kappa_s/\|\nabla f\|^2$ is  invariant for any invariant curve. Calculating this invariant
+%hence $\kappa_s/\|\nabla f\|^2$ is  invariant for any invariant curve. 
+%Calculating this invariant
 %for the level sets of $f$ and for their orthogonal curves yields two invariants of $f$ that
@@
 
-The 0th order moving frame translates $(x,y)$ to $(0,0)$.
-We can therefore take $j=k=0$; we will also take $l=1$.
+Requiring that $\bar f = f$ again enables us to clear the translate coefficients, so $k=k=0$; for convenience we will also take $l=1$.
 This leaves 6 group parameters $(a,b,c,d,g,h)$ to be determined.
-First we prolong the group action to 3rd derivatives of $f$.
-Since there are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 3 invariants.
+For free action it is necessary to prolong the group action to 3rd derivatives of $f$.
+Since there are 9 derivatives of $f$ of order 1, 2, and 3, there will be at least 3 invariants.
 
@@
 \label{eq:prolong}
-\left(
+%\rotatebox{90}{$
+\left[
 \begin{array}{c}
@@
  \end{array}
- \right)
+ \right]
  = 
-\left(
+\left[
 \begin{array}{ccccccccc}
@@
 \end{array}
-\right)\left(
+\right]\left[
 \begin{array}{c}
@@
  \end{array}
- \right).
+ \right].%$}
  \end{equation}
@@
 
-Another invariant of $A(2)$ was
+Another invariant of $A(2)$ was:
 
@@
 
-For completeness we write out the invariants explicitly:
+For completeness we write out the invariant signature we use explicitly:
 
@@
 
-\subsection{Colour}
+\subsection{Colour Images}
 
@@
 For $k$ colours, signature sets of dimension up to $k + k(k+1)/2$ can be chosen from the invariants $f^i$ and $f^i_m f^j_m$ for $i,j=1,\dots, k$.
-
-Note that for $k\ge 3$ the 3-dimensional signature $(f^1,f^2,f^3)$ is invariant under all local planar diffeomorphisms; a higher-dimensional signature, involving at least first derivatives, is therefore required.
-
-However, there is a complication, which is that the information in the channels is not independent: colour is built by the intensities in the three channels, and so it there is correlation between them.
+The situation is more complicated that it first appears because the information in the channels is not independent: colour is built by the intensities in the three channels, and so it there is correlation between them.
 This means that the invariant signature identified next are na\"ive, and should be viewed as best-case scenarios.
 We briefly sketch some possibilities for some of the groups that we have considered earlier.
+
+Note that for $k\ge 3$ the 3-dimensional signature $(f^1,f^2,f^3)$ is invariant under all local planar diffeomorphisms; a higher-dimensional signature, involving at least first derivatives, is therefore required.
 

### 2020-10-06 paper/newpaper.tex
Bug fix
Words

@@
 \begin{keywords}
+
 \end{keywords}
@@
 
-Shapes/objects/images can be acted on by simple transformations that change
-their appearance. We want to recognise the objects or identify the set of
-transformations. If the set is a group, then we can seek to either identify
-the group or solve the equivalence problem by
-\begin{enumerate}
-    \item Registration, or
-    \item Invariance.
-\end{enumerate}
-The first is commonly studied but is computationally expensive and prone to
-local minima. If you're not interested in the actual transformation it is
-therefore to be avoided. Here we'll consider invariance. There are many
-choices of type e.g. Fourier, integral, or differential invariants. The
-last set are cheap to compute and have nice theoretical properties but are
-not robust to noise. However, we'll use them anyway. This paper is a
+Biologists differentiate between the {\em form} of an object, and the {\em shape}, being the part of form that is unaffected by size.
+More generally, the appearance of a fixed object in a set of images can vary markedly depending upon such variables as change of pose and relative position to the camera, even though the object itself does not change.
+Such variations highlight the importance of `shape', as opposed to `form', in object recognition.
+
+It is natural to seek representations of objects that vary only with regard to shape change, rather than to any change in form.
+If the space of objects in denoted $M$ and the non-shape transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$.
+This could be done, for example, by transforming all objects to match a chosen target one by registration.
+Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{} will transform all of the shapes into the reference frame of one template example.
+However, analysis on these quotient spaces is rarely simple~\cite{}.
+An alternative option is to seek $\mathcal{G}$-invariant functions on $M$ and use the theory of invariants, which is what we consider here.
+
+Invariant signatures -- self-equivalences
+Different sorts of invariant, and their properties.
+local invariants: occlusions OK
+derivatives: noise is not
+
+have not removed the recognition problem, just removed the group variation.
+
+%Shapes/objects/images can be acted on by simple transformations that change
+%their appearance. We want to recognise the objects or identify the set of
+%transformations. If the set is a group, then we can seek to either identify
+%the group or solve the equivalence problem by
+%\begin{enumerate}
+    %\item Registration, or
+    %\item Invariance.
+%\end{enumerate}
+%The first is commonly studied but is computationally expensive and prone to
+%local minima. If you're not interested in the actual transformation it is
+%therefore to be avoided. Here we'll consider invariance. There are many
+%choices of type e.g. Fourier, integral, or differential invariants. The
+%last set are cheap to compute and have nice theoretical properties but are
+%not robust to noise. However, we'll use them anyway.
+
+This paper is a
 tutorial on differential invariants for planar Lie groups (e.g.
@@
 
-Some examples, plus mention Kendall shape.
-
-The setting that we will consider is a transformation group $\mathcal{G}$
-acting on a manifold $\mathcal{M}$ of dimension $n$. A $d$-th order
-differential invariant is a local scalar function $I: J^{d} (\mathbb{R},
-\mathcal{M} ) \to \mathbb{R}$ that is invariant under the action of
-$\mathcal{G}$, i.e., $I(g(x,u^{(d)})) = I(x, u^{(d)}) \forall g \in
-\mathcal{G}$, where $J^{d}$ denotes the $d$-th order jet space.
-
-\subsection{Transformation notation}
-Most of the time we will work on grey-scale transformations of two-dimensional images.
-In this setting, we define the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$:
+\subsection{Notation}
+
+We define a {\em $k$-colour image} as a triple $(f,\Omega,k)$ where $\Omega\subset\R^n$ (typically, images are planar, so $n=2$), $1\le k\in\mathbb{Z}$ is the number of colour channels, and $f\colon\Omega\to\R^k$.
+The function $f$ will be taken to be as smooth as necessary.
+Consider a (finite or infinite-dimensional) local transformation group $\mathcal{G}$.
+A transformation $\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) = (f\circ\varphi^{-1},\varphi(\Omega),k)$.
+For many of our examples we consider greyscale images, so $k=1$, but we discuss colour images in Section~\ref{sec:colour}.
+Also, since we work locally, we will usually omit the domain $\Omega$.
+
+In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$.
+This is known as the jet space, or jet bundle~\cite{OlverJets}.
+The $d$-th order jet space $J^d$ consists of the function itself and the set of all partial derivatives of the function up to order $d$.
+(Note that there are $\left( \begin{array}{c} d+k-1 \\ k \end{array} \right)$ partial derivatives of order $d$).
+As the group $\mathcal{G}$ is local, it acts naturally on derivatives of the transformation, and so each individual transformation $\varphi \in \mathcal{G}$ can be prolonged to act on the jet space $J^d$.
+We can thus prolong the action of the group and consider the action of $\mathcal{G}$ on not just $f$, but all derivatives of $f$ up to order $d$.
+A $d$-th order differential invariant is then a local scalar function $I: J^{d} (f,\Omega, k) \to \mathbb{R}$ that is invariant under the action of $\mathcal{G}$, i.e., $I(\varphi(f,\Omega, k)) = I(f, \Omega, k) \forall \varphi \in \mathcal{G}$.
+
+An $m$-dimensional signature set is the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e., the set $\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$.
+A signature set is complete for $f$ if it determines $f$ up to transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
+Where the signature set is not complete, it is still desirable that the set of objects that are indistinguishable from other be as small as possible.
+Useful properties for invariants are discussed in detail in~\cite{UsMobius}.
+
+NEED TO TALK ABOUT WHEN IT IS SINGULAR
+
+For the case of two-dimensional greyscale images it is often convenient to work in coordinates.
+In this case the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$ is given by:
 \begin{equation}\label{eq:transformation}
-  \mathbf{x} \mapsto \bar{\mathbf{x}} = \varphi(\mathbf{x})
+  \mathbf{x} \mapsto \bar{\mathbf{x}} = \varphi(\mathbf{x}).
 \end{equation}
@@
 
-Mention colour here.
-
-\subsection{Stuff from dispaper to tidy}
-====
-Let $G$ be a (finite or infinite-dimensional) local planar transformation
-group.  A {\em $k$-colour image} is a triple $(f,\Omega,k)$ where
-$\Omega\subset\R^2$, $1\le k\in\mathbb{Z}$, and $f\colon\Omega\to\R^k$. The
-function $f$ will be taken to be as smooth as necessary.  A transformation
-$\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) =
-(f\circ\varphi^{-1},\varphi(\Omega),k)$.  (As we work locally, we will
-usually omit the domain $\Omega$; if the number of colours $k$ is not
-given, we assume $k=1$.)  A differential invariant is an invariant of the
-prolonged action of $G$ on the derivatives of $f$, i.e., a function $I$ of
-the values of $f$ and its derivatives at a point such that $I(f)(x,y) =
-I(\varphi\cdot f)(\varphi(x,y))$. An {\em $m$-dimensional signature set} is
-the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e. the set
-$\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$.  A signature set is complete
-for $f$ if it determines $f$ up to transformations from $G$, i.e. if
-$\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies
-there exists a transformation $\varphi\in G$ such that $\tilde f =
-\varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
-
-Signatures
-
-Idea, some notation, then completeness, bad set, have not removed the recognition problem, just removed the group variation.
-
+\subsection{Relevant Literature}
 ---
@@
 argue that these should be approximated in a group-invariant way. For example, for the Euclidean
-group, the signature is the shape (; s) regarded as a subset of R2. The claimed advantages
+group, the signature is the shape \todo[inline]{something didn't copy paste correctly here} (??; ??s) regarded as a subset of R2. The claimed advantages
 of the approach are that the signature determines the shape; that it does not depend on the
@@
 
+JUSTIFY THIS SET OF GROUPS
+
 \todo[inline]{Use T(2) as an example}
-
-local invariants: occlusions OK
-derivatives: noise is not
-
-signatures, dimensions, orders
-Bad set, completeness
 
@@
 
-\section{Differential invariants of $E(2)$ through tensor contraction}
-While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$.
-In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance, as they are equivalent; we therefore use subscript indices exclusively.
-
-In this setting, a Euclidean transformation acting on $\mathbb{R}^2$ is given
-by an expression of the form:
-\begin{equation*}
-  \bar{x}_i = a_{ij}x_j + b_j,
-\end{equation*}
-using the Einstein summation convention. The orthogonality condition is that $a_{ik}a_{jk} = a_{ki}a_{kj} = \delta_{ij}$.
-
-With respect to $\mathbb{R}^2$, a Cartesian tensor of rank $p$, or $p$-tensor is a $2^p$-tuple of real numbers $C_{i_1\ldots i_p}$ whose components transform under a Euclidean transformation as:
-\begin{equation*}
-  \bar{C}_{i_1\ldots i_p} = a_{i_1j_1}\cdots a_{i_pj_p} C_{j_1\ldots j_p}
-\end{equation*}
-and a $0$-tensor is a scalar, or invariant.
-
-The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}} \cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor.
-\todo[inline]{Cite Florack et al, 1993} Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial f / \partial_{i_1} \cdots \partial_{i_p}$ will give a Euclidean invariant.
-
-For example, up to second derivatives, we have the following Euclidean invariants, expressed as tensor contractions:
-\begin{align*}
-  f &= f \\
-  f_if_i &= f_x^2 + f_y^2 \\
-  f_{ii} &= f_{xx}^2 + f_{yy}^2 \\
-  f_{ij} f_{ij} &= f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
-  f_i f_j f_{ij} &= f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}
-\end{align*}
-
-While we can construct any number of invariants this way, there is no guarantee of functional independence of the constructed invariants.
-We will address this issue in Section~\ref{sec:movingframes} when we construct invariants of $E(2)$ and other groups using the method of moving frames.
-
-\todo[inline]{Expand to Sim(2)}
-\todo[inline]{Introduce image that we are going to use in subsequent examples}
-\todo[inline]{Introduce signatures - 3D and 4D perhaps?}
-
-\section{Differential invariants through transvectants}
-
-One way to compute invariants is to compare the action of group elements on separate copies of the underlying space.
-For images, this is typically $\mathbb{R}^2$; colour images in $\mathbb{R}^{2k}$ will be considered in Section~\ref{sec:aaah}.
-
-We will demonstrate this for the affine group $A(2)$ and its subgroup
-$SA(2)$ where, following the treatment in~\cite{OlverCIT}, this leads to
-Cayley's Omega Process~\cite{Cayley}.
-
-Consider $\mathbf{x}_i \in \mathbb{R}^2, i=1,2$, so that $\mathbf{x}_i$ can
-be written in coordinates as $(x_i, y_i)$.
-Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$.
-Now consider applying the same affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + \mathbf{b}$ where $A \in GL(2,\mathbb{R}$) and $\mathbf{b} \in \mathbb{R}^2$.
-Then the Omega Process is a second-order differential operator defined by:
-\begin{equation}
-\Omega_{ij} = \begin{vmatrix} \frac{\partial}{\partial x_i} &
-\frac{\partial}{\partial y_i} \\ \frac{\partial}{\partial x_j} &
-\frac{\partial}{\partial y_j} \end{vmatrix} = 
-\frac{\partial^2}{\partial x_i
-\partial y_j} - \frac{\partial^2}{\partial x_j \partial y_i}.
-\end{equation}
-
-Under the above affine transformation, $\Omega_{ij} \mapsto (\det A)^{-1}
-\Omega_{ij}$. Note that $(\det A)^{-1}$ has no dependence on the coordinates.
-The Omega Process can be applied to pairs of smooth functions as follows,
-writing $\frac{\partial f}{\partial x}$ as $f_x$:
-
-\begin{equation}
-\Omega_{ij} \left(f(x_i, y_i) g(x_j, y_j)\right) = f_{x_i}g_{y_j} - f_{y_i}g_{x_j}
-\end{equation}
-
-Identifying $x_i = x_j = x, y_i = y_j = y$ gives us functions of $x$ and $y$
-that only vary by a scaling factor of $(\det A)^{-1}$ when $\mathbf{x}$ is
-mapped by an affine transformation. This matches the definition of a
-first-order partial transvectant of two functions:
-
-\begin{equation}
-\mbox{tr} \Omega_{ij} f(x_i, y_i) g(x_j, y_j),
-\end{equation}
-
-\noindent where $\mbox{tr}$  is the operator that identifies the coordinates of each function $x_i = x_j = x, y_i = y_j = y$.
-
-This can be generalised to $n$ functions $f^{(1)}(x_1, y_1), \ldots, f^{(n)}(x_n, y_n)$ and $r$-th order~\cite{Olver} to define a partial transvectant as:
-
-\begin{equation}
-\mbox{tr} \left[\left( \Pi_{k=1}^r \Omega_{i_k j_k} \right) f^{(1)}(x_1, y_1)
-f^{(2)}(x_2, y_2), \ldots f^{(n)} (x_n, y_n)\right]
-\end{equation}
-where $i_k \neq j_k \in \{1, \ldots, n\}$.
-
-Under this formula we end with a factor $(\det A)^{-r}$ in place of $(\det
-A)^{-1}$ that we saw previously, when all $n$ copies of $\mathbb{R}^2$ are
-transformed by the same affine function $\mathbf{x} \mapsto A\mathbf{x} +
-\mathbf{b}$. $r$ is referred to as the weight of the partial
-transvectant. It can also be useful to consider the maximum order of
-derivative in the transvectant, which we term degree, e.g., $f_{xy}^2 f_x
-f_y$ has degree 2. Note also that the individual pairwise Omega processes commute.
-
-For the current case it is sufficient to consider $n$ copies of the same
-function $f$. If we represent each copy (of $\mathbb{R}^2$) as a node on a
-undirected graph, and each Omega process $\Omega_{ij}$ as an edge joining
-nodes $i$ and $j$, a partial transvectant can be compactly represented in a
-graphical form.
-
-For example, consider a weight $2$ transvectant defined as
-\begin{align*}
-    \mbox{tr} &\left[(\Omega_{12}\Omega_{12}) f(x_1, y_1)f(x_2, y_2)\right] \\
-    &= \mbox{tr}\left[(\partial_{x_1 y_2} - \partial_{x_2y_1})(\partial_{x_1 y_2} -
-    \partial_{x_2y_1})f(x_1, y_1)f(x_2, y_2)\right]\\
-    &= \mbox{tr}\left[\left(\partial_{x_1 y_2} - \partial_{x_2 y_1}\right)\left(f_x(x_1, y_1)f_y(x_2, y_2) - f_y(x_1, y_1)f_x(x_2, y_2)\right)\right] \\
-    &= \mbox{tr}\left[f_{xx}(x_1, y_1)f_{yy}(x_2, y_2) - f_{xy}(x_1, y_1)f_{xy}(x_2, y_2)\right] \\
-    &= f_{xx}(x, y) f_{yy}(x, y) - f_{xy}(x, y)^2
-\end{align*}
-This is a degree $2$ partial transvectant as it involves derivatives of $f$
-up to second order, and can be represented graphically by the following
-diagram,
-\begin{center}
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
-    \draw[-] (1) to [out=30,in=150] (2);
-    \draw[-] (1) to [out=-30,in=-150] (2);
-\end{tikzpicture}
-\end{center}
-where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$.
-Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} shows all possible nonzero partial
-transvectants of $A_2$ up to weight $4$ that can be generated in this way.
-Note that the weight is the number of edges in the graph.
-
-\begin{table}
-\centering
-\begin{tabular}{cccp{11cm}}
-Degree & Weight & Diagram & Partial transvectant\\
-\hline
-2 & 2 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
-    \draw[-] (1) to [out=30,in=150] (2);
-    \draw[-] (1) to [out=-30,in=-150] (2);
-\end{tikzpicture}
-& $2 f_{xx} f_{yy} - 2 \left(f_{xy}\right)^{2}$ \\
-
-2 & 2 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
-    \draw[-] (1) to (2);
-    \draw[-] (1) to (3);
-\end{tikzpicture}
-& $\left(f_{x}\right)^{2} f_{yy} - 2 f_{x} f_{y} f_{xy} + f_{xx}
-\left(f_{y}\right)^{2}$ \\
-
-2 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
-    \draw[-] (1) to (2);
-    \draw[-] (2) to (3);
-    \draw[-] (3) to (4);
-    \draw[-] (4) to (1);
-\end{tikzpicture}
-& $2 \left(f_{xx}\right)^{2} \left(f_{yy}\right)^{2} - 4 f_{xx} f_{yy} \left(f_{xy}\right)^{2} + 2 \left(f_{xy}\right)^{4}$ \\
-
-2 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
-    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
-    \draw[-] (1) to (2);
-    \draw[-] (2) to (3);
-    \draw[-] (3) to (4);
-    \draw[-] (4) to (5);
-\end{tikzpicture}
-& $\left(f_{x}\right)^{2} f_{xx} \left(f_{yy}\right)^{2} - \left(f_{x}\right)^{2} f_{yy} \left(f_{xy}\right)^{2} - 2 f_{x} f_{xx} f_{y} f_{yy} f_{xy} + 2 f_{x} f_{y} \left(f_{xy}\right)^{3} + \left(f_{xx}\right)^{2} \left(f_{y}\right)^{2} f_{yy} - f_{xx} \left(f_{y}\right)^{2} \left(f_{xy}\right)^{2}$ \\
-
-3 & 3 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
-    \draw[-] (1) to [out=-150,in=90] (2);
-    \draw[-] (1) to [out=-90,in=30] (2);
-    \draw[-] (1) to (3);
-\end{tikzpicture}
-& $- f_{x} f_{xx} f_{yyy} - f_{x} f_{yy} f_{xxy} + 2 f_{x} f_{xy} f_{xyy} +
-f_{xx} f_{y} f_{xyy} + f_{xxx} f_{y} f_{yy} - 2 f_{y} f_{xy} f_{xxy}$ \\
-
-3 & 3 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
-    \draw[-] (1) to (2);
-    \draw[-] (1) to (3);
-    \draw[-] (1) to (4);
-\end{tikzpicture}
-& $- \left(f_{x}\right)^{3} f_{yyy} + 3 \left(f_{x}\right)^{2} f_{y} f_{xyy} - 3 f_{x} \left(f_{y}\right)^{2} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3}$  \\
-
-3 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
-    \draw[-] (1) to [out=-150,in=90] (2);
-    \draw[-] (1) to [out=-90,in=30] (2);
-    \draw[-] (1) to (3);
-    \draw[-] (2) to (3);
-\end{tikzpicture}
-& $2 f_{xx} f_{yyy} f_{xxy} - 2 f_{xx} \left(f_{xyy}\right)^{2} + 2 f_{xxx}
-f_{yy} f_{xyy} - 2 f_{xxx} f_{yyy} f_{xy} - 2 f_{yy}
-\left(f_{xxy}\right)^{2} + 2 f_{xy} f_{xyy} f_{xxy}$ \\
-
-%=====
-
-3 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
-    \draw[-] (1) to [out=-120,in=120] (2);
-    \draw[-] (1) to [out=-60,in=60] (2);
-    \draw[-] (2) to (3);
-    \draw[-] (3) to (4);
-\end{tikzpicture}
-& $- f_{x} f_{xx} f_{yy} f_{xyy} + f_{x} f_{xx} f_{yyy} f_{xy} - f_{x} f_{xxx} \left(f_{yy}\right)^{2} + 3 f_{x} f_{yy} f_{xy} f_{xxy} - 2 f_{x} \left(f_{xy}\right)^{2} f_{xyy} - \left(f_{xx}\right)^{2} f_{y} f_{yyy} - f_{xx} f_{y} f_{yy} f_{xxy} + 3 f_{xx} f_{y} f_{xy} f_{xyy} + f_{xxx} f_{y} f_{yy} f_{xy} - 2 f_{y} \left(f_{xy}\right)^{2} f_{xxy}$ \\
-
-3 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
-    \draw[-] (1) to [out=-120,in=120] (2);
-    \draw[-] (1) to [out=-60,in=60] (2);
-    \draw[-] (2) to (3);
-    \draw[-] (1) to (4);
-\end{tikzpicture}
-& $2 \left(f_{x}\right)^{2} f_{yyy} f_{xxy} - 2 \left(f_{x}\right)^{2} \left(f_{xyy}\right)^{2} - 2 f_{x} f_{xxx} f_{y} f_{yyy} + 2 f_{x} f_{y} f_{xyy} f_{xxy} + 2 f_{xxx} \left(f_{y}\right)^{2} f_{xyy} - 2 \left(f_{y}\right)^{2} \left(f_{xxy}\right)^{2}$ \\
-
-% =========
-3 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
-    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
-    \draw[-] (1) to (2);
-    \draw[-] (1) to (3);
-    \draw[-] (1) to (4);
-    \draw[-] (4) to (5);
-\end{tikzpicture}
-& $- \left(f_{x}\right)^{3} f_{yy} f_{xyy} + \left(f_{x}\right)^{3} f_{yyy} f_{xy} - \left(f_{x}\right)^{2} f_{xx} f_{y} f_{yyy} + 2 \left(f_{x}\right)^{2} f_{y} f_{yy} f_{xxy} - \left(f_{x}\right)^{2} f_{y} f_{xy} f_{xyy} + 2 f_{x} f_{xx} \left(f_{y}\right)^{2} f_{xyy} - f_{x} f_{xxx} \left(f_{y}\right)^{2} f_{yy} - f_{x} \left(f_{y}\right)^{2} f_{xy} f_{xxy} - f_{xx} \left(f_{y}\right)^{3} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3} f_{xy}$ \\
-\end{tabular}
-\caption{Details and graphical representations of all partial transvectants up to degree $3$ of copies of a function $f$ under a transformation in $A(2)$.}
-\label{tab:transvectants1}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{cccp{11cm}}
-Degree & Weight & Diagram & Partial transvectant\\
-\hline
-4 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
-    \draw[-] (1) to [out=30,in=150] (2);
-    \draw[-] (1) to [out=-30,in=-150] (2);
-    \draw[-] (1) to [out=10,in=170] (2);
-    \draw[-] (1) to [out=-10,in=-170] (2);
-\end{tikzpicture}
-& $f_{xxxx} f_{yyyy} - 4 f_{xyyy} f_{xxxy} + 3 f_{xxyy}^2$ \\
-
-4 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
-    \draw[-] (1) to [out=-150,in=90] (2);
-    \draw[-] (1) to [out=-90,in=30] (2);
-    \draw[-] (1) to [out=-90,in=150] (3);
-    \draw[-] (1) to [out=-30,in=90] (3);
-\end{tikzpicture}
-& $ f_{xx}^2 f_{yyyy} + 2 f_{xx} f_{yy} f_{xxyy} - 4 f_{xx} f_{xy} f_{xyyy} - 4 f_{yy} f_{xy} f_{xxxy} + 4 f_{xy}^2 f_{xxyy} + f_{xxxx} f_{yy}^2$ \\
-
-4 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
-    \draw[-] (1) to [out=-150,in=90] (2);
-    \draw[-] (1) to [out=-90,in=30] (2);
-    \draw[-] (1) to (2);
-    \draw[-] (1) to (3);
-\end{tikzpicture} 
-& $ f_{x} f_{xxx} f_{yyyy} - f_x f_{yyy} f_{xxxy} + 3 f_{x} f_{xyy} f_{xxyy} - 3 f_x f_{xyyy} f_{xxy} - f_{xxx} f_y f_{xyyy} + f_{xxxx} f_y f_{yyy} - 3 f_y f_{xyy} f_{xxxy} + 3 f_y f_{xxy} f_{xxyy}$ \\
-
-4 & 4 &
-\begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
-    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
-    \draw[-] (1) to (2);
-    \draw[-] (1) to (3);
-    \draw[-] (1) to (4);
-    \draw[-] (1) to (5);
-\end{tikzpicture}
-& $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\
-\end{tabular}
-\caption{Details and graphical representations of all partial transvectants of weight $4$ of copies of a function $f$ under a transformation in $A(2)$.}
-\label{tab:transvectants2}
-\end{table}
-
-\todo{Explain}
-
-\subsection{Signatures of $SA(2)$ and $A(2)$}
-Recall that invariants of a supergroup are automatically invariants of any of
-its subgroups.
-For example, invariants of $A(2)$ are automatically invariants of $SA(2)$, but not necessarily vice versa.
-Any of the partial transvectants found in Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} are invariants of $SA(2)$ (as the determinant is $1$) but only up to scale factor ($\det A^{-r}$) of $A(2)$.
-
-Hence, we can form a signature for $SA(2)$ by choosing any combination of
-partial transvectants. We'll choose a signature with three components so that
-it can be visualised as a three-dimensional surface; note that this will not
-be complete and may well have a very large bad set. For example, we can choose the function value together with the first two partial transvectants to form the signature:
-\begin{equation*}
-    \left(f, f_{xx}f_{yy}-f_{xy}^2, f_x^2f_{yy} - 2f_xf_yf_{xy} + f_{xx}f_y^2\right)
-\end{equation*}
-
-\subsubsection{Example}
-Consider as our image, the function $f(x, y) = 0.5 - 0.2x - 0.3y - 0.05x^2 +
-0.03xy + 0.04y^2 + 0.03y^3 +0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3$
-defined on $[0, 1]\times[0, 1]$.
-\todo[inline]{remake figure with modified matrix. Also modify function so it has some features like a critical point}
-We'll subject our image to a special affine transformation:
-\begin{equation*}
-\mathbf{x} \mapsto \frac{1}{1.1}\begin{bmatrix} 0.6875 & 1.1 \\ -0.6 & 0.8 \end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
-\end{equation*}
-
-Fig.~\ref{fig:SA2} shows the function as a greyscale image, the transformed
-function, and the signatures of both the untransformed and transformed
-images.
-\begin{figure}
-\centering
-\includegraphics[width=.45\textwidth]{Figs/f_transformed_SA2.png}
-\includegraphics[width=.45\textwidth]{Figs/SA2_signature.png}
-\caption{\todo[inline]{add extra crap} A sample $SA(2)$ Transform and 3D signature. Mention what's going on with the grid.}
-\label{fig:SA2}
-\end{figure}
-
-\subsubsection{Moving on to $A(2)$, \ldots}
-Using the same function as an example, 
-\begin{figure}
-\centering
-\includegraphics[width=.45\textwidth]{Figs/f_transformed_A2.png}
-\includegraphics[width=.45\textwidth]{Figs/A2_signature.png}
-\caption{A sample $A(2)$ Transform and 3D signature.}
-\label{fig:A2}
-\end{figure}
-
-For $A(2)$ the weight of the partial transvectants prevents them from being invariants.
-They can be normalised by choosing only those where all components have the same weight and projecting them onto a unit hypersphere.
-Instead, we select ratios of partial transvectants.
-It is beneficial to choose the numerator and denominator so that they have different critical points, which can be achieved by adding together partial transvectants of the same weight as appropriate.
-
-====
-
 We consider as our image, the following function, defined on $[-1, 1]
@@
 
-Discussion of singularities.
-
-And then a list of explicit invariants by group.
-
-And the signatures.
+\section{Differential invariants of $E(2)$ through tensor contraction}
+While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$.
+In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance, as they are equivalent; we therefore use subscript indices exclusively.
+
+In this setting, a Euclidean transformation acting on $\mathbb{R}^2$ is given
+by an expression of the form:
+\begin{equation*}
+  \bar{x}_i = a_{ij}x_j + b_j,
+\end{equation*}
+using the Einstein summation convention. The orthogonality condition is that $a_{ik}a_{jk} = a_{ki}a_{kj} = \delta_{ij}$.
+
+With respect to $\mathbb{R}^2$, a Cartesian tensor of rank $p$, or $p$-tensor is a $2^p$-tuple of real numbers $C_{i_1\ldots i_p}$ whose components transform under a Euclidean transformation as:
+\begin{equation*}
+  \bar{C}_{i_1\ldots i_p} = a_{i_1j_1}\cdots a_{i_pj_p} C_{j_1\ldots j_p}
+\end{equation*}
+and a $0$-tensor is a scalar, or invariant.
+
+The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}} \cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor.
+\todo[inline]{Cite Florack et al, 1993} Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial f / \partial_{i_1} \cdots \partial_{i_p}$ will give a Euclidean invariant.
+
+For example, up to second derivatives, we have the following Euclidean invariants, expressed as tensor contractions:
+\begin{align*}
+  f &= f \\
+  f_if_i &= f_x^2 + f_y^2 \\
+  f_{ii} &= f_{xx}^2 + f_{yy}^2 \\
+  f_{ij} f_{ij} &= f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
+  f_i f_j f_{ij} &= f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}
+\label{eq:se2}
+\end{align*}
+
+While we can construct any number of invariants this way, there is no guarantee of functional independence of the constructed invariants.
+We will address this issue in Section~\ref{sec:movingframes} when we construct invariants of $E(2)$ and other groups using the method of moving frames.
+
+\todo[inline]{Expand to Sim(2)}
+\todo[inline]{Introduce image that we are going to use in subsequent examples}
+\todo[inline]{Introduce signatures - 3D and 4D perhaps?}
+
+\section{Differential invariants through transvectants}
+
+Another way to compute invariants is to compare the action of group elements on separate copies of the underlying space (here, $\mathbb{R}^2$).
+
+We will demonstrate this for the affine group $A(2)$ and its subgroup
+$SA(2)$ where, following the treatment in~\cite{OlverCIT}, this leads to
+Cayley's Omega Process~\cite{Cayley}.
+
+Consider $\mathbf{x}_i \in \mathbb{R}^2, i=1,2$, so that $\mathbf{x}_i$ can
+be written in coordinates as $(x_i, y_i)$.
+Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$.
+Now consider applying the same affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + \mathbf{b}$ where $A \in GL(2,\mathbb{R}$) and $\mathbf{b} \in \mathbb{R}^2$.
+Then the Omega Process is a second-order differential operator defined by:
+\begin{equation}
+\Omega_{ij} = \begin{vmatrix} \frac{\partial}{\partial x_i} &
+\frac{\partial}{\partial y_i} \\ \frac{\partial}{\partial x_j} &
+\frac{\partial}{\partial y_j} \end{vmatrix} = 
+\frac{\partial^2}{\partial x_i
+\partial y_j} - \frac{\partial^2}{\partial x_j \partial y_i}.
+\end{equation}
+
+Under the above affine transformation, $\Omega_{ij} \mapsto (\det A)^{-1}
+\Omega_{ij}$. Note that $(\det A)^{-1}$ has no dependence on the coordinates.
+The Omega Process can be applied to pairs of smooth functions as follows,
+writing $\frac{\partial f}{\partial x}$ as $f_x$:
+
+\begin{equation}
+\Omega_{ij} \left(f(x_i, y_i) g(x_j, y_j)\right) = f_{x_i}g_{y_j} - f_{y_i}g_{x_j}.
+\end{equation}
+
+Identifying $x_i = x_j = x, y_i = y_j = y$ gives us functions of $x$ and $y$
+that only vary by a scaling factor of $(\det A)^{-1}$ when $\mathbf{x}$ is
+mapped by an affine transformation. This matches the definition of a
+first-order partial transvectant of two functions:
+
+\begin{equation}
+\mbox{tr} \Omega_{ij} f(x_i, y_i) g(x_j, y_j),
+\end{equation}
+
+\noindent where $\mbox{tr}$  is the operator that identifies the coordinates of each function $x_i = x_j = x, y_i = y_j = y$.
+
+This can be generalised to $n$ functions $f^{(1)}(x_1, y_1), \ldots, f^{(n)}(x_n, y_n)$ and $r$-th order~\cite{Olver} to define a partial transvectant as:
+
+\begin{equation}
+\mbox{tr} \left[\left( \Pi_{k=1}^r \Omega_{i_k j_k} \right) f^{(1)}(x_1, y_1)
+f^{(2)}(x_2, y_2), \ldots f^{(n)} (x_n, y_n)\right],
+\end{equation}
+where $i_k \neq j_k \in \{1, \ldots, n\}$.
+
+Under this formula we end with a factor $(\det A)^{-r}$ in place of $(\det
+A)^{-1}$ that we saw previously, when all $n$ copies of $\mathbb{R}^2$ are
+transformed by the same affine function $\mathbf{x} \mapsto A\mathbf{x} +
+\mathbf{b}$. $r$ is referred to as the weight of the partial
+transvectant. It can also be useful to consider the maximum order of
+derivative in the transvectant, which we term degree, e.g., $f_{xy}^2 f_x
+f_y$ has degree 2. Note also that the individual pairwise Omega processes commute.
+
+For the current case it is sufficient to consider $n$ copies of the same
+function $f$. If we represent each copy (of $\mathbb{R}^2$) as a node on a
+undirected graph, and each Omega process $\Omega_{ij}$ as an edge joining
+nodes $i$ and $j$, a partial transvectant can be compactly represented in a
+graphical form.
+
+For example, consider a weight $2$ transvectant defined as:
+\begin{align*}
+    \mbox{tr} &\left[(\Omega_{12}\Omega_{12}) f(x_1, y_1)f(x_2, y_2)\right] \\
+    &= \mbox{tr}\left[(\partial_{x_1 y_2} - \partial_{x_2y_1})(\partial_{x_1 y_2} -
+    \partial_{x_2y_1})f(x_1, y_1)f(x_2, y_2)\right]\\
+    &= \mbox{tr}\left[\left(\partial_{x_1 y_2} - \partial_{x_2 y_1}\right)\left(f_x(x_1, y_1)f_y(x_2, y_2) - f_y(x_1, y_1)f_x(x_2, y_2)\right)\right] \\
+    &= \mbox{tr}\left[f_{xx}(x_1, y_1)f_{yy}(x_2, y_2) - f_{xy}(x_1, y_1)f_{xy}(x_2, y_2)\right] \\
+    &= f_{xx}(x, y) f_{yy}(x, y) - f_{xy}(x, y)^2.
+\end{align*}
+This is a degree $2$ partial transvectant as it involves derivatives of $f$
+up to second order, and can be represented graphically by the following
+diagram:
+\begin{center}
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
+    \draw[-] (1) to [out=30,in=150] (2);
+    \draw[-] (1) to [out=-30,in=-150] (2);
+\end{tikzpicture}
+\end{center}
+where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$.
+Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} shows all possible nonzero partial
+transvectants of $A_2$ up to weight $4$ that can be generated in this way.
+Note that the weight is the number of edges in the graph.
+
+\begin{table}
+\centering
+\begin{tabular}{cccp{11cm}}
+Degree & Weight & Diagram & Partial transvectant\\
+\hline
+2 & 2 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
+    \draw[-] (1) to [out=30,in=150] (2);
+    \draw[-] (1) to [out=-30,in=-150] (2);
+\end{tikzpicture}
+& $2 f_{xx} f_{yy} - 2 \left(f_{xy}\right)^{2}$ \\
+
+2 & 2 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+\end{tikzpicture}
+& $\left(f_{x}\right)^{2} f_{yy} - 2 f_{x} f_{y} f_{xy} + f_{xx}
+\left(f_{y}\right)^{2}$ \\
+
+2 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to (2);
+    \draw[-] (2) to (3);
+    \draw[-] (3) to (4);
+    \draw[-] (4) to (1);
+\end{tikzpicture}
+& $2 \left(f_{xx}\right)^{2} \left(f_{yy}\right)^{2} - 4 f_{xx} f_{yy} \left(f_{xy}\right)^{2} + 2 \left(f_{xy}\right)^{4}$ \\
+
+2 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
+    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
+    \draw[-] (1) to (2);
+    \draw[-] (2) to (3);
+    \draw[-] (3) to (4);
+    \draw[-] (4) to (5);
+\end{tikzpicture}
+& $\left(f_{x}\right)^{2} f_{xx} \left(f_{yy}\right)^{2} - \left(f_{x}\right)^{2} f_{yy} \left(f_{xy}\right)^{2} - 2 f_{x} f_{xx} f_{y} f_{yy} f_{xy} + 2 f_{x} f_{y} \left(f_{xy}\right)^{3} + \left(f_{xx}\right)^{2} \left(f_{y}\right)^{2} f_{yy} - f_{xx} \left(f_{y}\right)^{2} \left(f_{xy}\right)^{2}$ \\
+
+3 & 3 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to (3);
+\end{tikzpicture}
+& $- f_{x} f_{xx} f_{yyy} - f_{x} f_{yy} f_{xxy} + 2 f_{x} f_{xy} f_{xyy} +
+f_{xx} f_{y} f_{xyy} + f_{xxx} f_{y} f_{yy} - 2 f_{y} f_{xy} f_{xxy}$ \\
+
+3 & 3 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+    \draw[-] (1) to (4);
+\end{tikzpicture}
+& $- \left(f_{x}\right)^{3} f_{yyy} + 3 \left(f_{x}\right)^{2} f_{y} f_{xyy} - 3 f_{x} \left(f_{y}\right)^{2} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3}$  \\
+
+3 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to (3);
+    \draw[-] (2) to (3);
+\end{tikzpicture}
+& $2 f_{xx} f_{yyy} f_{xxy} - 2 f_{xx} \left(f_{xyy}\right)^{2} + 2 f_{xxx}
+f_{yy} f_{xyy} - 2 f_{xxx} f_{yyy} f_{xy} - 2 f_{yy}
+\left(f_{xxy}\right)^{2} + 2 f_{xy} f_{xyy} f_{xxy}$ \\
+
+%=====
+
+3 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to [out=-120,in=120] (2);
+    \draw[-] (1) to [out=-60,in=60] (2);
+    \draw[-] (2) to (3);
+    \draw[-] (3) to (4);
+\end{tikzpicture}
+& $- f_{x} f_{xx} f_{yy} f_{xyy} + f_{x} f_{xx} f_{yyy} f_{xy} - f_{x} f_{xxx} \left(f_{yy}\right)^{2} + 3 f_{x} f_{yy} f_{xy} f_{xxy} - 2 f_{x} \left(f_{xy}\right)^{2} f_{xyy} - \left(f_{xx}\right)^{2} f_{y} f_{yyy} - f_{xx} f_{y} f_{yy} f_{xxy} + 3 f_{xx} f_{y} f_{xy} f_{xyy} + f_{xxx} f_{y} f_{yy} f_{xy} - 2 f_{y} \left(f_{xy}\right)^{2} f_{xxy}$ \\
+
+3 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \draw[-] (1) to [out=-120,in=120] (2);
+    \draw[-] (1) to [out=-60,in=60] (2);
+    \draw[-] (2) to (3);
+    \draw[-] (1) to (4);
+\end{tikzpicture}
+& $2 \left(f_{x}\right)^{2} f_{yyy} f_{xxy} - 2 \left(f_{x}\right)^{2} \left(f_{xyy}\right)^{2} - 2 f_{x} f_{xxx} f_{y} f_{yyy} + 2 f_{x} f_{y} f_{xyy} f_{xxy} + 2 f_{xxx} \left(f_{y}\right)^{2} f_{xyy} - 2 \left(f_{y}\right)^{2} \left(f_{xxy}\right)^{2}$ \\
+
+% =========
+3 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
+    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+    \draw[-] (1) to (4);
+    \draw[-] (4) to (5);
+\end{tikzpicture}
+& $- \left(f_{x}\right)^{3} f_{yy} f_{xyy} + \left(f_{x}\right)^{3} f_{yyy} f_{xy} - \left(f_{x}\right)^{2} f_{xx} f_{y} f_{yyy} + 2 \left(f_{x}\right)^{2} f_{y} f_{yy} f_{xxy} - \left(f_{x}\right)^{2} f_{y} f_{xy} f_{xyy} + 2 f_{x} f_{xx} \left(f_{y}\right)^{2} f_{xyy} - f_{x} f_{xxx} \left(f_{y}\right)^{2} f_{yy} - f_{x} \left(f_{y}\right)^{2} f_{xy} f_{xxy} - f_{xx} \left(f_{y}\right)^{3} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3} f_{xy}$ \\
+\end{tabular}
+\caption{Details and graphical representations of all partial transvectants up to degree $3$ of copies of a function $f$ under a transformation in $A(2)$.}
+\label{tab:transvectants1}
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{cccp{11cm}}
+Degree & Weight & Diagram & Partial transvectant\\
+\hline
+4 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
+    \draw[-] (1) to [out=30,in=150] (2);
+    \draw[-] (1) to [out=-30,in=-150] (2);
+    \draw[-] (1) to [out=10,in=170] (2);
+    \draw[-] (1) to [out=-10,in=-170] (2);
+\end{tikzpicture}
+& $f_{xxxx} f_{yyyy} - 4 f_{xyyy} f_{xxxy} + 3 f_{xxyy}^2$ \\
+
+4 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to [out=-90,in=150] (3);
+    \draw[-] (1) to [out=-30,in=90] (3);
+\end{tikzpicture}
+& $ f_{xx}^2 f_{yyyy} + 2 f_{xx} f_{yy} f_{xxyy} - 4 f_{xx} f_{xy} f_{xyyy} - 4 f_{yy} f_{xy} f_{xxxy} + 4 f_{xy}^2 f_{xxyy} + f_{xxxx} f_{yy}^2$ \\
+
+4 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \draw[-] (1) to [out=-150,in=90] (2);
+    \draw[-] (1) to [out=-90,in=30] (2);
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+\end{tikzpicture} 
+& $ f_{x} f_{xxx} f_{yyyy} - f_x f_{yyy} f_{xxxy} + 3 f_{x} f_{xyy} f_{xxyy} - 3 f_x f_{xyyy} f_{xxy} - f_{xxx} f_y f_{xyyy} + f_{xxxx} f_y f_{yyy} - 3 f_y f_{xyy} f_{xxxy} + 3 f_y f_{xxy} f_{xxyy}$ \\
+
+4 & 4 &
+\begin{tikzpicture}[baseline=0]
+    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
+    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
+    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
+    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
+    \draw[-] (1) to (2);
+    \draw[-] (1) to (3);
+    \draw[-] (1) to (4);
+    \draw[-] (1) to (5);
+\end{tikzpicture}
+& $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\
+\end{tabular}
+\caption{Details and graphical representations of all partial transvectants of weight $4$ of copies of a function $f$ under a transformation in $A(2)$.}
+\label{tab:transvectants2}
+\end{table}
+
+\todo[inline]{Explain}
+
+\subsection{Signatures of $SA(2)$ and $A(2)$}
+Recall that invariants of a supergroup are automatically invariants of any of
+its subgroups.
+For example, invariants of $A(2)$ are automatically invariants of $SA(2)$, but not necessarily vice versa.
+Any of the partial transvectants found in Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} are invariants of $SA(2)$ (as the determinant is $1$), but only up to scale factor ($\det A^{-r}$) of $A(2)$.
+
+Hence, we can form a signature for $SA(2)$ by choosing any combination of
+partial transvectants. We'll choose a signature with three components so that
+it can be visualised as a three-dimensional surface; note that this will not
+be complete and may well have a very large bad set. For example, we can choose the function value together with the first two partial transvectants to form the signature:
+\begin{equation*}
+    \left(f, f_{xx}f_{yy}-f_{xy}^2, f_x^2f_{yy} - 2f_xf_yf_{xy} + f_{xx}f_y^2\right).
+\end{equation*}
+
+\subsubsection{Example}
+Consider as our image, the function $f(x, y) = 0.5 - 0.2x - 0.3y - 0.05x^2 +
+0.03xy + 0.04y^2 + 0.03y^3 +0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3$
+defined on $[0, 1]\times[0, 1]$.
+\todo[inline]{remake figure with modified matrix. Also modify function so it has some features like a critical point}
+We'll subject our image to a special affine transformation:
+\begin{equation*}
+\mathbf{x} \mapsto \frac{1}{1.1}\begin{bmatrix} 0.6875 & 1.1 \\ -0.6 & 0.8 \end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
+\end{equation*}
+
+Fig.~\ref{fig:SA2} shows the function as a greyscale image, the transformed
+function, and the signatures of both the untransformed and transformed
+images.
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_SA2.png}
+\includegraphics[width=.45\textwidth]{Figs/SA2_signature.png}
+\caption{\todo[inline]{add extra crap} A sample $SA(2)$ Transform and 3D signature. Mention what's going on with the grid.}
+\label{fig:SA2}
+\end{figure}
+
+\subsubsection{Moving on to $A(2)$, \ldots}
+Using the same function as an example, 
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_A2.png}
+\includegraphics[width=.45\textwidth]{Figs/A2_signature.png}
+\caption{A sample $A(2)$ Transform and 3D signature.}
+\label{fig:A2}
+\end{figure}
+
+For $A(2)$ the weight of the partial transvectants prevents them from being invariants.
+They can be normalised by choosing only those where all components have the same weight and projecting them onto a unit hypersphere.
+Instead, we select ratios of partial transvectants.
+It is beneficial to choose the numerator and denominator so that they have different critical points, which can be achieved by adding together partial transvectants of the same weight as appropriate.
 
@@
 
-\todo[inline]{This needs a friendly introduction, or at least a pointer to the notebooks}
-
-Idea is that it is the transformation back to the cross-section.
-
-The method of moving frames enables one to identify invariants under the action of groups of transformations.
-It has a long history, as summarised in \cite{Olver14}; particularly noteworthy contributions are by Cartan~\cite{Cartan37} and Olver and co-authors; see~\cite{Olver14} for an overview, and note particularly for an application to~\cite{Calabi98}.
+So far the methods that we have seen to can construct differential invariants for particular groups are not directly generalisable.
+It is natural to ask if there is an algorithmic approach that will yield invariants more directly.
+The answer is a partial yes.
+There is a general method, based on Cartan's method of moving frames, that is generally applicable, but finding good solutions with it still requires some ingenuity in general.
+We introduce the method here and then demonstrate its use to find invariants to further groups.
+
+A moving frame is a mapping into a group $\mathcal{G}$ that provides a frame of reference along a curve.
+Cartan's method of moving frames generalises the concept to a homogeneous space of a Lie group $\mathcal{G}$.
+When defined on the principal bundle it defines a $\mathcal{G}$-equivariant mapping, which enables one to identify invariants under the action of groups of transformations.
+The method of moving frames has a long history, as summarised in \cite{Olver14}; particularly noteworthy contributions are by Cartan~\cite{Cartan37} and Olver and co-authors; see~\cite{Olver14} for an overview, and note particularly for an application to~\cite{Calabi98}.
 The method is described in detail in~\cite{OlverCIT}.
 
-A right moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$.
-
-In order to construct differential invariants to the action of Lie group $\mathcal{G}$ acting on manifold $\mathcal{M}$, the procedure can be summarised as follows:
+A (right-) moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$, where $z \in J^d$.
+The procedure to construct differential invariants to the action of Lie group $\mathcal{G}$ acting on manifold $\mathcal{M}$ using the method of moving frames is as follows:
 
 \begin{enumerate}
-\item Prolong the group action to the jet space of $n$-th order derivatives (using implicit differentiation): $F: J^n \to \mathbb{R}$. 
+\item Prolong the group action to the jet space of $d$-th order derivatives (using implicit differentiation): $F: J^d \to \mathbb{R}$. 
 \item Apply Cartan normalisation:
     \begin{enumerate}
-    \item Choose a local cross-section to the group orbits, i.e., a ($n - \dim \mathcal{G}$)-dimensional submanifold $\mathcal{K}$ that intersects transversally at most once with each orbit
-    \item $\mathcal{K}$ is specified by $\dim \mathcal{G}$ independent equations $Z_i (z) = c_i$, for $z \in J^n$,  and $Z_i$ scalar-valued functions and $c_i$ constants.
+    \item Choose a local cross-section to the group orbits, i.e., a ($d - \dim \mathcal{G}$)-dimensional submanifold $\mathcal{K}$ that intersects transversally at most once with each orbit
+    \item $\mathcal{K}$ is specified by $\dim \mathcal{G}$ independent equations $Z_i (z) = c_i$, for $z \in J^d$,  and $Z_i$ scalar-valued functions and $c_i$ constants.
     \item The right moving frame $g = \rho(z)$ is found by solving the normalisation questions $Z_i (g \cdot z) = c_i$ for the group parameters $g$ (in terms of $z$).
+In other words, the moving frame is the transformation back to the cross-section.
     \end{enumerate}
@@
 Olver uses the group $SE(2)$ on curves as an example~\cite{Olver}, recovering the Euclidean curvature as a second-order invariant.
-As an example, we use it to compute invariants to $SE(2)$ on the plane, before moving on to two other planar Lie group examples: the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).
+We continue this example to compute invariants to $SE(2)$ on the plane, before moving on to other planar Lie group examples: $E(2)$, the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).
+Finally, we apply it to an infinite-dimensional pseudo-Lie group, the conformal diffeomorphisms.
 
 \subsection{The Special Euclidean Group $SE(2)$}
-An element of the special Euclidean group $SE(2)$ acts on an element $(x, y)$ of $\mathbb{R}^2$ to produce $(\bar{x}, \bar{y})$ as 
+
+An element of the special Euclidean group $SE(2)$ acts on an element $(x, y)$ of $\mathbb{R}^2$ to produce $(\bar{x}, \bar{y})$ as:
 \begin{equation*}
@@
 y, f, f_x, f_y, f_{xx}, f_{xy}, f_{yy})$ via the chain rule. The
-transformation rule for the derivatives is given by
+transformation rule for the derivatives is given by:
 \begin{equation}
@@
   I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) &&(= I_1\bar{f}_{\bar{x}\bar{y}})\\
-  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}})
+  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}}).
 \end{aligned}
@@
 to use a second derivative term to determine $\varepsilon$ for the moving
-frame. The derivative transformations are given by
+frame. The derivative transformations are given by:
 \begin{equation}
@@
 the $\bar{f}_{\bar{x}\bar{y}}$ term. Substituting in for $\cos\theta,
-\sin\theta$, we see that
+\sin\theta$, we see that:
 \begin{equation*}
     \bar{f}_{\bar{x}\bar{y}} = \frac{\varepsilon(f_xf_y(f_{yy} - f_{xx}) + (f_x^2 -
-    f_y^2)f_{xy})}{f_x^2 + f_y^2}
+    f_y^2)f_{xy})}{f_x^2 + f_y^2}.
 \end{equation*}
@@
   &&(= I_1\lvert \bar{f}_{\bar{x}\bar{y}}\rvert)\\
-  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}})
+  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}}).
 \end{aligned}
@@
 These invariants are a functionally independent, complete, set of polynomial differential invariants up to second derivatives.
-Note that the invariants found previously by tensor contraction can be expressed in terms of these:
+Note that the invariants found previously by tensor contraction (\cite{eq:se2}) can be expressed in terms of these:
 \begin{align*}
@@
 The M\"obius group $\mathrm{PSL}(2,\mathbb{C})$ acts on the Riemann sphere
-$\overline{\mathbb{C}} = \mathbb{C}\cup\infty$ by 
-$$ \phi\colon \overline{\mathbb{C}} \to \overline{\mathbb{C}},\quad \phi(z) = \frac{\alpha z + \beta}{\gamma z + \delta},\quad \alpha,\beta,\gamma,\delta\in\mathbb{C}, \quad
-\alpha\delta-\beta\gamma\ne 0.$$
+$\overline{\mathbb{C}} = \mathbb{C}\cup\infty$ by:
+\begin{equation} 
+\phi\colon \overline{\mathbb{C}} \to \overline{\mathbb{C}},\quad \phi(z) = \frac{\alpha z + \beta}{\gamma z + \delta},\quad \alpha,\beta,\gamma,\delta\in\mathbb{C}, \quad
+\alpha\delta-\beta\gamma\ne 0.
+\end{equation}
 
@@
 
-\item The 2nd order invariant is then given by $\bar f_{xx}$ using Equation~(\ref{eqn:mobius}); it is 
+\item The 2nd order invariant is then given by $\bar f_{xx}$ using Equation~(\ref{eqn:mobius}); it is:
 $$\bar f_{xx} = \frac{f_{xx}+f_{yy}}{f_x^2 + f_y^2}.$$
@@
  3 f_y ^2 f_x ^3 f_{xxy} - f_y ^5 f_{xxx} - 
- f_y ^3 f_x ^2 f_{xxx}
+ f_y ^3 f_x ^2 f_{xxx}.
 $
@@
 
-We consider the 8-dimensional group $\mathrm{PSL}(3,\R)$ acting on $\R^2$ by projective transformations, i.e., $$(x,y) \mapsto \left(\frac{a x + b y + j}{l + g x + h y}, \frac{c x + d y + k}{l+ g x + h y}\right).$$
-
-Requiring that $\bar f = f$ again enables us to clear the translate coefficients, so $k=k=0$; for convenience we will also take $l=1$.
+We consider the 8-dimensional group $\mathrm{PSL}(3,\R)$ acting on $\R^2$ by projective transformations, i.e., 
+\begin{equation}
+(x,y) \mapsto \left(\frac{a x + b y + j}{l + g x + h y}, \frac{c x + d y + k}{l+ g x + h y}\right).
+\end{equation}
+
+Requiring that $\bar f = f$ again enables us to clear the translation coefficients, so $k=k=0$; for convenience we will also take $l=1$.
 This leaves 6 group parameters $(a,b,c,d,g,h)$ to be determined.
@@
 
+\todo[inline]{How to write this?}
 The prolonged action is:
@@
 However, these signatures can be simplified and made more robust.
-Their structure suggests considering the combination $J_1 - J_3^2$, which turns out to obey
+Their structure suggests considering the combination $J_1 - J_3^2$, which turns out to obey:
 $$J_1 - J_3^2 = 144 D^4 P_4.$$
@@
 $$P_4 = -4(\det f_{ij})^2 + Q_4,$$
-where $Q_4$ is a polynomial of degree 4 that vanishes when $f_x=f_y=0$. Hence, the relative invariant of weight 12
+where $Q_4$ is a polynomial of degree 4 that vanishes when $f_x=f_y=0$. Hence, the relative invariant of weight 12:
 $$ (D^6, P_4^3, (E^2-12D P_5)^2)$$
@@
  f_{y}  f_{yyy}  f_x  f_{xxx}  - 
- 2 f_{y}  f_{yy}  f_{xy}  f_{xxx}  + f_{y} ^2 f_{xyy}  f_{xxx} $
+ 2 f_{y}  f_{yy}  f_{xy}  f_{xxx}  + f_{y} ^2 f_{xyy}  f_{xxx}, $
 
@@
  f_{y} ^2 f_{yy}  f_{x}  f_{xxx}  + 
- f_{y} ^3 f_{xy}  f_{xxx} $
+ f_{y} ^3 f_{xy}  f_{xxx}. $
 
@@
 Further invariants can be found by noting that, for any planar transformation group and any two invariants
-$I^1$ and $I^2$, $\nabla I^1 \times \nabla I^2$ is a relative invariant of weight 1; that is,
+$I^1$ and $I^2$, $\nabla I^1 \times \nabla I^2$ is a relative invariant of weight 1; that is:
 $$\nabla I^1 \times \nabla I^2\mapsto (\det \phi')(\nabla I^1 \times \nabla I^2).$$
@@
 \end{figure}
-
-\section{Extension to larger groups, role of colour, etc.}
-\label{sec:aaah}
-
-Define diffeo here
 
@@
 
-\subsection{Colour Images}
-
-Thus far we have only considered greyscale images.
+\section{Colour Images}\label{sec:colour}
+
+The formulation we provided in the introduction considered $k$ channels of information.
+However, thus far we have considered only greyscale images ($k=1$).
 However, most images are three-channel colour (typically represented as RBG values), and multi-spectral images can have hundreds of channels of measurement.
@@
 For $k$ colours, signature sets of dimension up to $k + k(k+1)/2$ can be chosen from the invariants $f^i$ and $f^i_m f^j_m$ for $i,j=1,\dots, k$.
-The situation is more complicated that it first appears because the information in the channels is not independent: colour is built by the intensities in the three channels, and so it there is correlation between them.
-This means that the invariant signature identified next are na\"ive, and should be viewed as best-case scenarios.
+
 We briefly sketch some possibilities for some of the groups that we have considered earlier.
+However, the situation is more complicated that it first appears because the information in the channels is not independent: colour is built by the intensities in the three channels, and so there is correlation between them.
+This means that the invariant signatures identified next are na\"ive, and should be viewed as best-case scenarios.
 
@@
 There are plenty of invariants formed from 1st derivatives, namely $\nabla f^i \times \nabla f^j$ for $i<j$.
-But these are all invariant under the bigger group $\mathrm{Diff}_{\mathrm{vol}}$ of local volume-preserving diffeomorphisms.
-So the Poisson brackets cannot form a complete invariant for $SA(2)$.
-Two derivatives are always needed no matter how many colours we have.
+However, these are all invariant under the bigger group $\mathrm{Diff}_{\mathrm{vol}}$ of local volume-preserving diffeomorphisms, and so the Poisson brackets cannot form a complete invariant for $SA(2)$: two derivatives are always needed no matter how many colours we have.
 The relation $SA(2)\subset \mathrm{Diff}_{\mathrm{vol}}$ acts an obstruction to $SA(2)$, an instance of the phenomenon of hidden symmetry.
@@
 There are plenty of invariants formed from two derivatives: already 9 when $k=2$.
-However, as with $SA(2)$, we can never get away with one derivative because all the 1-derivative invariants,such as $\{f^1,f^2\}/\{f^1,f^3\}$ are also invariant under $\mathrm{Diff}_{\mathrm{vol}}$ (even though $A(2)$ is not even a subgroup of $\mathrm{Diff}_{\mathrm{vo}l}$).
+However, as with $SA(2)$, we can never get away with one derivative because all the 1-derivative invariants, such as $\{f^1,f^2\}/\{f^1,f^3\}$, are also invariant under $\mathrm{Diff}_{\mathrm{vol}}$ (even though $A(2)$ is not even a subgroup of $\mathrm{Diff}_{\mathrm{vo}l}$).
 
@@
 \end{tabular}
-\caption{Number of derivatives of $f$ needed to construct a differential invariant signature of $f$ as a function of the group $G$ and the number of colours $k$ of $f$.
+\caption{Number of derivatives of $f$ needed to construct a differential invariant signature of $f$ as a function of the group $\mathcal{G}$ and the number of colours $k$ of $f$.
 The entry `--' indicates that there is no differential invariant signature in that case.}

### 2020-11-02 paper/newpaper.tex
Tidy up of figures. Can be programatically generated now

@@
 It is natural to seek representations of objects that vary only with regard to shape change, rather than to any change in form.
-If the space of objects in denoted $M$ and the non-shape transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$.
+If the space of objects is denoted $M$ and the non-shape transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$.
 This could be done, for example, by transforming all objects to match a chosen target one by registration.
@@
 
-\section{Differential invariants of $E(2)$ through tensor contraction}
+\section{Differential invariants of E(2) through tensor contraction}
 While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$.
-In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance, as they are equivalent; we therefore use subscript indices exclusively.
+In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance as they are equivalent.
+We therefore use subscript indices exclusively.
 
@@
 
-The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}} \cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor.
-\todo[inline]{Cite Florack et al, 1993} Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial f / \partial_{i_1} \cdots \partial_{i_p}$ will give a Euclidean invariant.
+The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}}\cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor.
+\todo[inline]{Cite Florack et al, 1993} Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial^p f / \partial_{x_{i_1}} \cdots \partial_{x_{i_p}}$ will give a Euclidean invariant.
 
@@
   f_if_i &= f_x^2 + f_y^2 \\
-  f_{ii} &= f_{xx}^2 + f_{yy}^2 \\
+  f_{ii} &= f_{xx} + f_{yy} \\
   f_{ij} f_{ij} &= f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
@@
 
-\subsection{Signatures of $SA(2)$ and $A(2)$}
+\subsection{Signatures of SA(2) and A(2)}
 Recall that invariants of a supergroup are automatically invariants of any of
@@
 
-\subsubsection{Moving on to $A(2)$, \ldots}
+\subsubsection{Moving on to A(2), \ldots}
 Using the same function as an example, 
@@
 
-\subsection{The Special Euclidean Group $SE(2)$}
+\subsection{The Special Euclidean Group SE(2)}
 

### 2020-11-02 code/make_figures.m

@@ -1,6 +1,8 @@
 %% Set up the function
 % We create a symbolic and a numeric version of the function, for future
 % reference.
+addpath signatures
+addpath transforms
 syms x y
 %f(x, y) = 0.01*(x - 1.5).^3 -0.02*(x - 1.5).^2.*(y + 1) + ...
 %    0.03*(x - 1.5)*(y + 1).^2 - 0.015*(y + 1).^3 + 0.9;
@@ -30,6 +32,13 @@ signatures.Mobius.sigfun = @Mobius_signature;
 signatures.PSL3R.tform = PSL3RTransform(1, 0.1, 0.05, 0.8, 0.2, -0.1);
 signatures.PSL3R.sigfun = @PSL3R_signature;
 
+
+%% Try out a particular group, and then save 3D axes info using the block below
+close all
+group = 'PSL3R';
+write_images = false;
+sig = generate_figures(f, signatures.(group), write_images);
+
 %% Save group=specific axes to file
 % Run this after generating a particular set of images to make sure they
 % are saved for next time that group is drawn
@@ -37,12 +46,18 @@ sig.save_camera()
 caminfo = sig.camera_info;
 save(strcat('images/', sig.group, '_cam.mat'), 'caminfo');
 
-%%
-close all
-group = 'SA2';
+%% Generate all images
 write_images = true;
-sig = generate_figures(f, signatures.(group), write_images);
+groups = {'SE2', 'E2', 'Sim2', 'SA2', 'A2', 'Mobius', 'PSL3R'};
+for k = 1:numel(groups)
+    gp = groups{k};
+    sig = generate_figures(f, signatures.(gp), write_images);
+end
 
+% Now run the script copyfigures.sh to trim the images and copy them to the 
+% paper directory
+
+%%
 function sig = generate_figures(f, gp, write_images)
 % Draw an image of the function
 sigfun = gp.sigfun;
@@ -62,7 +77,7 @@ if write_images
     print('-r200', '-dpng', strcat('images/', sig.group, '_before.png'));
     clf()
     sigp.draw_image()
-    print('-r200', '-dpng', strcat('images/', sig.group, '_after.png'));
+    print('-r200', '-dpng', strcat('images/f_transformed_', sig.group));
 else
     subplot(1,2,1)
     sig.draw_image()

### 2020-11-02 code/signatures/A2_signature.m

@@ -1,13 +1,13 @@
-function out = A2_new(f, varargin)
+function out = A2_signature(f, varargin)
 derivative_order = 3;
 group = 'A2';
 out = signature_switch(f, @evaluate, derivative_order, group, varargin{:});
     function sig = evaluate(derivs)
         [f, fx, fy, fxx, fxy, fyy, fxxx, fxxy, fxyy, fyyy] = derivs{:};
-        C = fx.^2.*fyy + fxx.*fy.^2 - 2*fx.*fxy.*fy;
-        D = fxx.*fyy - fxy.^2;
-        E = fx.^3.*fyyy - fxxx.*fy.^3 + 3*fx.*fxxy.*fy.^2 - 3*fx.^2.*fxyy.*fy;
-        
-        sig = {f, I1, I2};
+        C = fx.^2.*fyy + fxx.*fy.^2 - 2*fx.*fxy.*fy; % weight 2
+        D = fxx.*fyy - fxy.^2; % weight 2
+        E = fx.^3.*fyyy - fxxx.*fy.^3 + 3*fx.*fxxy.*fy.^2 - 3*fx.^2.*fxyy.*fy; % weight 4
+        denom = sqrt(C.^4 + D.^4 + E.^2);
+        sig = {f.*C.^2./denom, f.*D.^2./denom, f.*E./denom};
     end
 end

### 2020-11-02 code/transforms/Sim2Transform.m

@@ -1,6 +1,7 @@
 classdef Sim2Transform < SpatialTransform2D
     properties
         theta
+        determinant
         tx % translation vector
         ty %
         lambda
@@ -8,8 +9,9 @@ classdef Sim2Transform < SpatialTransform2D
         s % cos theta
     end
     methods
-        function obj = Sim2Transform(theta, tx, ty, lambda) 
+        function obj = Sim2Transform(theta, determinant, tx, ty, lambda) 
             obj.theta = theta;
+            obj.determinant = determinant;
             obj.tx = tx;
             obj.ty = ty;
             obj.lambda = lambda;
@@ -18,13 +20,13 @@ classdef Sim2Transform < SpatialTransform2D
         end
         
         function [xnew, ynew] = forward_coords(obj, x, y)
-            xnew = obj.lambda*(obj.c*x - obj.s*y) + obj.tx;
+            xnew = obj.lambda*obj.determinant*(obj.c*x - obj.s*y) + obj.tx;
             ynew = obj.lambda*(obj.s*x + obj.c*y) + obj.ty;
         end
         
         function [xnew, ynew] = reverse_coords(obj, x, y)
-            xnew = 1/obj.lambda*(obj.c*(x - obj.tx) + obj.s*(y - obj.ty));
-            ynew = 1/obj.lambda*(-obj.s*(x - obj.tx) + obj.c*(y - obj.ty));
+            xnew = 1/obj.lambda*(obj.c*obj.determinant*(x - obj.tx) + obj.s*(y - obj.ty));
+            ynew = 1/obj.lambda*(-obj.s*obj.determinant*(x - obj.tx) + obj.c*(y - obj.ty));
         end
     end
         

### 2020-11-09 paper/newpaper.tex
minor

@@
 
-Biologists differentiate between the {\em form} of an object, and the {\em shape}, being the part of form that is unaffected by size.
+Biologists differentiate between the {\em form} of an object, and the {\em shape}, being the part of form that is unaffected by size and orientation.
 More generally, the appearance of a fixed object in a set of images can vary markedly depending upon such variables as change of pose and relative position to the camera, even though the object itself does not change.
-Such variations highlight the importance of `shape', as opposed to `form', in object recognition.
-
-It is natural to seek representations of objects that vary only with regard to shape change, rather than to any change in form.
+This is even more noticeable in scenes that consist of multiple objects at different distances and orientations from the camera and any fixed background.
+The appearances of each individual object will then vary independently as a constant camera motion or other such transformation is applied.
+Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the projective or affine groups, but they could also be conformal.
+Regardless of which group appears to act, such variations highlight the importance of `shape', as opposed to `form', in object recognition.
+
+For image recognition it is then natural to seek representations of objects that vary only with regard to shape change, rather than to any change in form.
 If the space of objects is denoted $M$ and the non-shape transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$.
-This could be done, for example, by transforming all objects to match a chosen target one by registration.
+One way to achieve this is by transforming all objects to match a chosen target one by registration (the transformation of the appearance of one shape to match another, typically by gradient descent on a matching function, see e.g.~\cite{}).
 Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{} will transform all of the shapes into the reference frame of one template example.
-However, analysis on these quotient spaces is rarely simple~\cite{}.
+However, analysis on these quotient spaces is rarely simple~\cite{}, and if one is interested in the object, and not the transformation, then it necessitates a lot of computational work for relatively little benefit.
 An alternative option is to seek $\mathcal{G}$-invariant functions on $M$ and use the theory of invariants, which is what we consider here.
-
+In this case, rather than considering the image of the object, one works with an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group.
+The question of how to compare invariant signatures is not considered further in this paper.
+
+Ideally an invariant signature would be complete, so that two objects share a signature if and only if they differ only by a transformation from $\mathcal{G}$.
+See, e.g.,~\cite{UsMobius} and references therein for more discussion about the desirable properties of a set of invariants for image and curve analysis.
+However, of particular saliance for object recognition in scenes is the need to be robust to occlusions, where one object obscures some part of another.
+This leads one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology.
+This is sufficient to compute, e.g., derivatives of an object.
+Olver et al. joint differential invars (aka semi-diff)
+MOMENTS
+
+When seeking 
 Invariant signatures -- self-equivalences
@@
 
-have not removed the recognition problem, just removed the group variation.
+not intensity transforms
 
@@
 A transformation $\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) = (f\circ\varphi^{-1},\varphi(\Omega),k)$.
-For many of our examples we consider greyscale images, so $k=1$, but we discuss colour images in Section~\ref{sec:colour}.
+For many of our examples we consider greyscale images, so $k=1$, although we will discuss colour images in Section~\ref{sec:colour}.
 Also, since we work locally, we will usually omit the domain $\Omega$.
@@
 A signature set is complete for $f$ if it determines $f$ up to transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
-Where the signature set is not complete, it is still desirable that the set of objects that are indistinguishable from other be as small as possible.
-Useful properties for invariants are discussed in detail in~\cite{UsMobius}.
 
@@
 
-The M\"obius action is locally identical to the full conformal group up to and including second order.
+The conformal diffeomorphisms provides a particularly nice example of the moving frame method.
+Define $\psi^{-1}(\bar{z}) = a_0 + a_1 \bar{z} + a_2 \bar{z}^2 + \dots = z$ where $z=x+iy$ and $a_i\in \mathbb{C}$.
+(Clearly $a_0$ is simply the translation to the origin).
+Note that at derivative order $n$ two real group parameters enter: $Re(a_n)$ and $Im(a_n)$.
+There are $n+1$ independent derivatives of $f$ of order $n$, so there must be at least $n-1$ independent invariants at each order.
+Working in real and imaginary coordinates, $f(x,y) = g(\bar{x}, \bar{y})$ and the moving frame computation proceeds as follows:
+
+At first order, $(a_1 + i b_i) (\bar{x} + i \bar{y}) = x + i y$. Then:
+\begin{align}
+g_{\bar{x}} &= f_x x_{\bar{x}} + f_y y_{\bar{x}} \\
+&= a_1 f_x + b_1 f_y \\
+g_{\bar{y}} &= f_x x_{\bar{y}} + f_y y_{\bar{y}} \\
+&= - b_1 f_x + 1_1 f_y 
+\end{align}
+
+Choosing $g_{\bar{x}} = 1$ and $\g_{\bar{y}} = 0$ gives $a_1 = f_x / (f_x^2 + f_y^2), \:\: b_1 = f_y / (f_x^2 + f_y^2)$.
+The second order computations give three equations, setting $g_{\bar{x} \bar{x}} = \g_{\bar{x} \bar{y}} = 0$ means that $g_{\bar{y} \bar{y}}$ gives the sole second-order invariant $f_{xx} + f_{yy} / (f_x^2 + f_y^2)$, which we also saw for the M\"bius group.
+
+At third order there are two more invariants, ***
+
+%However, we first note that the M\"obius action is locally identical to the full conformal group up to and including second order.
 Therefore, there are no new conformal invariants, apart from the M\"obius ones, up to second order.
-Rather than applying the method of moving frames (which has been extended to Lie pseduo-groups in~\cite{}), we perform a direct calculation using the defining geometric properties of the conformal group.
-
-At second order, we first consider the action of conformal maps on the Euclidean invariants $f_i f_i$ and $f_{ii}$.
-
-Let $\psi := \varphi^{-1}$. For any diffeomorphism, the derivatives of $f$ transform as
-$$f_i \mapsto f_j \psi^j_i$$
-and
-$$f_{ij} \mapsto f_{kl} \psi^k_i\psi^l_j + f_{k}\psi^k_{ij}.$$
-Therefore the Laplacian of $f$ transforms as
-$$ f_{ii} \mapsto f_{kl} \psi^k_i \psi^l_i + f_k \psi^k_{ii}.$$
-When $\psi=u + i v$ is conformal, $\psi_{k,ii}=0$ because the components of conformal maps are harmonic functions,
-and the Cauchy-Riemann equations give $\psi_{k,i}\psi_{l,i} = (u_x^2 + u_y^2)\delta_{kl}$. Therefore,
-$$ f_{ii} \mapsto f_{ii}(u_x^2+u_y^2).$$
-Here $u_x^2+u_y^2=\det\psi^k_i$ is the local scaling factor of the transformation.
-Note also that
-$$f_i f_i \mapsto f_k f_l \psi_{k,i} \psi_{l,i} = f_k f_k (u_x^2 + u_y^2).$$
-That is, $f_{ii}$ and $f_i f_i$ are both relative invariants of weight 2, while $f_{ii}/(f_i f_i)$ is a conformal invariant, as we saw for the M\"obius group.
+It is possible to identify some invariants via direct calculation using the defining geometric properties of the conformal group.
+
+%At second order, we first consider the action of conformal maps on the Euclidean invariants $f_i f_i$ and $f_{ii}$.
+
+%Let $\psi := \varphi^{-1}$. For any diffeomorphism, the derivatives of $f$ transform as
+%$$f_i \mapsto f_j \psi^j_i$$
+%and
+%$$f_{ij} \mapsto f_{kl} \psi^k_i\psi^l_j + f_{k}\psi^k_{ij}.$$
+%Therefore the Laplacian of $f$ transforms as
+%$$ f_{ii} \mapsto f_{kl} \psi^k_i \psi^l_i + f_k \psi^k_{ii}.$$
+%When $\psi=u + i v$ is conformal, $\psi_{k,ii}=0$ because the components of conformal maps are harmonic functions,
+%and the Cauchy-Riemann equations give $\psi_{k,i}\psi_{l,i} = (u_x^2 + u_y^2)\delta_{kl}$. Therefore,
+%$$ f_{ii} \mapsto f_{ii}(u_x^2+u_y^2).$$
+%Here $u_x^2+u_y^2=\det\psi^k_i$ is the local scaling factor of the transformation.
+%Note also that
+%$$f_i f_i \mapsto f_k f_l \psi_{k,i} \psi_{l,i} = f_k f_k (u_x^2 + u_y^2).$$
+%That is, $f_{ii}$ and $f_i f_i$ are both relative invariants of weight 2, while $f_{ii}/(f_i f_i)$ is a conformal invariant, as we saw for the M\"obius group.
 By itself, it is not useful for images as it is singular at critical points of $f$.
 
-At higher order,  representing $\psi(z) = a_0 + a_1 z + a_2 z^2 + \dots$ where $z=x+iy$ and $a_i\in \mathbb{C}$ shows that 2 real group parameters, $Re(a_n)$ and $Im(a_n)$, enter at order $n$.
-There are $n+1$ independent derivatives of $f$ of order $n$, so there must be at least $n-1$ independent invariants of order $n$.
-(For $n=2$, we have we have found the single invariant above.)
-
-The transformation of 1st derivatives is more clearly written in complex variables as $$ f_x + i f_y \mapsto a_1 (f_x + i f_y).$$ Given any two real invariants $g,h$, the real and imaginary parts of $(g_x+i g_y)(h_x-i h_y)$ are relative invariants of weight 2.
+%The transformation of 1st derivatives is more clearly written in complex variables as $$ f_x + i f_y \mapsto a_1 (f_x + i f_y).$$ Given any two real invariants $g,h$, the real and imaginary parts of $(g_x+i g_y)(h_x-i h_y)$ are relative invariants of weight 2.
 This generates the required two invariants of order 3.
@@
 They can be written explicitly as functions of the basic invariants of $SE(2)$ as
-$$J_3 = f_k f_k f_{iij}f_j - 2 f_{ii} f_{jk} f_j f_k$$
-and (writing $a_i\times b_i$ for $a_1 b_2 - b_2 a_1$)
-$$ J_4 = f_k f_k f_{iij}\times f_j - 2 f_{ii} f_{jk} f_k\times f_j.$$
-Under conformal maps we have
-$$ (J_1,J_2,J_3,J_4) \mapsto (|a_1|^2 J_1, |a_1|^2 J_2, |a_1|^6 J_3,|a_1|^6 J_4).$$
-
-Therefore, projecting $(J_1^3,J_2^3,J_3)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^2$.
+%$$J_3 = f_k f_k f_{iij}f_j - 2 f_{ii} f_{jk} f_j f_k$$
+%and (writing $a_i\times b_i$ for $a_1 b_2 - b_2 a_1$)
+%$$ J_4 = f_k f_k f_{iij}\times f_j - 2 f_{ii} f_{jk} f_k\times f_j.$$
+%Under conformal maps we have
+%$$ (J_1,J_2,J_3,J_4) \mapsto (|a_1|^2 J_1, |a_1|^2 J_2, |a_1|^6 J_3,|a_1|^6 J_4).$$
+
+%Therefore, projecting $(J_1^3,J_2^3,J_3)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^2$.
 It is continuous at all $(x,y)$ such that $J_1$, $J_2$, and $J_3$ are not simultaneously equal to zero.
@@
 
-Similarly, projecting $(J_1^3,J_2^3,J_3,J_4)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^3$.
+%Similarly, projecting $(J_1^3,J_2^3,J_3,J_4)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^3$.
 This is also singular when $f_1=f_2=f_{ii}=0$.

### 2020-11-09 paper/newpaper.tex
Updates to conformal

@@
 
-Including $J_2$ in addition provides a 4-dimensional signature set, but does not increase the codimension of the set of bad images.
+Including $J_2$ in addition provides a 4-dimensional signature set, but does not increase the codimension of the set of bad images.%
 
@@
 
-The conformal diffeomorphisms provides a particularly nice example of the moving frame method.
-Define $\psi^{-1}(\bar{z}) = a_0 + a_1 \bar{z} + a_2 \bar{z}^2 + \dots = z$ where $z=x+iy$ and $a_i\in \mathbb{C}$.
-(Clearly $a_0$ is simply the translation to the origin).
-Note that at derivative order $n$ two real group parameters enter: $Re(a_n)$ and $Im(a_n)$.
-There are $n+1$ independent derivatives of $f$ of order $n$, so there must be at least $n-1$ independent invariants at each order.
-Working in real and imaginary coordinates, $f(x,y) = g(\bar{x}, \bar{y})$ and the moving frame computation proceeds as follows:
-
-At first order, $(a_1 + i b_i) (\bar{x} + i \bar{y}) = x + i y$. Then:
-\begin{align}
-g_{\bar{x}} &= f_x x_{\bar{x}} + f_y y_{\bar{x}} \\
-&= a_1 f_x + b_1 f_y \\
-g_{\bar{y}} &= f_x x_{\bar{y}} + f_y y_{\bar{y}} \\
-&= - b_1 f_x + 1_1 f_y 
-\end{align}
-
-Choosing $g_{\bar{x}} = 1$ and $\g_{\bar{y}} = 0$ gives $a_1 = f_x / (f_x^2 + f_y^2), \:\: b_1 = f_y / (f_x^2 + f_y^2)$.
-The second order computations give three equations, setting $g_{\bar{x} \bar{x}} = \g_{\bar{x} \bar{y}} = 0$ means that $g_{\bar{y} \bar{y}}$ gives the sole second-order invariant $f_{xx} + f_{yy} / (f_x^2 + f_y^2)$, which we also saw for the M\"bius group.
-
-At third order there are two more invariants, ***
+The conformal diffeomorphisms provides a particularly nice example of the
+moving frame method. Letting $z = x + iy$, let $\bar{z} = \psi(z)$ be a conformal
+mapping. It's convenient to work with the inverse transformation, so let
+\begin{equation*}
+    z = \psi^{-1}(\bar{z}) = c_0 + c_1 \bar{z} + c_2 \bar{z}^2 +
+    c_3\bar{z}^3 + \cdots
+\end{equation*}
+where $c_i = a_i + ib_i \in \mathbb{C}$.  Because the group is infinite
+dimensional, we need to work on the prolongation of $\psi$ to the jet space
+$J^\infty = \{x, y, f, f_x, f_y, \ldots\}$ including all of its
+derivatives. To make $\psi$ into a moving frame, we specify the
+cross-section and solve for parameters in stages. We begin with $\bar{x} =
+\bar{y} = 0$. This yeilds $c_0 = z$. To find $c_1 = a_1 + i b_1$ we need
+two constraints. Differentiating $f(x, y) = \bar{f}(\bar{x}, \bar{y})$ and
+substituting in our existing cross section constraints $\bar{x} = \bar{y} = 0$ gives
+\begin{align*}
+    \bar{f}_{\bar{x}} = f_x x_{\bar{x}} + f_y y_{\bar{x}} &= a_1 f_x + b_1
+    f_y, \\
+    \bar{f}_{\bar{y}} = f_x x_{\bar{y}} + f_y y_{\bar{y}} &= -b_1 f_x + a_1
+    f_y. 
+\end{align*}
+Note that $\bar{x} = \bar{y} = 0$ removes all higher order derivatives from
+the cross section equation. Adding two extra constraints to the cross
+section, $\bar{f}_{\bar{x}} = 1, \bar{f}_{\bar{y}} = 0$, this system is readily
+solved to give 
+\begin{equation*}
+    \begin{aligned}
+        a_1 &= f_x / (f_x^2 + f_y^2), &  b_1 &= f_y / (f_x^2 + f_y^2).
+    \end{aligned}
+\end{equation*}
+We then repeat the process, this time using the second derivative
+computations. This time, there are two new parameters, $a_2, b_2$, to solve
+for, but there are three derivatives. We use the cross section equations
+$\bar{f}_{\bar{x}\bar{x}} = 0, \bar{f}_{\bar{x}\bar{y}} = 0$ to solve for
+$a_2$ and $b_2$, the remaining derivative $\bar{f}_{\bar{y}\bar{y}}$ is then the
+sole second order invariant, which we also saw for the M\"obius group: 
+\begin{equation*}
+    \bar{f}_{\bar{y}\bar{y}} = \frac{f_{xx} + f_{yy}}{f_x^2 + f_y^2}.
+\end{equation*}
+Continuing in this way, at derivative order $n$ two real group parameters
+enter: $a_n$ and $b_n$. There are $n+1$ independent derivatives of $f$ of
+order $n$, so there must be $n-1$ new independent invariants at each order.
+
+At third order there are two more invariants, using the constraints
+$\bar{f}_{\bar{x}\bar{x}\bar{x}} = 0, \bar{f}_{\bar{x}\bar{x}\bar{y}} = 0$,
+the remaining derivatives are invariant:
+\begin{align*}
+    \bar{f}_{\bar{x}\bar{y}\bar{y}} &= \frac{f_y^3f_{yyy} + f_x^2f_yf_{yyy}
+            -2f_y^2f_{yy}^2 - 2f_{xx}f_y^2f_{yy} -
+            4f_xf_{xy}f_yf_{yy} - 2f_x^2 f_{xx}f_{yy} + f_{xxy}f_y^3 +
+            f_x^2 f_{xxy}f_y - 4 f_x f_{xy} f_{xx} f_y + f_x^3 f_{xxx} -
+        2f_x^2 f_{xx}^2 + f_x^3 f_{xyy}}{(f_x^2 + f_y^2)^3} \\
+        \bar{f}_{\bar{y}\bar{y}\bar{y}} &= \frac{f_xf_y^2f_{yyy} +
+        f_x^3f_{yyy} - 2f_x f_y f_{yy}^2 + 2f_{xy}f_y^2f_{yy} -
+    2f_x^2f_{xy}f_{yy} - f_{xxx}f_y^3 - f_{xyy}f_y^3 + f_xf_{xxy}f_y^2 +
+2f_{xy}f_{xx}f_y^2 - f_x^2 f_{xxx} f_y + 2f_xf_{xx}^2 f_y - f_x^2 f_{xyy}
+f_y + f_x^3 f_{xxy} - 2f_x^2 f_{xy} f_{xx} }{(f_x^2 + f_y^2)^3 }
+\end{align*}
 

### 2020-11-10 paper/newpaper.tex
Bars added etc.

@@
 \begin{array}{c}
-  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} 
+  \bar f_{\bar x} \\ \bar f_{\bar y} \\ \bar f_{\bar x \bar x} \\ \bar f_{\bar x \bar y} \\ \bar f_{\bar y \bar y} 
  \end{array}
@@
 \begin{enumerate}
-\item The frame $\bar f_x=1$, $\bar f_y=0$ determines the group parameters
+\item The frame $\bar f_{\bar x}=1$, $\bar f_{\bar y}=0$ determines the group parameters:
 $$ a = f_x/(f_x^2 + f_y^2),\quad b = f_y/(f_x^2 f_y^2).$$
 
-\item The frame $\bar f_{xy}=\bar f_{yy}=0$ determines the group parameters
+\item The frame $\bar f_{\bar x \bar y}=\bar f_{\bar y \bar y}=0$ determines the next group parameters:
 $$ c = (2 f_xf_yf_{xyy} - f_{xx}f_y^2 - f_{yy}f_x^2)/(2 f_x^2 + f_y^2)^2$$
@@
 
-\item The 2nd order invariant is then given by $\bar f_{xx}$ using Equation~(\ref{eqn:mobius}); it is:
-$$\bar f_{xx} = \frac{f_{xx}+f_{yy}}{f_x^2 + f_y^2}.$$
+\item The second-order invariant is then given by $\bar f_{\bar x \bar x}$ using Equation~(\ref{eqn:mobius}); it is:
+$$\bar f_{bar x \bar x} = \frac{f_{xx}+f_{yy}}{f_x^2 + f_y^2}.$$
 \end{enumerate}
@@
 
-The four 3rd order invariants can be deduced from the moving frame.
+The four third-order invariants can be deduced from the moving frame.
 They are rational functions with numerators of degree 6 and denominators $(f_x^2 + f_y^2)^4$, and are relative invariants of weight 8.
-We want to work with polynomials, and so clear denominators.
-We choose to use $M_1 = (f_{xx} + f_{yy})^4$ and two of the four 3rd order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where:
+Clearing denominators so as to work with polynomials, we choose $M_1 = (f_{xx} + f_{yy})^4$ and two of the four third-order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where:
 $M_2=
@@
 
-The image $f$ and these 3 relative invariants of weight 8 provide a 3-dimensional signature; an example is shown in Figure~\ref{fig:mobius}, although note that it is singular when $f_x=f_y=f_{xx}+f_{yy}=0$, a codimension 1 phenomenon for images.
+The image $f$ and these 3 relative invariants of weight 8 provide a three-dimensional signature; an example is shown in Figure~\ref{fig:mobius}, although note that it is singular when $f_x=f_y=f_{xx}+f_{yy}=0$, a codimension 1 phenomenon for images.
 
@@
 
-We consider the 8-dimensional group $\mathrm{PSL}(3,\R)$ acting on $\R^2$ by projective transformations, i.e., 
+We consider the eight-dimensional group $\mathrm{PSL}(3,\R)$ acting on $\R^2$ by projective transformations, i.e., 
 \begin{equation}
@@
 
-Requiring that $\bar f = f$ again enables us to clear the translation coefficients, so $k=k=0$; for convenience we will also take $l=1$.
+Requiring that $\bar f = f$ enables us to clear the translation coefficients, so $j=k=0$; for convenience we will also take $l=1$.
 This leaves 6 group parameters $(a,b,c,d,g,h)$ to be determined.
@@
 
-\todo[inline]{How to write this?}
 The prolonged action is:
@@
 \begin{array}{c}
-  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
+  \bar f_{\bar x} \\ \bar f_{\bar y} \\ \bar f_{\bar x \bar x} \\ \bar f_{\bar x \bar y} \\ \bar f_{\bar y \bar y} \\ \bar f_{\bar x \bar x \bar x} \\ \bar f_{\bar x \bar x \bar y} \\ \bar f_{\bar x \bar y \bar y} \\ \bar f_{ \bar y \bar y \bar y}
  \end{array}
@@
  6 a g^2 & 6 c g^2 & -6 a^2 g & -12 a c g & -6 c^2 g & a^3 & 3 a^2 c & 3 a c^2 & c^3 \\
- 2 g (b g+2 a h) & 2 g (d g+2 c h) & -2 a (2 b g+a h) & -4 (b c g+a d g+a c h) & -2 c (2 d
-   g+c h) & a^2 b & a (2 b c+a d) & c (b c+2 a d) & c^2 d \\
- 2 h (2 b g+a h) & 2 h (2 d g+c h) & -2 b (b g+2 a h) & -4 (b d g+b c h+a d h) & -2 d (d g+2
-   c h) & a b^2 & b (b c+2 a d) & d (2 b c+a d) & c d^2 \\
+ 2 g \alpha_1 & 2 g \beta_1 & -2 a \alpha_2 & -4 \delta_1 & -2 c \beta_2
+   & a^2 b & a \gamma_1 & c \gamma_1 & c^2 d \\
+ 2 h \alpha_2 & 2 h \beta_2 & -2 b \alpha_1 & -4 = \delta_2 & -2 d \beta_1
+   & a b^2 & b \gamma_1 & d \gamma_2 & c d^2 \\
  6 b h^2 & 6 d h^2 & -6 b^2 h & -12 b d h & -6 d^2 h & b^3 & 3 b^2 d & 3 b d^2 & d^3 \\
@@
 
-The affine group $A(2)$ is a subgroup of $\mathrm{PSL}(3,\R)$.
-In the analysis of that group, in Section~\ref{}, the invariant $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$ was identified.
-Under a general action of $\phi \in \mathrm{PSL}(3,\R)$, $D$ is a relative invariant (that is, the value is multiplied by a certain factor under group transformations):
+\noindent where $\alpha_1 = b g + 2 a h, \alpha_2 = 2 b g + a h$, $\beta_1 = d g + 2 c h, \beta_2 = 2 d g + c h$, $\gamma_1 = b c + 2 a d, \gamma_2= 2 b c + a d$, and $\delta_1 = (b c g+a d g+a c h), \delta_2 = (b d g+b c h+a d h)$.
+%\left[
+%\begin{array}{ccccccccc}
+ %a & c & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ %b & d & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ %-2 a g & -2 c g & a^2 & 2 a c & c^2 & 0 & 0 & 0 & 0 \\
+ %-b g-a h & -d g-c h & a b & b c+a d & c d & 0 & 0 & 0 & 0 \\
+ %-2 b h & -2 d h & b^2 & 2 b d & d^2 & 0 & 0 & 0 & 0 \\
+ %6 a g^2 & 6 c g^2 & -6 a^2 g & -12 a c g & -6 c^2 g & a^3 & 3 a^2 c & 3 a c^2 & c^3 \\
+ %2 g (b g+2 a h) & 2 g (d g+2 c h) & -2 a (2 b g+a h) & -4 (b c g+a d g+a c h) & -2 c (2 d
+   %g+c h) & a^2 b & a (2 b c+a d) & c (b c+2 a d) & c^2 d \\
+ %2 h (2 b g+a h) & 2 h (2 d g+c h) & -2 b (b g+2 a h) & -4 (b d g+b c h+a d h) & -2 d (d g+2
+   %c h) & a b^2 & b (b c+2 a d) & d (2 b c+a d) & c d^2 \\
+ %6 b h^2 & 6 d h^2 & -6 b^2 h & -12 b d h & -6 d^2 h & b^3 & 3 b^2 d & 3 b d^2 & d^3 \\
+%\end{array}
+%\right]
+
+%%A direct calculation using (\ref{eq:prolong}) shows that the same transformation rule (\ref{eq:D}) holds for $\phi\in\mathrm{PSL}(3,\R)$.
+That is, $D$ is a relative invariant of weight 2 of this action.
+%Both $D$ and $E$ will be useful quantities shortly, but note that, from (\ref{eq:D}), the sign of $D$ is invariant and therefore the choice of moving frame must depend on its sign.
+
+We begin by choosing the frames $\bar f_{\bar x} = 1$ and $\bar f_{\bar y}=  0$, which determine the group parameters $a = (1-c f_y)/f_x.$ and $b = -d f_y/f_x$.
+Direction substition then shows that $\bar f_{\bar y \bar y} = D d^2 / f_x^2$, where $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$.
+
+Under a general action of $\phi \in \mathrm{PSL}(3,\R)$, $D$ is a relative invariant (that is, the value is multiplied by a certain factor under group transformations) of weight 2:
 \begin{equation}
@@
 
-Another invariant of $A(2)$ was:
-
-\begin{equation}
-E := f_{yyy}f_x^3 - 3 f_{xyy}f_x f_y^2 + 3 f_{xxy}f_x^2 f_y - f_{xxx}f_y^3.
-\end{equation}
-
-%A direct calculation using (\ref{eq:prolong}) shows that the same transformation rule (\ref{eq:D}) holds for $\phi\in\mathrm{PSL}(3,\R)$.
-That is, $D$ is a relative invariant of weight 2 of this action.
-Both $D$ and $E$ will be useful quantities shortly, but note that, from (\ref{eq:D}), the sign of $D$ is invariant and therefore the choice of moving frame must depend on its sign.
-We begin by choosing the frames $\bar f_x = 1$ and $\bar f_y=  0$, which determine the group parameters $a = (1-c f_y)/f_x.$ and $b = -d f_y/f_x$.
-Direction substition then shows that $\bar f_{yy} = d^2 D/f_x^2$.
-We assume that $D>0$ (if it is negative, relatively little changes in the following derivation) and choose the frame $\bar f_{yy} = 1$, so that $d = f_x/D^{1/2}.$
-
-The frame $\bar f_{yyy} = 0$ determines the group parameter $ h = \frac{d(f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2 f_{xxy} - f_y^3 f_{xxx})}{6 f_x D},$ while $\bar f_{xyy}=0$ provides $ c = \frac{h f_x^2}{d D} - \frac{f_x f_{xy} - f_y f_{xx}}{D}$, and $\bar f_{xx}=0$ gives $ g = \frac{1}{2 f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$
-
-Having determined the frame, any function of the remaining derivatives $\bar f_{xxx}$, $\bar f_{xxy}$, and $\bar f_{yyy}$, as given in Equation~(\ref{eq:prolong}), provides invariants.
+It is also an invariant of $A(2)$, which is a subgroup of $\mathrm{PSL}(3,\R)$.
+Note that the sign of $D$ does not change.
+We assume that $D>0$ (if it is negative, relatively little changes in the following derivation) and choose the frame $\bar f_{ \bar y \bar y} = 1$, so that $d = f_x/D^{1/2}.$
+
+The frame $\bar f_{ \bar y \bar y \bar y} = 0$ determines the group parameter $ h = \frac{d(f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2 f_{xxy} - f_y^3 f_{xxx})}{6 f_x D},$ while $\bar f_{ \bar x \bar y \bar y}=0$ provides $ c = \frac{h f_x^2}{d D} - \frac{f_x f_{xy} - f_y f_{xx}}{D}$, and $\bar f_{ \bar x \bar x}=0$ gives $ g = \frac{1}{2 f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$ In fact, the denominator of the expression for $h$ was another invariant of $A(2)$; we label it $E$ for convenience.
+
+%\begin{equation}
+%E := f_{yyy}f_x^3 - 3 f_{xyy}f_x f_y^2 + 3 f_{xxy}f_x^2 f_y - f_{xxx}f_y^3.
+%\end{equation}
+
+Having determined the frame, any function of the remaining derivatives $\bar f_{ \bar x \bar x \bar x}$, $\bar f_{ \bar x \bar x \bar y}$, and $\bar f_{ \bar y \bar y \bar y}$, as given in Equation~(\ref{eq:prolong}), provides invariants.
 We choose: $$ (f_{xxx}, f_{xxy}^2, f_{xyy})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right)$$, where (with $P_n$ denoting a polynomial of degree $n$):
@@
 The $J_i$ are polynomials of degree 16, 24, and 8, respectively, and are extremely complicated when written out explicitly.
-They do have one benefit, though, which is that they  all have denominators given by integer powers of $D$, resolving the issue caused by the sign of $D$.
-Therefore, $$ (D^{18}, J_1^3, J_2^2, J_3^6)$$ are all relative invariants of weight 36; so projecting any subset of them of them to a sphere yields a 3rd order invariant signature.
+They do have one benefit, though, which is that they  all have denominators given by integer powers of $D$, resolving the ambiguity caused by the sign of $D$.
+Therefore, $$ (D^{18}, J_1^3, J_2^2, J_3^6)$$ are all relative invariants of weight 36, and so projecting any subset of them of them to a sphere yields a third-order invariant signature.
 
@@
 However, these signatures can be simplified and made more robust.
-Their structure suggests considering the combination $J_1 - J_3^2$, which turns out to obey:
+Their structure suggests considering the combination $J_1 - J_3^2$, which obeys:
 $$J_1 - J_3^2 = 144 D^4 P_4.$$
@@
 As $J_1/D^6$ and $J_3/D^3$ are invariant, so is $P_4/D^2$. 
-Moreover, the numerator of this new invariant does not vanish at critical points.  It has the structure
+Moreover, the numerator of this new invariant does not vanish at critical points.  It has the structure:
 $$P_4 = -4(\det f_{ij})^2 + Q_4,$$
@@
 can be projected to $S^2$, yielding a projective invariant of images that is singular only when $D=E=P_4=0$, which is a codimension 1 phenomenon, since  $D=E=0\Rightarrow P_4=0$.
-In particular, at critical points it tends to
-$(0, (2\det f_{ij})^6, 0),$ and hence critical points with $\det f_{ij}\ne 0$ have signature $(0,1,0)$.
-
+In particular, at critical points it tends to:
+$(0, (2\det f_{ij})^6, 0),$ and hence critical points with $\det f_{ij}\ne 0$ have signature value $(0,1,0)$.
+Including $J_2$ provides a 4-dimensional signature set, but does not increase the codimension of the set of bad images.
+
+\todo[inline]{Is this useful? Is it what we actually use? If so, fix the names...}
 For completeness we write out the invariant signature we use explicitly:
@@
 
-Including $J_2$ in addition provides a 4-dimensional signature set, but does not increase the codimension of the set of bad images.%
-
 Further invariants can be found by noting that, for any planar transformation group and any two invariants
@@
 $$\nabla I^1 \times \nabla I^2\mapsto (\det \phi')(\nabla I^1 \times \nabla I^2).$$
-Applying this operation to $f$ and the 4 3rd order invariants yields $5\cdot4/2=10$ 4th order invariants.
+Applying this operation to $f$ and the four third-order invariants yields $5\cdot4/2=10$ fourth-order invariants.
 
@@
 \subsection{Conformal Diffeomorphisms $\mathbf{Diff}_{\mathbf{con}}$}
-
-\todo[inline]{Put the moving frame version here}
 
@@
 This generates the required two invariants of order 3.
-(We have repeated and confirmed this calculation using the method of moving frames.) Specifically, let $J_1 = f_i f_i$ and  $J_2 = f_{ii}$, so that  $g = J_2/J_1$ is invariant.
+(We have repeated and confirmed this calculation using the method of moving frames.)
+
+\todo[inline]{Fix up this bit to be correct and complete for what we do}
+Specifically, let $J_1 = f_i f_i$ and  $J_2 = f_{ii}$, so that  $g = J_2/J_1$ is invariant.
 We want to work with polynomials, so we clear denominators and let $J_3+iJ_4 = J_1^2 (g_x + i g_y)  (f_x - i f_y)$.
@@
 They can be written explicitly as functions of the basic invariants of $SE(2)$ as
-%$$J_3 = f_k f_k f_{iij}f_j - 2 f_{ii} f_{jk} f_j f_k$$
-%and (writing $a_i\times b_i$ for $a_1 b_2 - b_2 a_1$)
-%$$ J_4 = f_k f_k f_{iij}\times f_j - 2 f_{ii} f_{jk} f_k\times f_j.$$
-%Under conformal maps we have
-%$$ (J_1,J_2,J_3,J_4) \mapsto (|a_1|^2 J_1, |a_1|^2 J_2, |a_1|^6 J_3,|a_1|^6 J_4).$$
-
-%Therefore, projecting $(J_1^3,J_2^3,J_3)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^2$.
+$$J_3 = f_k f_k f_{iij}f_j - 2 f_{ii} f_{jk} f_j f_k$$
+and (writing $a_i\times b_i$ for $a_1 b_2 - b_2 a_1$)
+$$ J_4 = f_k f_k f_{iij}\times f_j - 2 f_{ii} f_{jk} f_k\times f_j.$$
+Under conformal maps we have
+$$ (J_1,J_2,J_3,J_4) \mapsto (|a_1|^2 J_1, |a_1|^2 J_2, |a_1|^6 J_3,|a_1|^6 J_4).$$
+
+Therefore, projecting $(J_1^3,J_2^3,J_3)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^2$.
 It is continuous at all $(x,y)$ such that $J_1$, $J_2$, and $J_3$ are not simultaneously equal to zero.
@@
 
-%Similarly, projecting $(J_1^3,J_2^3,J_3,J_4)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^3$.
+Similarly, projecting $(J_1^3,J_2^3,J_3,J_4)$ to the unit sphere, together with $f$ itself, provides a conformal signature set in $\R\times S^3$.
 This is also singular when $f_1=f_2=f_{ii}=0$.

### 2020-11-10 paper/newpaper.tex
incremental

@@
 
-Biologists differentiate between the {\em form} of an object, and the {\em shape}, being the part of form that is unaffected by size and orientation.
-More generally, the appearance of a fixed object in a set of images can vary markedly depending upon such variables as change of pose and relative position to the camera, even though the object itself does not change.
-This is even more noticeable in scenes that consist of multiple objects at different distances and orientations from the camera and any fixed background.
-The appearances of each individual object will then vary independently as a constant camera motion or other such transformation is applied.
-Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the projective or affine groups, but they could also be conformal.
-Regardless of which group appears to act, such variations highlight the importance of `shape', as opposed to `form', in object recognition.
-
-For image recognition it is then natural to seek representations of objects that vary only with regard to shape change, rather than to any change in form.
-If the space of objects is denoted $M$ and the non-shape transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$.
-One way to achieve this is by transforming all objects to match a chosen target one by registration (the transformation of the appearance of one shape to match another, typically by gradient descent on a matching function, see e.g.~\cite{}).
-Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{} will transform all of the shapes into the reference frame of one template example.
+%Biologists differentiate between the {\em form} of an object, and the {\em shape}, being the part of form that is unaffected by size and orientation. 
+The appearance of a fixed object in a set of images can vary markedly depending upon such variables as pose and position relative to the camera, even though the object itself does not change.
+This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera and any fixed background.
+The appearance of each individual object will then vary independently as a constant camera motion or other such transformation is applied.
+Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.
+%Regardless of which group appears to act, such variations highlight the importance of `shape', as opposed to `form', in object recognition.
+
+For image recognition it is then natural to seek representations of objects that do not change as these various transformation groups act.
+If the space of objects is denoted $M$ and the appearance transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$.
+One way to achieve this is by transforming all objects to match a chosen target object by registration (the transformation of the appearance of one shape to match another, typically by gradient descent on a matching function, see e.g.~\cite{}).
+Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{} will place all of the shapes into the reference frame of one template example.
 However, analysis on these quotient spaces is rarely simple~\cite{}, and if one is interested in the object, and not the transformation, then it necessitates a lot of computational work for relatively little benefit.
-An alternative option is to seek $\mathcal{G}$-invariant functions on $M$ and use the theory of invariants, which is what we consider here.
+An alternative option is to seek $\mathcal{G}$-invariant functions on $M$, which is what we consider here.
 In this case, rather than considering the image of the object, one works with an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group.
-The question of how to compare invariant signatures is not considered further in this paper.
-
-Ideally an invariant signature would be complete, so that two objects share a signature if and only if they differ only by a transformation from $\mathcal{G}$.
-See, e.g.,~\cite{UsMobius} and references therein for more discussion about the desirable properties of a set of invariants for image and curve analysis.
+This reduces the recognition problem to recognising higher-dimensional invariant signatures.
+
+Something about signatures
+3. The signature must vary continuously with respect to the image, either for all smooth
+images or for all except a set of sufficiently high codimension. This is essential if the
+signature is to be used to detect similarity of images, but it fails for the rational
+invariants found in the literature.
+Invariant signatures -- self-equivalences
+
+The theory of invariants has a rich mathematical history~\cite{}.
+
 However, of particular saliance for object recognition in scenes is the need to be robust to occlusions, where one object obscures some part of another.
@@
 
-When seeking 
-Invariant signatures -- self-equivalences
-Different sorts of invariant, and their properties.
-local invariants: occlusions OK
 derivatives: noise is not
-
 not intensity transforms
 
-%Shapes/objects/images can be acted on by simple transformations that change
-%their appearance. We want to recognise the objects or identify the set of
-%transformations. If the set is a group, then we can seek to either identify
-%the group or solve the equivalence problem by
-%\begin{enumerate}
-    %\item Registration, or
-    %\item Invariance.
-%\end{enumerate}
-%The first is commonly studied but is computationally expensive and prone to
-%local minima. If you're not interested in the actual transformation it is
-%therefore to be avoided. Here we'll consider invariance. There are many
-%choices of type e.g. Fourier, integral, or differential invariants. The
-%last set are cheap to compute and have nice theoretical properties but are
-%not robust to noise. However, we'll use them anyway.
-
-This paper is a
-tutorial on differential invariants for planar Lie groups (e.g.
+We consider a wide range of planar groups, both finite-dimensional Lie groups and infinite-dimensional pseudo-Lie ones; as we shall show, the lattice structure of the set of groups influences the relationship between the sets of invariants for the different groups.
+
+Ideally, an invariant signature would be complete, so that the image is exactly determined up to a transformation, and two objects share a signature if and only if they differ only by a transformation from $\mathcal{G}$.
+However, this often requires signatures in many dimensions, and potentially also more derivatives of the image.
+For many applications an incomplete signature is sufficient, and is what we consider here.
+See, e.g.,~\cite{UsMobius} and references therein for more discussion about the desirable properties of a set of invariants for image and curve analysis.
+
+In this paper we provide a tutorial on differential invariants for planar Lie groups (e.g.
 Euclidean, affine, projective) since they are relatively simple, useful,
 and relevant to images. We'll use these to demonstrate the methods of
-constructing and using differential invariant signatures. Note that this
-reduces the recognition problem to recognising higher-dimensional
-differential invariant signatures. We'll mention some approaches to this.
-See the companion paper for an implementation.
+constructing and using differential invariant signatures.
+
+Different sorts of invariant, and their properties.
+
+The question of how to compare invariant signatures is not considered further in this paper.
 
@@
 
+SURF and that kind of crap
+
 An algorithm to compute invariants and determine complete signature sets is
@@
 This is a degree $2$ partial transvectant as it involves derivatives of $f$
-up to second order, and can be represented graphically by the following
+up to second-order, and can be represented graphically by the following
 diagram:
@@
 This leaves 4 group parameters $a,b,c,d$, where $\alpha = a + i b$, $\gamma = c + i d$, to be determined as follows.
-We prolong the action to 2nd derivatives of $f$, which is sufficient to allow the group to act freely.
+We prolong the action to second derivatives of $f$, which is sufficient to allow the group to act freely.
 There are 5 derivatives of $f$ up to order 2, so there will be at least 1 invariant.
@@
 $a_2$ and $b_2$, the remaining derivative $\bar{f}_{\bar{y}\bar{y}}$ is then the
-sole second order invariant, which we also saw for the M\"obius group: 
+sole second-order invariant, which we also saw for the M\"obius group: 
 \begin{equation*}
@@
 The formulation we provided in the introduction considered $k$ channels of information.
-However, thus far we have considered only greyscale images ($k=1$).
-However, most images are three-channel colour (typically represented as RBG values), and multi-spectral images can have hundreds of channels of measurement.
-It then becomes natural to consider how to use this information in the computation of invariants.
-The hope is that by constructing invariants using different colour channels, fewer derivatives need to be computed.
-For $k$ colours, signature sets of dimension up to $k + k(k+1)/2$ can be chosen from the invariants $f^i$ and $f^i_m f^j_m$ for $i,j=1,\dots, k$.
-
-We briefly sketch some possibilities for some of the groups that we have considered earlier.
+So far we have considered only greyscale images ($k=1$), but most real images are three-channel colour (RBG), and multi-spectral images can have hundreds of channels of measurement.
+It is therefore natural to consider whether this information is useful for the computation of invariants.
+
+The hope is that by constructing invariants using different colour channels, fewer derivatives are needed: for $k$ colours, signature sets of dimension up to $k + k(k+1)/2$ can be chosen from the invariants $f^i$ and $f^i_m f^j_m$ for $i,j=1,\dots, k$.
 However, the situation is more complicated that it first appears because the information in the channels is not independent: colour is built by the intensities in the three channels, and so there is correlation between them.
-This means that the invariant signatures identified next are na\"ive, and should be viewed as best-case scenarios.
-
-Note that for $k\ge 3$ the 3-dimensional signature $(f^1,f^2,f^3)$ is invariant under all local planar diffeomorphisms; a higher-dimensional signature, involving at least first derivatives, is therefore required.
-
+We briefly sketch some possibilities for some of the groups that we have considered earlier, but note that the correlation means that the invariant signatures identified next are na\"ive, and should be viewed as best-case scenarios.
+
+\begin{description}
+\item[$E(2)$]
 Considering $E(2)$, for $k\ge 2$, first derivatives suffice.
-For $SA(2)$,  we are seeking invariants of $k V_1 \oplus k V_2 \oplus \dots$.
-One can take transvectants of any components of $f$ to get invariants.
-For $k=2$ colours, there is only one  invariant formed from 1st derivatives, namely $((f^1)',(f^2)')_x = f^1_x f^2_y - f^1_y f^2_x$ (the Poisson bracket $\{f^1,f^2\}$).
+However, note that for $k\ge 3$ the three-dimensional signature $(f^1,f^2,f^3)$ is invariant under all local planar diffeomorphisms and so a higher-dimensional signature, involving at least first derivatives, is required.
+\item[$SA(2)$]
+For $SA(2)$, one can take transvectants of any components of $f$ to get invariants.
+For $k=2$ colours, there is only one  invariant formed from first derivatives, namely $((f^1)',(f^2)')_x = f^1_x f^2_y - f^1_y f^2_x$ (the Poisson bracket $\{f^1,f^2\}$).
 So again two derivatives are necessary, even for a 3-dimensional signature.
 
-For $k\ge 3$ colours, a new phenomenon enters.
-There are plenty of invariants formed from 1st derivatives, namely $\nabla f^i \times \nabla f^j$ for $i<j$.
+For $k\ge 3$ colours there are plenty of invariants formed from first derivatives, namely $\nabla f^i \times \nabla f^j$ for $i<j$.
 However, these are all invariant under the bigger group $\mathrm{Diff}_{\mathrm{vol}}$ of local volume-preserving diffeomorphisms, and so the Poisson brackets cannot form a complete invariant for $SA(2)$: two derivatives are always needed no matter how many colours we have.
 The relation $SA(2)\subset \mathrm{Diff}_{\mathrm{vol}}$ acts an obstruction to $SA(2)$, an instance of the phenomenon of hidden symmetry.
-
+\item[$A(2)$]
 The same problem occurs with $A(2)$.
 There are plenty of invariants formed from two derivatives: already 9 when $k=2$.
-However, as with $SA(2)$, we can never get away with one derivative because all the 1-derivative invariants, such as $\{f^1,f^2\}/\{f^1,f^3\}$, are also invariant under $\mathrm{Diff}_{\mathrm{vol}}$ (even though $A(2)$ is not even a subgroup of $\mathrm{Diff}_{\mathrm{vo}l}$).
-
+However, as with $SA(2)$, we can never get away with one derivative because all the first-derivative invariants, such as $\{f^1,f^2\}/\{f^1,f^3\}$, are also invariant under $\mathrm{Diff}_{\mathrm{vol}}$ (even though $A(2)$ is not even a subgroup of $\mathrm{Diff}_{\mathrm{vo}l}$).
+\item[$PSL(2,\mathbb{C})$]
 Recall that M\"obius and conformal transformations cannot be distinguished by their action on second derivatives.
-Therefore at least 3 derivatives are needed, no matter how many colours we have.
+Therefore at least three derivatives are needed, no matter how many colours we have.
 We can use, for example, the invariants arising from the curvature of the level sets of each colour.
 Replacing the relative invariant $\|\nabla f\|^2$ by $\sum_{j=1}^k \|\nabla f^j\|^2$, and $f_{ii}$ by $\sum_{j=1}^k (f^j_{ii})^2$, increases the codimension of the singular images from 1 to $3k-2$.
-
-In $PSL(3, \mathbb{R})$ for $2$-colour images, there are 3 second order relative invariants of weight 2, namely $(D_1,D_2,(\nabla f^1\times \nabla f^2)^2)$.
-Together with $(f^1,f^2)$, these yield a 4-dimensional $\mathbb{R}^2\times S^2$-valued signature using only 2nd derivatives.
-With $k>2$ colours there are many more 2nd order invariants; however, as the action of the projective group on 1st derivatives is indistinguishable from that of the full diffeomorphism group, it is not possible to have a 1st order signature that distinguishes projectively-related images from diffeomorphically-related ones.
-
-For the infinite-dimensional group $\mathrm{Diff}_{\mathrm{con}}$, first order signature sets are possible for $k \ge 2$ colours.
-They are formed from the relative invariants $(f^j_1 + i f^j_2)(f^m_1 - i f^m_2)$ of weight 2.
-We illustrate this using the Hopf fibration for $k=2$.
-The weight 2 relative invariant $$J = (2(f^1_1 + i f^1_2)(f^2_1 - i f^2_2), ||\nabla f^1\|^2 - \|\nabla f^2\|^2)$$ obeys $\|J\|^2 = \|\nabla f^1\|^2 + \|\nabla f^2\|^2$, hence projecting to the unit sphere shows that $(f^1,f^2,J/\|J\|)$ provides a 4-dimensional signature set that is singular only when $\nabla f^1 = \nabla f^2 = 0$, a codimension 2 phenomenon for images.
-
+\item[$PSL(3,\mathbb{R})$]
+In $PSL(3, \mathbb{R})$ for $2$-colour images, there are three second-order relative invariants of weight 2, namely $(D_1,D_2,(\nabla f^1\times \nabla f^2)^2)$.
+Together with $(f^1,f^2)$, these yield a 4-dimensional $\mathbb{R}^2\times S^2$-valued signature using only second derivatives.
+With $k>2$ colours there are many more second-order invariants; however, as the action of the projective group on first derivatives is indistinguishable from that of the full diffeomorphism group, it is not possible to have a first-order signature that distinguishes projectively-related images from diffeomorphically-related ones.
+\item[$\mathrm{Diff}_{\mathrm{vol}}$]
 When $k\ge 2$ in $\mathrm{Diff}_{\mathrm{vol}}$ there are $k(k-1)/2$ first-order invariants $ \nabla f^i \times \nabla f^j$.
@@
 Thus, $f^2$ is determined by the signature up to a translation in $y$, i.e., an area-preserving map.
-
+\item[$\mathrm{Diff}_{\mathrm{con}}$]
+For the infinite-dimensional group $\mathrm{Diff}_{\mathrm{con}}$, first-order signature sets are possible for $k \ge 2$ colours.
+They are formed from the relative invariants $(f^j_1 + i f^j_2)(f^m_1 - i f^m_2)$ of weight 2.
+We illustrate this using the Hopf fibration for $k=2$.
+The weight 2 relative invariant $$J = (2(f^1_1 + i f^1_2)(f^2_1 - i f^2_2), ||\nabla f^1\|^2 - \|\nabla f^2\|^2)$$ obeys $\|J\|^2 = \|\nabla f^1\|^2 + \|\nabla f^2\|^2$, hence projecting to the unit sphere shows that $(f^1,f^2,J/\|J\|)$ provides a 4-dimensional signature set that is singular only when $\nabla f^1 = \nabla f^2 = 0$, a codimension 2 phenomenon for images.
+\item[$\mathrm{Diff}$]
 In the full diffeomorphism group there are no differential invariants using 1 or 2 colours.
@@
 We therefore take $k\ge 3$.
-This provides the first order relative invariants of weight 1 $\nabla f^i\times \nabla f^j$, and hence a first order signature.
-However, a 0th order signature set is possible: $(f^1,\dots,f^k)$.
+This provides the first-order relative invariants of weight 1 $\nabla f^i\times \nabla f^j$, and hence a first-order signature.
+However, a zeroth-order signature set is possible: $(f^1,\dots,f^k)$.
 This is the image of the image.
@@
 We can choose coordinates so that $f^1=x$ and $f^2=y$; then the signature locally determines $f^3,\dots,f^k$ as functions of $f^1$ and $f^2$, i.e., the image.
+\end{description}
 
@@
 
-E2:
 {\bf Aside 3. Role of the invariants} 
-All of the 2nd order differential invariants play known roles in geometric analysis:
+All of the second-order differential invariants play known roles in geometric analysis:
 \begin{enumerate}
@@
 \item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is also a Lagrangian density for $-2(f_{xx} f_{yy} - f_{xy}^2)$, which arises in the Monge--Amp\`ere equations and
-can be written in terms of the final 2nd order invariant as $-2 (f_{xx} f_{yy} - f_{xy}^2) = 2 f_{xy}^2 - f_{xx}^2 - f_{yy}^2$
+can be written in terms of the final second-order invariant as $-2 (f_{xx} f_{yy} - f_{xy}^2) = 2 f_{xy}^2 - f_{xx}^2 - f_{yy}^2$
 \end{enumerate}

### 2020-11-10 paper/newpaper.tex
now

@@
 \item The second-order invariant is then given by $\bar f_{\bar x \bar x}$ using Equation~(\ref{eqn:mobius}); it is:
-$$\bar f_{bar x \bar x} = \frac{f_{xx}+f_{yy}}{f_x^2 + f_y^2}.$$
+$$\bar f_{\bar x \bar x} = \frac{f_{xx}+f_{yy}}{f_x^2 + f_y^2}.$$
 \end{enumerate}
@@
 Clearing denominators so as to work with polynomials, we choose $M_1 = (f_{xx} + f_{yy})^4$ and two of the four third-order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where:
-$M_2=
+$$M_2=
 f_y ^5 f_{yyy} + \frac{9}{2} f_y ^2 f_{yy}^2 f_x ^2 + 
@@
  f_x ^5 f_{xxx}, 
- $
-
- $M_3=-3 f_y  f_{yy}^2 f_x ^3 + 
+ $$
+
+ $$M_3=-3 f_y  f_{yy}^2 f_x ^3 + 
  f_y ^2 f_{yyy} f_x ^3 + f_{yyy} f_x ^5 + 
@@
  f_y ^3 f_x ^2 f_{xxx}.
-$
+$$
 
@@
    & a^2 b & a \gamma_1 & c \gamma_1 & c^2 d \\
- 2 h \alpha_2 & 2 h \beta_2 & -2 b \alpha_1 & -4 = \delta_2 & -2 d \beta_1
+ 2 h \alpha_2 & 2 h \beta_2 & -2 b \alpha_1 & -4 \delta_2 & -2 d \beta_1
    & a b^2 & b \gamma_1 & d \gamma_2 & c d^2 \\

### 2020-11-10 paper/newpaper.tex
minor

@@
 We begin by choosing the frames $\bar f_{\bar x} = 1$ and $\bar f_{\bar y}=  0$, which determine the group parameters $a = (1-c f_y)/f_x.$ and $b = -d f_y/f_x$.
-Direction substition then shows that $\bar f_{\bar y \bar y} = D d^2 / f_x^2$, where $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$.
-
-Under a general action of $\phi \in \mathrm{PSL}(3,\R)$, $D$ is a relative invariant (that is, the value is multiplied by a certain factor under group transformations) of weight 2:
-\begin{equation}
-\label{eq:D}
-D \mapsto (\det \phi')^2 D\circ \phi.
-\end{equation}
-
-It is also an invariant of $A(2)$, which is a subgroup of $\mathrm{PSL}(3,\R)$.
-Note that the sign of $D$ does not change.
-We assume that $D>0$ (if it is negative, relatively little changes in the following derivation) and choose the frame $\bar f_{ \bar y \bar y} = 1$, so that $d = f_x/D^{1/2}.$
+Direction substition then shows that $\bar f_{\bar y \bar y} = D d^2 / f_x^2$, where $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$, which we saw earlier as an invariant of $A(2)$, which is a subgroup of $\mathrm{PSL}(3,\R)$.
+Note that $D$ and $\bar f_{\bar y \bar y}$ have the same sign; in what follows we assume that $D>0$ (if it is negative, relatively little changes in the following derivation) and choose the frame $\bar f_{ \bar y \bar y} = 1$, so that $d = f_x/D^{1/2}.$
 

### 2020-11-11 paper/newpaper.tex
Minor tweaks to conformal section

@@
 The conformal diffeomorphisms provides a particularly nice example of the
-moving frame method. Letting $z = x + iy$, let $\bar{z} = \psi(z)$ be a conformal
-mapping. It's convenient to work with the inverse transformation, so let
+moving frame method. Because the group is infinite dimensional, we need to
+prolong the group action to the infinite jet space $J^{\infty}$ with
+elements of the form $(x, y, f, f_x, f_y, f_{xx}, f_{xy}, f_{yy}, \ldots)$.
+Recall the moving frame produces a conformal map $\psi$ for each element of
+$J^\infty$ that maps it to a suitably chosen cross section.
+
+It's convenient to work in the complex variable $z = x + iy$. Without loss of
+generality, we can assume $x = y = 0$. We begin the construction of our
+cross section by choosing $\bar{x} = \bar{y} = 0$. Then, $\psi^{-1}$ 
+can be represented locally by a Taylor series of the form
 \begin{equation*}
-    z = \psi^{-1}(\bar{z}) = c_0 + c_1 \bar{z} + c_2 \bar{z}^2 +
-    c_3\bar{z}^3 + \cdots
+    z = \psi^{-1}(\bar{z}) = c_1 \bar{z} + c_2 \bar{z}^2 + c_3\bar{z}^3 + \cdots
 \end{equation*}
-where $c_i = a_i + ib_i \in \mathbb{C}$.  Because the group is infinite
-dimensional, we need to work on the prolongation of $\psi$ to the jet space
-$J^\infty = \{x, y, f, f_x, f_y, \ldots\}$ including all of its
-derivatives. To make $\psi$ into a moving frame, we specify the
-cross-section and solve for parameters in stages. We begin with $\bar{x} =
-\bar{y} = 0$. This yeilds $c_0 = z$. To find $c_1 = a_1 + i b_1$ we need
-two constraints. Differentiating $f(x, y) = \bar{f}(\bar{x}, \bar{y})$ and
-substituting in our existing cross section constraints $\bar{x} = \bar{y} = 0$ gives
+where $c_k = a_k + ib_k, k = 1, 2, \ldots$. We solve for the parameters
+$a_k, b_k$ in stages.  To find $c_1 = a_1 + i b_1$ we need two constraints.
+Differentiating $f(x, y) = \bar{f}(\bar{x}, \bar{y})$ and substituting in
+our existing cross section constraints $\bar{x} = \bar{y} = 0$ gives
 \begin{align*}
@@
 order $n$, so there must be $n-1$ new independent invariants at each order.
-
-At third order there are two more invariants, using the constraints
+Hence at third order there are two more invariants, using the constraints
 $\bar{f}_{\bar{x}\bar{x}\bar{x}} = 0, \bar{f}_{\bar{x}\bar{x}\bar{y}} = 0$,

### 2020-11-12 paper/newpaper.tex
minor

@@
 However, analysis on these quotient spaces is rarely simple~\cite{}, and if one is interested in the object, and not the transformation, then it necessitates a lot of computational work for relatively little benefit.
+
 An alternative option is to seek $\mathcal{G}$-invariant functions on $M$, which is what we consider here.
 In this case, rather than considering the image of the object, one works with an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group.
-This reduces the recognition problem to recognising higher-dimensional invariant signatures.
-
-Something about signatures
-3. The signature must vary continuously with respect to the image, either for all smooth
-images or for all except a set of sufficiently high codimension. This is essential if the
+These signatures are typically of a higher dimensionality that the original image.
+
+The theory of invariants has a rich mathematical history~\cite{}.
+
+Olver et al. joint differential invars (aka semi-diff)
+MOMENTS
+
+In order for the invariant signatures to be useful to identify similarity in images, there are two key considerations: they must vary continuously with respect to the image, either for all smooth images or for all except a set of sufficiently high codimension, and they must be robust with respect to occlusions, where one object obscures some part of another.
+These constraints lead to the
+This leads one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology.
+This is sufficient to compute, e.g., derivatives of an object.
+This fails for a variety of 
+However, of particular saliance for object recognition in scenes is the need to be robust to occlusions,
+
+The introduction of an invariant signature reduces the recognition problem to one of comparing the higher-dimensional signatures that encode the desired self-equivalences.
+In this paper we introduce the mathematical considerations necessary to construct invariant signatures to the planar Lie groups that can transform 2D images.
+We consider a wide range of planar groups, both finite-dimensional Lie groups and infinite-dimensional pseudo-Lie ones; as we shall show, the lattice structure of the set of groups influences the relationship between the sets of invariants for the different groups.
+We provide sample signature sets for the various groups we consider, and examples of the appearance of those signatures for transformations of a simple, smooth image, but do not consider the question of a complete practical implementation.
+We do not consider the matching of the signatures, for which several methods already exist, such as~\cite{}.
+
+This is essential if the
 signature is to be used to detect similarity of images, but it fails for the rational
 invariants found in the literature.
-Invariant signatures -- self-equivalences
-
-The theory of invariants has a rich mathematical history~\cite{}.
-
-However, of particular saliance for object recognition in scenes is the need to be robust to occlusions, where one object obscures some part of another.
-This leads one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology.
-This is sufficient to compute, e.g., derivatives of an object.
-Olver et al. joint differential invars (aka semi-diff)
-MOMENTS
 
@@
 not intensity transforms
-
-We consider a wide range of planar groups, both finite-dimensional Lie groups and infinite-dimensional pseudo-Lie ones; as we shall show, the lattice structure of the set of groups influences the relationship between the sets of invariants for the different groups.
 
@@
 
-In this paper we provide a tutorial on differential invariants for planar Lie groups (e.g.
-Euclidean, affine, projective) since they are relatively simple, useful,
-and relevant to images. We'll use these to demonstrate the methods of
-constructing and using differential invariant signatures.
-
 Different sorts of invariant, and their properties.
-
-The question of how to compare invariant signatures is not considered further in this paper.
 
@@
 %Groups we've done:
-
 %translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
@@
 
-\todo[inline]{visual obstruction}
-
-\section{Differential invariants of E(2) through tensor contraction}
+\section{Differential invariants through tensor contraction}
 While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$.
@@
 \item[$\mathrm{Diff}$]
+\todo[Move this one out]
 In the full diffeomorphism group there are no differential invariants using 1 or 2 colours.
@@
 
-\section{Use in practice; noise, singularities}
- \todo[inline]{Experimental}
-
-Some calculation detail
-
-\todo[inline]{Signature examples}
-\todo[inline]{Alien: Smoothing, noise}
-\todo[inline]{Spot the group?}
-
 \section{Conclusions}
@@
 \todo[inline]{Is there a general theory - syzygy??}
+\todo[inline]{Difficulties of a practical implementation}
 

### 2020-11-16 paper/newpaper.tex
refs
bibupdates

@@
 \usepackage{array}
+\usepackage{natbib}
 
@@
 If the space of objects is denoted $M$ and the appearance transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$.
-One way to achieve this is by transforming all objects to match a chosen target object by registration (the transformation of the appearance of one shape to match another, typically by gradient descent on a matching function, see e.g.~\cite{}).
-Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{} will place all of the shapes into the reference frame of one template example.
-However, analysis on these quotient spaces is rarely simple~\cite{}, and if one is interested in the object, and not the transformation, then it necessitates a lot of computational work for relatively little benefit.
+One way to achieve this is by transforming all objects to match a chosen target object by registration (the transformation of the appearance of one shape to match another, typically by gradient descent on a matching function, see e.g.~\cite{Modersitzki03}).
+Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{Kendall1989} will place all of the shapes into the reference frame of one template example.
+However, analysis on these quotient spaces is rarely simple (see e.g.,~\cite{Marsland19b} for a basic primer), and if one is interested in the object, and not the transformation, then it necessitates a lot of computational work for relatively little benefit.
 
 An alternative option is to seek $\mathcal{G}$-invariant functions on $M$, which is what we consider here.
-In this case, rather than considering the image of the object, one works with an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group.
-These signatures are typically of a higher dimensionality that the original image.
-
-The theory of invariants has a rich mathematical history~\cite{}.
-
-Olver et al. joint differential invars (aka semi-diff)
-MOMENTS
+In this case, rather than considering the image of the object, one constructs an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group.
+This has been considered extensively by Olver and co-authors for the case of outlines of objects~\cite{Calabi1998,Hoff2013}.
+In this paper we consider the case of signatures for images rather than curve outlines.
+
+The introduction of an invariant signature reduces the recognition problem to one of comparing the higher-dimensional signatures (typically the signatures need to be at least three dimensional for planar images) that encode the desired self-equivalences.
+In this paper we introduce the mathematical considerations necessary to construct invariant signatures to the planar Lie groups (and some infinite-dimensional, pseudo-Lie groups too) that can transform 2D images.
+As we shall show, the lattice structure of the set of groups influences the relationship between the sets of invariants for the different groups.
+We provide sample signature sets for the various groups we consider, and examples of the appearance of those signatures for transformations of a simple, smooth image, but do not consider the question of a complete practical implementation.
+We do not consider the classification of the signatures, for which either a standard image recognition algorithm can be used (see, e.g.,~\cite{Zhang20} for a survey), or a matching method such as~\cite{UsCurrents} can be used.
 
 In order for the invariant signatures to be useful to identify similarity in images, there are two key considerations: they must vary continuously with respect to the image, either for all smooth images or for all except a set of sufficiently high codimension, and they must be robust with respect to occlusions, where one object obscures some part of another.
-These constraints lead to the
-This leads one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology.
+These constraints lead one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology.
 This is sufficient to compute, e.g., derivatives of an object.
-This fails for a variety of 
-However, of particular saliance for object recognition in scenes is the need to be robust to occlusions,
-
-The introduction of an invariant signature reduces the recognition problem to one of comparing the higher-dimensional signatures that encode the desired self-equivalences.
-In this paper we introduce the mathematical considerations necessary to construct invariant signatures to the planar Lie groups that can transform 2D images.
-We consider a wide range of planar groups, both finite-dimensional Lie groups and infinite-dimensional pseudo-Lie ones; as we shall show, the lattice structure of the set of groups influences the relationship between the sets of invariants for the different groups.
-We provide sample signature sets for the various groups we consider, and examples of the appearance of those signatures for transformations of a simple, smooth image, but do not consider the question of a complete practical implementation.
-We do not consider the matching of the signatures, for which several methods already exist, such as~\cite{}.
-
-This is essential if the
-signature is to be used to detect similarity of images, but it fails for the rational
-invariants found in the literature.
-
-derivatives: noise is not
-not intensity transforms
+For this reason we focus on differential invariants.
+The disadvantage of such invariants, as we shall discuss, is the need to compute several orders of spatial derivative of the image.
 
@@
 See, e.g.,~\cite{UsMobius} and references therein for more discussion about the desirable properties of a set of invariants for image and curve analysis.
-
-Different sorts of invariant, and their properties.
 
@@
 In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$.
-This is known as the jet space, or jet bundle~\cite{OlverJets}.
+This is known as the jet space, or jet bundle~\cite{OlverEIS}.
 The $d$-th order jet space $J^d$ consists of the function itself and the set of all partial derivatives of the function up to order $d$.
@@
 \subsection{Relevant Literature}
+The theory of invariants has a rich mathematical history, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview. Of most relevance to us here 
+\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872}
+
+\cite{Olver2005,Cartan35}
+
+This is essential if the
+signature is to be used to detect similarity of images, but it fails for the rational
+invariants found in the literature.
+
+not intensity transforms
+
+Different sorts of invariant, and their properties.
+
+Signature
+
+Relative invars
+Joint sigs
+\cite{Fels1997,Olver2013,Arora2009}
+
+Diff Invs
+\cite{Florack1993,Olver2007,Bouton1898}
+
+Projective invars
+\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}
+
+Moments
+\cite{Hickman2011,Abu-Mostafa1984,Kakarala2010,Flusser2009,Papakostas2013}
+
+FFT
+\cite{Reddy1996,Gauthier2008,Kakarala2011,Smach2007}
+
+Integral invar
+\cite{Manay2006,Negrinho2013,Ghorbel1994,Turski2006}
+
+There has been a long-standing interest in constructing invariants for image recognition.
+\cite{VanGool1995,Wood1996,Zhang2019,Faugeras1994,Gros1992,Taubin1992,Lenz1990,Florack1993}
+
+\cite{SURF}
+
 ---
@@
 An algorithm to compute invariants and determine complete signature sets is
-described in \cite{olver2001}. First, the entire set of invariants is
+described in \cite{Olver2005}. First, the entire set of invariants is
 computed using the method of moving frames. Second, determine the
@@
 $SA(2)$ where, following the treatment in~\cite{OlverCIT}, this leads to
-Cayley's Omega Process~\cite{Cayley}.
+Cayley's Omega Process~\cite{Cayley1846}.
 
@@
 
-This can be generalised to $n$ functions $f^{(1)}(x_1, y_1), \ldots, f^{(n)}(x_n, y_n)$ and $r$-th order~\cite{Olver} to define a partial transvectant as:
+This can be generalised to $n$ functions $f^{(1)}(x_1, y_1), \ldots, f^{(n)}(x_n, y_n)$ and $r$-th order~\cite{OlverEIS} to define a partial transvectant as:
 
@@
 When defined on the principal bundle it defines a $\mathcal{G}$-equivariant mapping, which enables one to identify invariants under the action of groups of transformations.
-The method of moving frames has a long history, as summarised in \cite{Olver14}; particularly noteworthy contributions are by Cartan~\cite{Cartan37} and Olver and co-authors; see~\cite{Olver14} for an overview, and note particularly for an application to~\cite{Calabi98}.
+The method of moving frames, which originated with Cartan~\cite{Cartan35}  has a long history, as summarised in \cite{Olver2005}.
+Olver and co-authors, in particular, have popularised the approach and made it applicable to image analysis, see~\cite{Olver2005} for an overview, and the original application paper ~\cite{Calabi1998}.
 The method is described in detail in~\cite{OlverCIT}.
@@
 These invariants are a functionally independent, complete, set of polynomial differential invariants up to second derivatives.
-Note that the invariants found previously by tensor contraction (\cite{eq:se2}) can be expressed in terms of these:
+Note that the invariants found previously by tensor contraction (\ref{eq:se2}) can be expressed in terms of these:
 \begin{align*}
@@
 Identifying $\R^2$ with $\mathbb{C}$, the M\"obius group is a real 6-dimensional local Lie group acting on $\mathbb{R}^2$.
-It is the smallest nonlinear planar group that contains $SE(2)$, and it also has direct applications in image processing since it arises in the {\em conformal camera} model of vision, in which scenes are projected radially onto a sphere \cite{lenz1990group,turski2004geometric}; it is also the set of biholomorphic maps of the Riemann sphere.
+It is the smallest nonlinear planar group that contains $SE(2)$, and it also has direct applications in image processing since it arises in the {\em conformal camera} model of vision, in which scenes are projected radially onto a sphere \cite{Lenz1990,Turski2004}; it is also the set of biholomorphic maps of the Riemann sphere.
 %Different shapes may be related by M\"obius transformations, as is explored by Petukhov \cite{petukhov1989non} for biological objects: in one example, the human skull grows approximately by M\"obius transformations.
@@
 \item[$\mathrm{Diff}$]
-\todo[Move this one out]
+\todo{Move this one out}
 In the full diffeomorphism group there are no differential invariants using 1 or 2 colours.
@@
 
+\bibliographystyle{plainnat}
+\bibliography{invariants}
+
 \end{document}

### 2020-11-16 code/test_symbolic.py
extraneous crap

@@ -1,0 +1,37 @@
+from sympy.abc import x, y
+from sympy import lambdify, sin, exp, pi
+import numpy as np
+from mayavi import mlab
+import matplotlib.pyplot as plt
+import invariants
+
+## Start by setting up the function and transformed function
+f = invariants.SymbolicImage(exp(-2*x**2 - 4*sin(0.5*x**2 + y)**2))
+theta = np.pi/4
+c = np.cos(theta)
+s = np.sin(theta)
+tform = invariants.E2Transform(1, 3*np.pi/4, 0, 0)
+f2 = f.transform(tform)
+
+## Plot the image and transformed image
+X, Y = np.mgrid[-1:1:200j, -1:1:200j]
+I1 = lambdify([x, y], f.f, "numpy")(X, Y)
+I2 = lambdify([x, y], f2.f, "numpy")(X, Y)
+
+fig, (ax1, ax2) = plt.subplots(1, 2)
+ax1.imshow(I1, vmin=0, vmax=1)
+ax2.imshow(I2, vmin=0, vmax=1)
+plt.show()
+
+##
+S = invariants.E2_signature(f)
+Sb = invariants.E2_signature(f2)
+X, Y = np.mgrid[-1:1:200j, -1:1:200j]
+Sn = [lambdify((x, y), S[i], "numpy")(X, Y) for i in range(3)]
+Sbn = [lambdify((x, y), Sb[i], "numpy")(X, Y) for i in range(3)]
+
+
+mlab.mesh(10*Sn[0], Sn[1], Sn[2], color=(0, 0, 1), opacity=0.5)
+mlab.mesh(10*Sbn[0], Sbn[1], Sbn[2], color=(1, 0, 0), opacity=0.5)
+mlab.show()
+

### 2020-11-16 paper/newpaper.tex

@@
 \section{Introduction}
-\todo[inline]{
-Richard: 
-Start on invariant tensor theorem
-Generate new pictures, add function details
-SE(2) jobs inline
-Mobius, Conformal -- finish code, tidy writing
-First bash at experimental section
-
-Stephen:
-Rearrange examples text to IVT section, write about signatures here
-Fix up tables, check bib
-Examples for SA(2), A(2) -- need to think about sig here
-Moving frame intro
-Projective -- tidy writing, especially the names of the invariants
-Colour
-First bash at conclusion
-
-Later:
-Introduction
-Count of derivatives and what to say
-}
-
-\todo[inline]{Examples to be numbered like theorems}
-\todo[inline]{This is a start. To be completed later.}
+%\todo[inline]{
+%Richard: 
+%Start on invariant tensor theorem
+%Generate new pictures, add function details
+%SE(2) jobs inline
+%Mobius, Conformal -- finish code, tidy writing
+%First bash at experimental section
+
+%Stephen:
+%Rearrange examples text to IVT section, write about signatures here
+%Fix up tables, check bib
+%Examples for SA(2), A(2) -- need to think about sig here
+%Moving frame intro
+%Projective -- tidy writing, especially the names of the invariants
+%Colour
+%First bash at conclusion
+
+%Later:
+%Introduction
+%Count of derivatives and what to say
+%}
+
+%\todo[inline]{Examples to be numbered like theorems}
+%\todo[inline]{This is a start. To be completed later.}
 
@@
 This has been considered extensively by Olver and co-authors for the case of outlines of objects~\cite{Calabi1998,Hoff2013}.
-In this paper we consider the case of signatures for images rather than curve outlines.
+In this paper we consider the case of signatures for images rather than outlines of curves.
 
@@
 See, e.g.,~\cite{UsMobius} and references therein for more discussion about the desirable properties of a set of invariants for image and curve analysis.
+
+In this paper we investigate differential invariant signatures for images and parts of images under planar spatial transformations, for both grayscale and colour images.
+The remainder of this introductory sectin provides a description of the notation that we use in this paper, followed by a summary of relevant work on invariants.
+We also introduce the way that we will present examples of the signatures for the various groups we consider.
+Following this, in the next three sections we describe three distinct methods of computing differential invariants: by tensor contraction, using the theory of transvectants, and via the method of moving frames, applying the methods to a variety of the planar Lie groups.
+We consider the difference that colour images make in Section~\ref{sec:colour}, and then discuss the number of derivatives required and the effect this has on the practicality of the method.
 
@@
 
-In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$.
-This is known as the jet space, or jet bundle~\cite{OlverEIS}.
+In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$ via the jet space~\cite{OlverEIS}.
 The $d$-th order jet space $J^d$ consists of the function itself and the set of all partial derivatives of the function up to order $d$.
-(Note that there are $\left( \begin{array}{c} d+k-1 \\ k \end{array} \right)$ partial derivatives of order $d$).
-As the group $\mathcal{G}$ is local, it acts naturally on derivatives of the transformation, and so each individual transformation $\varphi \in \mathcal{G}$ can be prolonged to act on the jet space $J^d$.
+(Note that there are $\left( \begin{array}{c} d+k-1 \\ k \end{array} \right)$ partial derivatives of order $d$.) As the group $\mathcal{G}$ is local, it acts naturally on derivatives of the transformation, and so each individual transformation $\varphi \in \mathcal{G}$ can be prolonged to act on the jet space $J^d$.
 We can thus prolong the action of the group and consider the action of $\mathcal{G}$ on not just $f$, but all derivatives of $f$ up to order $d$.
 A $d$-th order differential invariant is then a local scalar function $I: J^{d} (f,\Omega, k) \to \mathbb{R}$ that is invariant under the action of $\mathcal{G}$, i.e., $I(\varphi(f,\Omega, k)) = I(f, \Omega, k) \forall \varphi \in \mathcal{G}$.
+It can also be useful to consider the maximum order of derivative in the invariant, which we term degree, e.g., $f_{xy}^2 f_x f_y$ has degree 2.
 
@@
 A signature set is complete for $f$ if it determines $f$ up to transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
+If the signature is not complete, then there will be a \emph{bad set} of images that cannot be differentiated between.
+***
 
@@
 computed using the method of moving frames. Second, determine the
-differential invariant order $s$ of $f$ \todo[inline]{we need to define the differential invariant order}. Then the signature set of a maximal
+differential invariant order $s$ of $f$. Then the signature set of a maximal
 set of functionally independent invariants of order $s+1$ is complete. A
@@
 \mathbf{b}$. $r$ is referred to as the weight of the partial
-transvectant. It can also be useful to consider the maximum order of
-derivative in the transvectant, which we term degree, e.g., $f_{xy}^2 f_x
-f_y$ has degree 2. Note also that the individual pairwise Omega processes commute.
+transvectant. Note that the individual pairwise Omega processes commute.
 
@@
 Hence, we can form a signature for $SA(2)$ by choosing any combination of
-partial transvectants. We'll choose a signature with three components so that
+partial transvectants. We choose a signature with three components so that
 it can be visualised as a three-dimensional surface; note that this will not
@@
 \todo[inline]{remake figure with modified matrix. Also modify function so it has some features like a critical point}
-We'll subject our image to a special affine transformation:
+We will subject our image to a special affine transformation:
 \begin{equation*}
@@
 An element of the Euclidean group $E(2)$ maps an element $(x, y)$ of
-$\mathbb{R}^2$ to $(\bar{x}, \bar{y})$ as 
+$\mathbb{R}^2$ to $(\bar{x}, \bar{y})$ as:
 \begin{equation*}

### 2020-11-16 paper/newpaper.tex
fixes

@@
 \begin{abstract}
+Object recognition, planar transformation, invariants, differential invariant signature, demo of 3 methods with examples for planar Lie groups, discussion of utility
 \end{abstract}
@@
 \begin{keywords}
-
+Object recognition, planar transformation, invariants, differential invariant signature
 \end{keywords}
@@
 \section{Introduction}
+\todo[inline]{
+Abstract
+Bad set, singular
+Literature
+Weight
+
+Example intro
+T(2)
+
+Sim(2) by contraction
+A(2) by transvectant
+
+When introduce each group, mention relevance to images?
+
+Friendly intro to moving frame
+Finish colour
+
+Discussion
+}
+
 %\todo[inline]{
@@
 
-Ideally, an invariant signature would be complete, so that the image is exactly determined up to a transformation, and two objects share a signature if and only if they differ only by a transformation from $\mathcal{G}$.
+Ideally, an invariant signature would be complete, so that the image is exactly determined by the signature up to a transformation, and two objects share a signature if and only if they differ only by a transformation from $\mathcal{G}$.
 However, this often requires signatures in many dimensions, and potentially also more derivatives of the image.
@@
 
-In this paper we investigate differential invariant signatures for images and parts of images under planar spatial transformations, for both grayscale and colour images.
-The remainder of this introductory sectin provides a description of the notation that we use in this paper, followed by a summary of relevant work on invariants.
+In this paper we investigate differential invariant signatures for images and parts of images under planar spatial transformations, primarily Lie groups, for both greyscale and colour images.
+The set of groups that we consider are shown as a lattice in Figure~\ref{fig:lattice}, where the size of the groups decrease as down the page, and the arrows denote the subgroup relationship.
+There is an important relationship between a group and its subgroups for invariants, which is that invariants of a group are automatically invariants of its subgroups.
+This means that differentiating between them requires care.
+
+The remainder of this introductory section provides a description of the notation that we use in this paper, followed by a summary of relevant work on invariants.
 We also introduce the way that we will present examples of the signatures for the various groups we consider.
@@
 We consider the difference that colour images make in Section~\ref{sec:colour}, and then discuss the number of derivatives required and the effect this has on the practicality of the method.
-
-\subsection{Notation}
-
-We define a {\em $k$-colour image} as a triple $(f,\Omega,k)$ where $\Omega\subset\R^n$ (typically, images are planar, so $n=2$), $1\le k\in\mathbb{Z}$ is the number of colour channels, and $f\colon\Omega\to\R^k$.
-The function $f$ will be taken to be as smooth as necessary.
-Consider a (finite or infinite-dimensional) local transformation group $\mathcal{G}$.
-A transformation $\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) = (f\circ\varphi^{-1},\varphi(\Omega),k)$.
-For many of our examples we consider greyscale images, so $k=1$, although we will discuss colour images in Section~\ref{sec:colour}.
-Also, since we work locally, we will usually omit the domain $\Omega$.
-
-In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$ via the jet space~\cite{OlverEIS}.
-The $d$-th order jet space $J^d$ consists of the function itself and the set of all partial derivatives of the function up to order $d$.
-(Note that there are $\left( \begin{array}{c} d+k-1 \\ k \end{array} \right)$ partial derivatives of order $d$.) As the group $\mathcal{G}$ is local, it acts naturally on derivatives of the transformation, and so each individual transformation $\varphi \in \mathcal{G}$ can be prolonged to act on the jet space $J^d$.
-We can thus prolong the action of the group and consider the action of $\mathcal{G}$ on not just $f$, but all derivatives of $f$ up to order $d$.
-A $d$-th order differential invariant is then a local scalar function $I: J^{d} (f,\Omega, k) \to \mathbb{R}$ that is invariant under the action of $\mathcal{G}$, i.e., $I(\varphi(f,\Omega, k)) = I(f, \Omega, k) \forall \varphi \in \mathcal{G}$.
-It can also be useful to consider the maximum order of derivative in the invariant, which we term degree, e.g., $f_{xy}^2 f_x f_y$ has degree 2.
-
-An $m$-dimensional signature set is the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e., the set $\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$.
-A signature set is complete for $f$ if it determines $f$ up to transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
-If the signature is not complete, then there will be a \emph{bad set} of images that cannot be differentiated between.
-***
-
-NEED TO TALK ABOUT WHEN IT IS SINGULAR
-
-For the case of two-dimensional greyscale images it is often convenient to work in coordinates.
-In this case the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$ is given by:
-\begin{equation}\label{eq:transformation}
-  \mathbf{x} \mapsto \bar{\mathbf{x}} = \varphi(\mathbf{x}).
-\end{equation}
-The transformed image is then defined to be:
-\begin{equation}\label{eq:fbarequalsf}
-  \bar{f}(\bar{\mathbf{x}}) = (f\circ\varphi^{-1})(\bar{\mathbf{x}}) = f(\mathbf{x}).
-\end{equation}
-Derivatives of $\bar{f}$ and $f$ can be related by the chain rule, for example the first order derivatives are given by:
-\begin{equation}\label{eq:prolongation}
-  \begin{aligned}
-    f_x &= \bar{f}_{\bar{x}} \bar{x}_x + \bar{f}_{\bar{y}}\bar{y}_x \\
-    f_y &= \bar{f}_{\bar{x}} \bar{x}_y + \bar{f}_{\bar{y}}\bar{y}_y \\
-  \end{aligned}
-\end{equation}
-where $\bar{x}_x = \frac{\partial \varphi_1}{\partial x}(x, y)$, et cetera. It is often convenient to work with $\varphi^{-1}$ instead, as in \S\ref{sec:movingframes}.
-
-\subsection{Relevant Literature}
-The theory of invariants has a rich mathematical history, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview. Of most relevance to us here 
-\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872}
-
-\cite{Olver2005,Cartan35}
-
-This is essential if the
-signature is to be used to detect similarity of images, but it fails for the rational
-invariants found in the literature.
-
-not intensity transforms
-
-Different sorts of invariant, and their properties.
-
-Signature
-
-Relative invars
-Joint sigs
-\cite{Fels1997,Olver2013,Arora2009}
-
-Diff Invs
-\cite{Florack1993,Olver2007,Bouton1898}
-
-Projective invars
-\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}
-
-Moments
-\cite{Hickman2011,Abu-Mostafa1984,Kakarala2010,Flusser2009,Papakostas2013}
-
-FFT
-\cite{Reddy1996,Gauthier2008,Kakarala2011,Smach2007}
-
-Integral invar
-\cite{Manay2006,Negrinho2013,Ghorbel1994,Turski2006}
-
-There has been a long-standing interest in constructing invariants for image recognition.
-\cite{VanGool1995,Wood1996,Zhang2019,Faugeras1994,Gros1992,Taubin1992,Lenz1990,Florack1993}
-
-\cite{SURF}
-
----
-TEXT FROM OUR MOBIUS PAPER
-Calabi et al. [9] propose the use of differential invariant signatures for shape analysis, and further
-argue that these should be approximated in a group-invariant way. For example, for the Euclidean
-group, the signature is the shape \todo[inline]{something didn't copy paste correctly here} (??; ??s) regarded as a subset of R2. The claimed advantages
-of the approach are that the signature determines the shape; that it does not depend on the
-choice of initial point on the curve or on parameterization by arclength, and that its G-invariance
-makes it robust; and that it is based on a general procedure for arbitrary objects and groups.
-See [2, 4, 9, 18, 30, 35, 36] for further developments and applications of the invariant signature.
-Although the signature at first sight appears to be complete (e.g., Theorem 5.2 in [9]),
-a more detailed treatment (e.g., [17, 28]) highlights the fact that it is not complete on shapes
-that contain singular parts { straight and circular segments in the Euclidean case. For these
-parts, the signature reduces to a point. Thus, for shapes that have nearly straight or nearly
-circular segments, the signature cannot be robust. In addition, while the signature does not
-depend on the starting point or the parameterization, it takes values in a very complicated set,
-namely, the planar shapes. To compare the invariants of two shapes requires comparing two
-shapes. Essentially, the parameterization-dependence has only been deferred to a later stage
-of the analysis (unless one is content to compare shapes visually). One approach to this is to
-weight the signature, see [32] for more details.
----
-
-SURF and that kind of crap
-
-An algorithm to compute invariants and determine complete signature sets is
-described in \cite{Olver2005}. First, the entire set of invariants is
-computed using the method of moving frames. Second, determine the
-differential invariant order $s$ of $f$. Then the signature set of a maximal
-set of functionally independent invariants of order $s+1$ is complete. A
-third step is possible, in which the dimension of the signature set is
-reduced by eliminating those invariants whose values can be computed from the
-values of derivatives of some subset of the invariants.
-
-While we follow this approach in general, in specific cases we have computed invariants using other techniques
-including the invariant tensor theorem and classical invariant theory.
-We shall see that this yields insights into the relationships between the different groups.
-We develop our approach through examples of progressively more complicated groups.
-===
-
-JUSTIFY THIS SET OF GROUPS
-
-\todo[inline]{Use T(2) as an example}
 
@@
 \caption{The lattice of groups considered in this paper. The edges identify subgroups.}
+\label{fig:lattice}
 \end{figure}
+
+\subsection{Concepts and Notation}
+
+We define a {\em $k$-colour image} as a triple $(f,\Omega,k)$ where $\Omega\subset\R^n$ (typically, images are planar, so $n=2$), $1\le k\in\mathbb{Z}$ is the number of colour channels, and $f\colon\Omega\to\R^k$.
+The function $f$ will be taken to be as smooth as necessary.
+Consider a (finite or infinite-dimensional) local transformation group $\mathcal{G}$.
+A transformation $\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) = (f\circ\varphi^{-1},\varphi(\Omega),k)$.
+For many of our examples we consider greyscale images, so $k=1$, although we will discuss colour images in Section~\ref{sec:colour}.
+Also, since we work locally, we will usually omit the domain $\Omega$.
+
+In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$ via the jet space~\cite{OlverEIS}.
+The $d$-th order jet space $J^d$ consists of the function itself and the set of all partial derivatives of the function up to order $d$.
+(Note that there are $\left( \begin{array}{c} d+k-1 \\ k \end{array} \right)$ partial derivatives of order $d$.) As the group $\mathcal{G}$ is local, it acts naturally on derivatives of the transformation, and so each individual transformation $\varphi \in \mathcal{G}$ can be prolonged to act on the jet space $J^d$.
+We can thus prolong the action of the group and consider the action of $\mathcal{G}$ on not just $f$, but all derivatives of $f$ up to order $d$.
+A $d$-th order differential invariant is then a local scalar function $I: J^{d} (f,\Omega, k) \to \mathbb{R}$ that is invariant under the action of $\mathcal{G}$, i.e., $I(\varphi(f,\Omega, k)) = I(f, \Omega, k) \forall \varphi \in \mathcal{G}$.
+It can also be useful to consider the maximum order of derivative in the invariant, which we term degree, e.g., $f_{xy}^2 f_x f_y$ has degree 2.
+
+An $m$-dimensional signature set is the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e., the set $\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$.
+A signature set is complete for $f$ if it determines $f$ up to transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
+If the signature is not complete, then there will be a \emph{bad set} of images that cannot be differentiated between.
+***
+
+NEED TO TALK ABOUT WHEN IT IS SINGULAR
+
+For the case of two-dimensional greyscale images it is often convenient to work in coordinates.
+In this case the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$ is given by:
+\begin{equation}\label{eq:transformation}
+  \mathbf{x} \mapsto \bar{\mathbf{x}} = \varphi(\mathbf{x}).
+\end{equation}
+The transformed image is then defined to be:
+\begin{equation}\label{eq:fbarequalsf}
+  \bar{f}(\bar{\mathbf{x}}) = (f\circ\varphi^{-1})(\bar{\mathbf{x}}) = f(\mathbf{x}).
+\end{equation}
+Derivatives of $\bar{f}$ and $f$ can be related by the chain rule, for example the first order derivatives are given by:
+\begin{equation}\label{eq:prolongation}
+  \begin{aligned}
+    f_x &= \bar{f}_{\bar{x}} \bar{x}_x + \bar{f}_{\bar{y}}\bar{y}_x \\
+    f_y &= \bar{f}_{\bar{x}} \bar{x}_y + \bar{f}_{\bar{y}}\bar{y}_y \\
+  \end{aligned}
+\end{equation}
+where $\bar{x}_x = \frac{\partial \varphi_1}{\partial x}(x, y)$, et cetera. %It is often convenient to work with $\varphi^{-1}$ instead, as in \S\ref{sec:movingframes}.
+
+\subsection{Relevant Literature}
+
+The theory of invariants has a rich mathematical history, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview. Of most relevance to us here 
+\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872}
+
+\cite{Olver2005,Cartan35}
+
+This is essential if the
+signature is to be used to detect similarity of images, but it fails for the rational
+invariants found in the literature.
+
+not intensity transforms
+
+Different sorts of invariant, and their properties.
+
+Signature
+
+Relative invars
+Joint sigs
+\cite{Fels1997,Olver2013,Arora2009}
+
+Diff Invs
+\cite{Florack1993,Olver2007,Bouton1898}
+
+Projective invars
+\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}
+
+Moments
+\cite{Hickman2011,Abu-Mostafa1984,Kakarala2010,Flusser2009,Papakostas2013}
+
+FFT
+\cite{Reddy1996,Gauthier2008,Kakarala2011,Smach2007}
+
+Integral invar
+\cite{Manay2006,Negrinho2013,Ghorbel1994,Turski2006}
+
+There has been a long-standing interest in constructing invariants for image recognition. 
+\cite{VanGool1995,Wood1996,Zhang2019,Faugeras1994,Gros1992,Taubin1992,Lenz1990,Florack1993}
+
+\cite{SURF}
+
+SURF and that kind of crap
+
+An algorithm to compute invariants and determine complete signature sets is
+described in \cite{Olver2005}. First, the entire set of invariants is
+computed using the method of moving frames. Second, determine the
+differential invariant order $s$ of $f$. Then the signature set of a maximal
+set of functionally independent invariants of order $s+1$ is complete. A
+third step is possible, in which the dimension of the signature set is
+reduced by eliminating those invariants whose values can be computed from the
+values of derivatives of some subset of the invariants.
+
+While we follow this approach in general, in specific cases we have computed invariants using other techniques
+including the invariant tensor theorem and classical invariant theory.
+We shall see that this yields insights into the relationships between the different groups.
+We develop our approach through examples of progressively more complicated groups.
+===
 
@@
 %translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
-
-We consider as our image, the following function, defined on $[-1, 1]
-\times:
-[-1, 1]$
+\subsection{Example signatures}
+
+In this paper our aim is develop the mathematical underpinnings of constructing differential invariant signatures for images under the action of planar Lie groups.
+However, as we develop the signature for each group, we will provide an example of the type of surface that the signature defines.
+Note that these will generally be three-dimensional representation of the planar image.
+
+The image we use is defined on $[-1,1] \times [-1,1]$ to be:
+
 \begin{equation}\label{eq:function}
-  \begin{split}
-    f(x, y) &= 0.5 - 0.2x - 0.3y - 0.05x^2 + 0.03xy + 0.04y^2 \\ 
-    &+ 0.03y^3 + 0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3.
-  \end{split}
-\end{equation}
-This function was chosen to have no critical points, and to be
-predominantly linear, so that the higher order derivatives were not too
-large. This was predominantly so the higher order terms in the signatures
-would not overwhelm the smaller terms. The function is depicted as a
-greyscale image in Figure~\ref{fig:function}
+**write me**
+\end{equation}
+
+The function is depicted as a greyscale image in Figure~\ref{fig:function}.
+On the left the image itself is shown, while on the right a version with a regular grid superimposed is given.
+This is useful for visualising both the transformation and how the image is mapped into the three-dimensional signature surface.
+
 \begin{figure}
   \centering
-  \includegraphics[width=12cm]{Figs/function}
+  \includegraphics[width=.45\textwidth]{Figs/function}
+  \includegraphics[width=.45\textwidth]{Figs/function_scanlines}
   \caption{The test function used in this document, from
@@
 
-We consider the signatures of this function under various transformation
-groups, as detailed throughout the main body of the paper and illustrate
-the signature in three dimensions. A grid is overlaid on the image of the
-function itself, as shown in Fig~\ref{fig:function_scanlines}. This grid is
-mapped to the signature surface to help understand what the signature looks
-like locally.
-\begin{figure}
-  \centering
-  \includegraphics[width=12cm]{Figs/function_scanlines}
-  \caption{The test function used in this document, from
-  Eq.~\eqref{eq:function} with a grid of lines
-overlaid.}\label{fig:function_scanlines}
-\end{figure}
+\subsection{Getting Started: Translations}
+
+The most basic transformation group of a image is the translation group $T(2): \phi(\mathbf{x}) = \mathbf{x} + \mathbf{t}$.
+
+We could explicitly write the calculation in Eq.~\ref{eq:prolongation} for this case, but instead provide an intuitive explanation.
+Consider a point in the original image, and the corresponding point in the transformed one.
+Clearly, the intensity value of the points match, and so do their first spatial derivatives.
+These three quantities can be used as coordinates in a new space, where the two image points will correspond.
+Computing these coordinates for all image points will define a surface in the new three-dimensional space, and the two images will produce the same surface, which we call the signature.
+
+Figure~\ref{fig:T2} shows (a) the original image, (b) the translated image by $x,y$, (c) the signature of one of them, (d) the superimposed pair of signatures. Now explain the missing bits.
 
 \section{Differential invariants through tensor contraction}
+
 While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$.
@@
 
-While we can construct any number of invariants this way, there is no guarantee of functional independence of the constructed invariants.
+While we can construct any number of invariants this way, there is no guarantee of functional independence between them.
 We will address this issue in Section~\ref{sec:movingframes} when we construct invariants of $E(2)$ and other groups using the method of moving frames.
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_SE2.png}
+\includegraphics[width=.45\textwidth]{Figs/SE2_signature.png}
+\caption{A sample $SE(2)$ Transform and 3D signature.}
+\label{fig:SE2}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_E2.png}
+\includegraphics[width=.45\textwidth]{Figs/E2_signature.png}
+\caption{A sample $E(2)$ Transform and 3D signature.}
+\label{fig:E2}
+\end{figure}
+
 \section{Differential invariants through transvectants}
 
-Another way to compute invariants is to compare the action of group elements on separate copies of the underlying space (here, $\mathbb{R}^2$).
+Another way to compute invariants is to compare the simultaneous action of a group element on separate copies of the underlying space (here, $\mathbb{R}^2$).
+By identifying these spaces with each other it is possible to construct a function known as a transvectant that is invariant up to a scale factor (a \emph{relative invariant}) to that group action.
 
@@
 Consider $\mathbf{x}_i \in \mathbb{R}^2, i=1,2$, so that $\mathbf{x}_i$ can
-be written in coordinates as $(x_i, y_i)$.
-Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$.
+be written in coordinates as $(x_i, y_i)$; a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$.
 Now consider applying the same affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + \mathbf{b}$ where $A \in GL(2,\mathbb{R}$) and $\mathbf{b} \in \mathbb{R}^2$.
@@
 Under the above affine transformation, $\Omega_{ij} \mapsto (\det A)^{-1}
-\Omega_{ij}$. Note that $(\det A)^{-1}$ has no dependence on the coordinates.
-The Omega Process can be applied to pairs of smooth functions as follows,
+\Omega_{ij}$, and is thus a relative invariant. Note that $(\det A)^{-1}$ has no dependence on the coordinates.
+The Omega Process can be applied to products of pairs of smooth functions as follows,
 writing $\frac{\partial f}{\partial x}$ as $f_x$:
@@
 transvectant. Note that the individual pairwise Omega processes commute.
+The concept of a relative invariant will be important in what follows.
 
 For the current case it is sufficient to consider $n$ copies of the same
-function $f$. If we represent each copy (of $\mathbb{R}^2$) as a node on a
+function $f$. If we represent each copy of $\mathbb{R}^2$ as a node on a
 undirected graph, and each Omega process $\Omega_{ij}$ as an edge joining
@@
     &= \mbox{tr}\left[\left(\partial_{x_1 y_2} - \partial_{x_2 y_1}\right)\left(f_x(x_1, y_1)f_y(x_2, y_2) - f_y(x_1, y_1)f_x(x_2, y_2)\right)\right] \\
-    &= \mbox{tr}\left[f_{xx}(x_1, y_1)f_{yy}(x_2, y_2) - f_{xy}(x_1, y_1)f_{xy}(x_2, y_2)\right] \\
-    &= f_{xx}(x, y) f_{yy}(x, y) - f_{xy}(x, y)^2.
+    &= \mbox{tr} 2 \left[f_{xx}(x_1, y_1)f_{yy}(x_2, y_2) - f_{xy}(x_1, y_1)f_{xy}(x_2, y_2)\right] \\
+    &= 2 f_{xx}(x, y) f_{yy}(x, y) - 2 f_{xy}(x, y)^2.
 \end{align*}
@@
 \end{center}
-where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$.
+where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$ (the names are purely for convenience).
+
 Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} shows all possible nonzero partial
@@
 
-\todo[inline]{Explain}
-
 \subsection{Signatures of SA(2) and A(2)}
@@
 \includegraphics[width=.45\textwidth]{Figs/SA2_signature.png}
-\caption{\todo[inline]{add extra crap} A sample $SA(2)$ Transform and 3D signature. Mention what's going on with the grid.}
+\caption{A sample $SA(2)$ transformation and 3D signature.}
 \label{fig:SA2}
@@
 \includegraphics[width=.45\textwidth]{Figs/A2_signature.png}
-\caption{A sample $A(2)$ Transform and 3D signature.}
+\caption{A sample $A(2)$ transformation and 3D signature.}
 \label{fig:A2}
@@
 For $A(2)$ the weight of the partial transvectants prevents them from being invariants.
-They can be normalised by choosing only those where all components have the same weight and projecting them onto a unit hypersphere.
-Instead, we select ratios of partial transvectants.
-It is beneficial to choose the numerator and denominator so that they have different critical points, which can be achieved by adding together partial transvectants of the same weight as appropriate.
-
-\begin{figure}
-\centering
-\includegraphics[width=.45\textwidth]{Figs/f_transformed_SE2.png}
-\includegraphics[width=.45\textwidth]{Figs/SE2_signature.png}
-\caption{A sample $SE(2)$ Transform and 3D signature.}
-\label{fig:SE2}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.45\textwidth]{Figs/f_transformed_E2.png}
-\includegraphics[width=.45\textwidth]{Figs/E2_signature.png}
-\caption{A sample $E(2)$ Transform and 3D signature.}
-\label{fig:E2}
-\end{figure}
+There are two options to create a signature.
+One is to select ratios of partial transvectants.
+It is then beneficial to choose the numerator and denominator so that they have different critical points, which can be achieved by adding together partial transvectants of the same weight as appropriate.
+Instead, we normalise the partial transvectants by choosing only those where all components have the same weight and projecting them onto the unit hypersphere.
+By multiplying these by the function (which takes values between 0 and 1) we create a signature enclosed by the unit hypersphere.
+An example is shown in Figure~\ref{fig:A2}.
 
@@
 
+** Given the importance of the conformal camera model ...
+
 The group of conformal diffeomorphisms is the subgroup of diffeomorphisms that are angle-preserving, i.e.,
@@
 
-It's convenient to work in the complex variable $z = x + iy$. Without loss of
+It is convenient to work in the complex variable $z = x + iy$. Without loss of
 generality, we can assume $x = y = 0$. We begin the construction of our
 cross section by choosing $\bar{x} = \bar{y} = 0$. Then, $\psi^{-1}$ 
-can be represented locally by a Taylor series of the form
+can be represented locally by a Taylor series of the form:
 \begin{equation*}
-    z = \psi^{-1}(\bar{z}) = c_1 \bar{z} + c_2 \bar{z}^2 + c_3\bar{z}^3 + \cdots
+    z = \psi^{-1}(\bar{z}) = c_1 \bar{z} + c_2 \bar{z}^2 + c_3\bar{z}^3 + \cdots,
 \end{equation*}
@@
 Differentiating $f(x, y) = \bar{f}(\bar{x}, \bar{y})$ and substituting in
-our existing cross section constraints $\bar{x} = \bar{y} = 0$ gives
+our existing cross section constraints $\bar{x} = \bar{y} = 0$ gives:
 \begin{align*}
@@
 section, $\bar{f}_{\bar{x}} = 1, \bar{f}_{\bar{y}} = 0$, this system is readily
-solved to give 
+solved to give :
 \begin{equation*}
@@
 
-\subsection{Volume-Preserving Diffeomorphisms $\mathbf{Diff_{vol}}$}
-
-The subgroup of volume-preserving diffeomorphisms are those diffeomorphisms that preserve the volume form, which in 2D is actually the area form.
-They can be defined by one function of two variables, the generating function $S$; one possibility is $S(x,y')$ where $(x,y)\mapsto(x',y')$ according to
-$$ x'=\frac{\partial S}{\partial y'},\quad y = \frac{\partial S}{\partial x}.$$
-
-Consider expanding $S$ in Taylor series.
-The linear terms in the map are determined from the quadratic terms in $S$, which contain 3 group parameters, and act on 2 coordinates, $f_x$ and $f_y$.
-The quadratic terms in the map are determined from the cubic terms in $S$, which contain 4 group parameters, and act on 3 coordinates, $f_{xx}$, $f_{xy}$, and $f_{yy}$.
-At order $n$ we have $n+2$ new group parameters acting on $n+1$ coordinates.
-Thus, barring some exceptional behaviour in the action, we do not expect any invariants at generic points.
-
-This can be confirmed by considering a small image patch with $f(x,y)=x.$ Let $v=\psi_y\partial/\partial_x - \psi_x\partial/\partial_y$ be the generator of an area-preserving map.
-The image $f$ transforms to $x + \varepsilon \psi_y(x,y)$ which (by choosing $\psi$ appropriately) can be any function close to $x$.
-
-At nongeneric points, there can be invariants.
-For example, the area enclosed in any level set of $f$ is invariant.
-At minima or maxima of $f$, this will lead to invariants expressed in terms of the derivatives of $f$.
-
 \section{Colour Images}\label{sec:colour}
@@
 With $k>2$ colours there are many more second-order invariants; however, as the action of the projective group on first derivatives is indistinguishable from that of the full diffeomorphism group, it is not possible to have a first-order signature that distinguishes projectively-related images from diffeomorphically-related ones.
-\item[$\mathrm{Diff}_{\mathrm{vol}}$]
-When $k\ge 2$ in $\mathrm{Diff}_{\mathrm{vol}}$ there are $k(k-1)/2$ first-order invariants $ \nabla f^i \times \nabla f^j$.
+\item[$\mathrm{Diff}_{\mathrm{con}}$]
+For the infinite-dimensional group $\mathrm{Diff}_{\mathrm{con}}$, first-order signature sets are possible for $k \ge 2$ colours.
+They are formed from the relative invariants $(f^j_1 + i f^j_2)(f^m_1 - i f^m_2)$ of weight 2.
+We illustrate this using the Hopf fibration for $k=2$.
+The weight 2 relative invariant $$J = (2(f^1_1 + i f^1_2)(f^2_1 - i f^2_2), ||\nabla f^1\|^2 - \|\nabla f^2\|^2)$$ obeys $\|J\|^2 = \|\nabla f^1\|^2 + \|\nabla f^2\|^2$, hence projecting to the unit sphere shows that $(f^1,f^2,J/\|J\|)$ provides a 4-dimensional signature set that is singular only when $\nabla f^1 = \nabla f^2 = 0$, a codimension 2 phenomenon for images.
+\end{description}
+
+\subsection{Infinite-dimensional Groups of Diffeomorphisms}
+
+We have already seen one example of an infinite-dimensional group, the 2D conformal diffeomorphisms.
+We here briefly consider two other groups: the volume-preserving diffeomorphisms, which act as the space of transformations of an incompressible fluid, and then the full group of planar diffeomorphisms, which are widely used in image registration~\cite{YounesBook}.
+
+The volume-preserving diffeomorphisms $\mathrm{Diff}_{\mathrm{vol}}$ are those diffeomorphisms that preserve the volume form (area form in 2D).
+They can be defined by one function of two variables, the generating function $S$; one possibility is $S(x,y')$ where $(x,y)\mapsto(x',y')$ according to:
+$$ x'=\frac{\partial S}{\partial y'},\quad y = \frac{\partial S}{\partial x}.$$
+
+Consider expanding $S$ in Taylor series.
+The linear terms in the map are determined from the quadratic terms in $S$, which contain 3 group parameters, and act on 2 coordinates, $f_x$ and $f_y$.
+The quadratic terms in the map are determined from the cubic terms in $S$, which contain 4 group parameters, and act on 3 coordinates, $f_{xx}$, $f_{xy}$, and $f_{yy}$.
+At order $n$ we have $n+2$ new group parameters acting on $n+1$ coordinates.
+Thus, barring some exceptional behaviour in the action, we do not expect any invariants at generic points.
+This can be confirmed by considering a small image patch with $f(x,y)=x.$ Let $v=\psi_y\partial/\partial_x - \psi_x\partial/\partial_y$ be the generator of an area-preserving map.
+The image $f$ transforms to $x + \varepsilon \psi_y(x,y)$ which (by choosing $\psi$ appropriately) can be any function close to $x$.
+
+At nongeneric points, there can be invariants.
+For example, the area enclosed in any level set of $f$ is invariant.
+At minima or maxima of $f$, this will lead to invariants expressed in terms of the derivatives of $f$.
+
+When considering colour images, for $k\ge 2$ in $\mathrm{Diff}_{\mathrm{vol}}$ there are $k(k-1)/2$ first-order invariants $ \nabla f^i \times \nabla f^j$.
 We consider the case $k=2$ and the 3-dimensional signature $$ (f^1,f^2, \nabla f^1 \times \nabla f^2).$$ This signature determines (generically and locally) the image up to an area-preserving map.
@@
 Thus, $f^2$ is determined by the signature up to a translation in $y$, i.e., an area-preserving map.
-\item[$\mathrm{Diff}_{\mathrm{con}}$]
-For the infinite-dimensional group $\mathrm{Diff}_{\mathrm{con}}$, first-order signature sets are possible for $k \ge 2$ colours.
-They are formed from the relative invariants $(f^j_1 + i f^j_2)(f^m_1 - i f^m_2)$ of weight 2.
-We illustrate this using the Hopf fibration for $k=2$.
-The weight 2 relative invariant $$J = (2(f^1_1 + i f^1_2)(f^2_1 - i f^2_2), ||\nabla f^1\|^2 - \|\nabla f^2\|^2)$$ obeys $\|J\|^2 = \|\nabla f^1\|^2 + \|\nabla f^2\|^2$, hence projecting to the unit sphere shows that $(f^1,f^2,J/\|J\|)$ provides a 4-dimensional signature set that is singular only when $\nabla f^1 = \nabla f^2 = 0$, a codimension 2 phenomenon for images.
-\item[$\mathrm{Diff}$]
-\todo{Move this one out}
-In the full diffeomorphism group there are no differential invariants using 1 or 2 colours.
+
+In the full diffeomorphism group $\mathrm{Diff}$ there are no differential invariants using 1 or 2 colours.
 For example, with $k=2$, for generic $f^1$, $f^2$ we can choose a diffeomorphism (i.e., choose local coordinates) so that $f^1=x$ and $f^2=y$.
@@
 We can choose coordinates so that $f^1=x$ and $f^2=y$; then the signature locally determines $f^3,\dots,f^k$ as functions of $f^1$ and $f^2$, i.e., the image.
-\end{description}
-
-\section{Conclusions}
+
+\section{Discussion}
 
@@
 
+Quick summary
+
+Table~\ref{tab:derivs} summarises one of the most important parameters of differential invariant signatures for the transformation groups that we have considered in this paper, namely the highest order of derivative of the image that is needed.
+While none of the groups need more than third-order differentiation, and usually less (especially for colour images), even this can be problematic for real images.
+Our aim in this paper has been to explore the mathematical theory required to compute the invariants.
+Producing a computationally robust method of calculating these invariants is not trivial.
+There are three primary considerations: noise/texture, flat areas, and the Florack thing.
+***
+
 \begin{table}[h]
@@
 \hline
-\# derivs. & $k=1$ & $k=2$ & $k=3$ \\
+ & \multicolumn{3}{|c|}{Degree} \\
+$\mathcal{G}$ & $k=1$ & $k=2$ & $k=3$ \\
 \hline
@@
 \end{tabular}
-\caption{Number of derivatives of $f$ needed to construct a differential invariant signature of $f$ as a function of the group $\mathcal{G}$ and the number of colours $k$ of $f$.
+\caption{Degree (order of highest derivative of $f$) needed to construct a differential invariant signature of $f$ as a function of the group $\mathcal{G}$ and the number of colours $k$ of $f$.
 The entry `--' indicates that there is no differential invariant signature in that case.}
+\label{tab:derivs}
 \end{center}
@@
 
-{\bf Aside 3. Role of the invariants} 
 All of the second-order differential invariants play known roles in geometric analysis:

### 2020-11-17 paper/newpaper.tex
getting there

@@
 Abstract
-Bad set, singular
 Literature
-Weight
-
-Example intro
-T(2)
 
@@
 A(2) by transvectant
-
-When introduce each group, mention relevance to images?
-
-Friendly intro to moving frame
-Finish colour
+Check signatures for Mobius etc.
 
 Discussion
+
+Make table fit
+
 }
@@
 An $m$-dimensional signature set is the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e., the set $\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$.
+See Section~\ref{sec:T2} for a basic example.
 A signature set is complete for $f$ if it determines $f$ up to transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
 If the signature is not complete, then there will be a \emph{bad set} of images that cannot be differentiated between.
-***
-
-NEED TO TALK ABOUT WHEN IT IS SINGULAR
+
+The methods we use to construct the invariants, particularly the moving frames, produces invariants that, when considered alone, are singular at certain points (for example, critical points).
+However, in all groups considered the invariants are rational functions of the derivatives of the function.
+Moreover, the denominators of these functions are powers of each other, and so it is possible to clear them, thus removing these singular points by a projection technique that will be introduced in Section~\ref{sec:Sim2}.
 
@@
 \end{equation}
+
 Derivatives of $\bar{f}$ and $f$ can be related by the chain rule, for example the first order derivatives are given by:
@@
 
+\subsubsection{Example}
+Consider as our image, the function $f(x, y) = 0.5 - 0.2x - 0.3y - 0.05x^2 +
+0.03xy + 0.04y^2 + 0.03y^3 +0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3$
+defined on $[0, 1]\times[0, 1]$.
+
 The function is depicted as a greyscale image in Figure~\ref{fig:function}.
@@
 \subsection{Getting Started: Translations}
-
-The most basic transformation group of a image is the translation group $T(2): \phi(\mathbf{x}) = \mathbf{x} + \mathbf{t}$.
+\label{sec:T2}
+
+The most basic transformation group of a image is the translation group $T(2): \phi(\mathbf{x}) = \mathbf{x} + \mathbf{t}$. These could arise from actions such as cropping a photo.
 
@@
 \section{Differential invariants through tensor contraction}
+\label{sec:contraction}
 
@@
 
-The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}}\cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor.
-\todo[inline]{Cite Florack et al, 1993} Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial^p f / \partial_{x_{i_1}} \cdots \partial_{x_{i_p}}$ will give a Euclidean invariant.
+The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}}\cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor~\cite{Florack1993}.
+Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial^p f / \partial_{x_{i_1}} \cdots \partial_{x_{i_p}}$ will give a Euclidean invariant.
 
@@
 
-\todo[inline]{Expand to Sim(2)}
-\todo[inline]{Introduce image that we are going to use in subsequent examples}
-\todo[inline]{Introduce signatures - 3D and 4D perhaps?}
+SE(2): rotation, Sim(2): zooming.
 
@@
 transvectant. Note that the individual pairwise Omega processes commute.
-The concept of a relative invariant will be important in what follows.
+
+The concept of a relative invariant will be important in the rest of this paper.
+It follows the definition given here, except that the function weighting the invariant is more general, see~\cite{Fels1997} for more details.
+In contrast to that paper, we will continue to use the term weight to represent the power to which the function is raised.
 
@@
 \begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
+    \node[draw,circle,minimum size=0.15cm] (1) at (-0.5,0) {1};
+    \node[draw,circle,minimum size=0.15cm] (2) at (0.5,0) {2};
     \draw[-] (1) to [out=30,in=150] (2);
@@
 \begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \node[draw,circle,minimum size=0.15cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.15cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.15cm] (3) at (0.5,0) {3};
     \draw[-] (1) to (2);
@@
 \begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \node[draw,circle,minimum size=0.15cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.15cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.15cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.15cm] (4) at (1,1) {4};
     \draw[-] (1) to (2);
@@
 \begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
-    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
+    \node[draw,circle,minimum size=0.15cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.15cm] (2) at (-0.9511,0.3090) {2};
+    \node[draw,circle,minimum size=0.15cm] (3) at (-0.5878,-.8090) {3};
+    \node[draw,circle,minimum size=0.15cm] (4) at (0.5878,-.8090) {4};
+    \node[draw,circle,minimum size=0.15cm] (5) at (0.9511,0.3090) {5};
     \draw[-] (1) to (2);
@@
 \begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
+    \node[draw,circle,minimum size=0.15cm] (1) at (0,0.866) {1};
+    \node[draw,circle,minimum size=0.15cm] (2) at (-0.5,0) {2};
+    \node[draw,circle,minimum size=0.15cm] (3) at (0.5,0) {3};
     \draw[-] (1) to [out=-150,in=90] (2);
@@
 \begin{tikzpicture}[baseline=0]
-    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
-    \node[draw,circle,minimum size=0.2cm] (2) at (0,0) {2};
-    \node[draw,circle,minimum size=0.2cm] (3) at (1,0) {3};
-    \node[draw,circle,minimum size=0.2cm] (4) at (1,1) {4};
+    \node[draw,circle,minimum size=0.15cm] (1) at (0,1) {1};
+    \node[draw,circle,minimum size=0.15cm] (2) at (0,0) {2};
+    \node[draw,circle,minimum size=0.15cm] (3) at (1,0) {3};
+    \node[draw,circle,minimum size=0.15cm] (4) at (1,1) {4};
     \draw[-] (1) to [out=-120,in=120] (2);
@@
 
-\subsection{Signatures of SA(2) and A(2)}
-Recall that invariants of a supergroup are automatically invariants of any of
-its subgroups.
+\subsection{Signatures of $SA(2)$ and $A(2)$}
+
+The action of the affine group $A(2)$ arises as the motions of planar objects far from a camera.
+Recall that invariants of a supergroup are automatically invariants of any of its subgroups.
 For example, invariants of $A(2)$ are automatically invariants of $SA(2)$, but not necessarily vice versa.
@@
 
-Hence, we can form a signature for $SA(2)$ by choosing any combination of
-partial transvectants. We choose a signature with three components so that
-it can be visualised as a three-dimensional surface; note that this will not
-be complete and may well have a very large bad set. For example, we can choose the function value together with the first two partial transvectants to form the signature:
+Hence, we can form a signature for $SA(2)$ by choosing any combination of partial transvectants.
+We choose a signature with three components so that it can be visualised as a three-dimensional surface; note that this will not be complete and may well have a very large bad set.
+For example, we can choose the function value together with the first two partial transvectants to form the signature:
 \begin{equation*}
@@
 
-\subsubsection{Example}
-Consider as our image, the function $f(x, y) = 0.5 - 0.2x - 0.3y - 0.05x^2 +
-0.03xy + 0.04y^2 + 0.03y^3 +0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3$
-defined on $[0, 1]\times[0, 1]$.
-\todo[inline]{remake figure with modified matrix. Also modify function so it has some features like a critical point}
-We will subject our image to a special affine transformation:
+We will subject our test image to the special affine transformation:
 \begin{equation*}
@@
 
-Fig.~\ref{fig:SA2} shows the function as a greyscale image, the transformed
-function, and the signatures of both the untransformed and transformed
-images.
+Fig.~\ref{fig:SA2} shows the signature of our test image under this transformation.
+
 \begin{figure}
@@
 
-So far the methods that we have seen to can construct differential invariants for particular groups are not directly generalisable.
+So far the methods that we have seen to construct differential invariants for particular groups are not directly generalisable.
 It is natural to ask if there is an algorithmic approach that will yield invariants more directly.
-The answer is a partial yes.
+The answer is a qualified yes.
 There is a general method, based on Cartan's method of moving frames, that is generally applicable, but finding good solutions with it still requires some ingenuity in general.
@@
 
-A moving frame is a mapping into a group $\mathcal{G}$ that provides a frame of reference along a curve.
-Cartan's method of moving frames generalises the concept to a homogeneous space of a Lie group $\mathcal{G}$.
-When defined on the principal bundle it defines a $\mathcal{G}$-equivariant mapping, which enables one to identify invariants under the action of groups of transformations.
-The method of moving frames, which originated with Cartan~\cite{Cartan35}  has a long history, as summarised in \cite{Olver2005}.
-Olver and co-authors, in particular, have popularised the approach and made it applicable to image analysis, see~\cite{Olver2005} for an overview, and the original application paper ~\cite{Calabi1998}.
+A moving frame is a mapping into a group $\mathcal{G}$ that provides a frame of reference along a manifold.
+It was extended by Cartan~\cite{Cartan35} to the `method of moving frames'.
+If the group $\mathcal{G}$ is a Lie group then it has a homogeneous space and a frame of reference can be applied on the manifold structure of the group.
+Considering the actions of such a transformation group it can enable the identification of invariants to that group since it defines a $\mathcal{G}$-equivariant mapping.
+A (right-) moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$, where $z \in J^d$.
+It is necessary~\cite{Olver2013} for the group act freely.
+This means that the group action needs to be extended to the entire jet space of derivatives up to order $d$ by implicit differentiation of the group action, a process known as prolongation.
+
+Olver and co-authors, in particular, have popularised the approach and made it applicable to object recognition, see~\cite{Olver2005} for an overview, and note particularly the original application paper~\cite{Calabi1998}.
 The method is described in detail in~\cite{OlverCIT}.
 
-A (right-) moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$, where $z \in J^d$.
 The procedure to construct differential invariants to the action of Lie group $\mathcal{G}$ acting on manifold $\mathcal{M}$ using the method of moving frames is as follows:
@@
 \begin{enumerate}
-\item Prolong the group action to the jet space of $d$-th order derivatives (using implicit differentiation): $F: J^d \to \mathbb{R}$. 
+\item Prolong the group action to the jet space of $d$-th order derivatives: $F: J^d \to \mathbb{R}$. 
 \item Apply Cartan normalisation:
@@
     \item $\mathcal{K}$ is specified by $\dim \mathcal{G}$ independent equations $Z_i (z) = c_i$, for $z \in J^d$,  and $Z_i$ scalar-valued functions and $c_i$ constants.
-    \item The right moving frame $g = \rho(z)$ is found by solving the normalisation questions $Z_i (g \cdot z) = c_i$ for the group parameters $g$ (in terms of $z$).
+    \item The right-moving frame $g = \rho(z)$ is found by solving the normalisation questions $Z_i (g \cdot z) = c_i$ for the group parameters $g$ (in terms of $z$).
 In other words, the moving frame is the transformation back to the cross-section.
@@
 
+Cartan normalisation can be considered as identifying a canonical subspace (with some coordinates fixed) in the jet space to which any point in the jet space can be mapped by a group action.
+
 Olver uses the group $SE(2)$ on curves as an example~\cite{Olver}, recovering the Euclidean curvature as a second-order invariant.
-We continue this example to compute invariants to $SE(2)$ on the plane, before moving on to other planar Lie group examples: $E(2)$, the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).
-Finally, we apply it to an infinite-dimensional pseudo-Lie group, the conformal diffeomorphisms.
+We continue this example to compute invariants to $SE(2)$ for images, before moving on to other planar Lie group examples: $E(2)$, the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).
+Finally, we apply the method to an infinite-dimensional pseudo-Lie group, the conformal diffeomorphisms.
 
@@
 
-\todo[inline]{c.f. transvectant formulae}
-
 \subsection{The Euclidean Group E(2)}
@@
 These invariants are a functionally independent, complete, set of polynomial differential invariants up to second derivatives.
-Note that the invariants found previously by tensor contraction (\ref{eq:se2}) can be expressed in terms of these:
+Note that the invariants found previously by tensor contraction Eq.
+(\ref{eq:se2}) in Section~\ref{sec:contraction} can be expressed in terms of these:
 \begin{align*}
@@
   f_if_i = f_x^2 + f_y^2 &= I_1 \\
-  f_{ii} = f_{xx}^2 + f_{yy}^2 &= \frac{I_2 + I_4}{I_1} \\
-  f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 &= I_2\\
-  f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy} &= \frac{I_2^2 + I_4^2 + 2I_3^2}{I_1^2}.
+  f_{ii} = f_{xx} + f_{yy} &= \frac{I_2 + I_4}{I_1} \\
+  f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 &= \frac{I_2^2 + I_4^2 + 2I_3^2}{I_1^2} \\
+  f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy} &= I_2.
 \end{align*}
@@
 
-The M\"obius group $\mathrm{PSL}(2,\mathbb{C})$ acts on the Riemann sphere
-$\overline{\mathbb{C}} = \mathbb{C}\cup\infty$ by:
+The M\"obius group $\mathrm{PSL}(2,\mathbb{C})$ acts on the Riemann sphere $\overline{\mathbb{C}} = \mathbb{C}\cup\infty$ by:
 \begin{equation} 
@@
 In order to find further invariants the prolongation to 3rd derivatives is required, which will result in at least another four invariants.
+This simple counting arguments works because the group acts freely on the prolongation.
 %There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 5 invariants.
-\todo[inline]{General thm for this earlier...}
 
@@
 Clearing denominators so as to work with polynomials, we choose $M_1 = (f_{xx} + f_{yy})^4$ and two of the four third-order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where:
-$$M_2=
+\begin{align} M_2&=
 f_y ^5 f_{yyy} + \frac{9}{2} f_y ^2 f_{yy}^2 f_x ^2 + 
@@
  9 f_y ^3 f_{yy} f_x  f_{xy} + 
- 3 f_y  f_{yy} f_x ^3 f_{xy} + \frac{3}{2} f_y ^4 f_{xy}^2 - 
- 9 f_y ^2 f_x ^2 f_{xy}^2 + \frac{3}{2} f_z ^4 f_{xy}^2 + 
+ 3 f_y  f_{yy} f_x ^3 f_{xy} + \frac{3}{2} f_y ^4 f_{xy}^2 \\ \nonumber
+ &- 9 f_y ^2 f_x ^2 f_{xy}^2 
++ \frac{3}{2} f_z ^4 f_{xy}^2 + 
  3 f_y ^4 f_x  f_{xyy} + 3 f_y ^2 f_x ^3 f_{xyy} + 
  3 f_y ^4 f_{yy} f_{xx} + 3 f_{yy} f_x ^4 f_{xx} + 
- 3 f_y ^3 f_x  f_{xy} f_{xx} - 
- 9 f_y  f_x ^3 f_{xy} f_{xx} + \frac{3}{2} f_y ^4 f_{xx}^2 + 
+ 3 f_y ^3 f_x  f_{xy} f_{xx} \\ \nonumber
+&- 9 f_y  f_x ^3 f_{xy} f_{xx} 
++ \frac{3}{2} f_y ^4 f_{xx}^2 + 
  \frac{9}{2} f_y ^2 f_x ^2 f_{xx}^2 + 3 f_y ^3 f_x ^2 f_{xxy} + 
@@
  f_x ^5 f_{xxx}, 
- $$
-
- $$M_3=-3 f_y  f_{yy}^2 f_x ^3 + 
+\end{align}
+
+\begin{align}
+M_3&=-3 f_y  f_{yy}^2 f_x ^3 + 
  f_y ^2 f_{yyy} f_x ^3 + f_{yyy} f_x ^5 + 
@@
  3 f_{yy} f_x ^4 f_{xy} - 6 f_y ^3 f_x  f_{xy}^2 + 
- 6 f_y  f_x ^3 f_{xy}^2 - 3 f_y ^3 f_x ^2 f_{xyy} - 
+ 6 f_y  f_x ^3 f_{xy}^2 \\ \nonumber
+&- 3 f_y ^3 f_x ^2 f_{xyy} - 
  3 f_y  f_x ^4 f_{xyy} - 3 f_y ^3 f_{yy} f_x  f_{xx} + 
  3 f_y  f_{yy} f_x ^3 f_{xx} + 3 f_y ^4 f_{xy} f_{xx} - 
- 9 f_y ^2 f_x ^2 f_{xy} f_{xx} + 
- 3 f_y ^3 f_x  f_{xx}^2 + 3 f_y ^4 f_x  f_{xxy} + 
+ 9 f_y ^2 f_x ^2 f_{xy} f_{xx} \\ \nonumber
+ &+ 3 f_y ^3 f_x  f_{xx}^2 + 3 f_y ^4 f_x  f_{xxy} + 
  3 f_y ^2 f_x ^3 f_{xxy} - f_y ^5 f_{xxx} - 
  f_y ^3 f_x ^2 f_{xxx}.
-$$
+\end{align}
 
@@
 
+The action of the projective group arises naturally through the movements of the camera watching planar objects.
 We consider the eight-dimensional group $\mathrm{PSL}(3,\R)$ acting on $\R^2$ by projective transformations, i.e., 
@@
 
+\todo[inline]{Problem here? fyyy is in MF and an invariant...}
 The frame $\bar f_{ \bar y \bar y \bar y} = 0$ determines the group parameter $ h = \frac{d(f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2 f_{xxy} - f_y^3 f_{xxx})}{6 f_x D},$ while $\bar f_{ \bar x \bar y \bar y}=0$ provides $ c = \frac{h f_x^2}{d D} - \frac{f_x f_{xy} - f_y f_{xx}}{D}$, and $\bar f_{ \bar x \bar x}=0$ gives $ g = \frac{1}{2 f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$ In fact, the denominator of the expression for $h$ was another invariant of $A(2)$; we label it $E$ for convenience.
@@
 Having determined the frame, any function of the remaining derivatives $\bar f_{ \bar x \bar x \bar x}$, $\bar f_{ \bar x \bar x \bar y}$, and $\bar f_{ \bar y \bar y \bar y}$, as given in Equation~(\ref{eq:prolong}), provides invariants.
-We choose: $$ (f_{xxx}, f_{xxy}^2, f_{xyy})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right)$$, where (with $P_n$ denoting a polynomial of degree $n$):
+We choose: $$ (f_{xxx}, f_{xxy}^2, f_{xyy})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right)\:,$$ where (with $P_n$ denoting a polynomial of degree $n$):
 $$ J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5.$$
@@
 
-** Given the importance of the conformal camera model ...
-
-The group of conformal diffeomorphisms is the subgroup of diffeomorphisms that are angle-preserving, i.e.,
+The conformal camera model is well known. The group of conformal diffeomorphisms is the subgroup of diffeomorphisms that are angle-preserving, i.e.,:
 
@@
 sole second-order invariant, which we also saw for the M\"obius group: 
-\begin{equation*}
+\begin{equation}
     \bar{f}_{\bar{y}\bar{y}} = \frac{f_{xx} + f_{yy}}{f_x^2 + f_y^2}.
-\end{equation*}
+\label{eqn:C1}
+\end{equation}
 Continuing in this way, at derivative order $n$ two real group parameters
@@
 the remaining derivatives are invariant:
-\begin{align*}
-    \bar{f}_{\bar{x}\bar{y}\bar{y}} &= \frac{f_y^3f_{yyy} + f_x^2f_yf_{yyy}
+\begin{align}
+    \bar{f}_{\bar{x}\bar{y}\bar{y}} &= \frac{1}{(f_x^2 + f_y^2)^3} \left[
+f_y^3f_{yyy} + f_x^2f_yf_{yyy}
             -2f_y^2f_{yy}^2 - 2f_{xx}f_y^2f_{yy} -
-            4f_xf_{xy}f_yf_{yy} - 2f_x^2 f_{xx}f_{yy} + f_{xxy}f_y^3 +
+            4f_xf_{xy}f_yf_{yy} - 2f_x^2 f_{xx}f_{yy} \right. \\ \nonumber
+&+ \left. f_{xxy}f_y^3 +
             f_x^2 f_{xxy}f_y - 4 f_x f_{xy} f_{xx} f_y + f_x^3 f_{xxx} -
-        2f_x^2 f_{xx}^2 + f_x^3 f_{xyy}}{(f_x^2 + f_y^2)^3} \\
-        \bar{f}_{\bar{y}\bar{y}\bar{y}} &= \frac{f_xf_y^2f_{yyy} +
+        2f_x^2 f_{xx}^2 + f_x^3 f_{xyy} \right] 
+\\ \label{eqn:C2}
+        \bar{f}_{\bar{y}\bar{y}\bar{y}} &= \frac{1}{(f_x^2 + f_y^2)^3} \left[
+f_xf_y^2f_{yyy} +
         f_x^3f_{yyy} - 2f_x f_y f_{yy}^2 + 2f_{xy}f_y^2f_{yy} -
-    2f_x^2f_{xy}f_{yy} - f_{xxx}f_y^3 - f_{xyy}f_y^3 + f_xf_{xxy}f_y^2 +
+    2f_x^2f_{xy}f_{yy} - f_{xxx}f_y^3 \right. \\ \nonumber
+&- \left. f_{xyy}f_y^3 + f_xf_{xxy}f_y^2 +
 2f_{xy}f_{xx}f_y^2 - f_x^2 f_{xxx} f_y + 2f_xf_{xx}^2 f_y - f_x^2 f_{xyy}
-f_y + f_x^3 f_{xxy} - 2f_x^2 f_{xy} f_{xx} }{(f_x^2 + f_y^2)^3 }
-\end{align*}
+f_y + f_x^3 f_{xxy} - 2f_x^2 f_{xy} f_{xx} \right] \label{eqn:C3}
+\end{align}
+
+Note that the denominators of all three of these equations are the same up to index.
+We therefore clear denominators as usual and form the three-dimensional signature ((\ref{eqn:C1})^2,(\ref{eqn:C2}),(\ref{eqn:C3})).
+We then project them into the unit sphere and multiply by $f$ to constrain them.
+This signature is continuous at all $(x,y)$ such that the three quantities are not simultaneously equal to zero, which occurs when $f_x = f_y = f_{xx} = f_{yy} = 0$, which is a codimension-1 phenomenon for images.
 
@@
 
-\todo[inline]{Fix up this bit to be correct and complete for what we do}
-Specifically, let $J_1 = f_i f_i$ and  $J_2 = f_{ii}$, so that  $g = J_2/J_1$ is invariant.
+%Specifically, let $J_1 = f_i f_i$ and  $J_2 = f_{ii}$, so that  $g = J_2/J_1$ is invariant.
 We want to work with polynomials, so we clear denominators and let $J_3+iJ_4 = J_1^2 (g_x + i g_y)  (f_x - i f_y)$.
@@
 
-\subsection{Infinite-dimensional Groups of Diffeomorphisms}
+\subsection{Infinite-dimensional groups of diffeomorphisms}
 
@@
 
-\todo[inline]{Number of derivatives}
-\todo[inline]{Noise; integral invariants, Fourier}
-\todo[inline]{Is there a general theory - syzygy??}
-\todo[inline]{Difficulties of a practical implementation}
+%\todo[inline]{Number of derivatives}
+%\todo[inline]{Noise; integral invariants, Fourier}
+%\todo[inline]{Is there a general theory - syzygy??}
+%\todo[inline]{Difficulties of a practical implementation}
 
@@
 
-All of the second-order differential invariants play known roles in geometric analysis:
+All of the second-order differential invariants of $E(2)$ play known roles in geometric analysis:
 \begin{enumerate}

### 2020-11-17 code/make_figures.m
Added T2 code

@@ -33,14 +33,13 @@ signatures.PSL3R.tform = PSL3RTransform(1, 0.1, 0.05, 0.8, 0.2, -0.1);
 signatures.PSL3R.sigfun = @PSL3R_signature;
 signatures.Diffcon.tform = DiffconTransform(2);
 signatures.Diffcon.sigfun = @Diffcon_signature;
-
+signatures.T2.tform = T2Transform(0.1, -0.2);
+signatures.T2.sigfun = @T2_signature;
 
 %% Try out a particular group, and then save 3D axes info using the block below
-signatures.Diffcon.tform = DiffconTransform(2);
-signatures.Diffcon.sigfun = @Diffcon_signature;
 close all
-group = 'Diffcon';
-write_images = false;
+group = 'T2';
+write_images = true;
 close all
 sig = generate_figures(f, signatures.(group), write_images);
 
@@ -53,8 +52,8 @@ save(strcat('images/', sig.group, '_cam.mat'), 'caminfo');
 
 %% Generate all images
 write_images = true;
-%groups = {'SE2', 'E2', 'Sim2', 'SA2', 'A2', 'Mobius', 'PSL3R', 'Conformal'};
-groups = {'Diffcon'};
+%groups = {'SE2', 'E2', 'Sim2', 'SA2', 'A2', 'Mobius', 'PSL3R', 'Diffcon', 'T2'};
+groups = {'T2'};
 for k = 1:numel(groups)
     gp = groups{k};
     sig = generate_figures(f, signatures.(gp), write_images);

### 2020-11-17 code/signatures/T2_signature.m

@@ -1,0 +1,13 @@
+function out = SE2_signature(f, varargin)
+derivative_order = 2;
+group = 'SE2';
+out = signature_switch(f, @evaluate, derivative_order, group, varargin{:});
+    function sig = evaluate(derivs)
+        [f, fx, fy, fxx, fxy, fyy] = derivs{:};
+        I0 = f;
+        I1 = fx.*fx + fy.*fy;
+        v = {fxx.*fx + fxy.*fy, fxy.*fx + fyy.*fy};
+        I2 = fx.*v{2} - fy.*v{1};
+        sig = {I0, I1, I2};
+    end
+end

### 2020-11-17 code/signatures/SE2_signature.m
fix booboo

@@ -11,3 +11,4 @@ out = signature_switch(f, @evaluate, derivative_order, group, varargin{:});
         sig = {I0, I1, I2};
     end
 end
+

### 2020-11-17 code/signatures/T2_signature.m

@@ -1,13 +1,12 @@
-function out = SE2_signature(f, varargin)
-derivative_order = 2;
-group = 'SE2';
+function out = T2_signature(f, varargin)
+derivative_order = 1;
+group = 'T2';
 out = signature_switch(f, @evaluate, derivative_order, group, varargin{:});
     function sig = evaluate(derivs)
-        [f, fx, fy, fxx, fxy, fyy] = derivs{:};
+        [f, fx, fy] = derivs{:};
         I0 = f;
-        I1 = fx.*fx + fy.*fy;
-        v = {fxx.*fx + fxy.*fy, fxy.*fx + fyy.*fy};
-        I2 = fx.*v{2} - fy.*v{1};
+        I1 = fx;
+        I2 = fy;
         sig = {I0, I1, I2};
     end
 end

### 2020-11-17 code/make_figures.m
T2 pictures, plus revert muckups

@@ -38,7 +38,7 @@ signatures.T2.sigfun = @T2_signature;
 
 %% Try out a particular group, and then save 3D axes info using the block below
 close all
-group = 'T2';
+group = 'SE2';
 write_images = true;
 close all
 sig = generate_figures(f, signatures.(group), write_images);

### 2020-11-17 paper/newpaper.tex
T2 section written

@@
 \begin{equation}\label{eq:function}
-**write me**
-\end{equation}
-
-\subsubsection{Example}
-Consider as our image, the function $f(x, y) = 0.5 - 0.2x - 0.3y - 0.05x^2 +
-0.03xy + 0.04y^2 + 0.03y^3 +0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3$
-defined on $[0, 1]\times[0, 1]$.
+f(x, y) = \exp(-2x^2 - 4\sin^2(y + 0.5x^2))
+\end{equation}
 
 The function is depicted as a greyscale image in Figure~\ref{fig:function}.
-On the left the image itself is shown, while on the right a version with a regular grid superimposed is given.
-This is useful for visualising both the transformation and how the image is mapped into the three-dimensional signature surface.
+On the left the image itself is shown, while on the right a version with a
+regular grid superimposed is given. This is useful for visualising both the
+transformation and how the image is mapped into the three-dimensional
+signature surface.
 
@@
   \includegraphics[width=.45\textwidth]{Figs/function}
-  \includegraphics[width=.45\textwidth]{Figs/function_scanlines}
-  \caption{The test function used in this document, from
-  Eq.~\eqref{eq:function}.}\label{fig:function}
+  \includegraphics[width=.45\textwidth]{Figs/function_scanlines}\\
+  \caption{The test function used in this document, from Eq.~\eqref{eq:function}.}\label{fig:function}
 \end{figure}
@@
 
-The most basic transformation group of a image is the translation group $T(2): \phi(\mathbf{x}) = \mathbf{x} + \mathbf{t}$. These could arise from actions such as cropping a photo.
-
-We could explicitly write the calculation in Eq.~\ref{eq:prolongation} for this case, but instead provide an intuitive explanation.
-Consider a point in the original image, and the corresponding point in the transformed one.
-Clearly, the intensity value of the points match, and so do their first spatial derivatives.
-These three quantities can be used as coordinates in a new space, where the two image points will correspond.
-Computing these coordinates for all image points will define a surface in the new three-dimensional space, and the two images will produce the same surface, which we call the signature.
-
-Figure~\ref{fig:T2} shows (a) the original image, (b) the translated image by $x,y$, (c) the signature of one of them, (d) the superimposed pair of signatures. Now explain the missing bits.
+The most basic transformation group of a image is the translation group
+$T(2) \colon \mathbb{R}^2 \to \mathbb{R}^2$ with elements of the form
+$\varphi(\mathbf{x}) = \mathbf{x} + \mathbf{t}$ for fixed $\mathbf{t}$.
+These could arise from actions such as cropping a photo.
+
+We could explicitly write the calculation in Eq.~\ref{eq:prolongation} for
+this case, but instead provide an intuitive explanation. Consider a point
+in the original image, and the corresponding point in the transformed one.
+Clearly, the intensity value of the points match, and so do their first
+spatial derivatives. These three quantities can be used as coordinates in a
+new space, where the two image points will correspond. Computing these
+coordinates for all image points will define a surface in the new
+three-dimensional space, and the two images will produce the same surface,
+which we call the signature.
+
+Figure~\ref{fig:T2} shows (a) the original image, (b) the translated image
+under the transformation $(x,y) \mapsto (x + 0.1, y - 0.2)$, (c) the
+signature of one of them, (d) the superimposed pair of signatures. The
+yellow lines in (c) correspond to where the yellow grid from (a) has been
+mapped to on the signature surface. In (d), notice that as some of the
+image has moved out of frame, there are parts of the signature near its
+boundary that do not overlap.
+
+\begin{figure}
+  \centering
+  \begin{tabular}{cc}
+  \includegraphics[width=.45\textwidth]{Figs/function_scanlines} &
+  \includegraphics[width=.45\textwidth]{Figs/f_transformed_T2} \\
+  (a) & (b) \\
+  \includegraphics[width=.45\textwidth]{Figs/T2_signature} &
+  \includegraphics[width=.45\textwidth]{Figs/T2_match} \\
+  (c) & (d)
+  \end{tabular}
+  \caption{(a), (b) The image before and after the T(2) transformation $(x,
+  y) \mapsto (x + 0.1, y - 0.2)$. (c) the signature of the
+  image (before translation). (d) the signature after the
+  translation superimposed.}\label{fig:T2}
+\end{figure}
 

### 2020-11-17 paper/newpaper.tex
I got in first to upset Richard

--- 2020-11-17 paper/newpaper.tex
@@
 \title{Differential invariant signatures for planar Lie group transformations of images}
-\author{Not-working authors }
+\author{Richard Brown, Stephen Marsland, and Robert McLachlan}
 
@@
 Discussion
-
-Make table fit
-
 }
 
-%\todo[inline]{
-%Richard: 
-%Start on invariant tensor theorem
-%Generate new pictures, add function details
-%SE(2) jobs inline
-%Mobius, Conformal -- finish code, tidy writing
-%First bash at experimental section
-
-%Stephen:
-%Rearrange examples text to IVT section, write about signatures here
-%Fix up tables, check bib
-%Examples for SA(2), A(2) -- need to think about sig here
-%Moving frame intro
-%Projective -- tidy writing, especially the names of the invariants
-%Colour
-%First bash at conclusion
-
-%Later:
-%Introduction
-%Count of derivatives and what to say
-%}
-
-%\todo[inline]{Examples to be numbered like theorems}
-%\todo[inline]{This is a start. To be completed later.}
-
-%Biologists differentiate between the {\em form} of an object, and the {\em shape}, being the part of form that is unaffected by size and orientation. 
 The appearance of a fixed object in a set of images can vary markedly depending upon such variables as pose and position relative to the camera, even though the object itself does not change.
@@
 Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.
-%Regardless of which group appears to act, such variations highlight the importance of `shape', as opposed to `form', in object recognition.
 
@@
 Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{Kendall1989} will place all of the shapes into the reference frame of one template example.
-However, analysis on these quotient spaces is rarely simple (see e.g.,~\cite{Marsland19b} for a basic primer), and if one is interested in the object, and not the transformation, then it necessitates a lot of computational work for relatively little benefit.
+However, analysis on these quotient spaces is rarely simple (see e.g.,~\cite{RiemannianStats} for a basic primer), and if one is interested in the object, and not the transformation, then it necessitates a lot of computational work for relatively little benefit.
 
@@
 
-The theory of invariants has a rich mathematical history, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview. Of most relevance to us here 
-\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872}
-
-\cite{Olver2005,Cartan35}
+Classical invariants
+
+The theory of invariants has a rich mathematical history, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview. Polynomials, then geometry.
+
+Lie
+
+\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872,Lie1884}
+
+A variety of function spaces have allowed for the creation of different sets of invariants for particular groups.
+For the Euclidean group, the Fourier transform provides a useful tool, and this can be extended to the affine group using the Fourier-Mellin transform and the bispectrum.
+Alternatively, integral invariants and moments can be computed.
+For the similarity group applied to images the seminal reference is \cite{Hu1962}, but see also~\cite{}.
+\cite{Hickman2011,Abu-Mostafa1984,Kakarala2010,Flusser2009,Papakostas2013}
+\cite{Manay2006,Negrinho2013,Ghorbel1994,Turski2006}
+\cite{Reddy1996,Gauthier2008,Kakarala2011,Smach2007}
+
+The other group that has been of particular interest for image analysis is the projective group, because of its ubiquity in images from cameras. Summarise these...
+\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}
+
+Diff invs and sigs
+
+An algorithm to compute differential and joint invariants and determine complete signature sets is described in \cite{Olver2005}.
+The entire set of invariants is computed using the method of moving frames (see Section~\ref{sec:MF}) and then the signature set of a maximal set of functionally independent invariants is identified.
+A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
+
+Joint sigs
+\cite{Fels1997,Olver2013,Arora2009}
+An intermediary role is played by the “semi-differential invariants” (or, as we would
+prefer they be known, “joint differential invariants”) introduced into vision by Van Gool et. al., [34],
+
+Diff Invs
+\cite{Florack1993,Olver2007,Bouton1898}
 
@@
 
-Different sorts of invariant, and their properties.
-
-Signature
-
-Relative invars
-Joint sigs
-\cite{Fels1997,Olver2013,Arora2009}
-
-Diff Invs
-\cite{Florack1993,Olver2007,Bouton1898}
-
-Projective invars
-\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}
-
-Moments
-\cite{Hickman2011,Abu-Mostafa1984,Kakarala2010,Flusser2009,Papakostas2013}
-
-FFT
-\cite{Reddy1996,Gauthier2008,Kakarala2011,Smach2007}
-
-Integral invar
-\cite{Manay2006,Negrinho2013,Ghorbel1994,Turski2006}
+** FIX FAUGERAS
 
@@
 SURF and that kind of crap
-
-An algorithm to compute invariants and determine complete signature sets is
-described in \cite{Olver2005}. First, the entire set of invariants is
-computed using the method of moving frames. Second, determine the
-differential invariant order $s$ of $f$. Then the signature set of a maximal
-set of functionally independent invariants of order $s+1$ is complete. A
-third step is possible, in which the dimension of the signature set is
-reduced by eliminating those invariants whose values can be computed from the
-values of derivatives of some subset of the invariants.
-
-While we follow this approach in general, in specific cases we have computed invariants using other techniques
-including the invariant tensor theorem and classical invariant theory.
-We shall see that this yields insights into the relationships between the different groups.
-We develop our approach through examples of progressively more complicated groups.
-===
 
@@
 \centering
-\begin{tabular}{cccp{11cm}}
+\begin{tabular}{cccp{9cm}}
 Degree & Weight & Diagram & Partial transvectant\\
@@
 \end{tikzpicture}
-& $\left(f_{x}\right)^{2} f_{xx} \left(f_{yy}\right)^{2} - \left(f_{x}\right)^{2} f_{yy} \left(f_{xy}\right)^{2} - 2 f_{x} f_{xx} f_{y} f_{yy} f_{xy} + 2 f_{x} f_{y} \left(f_{xy}\right)^{3} + \left(f_{xx}\right)^{2} \left(f_{y}\right)^{2} f_{yy} - f_{xx} \left(f_{y}\right)^{2} \left(f_{xy}\right)^{2}$ \\
+& $\left(f_{x}\right)^{2} f_{xx} \left(f_{yy}\right)^{2} - \left(f_{x}\right)^{2} f_{yy} \left(f_{xy}\right)^{2} - 2 f_{x} f_{xx} f_{y} f_{yy} f_{xy} 
+ + 2 f_{x} f_{y} \left(f_{xy}\right)^{3} + \left(f_{xx}\right)^{2} \left(f_{y}\right)^{2} f_{yy} - f_{xx} \left(f_{y}\right)^{2} \left(f_{xy}\right)^{2}$ \\
 
@@
 Note that the denominators of all three of these equations are the same up to index.
-We therefore clear denominators as usual and form the three-dimensional signature ((\ref{eqn:C1})^2,(\ref{eqn:C2}),(\ref{eqn:C3})).
+We therefore clear denominators as usual and form the three-dimensional signature ((\ref{eqn:C1})$^3$,(\ref{eqn:C2}),(\ref{eqn:C3})).
 We then project them into the unit sphere and multiply by $f$ to constrain them.
@@
 
-Quick summary
-
-Table~\ref{tab:derivs} summarises one of the most important parameters of differential invariant signatures for the transformation groups that we have considered in this paper, namely the highest order of derivative of the image that is needed.
+The recognition of objects within images as their appearance changes based on camera motion remains an unsolved problem.
+In this paper we have used three different methods of computing differential invariant signatures to identify appropriate signatures for images transformed under the planar Lie groups that are of interest for this question.
+The resulting three-dimensional signatures are not always complete, but they are relatively fast to compute.
+
+Table~\ref{tab:derivs} summarises one of the most important parameters of differential invariant signatures for the transformation groups that we have considered, namely the highest order of derivative of the image that is needed.
 While none of the groups need more than third-order differentiation, and usually less (especially for colour images), even this can be problematic for real images.
 Our aim in this paper has been to explore the mathematical theory required to compute the invariants.
-Producing a computationally robust method of calculating these invariants is not trivial.
-There are three primary considerations: noise/texture, flat areas, and the Florack thing.
-***
 
@@
 
-All of the second-order differential invariants of $E(2)$ play known roles in geometric analysis:
-\begin{enumerate}
+Producing a computationally robust method of numerically approximating derivatives and hence invariants is not trivial, particularly for the higher-orders, where noise and rounding errors can dominate.
+There are three primary considerations: noise and texture; flat areas, where the derivatives are all identically zero; and the fact that conventional numerical differentiation is not well-posed~\cite{Florack1993}.
+Some considerations of these points and some potential approaches to solving them for practical implementations are considered in~\cite{Calabi1998} and~\cite{Florack1993}.
+However, the question of how to create a full and effective implementation remains an open problem.
+
+Finally, we note that there is underlying mathematical structure that we have not fully exposed.
+For example, all of the second-order differential invariants of $E(2)$ play known roles in geometric analysis:
+
+\begin{itemize}
 \item $f_x^2 + f_y^2=\|\nabla f\|^2$ is the Lagrangian density for the Laplacian;
@@
 \item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is the `infinity-Laplacian'; 
-\item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is also a Lagrangian density for $-2(f_{xx} f_{yy} - f_{xy}^2)$, which arises in the Monge--Amp\`ere equations and
-can be written in terms of the final second-order invariant as $-2 (f_{xx} f_{yy} - f_{xy}^2) = 2 f_{xy}^2 - f_{xx}^2 - f_{yy}^2$
-\end{enumerate}
-In addition, we shall see in later sections that functions of these invariants are invariants or
-relative invariants for many groups that contain $E(2)$, namely $Sim(2)$, $SA(2)$, $A(2)$, $PSL(3,\mathbb{R})$, $PSL(2,\mathbb{C})$, and the conformal group.
+\item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is also a Lagrangian density for $-2(f_{xx} f_{yy} - f_{xy}^2)$, which arises in the Monge--Amp\`ere equations and can be written in terms of the final second-order invariant as $-2 (f_{xx} f_{yy} - f_{xy}^2) = 2 f_{xy}^2 - f_{xx}^2 - f_{yy}^2$
+\end{itemize}
+
+Functions of these invariants are invariants or relative invariants for many groups that contain $E(2)$, such as those that we have considered in this paper. Syzygies.
 

### 2020-11-17 paper/newpaper.tex
progress

@@
 
-\subsection{Relevant Literature}
-
-Classical invariants
-
-The theory of invariants has a rich mathematical history, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview. Polynomials, then geometry.
-
-Lie
-
-\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872,Lie1884}
-
-A variety of function spaces have allowed for the creation of different sets of invariants for particular groups.
-For the Euclidean group, the Fourier transform provides a useful tool, and this can be extended to the affine group using the Fourier-Mellin transform and the bispectrum.
-Alternatively, integral invariants and moments can be computed.
-For the similarity group applied to images the seminal reference is \cite{Hu1962}, but see also~\cite{}.
-\cite{Hickman2011,Abu-Mostafa1984,Kakarala2010,Flusser2009,Papakostas2013}
-\cite{Manay2006,Negrinho2013,Ghorbel1994,Turski2006}
-\cite{Reddy1996,Gauthier2008,Kakarala2011,Smach2007}
-
-The other group that has been of particular interest for image analysis is the projective group, because of its ubiquity in images from cameras. Summarise these...
-\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}
-
-Diff invs and sigs
-
-An algorithm to compute differential and joint invariants and determine complete signature sets is described in \cite{Olver2005}.
-The entire set of invariants is computed using the method of moving frames (see Section~\ref{sec:MF}) and then the signature set of a maximal set of functionally independent invariants is identified.
-A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
-
-Joint sigs
-\cite{Fels1997,Olver2013,Arora2009}
-An intermediary role is played by the “semi-differential invariants” (or, as we would
-prefer they be known, “joint differential invariants”) introduced into vision by Van Gool et. al., [34],
-
-Diff Invs
-\cite{Florack1993,Olver2007,Bouton1898}
-
-This is essential if the
-signature is to be used to detect similarity of images, but it fails for the rational
-invariants found in the literature.
-
-not intensity transforms
-
-** FIX FAUGERAS
-
-There has been a long-standing interest in constructing invariants for image recognition. 
-\cite{VanGool1995,Wood1996,Zhang2019,Faugeras1994,Gros1992,Taubin1992,Lenz1990,Florack1993}
-
-\cite{SURF}
-
-SURF and that kind of crap
-
-%Groups we've done:
-%translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
 \subsection{Example signatures}
@@
 
+\subsection{Relevant Literature}
+
+Classical invariants
+
+The theory of invariants has a rich mathematical history, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview. Polynomials, then geometry.
+
+Lie
+
+\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872,Lie1884}
+
+A variety of function spaces have allowed for the creation of different sets of invariants for particular groups.
+For the Euclidean group, the Fourier transform provides a useful tool, and this can be extended to the affine group using the Fourier-Mellin transform and the bispectrum.
+Alternatively, integral invariants and moments can be computed.
+For the similarity group applied to images the seminal reference is \cite{Hu1962}, but see also~\cite{}.
+\cite{Hickman2011,Abu-Mostafa1984,Kakarala2010,Flusser2009,Papakostas2013}
+\cite{Manay2006,Negrinho2013,Ghorbel1994,Turski2006}
+\cite{Reddy1996,Gauthier2008,Kakarala2011,Smach2007}
+
+The other group that has been of particular interest for image analysis is the projective group, because of its ubiquity in images from cameras. Summarise these...
+\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}
+
+Diff invs and sigs
+
+An algorithm to compute differential and joint invariants and determine complete signature sets is described in \cite{Olver2005}.
+The entire set of invariants is computed using the method of moving frames (see Section~\ref{sec:MF}) and then the signature set of a maximal set of functionally independent invariants is identified.
+A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
+
+Joint sigs
+\cite{Fels1997,Olver2013,Arora2009}
+An intermediary role is played by the “semi-differential invariants” (or, as we would
+prefer they be known, “joint differential invariants”) introduced into vision by Van Gool et. al., [34],
+
+Diff Invs
+\cite{Florack1993,Olver2007,Bouton1898}
+
+This is essential if the
+signature is to be used to detect similarity of images, but it fails for the rational
+invariants found in the literature.
+
+not intensity transforms
+
+** FIX FAUGERAS
+
+There has been a long-standing interest in constructing invariants for image recognition. 
+\cite{VanGool1995,Wood1996,Zhang2019,Faugeras1994,Gros1992,Taubin1992,Lenz1990,Florack1993}
+
+\cite{SURF}
+
+SURF and that kind of crap
+
+%Groups we've done:
+%translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
 \section{Differential invariants through tensor contraction}
@@
 \noindent where $\alpha_1 = b g + 2 a h, \alpha_2 = 2 b g + a h$, $\beta_1 = d g + 2 c h, \beta_2 = 2 d g + c h$, $\gamma_1 = b c + 2 a d, \gamma_2= 2 b c + a d$, and $\delta_1 = (b c g+a d g+a c h), \delta_2 = (b d g+b c h+a d h)$.
-%\left[
-%\begin{array}{ccccccccc}
- %a & c & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
- %b & d & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
- %-2 a g & -2 c g & a^2 & 2 a c & c^2 & 0 & 0 & 0 & 0 \\
- %-b g-a h & -d g-c h & a b & b c+a d & c d & 0 & 0 & 0 & 0 \\
- %-2 b h & -2 d h & b^2 & 2 b d & d^2 & 0 & 0 & 0 & 0 \\
- %6 a g^2 & 6 c g^2 & -6 a^2 g & -12 a c g & -6 c^2 g & a^3 & 3 a^2 c & 3 a c^2 & c^3 \\
- %2 g (b g+2 a h) & 2 g (d g+2 c h) & -2 a (2 b g+a h) & -4 (b c g+a d g+a c h) & -2 c (2 d
-   %g+c h) & a^2 b & a (2 b c+a d) & c (b c+2 a d) & c^2 d \\
- %2 h (2 b g+a h) & 2 h (2 d g+c h) & -2 b (b g+2 a h) & -4 (b d g+b c h+a d h) & -2 d (d g+2
-   %c h) & a b^2 & b (b c+2 a d) & d (2 b c+a d) & c d^2 \\
- %6 b h^2 & 6 d h^2 & -6 b^2 h & -12 b d h & -6 d^2 h & b^3 & 3 b^2 d & 3 b d^2 & d^3 \\
-%\end{array}
-%\right]
-
-%%A direct calculation using (\ref{eq:prolong}) shows that the same transformation rule (\ref{eq:D}) holds for $\phi\in\mathrm{PSL}(3,\R)$.
-That is, $D$ is a relative invariant of weight 2 of this action.
-%Both $D$ and $E$ will be useful quantities shortly, but note that, from (\ref{eq:D}), the sign of $D$ is invariant and therefore the choice of moving frame must depend on its sign.
-
-We begin by choosing the frames $\bar f_{\bar x} = 1$ and $\bar f_{\bar y}=  0$, which determine the group parameters $a = (1-c f_y)/f_x.$ and $b = -d f_y/f_x$.
-Direction substition then shows that $\bar f_{\bar y \bar y} = D d^2 / f_x^2$, where $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$, which we saw earlier as an invariant of $A(2)$, which is a subgroup of $\mathrm{PSL}(3,\R)$.
-Note that $D$ and $\bar f_{\bar y \bar y}$ have the same sign; in what follows we assume that $D>0$ (if it is negative, relatively little changes in the following derivation) and choose the frame $\bar f_{ \bar y \bar y} = 1$, so that $d = f_x/D^{1/2}.$
+
+We begin the construction of the moving frame by choosing $\bar f_{\bar x}
+= 1$ and $\bar f_{\bar y}=  0$, which determine the group parameters $a =
+(1-c f_y)/f_x.$ and $b = -d f_y/f_x$. Direction substition then shows that
+$\bar f_{\bar y \bar y} = D d^2 / f_x^2$, where $D = f_{x}^2 f_{yy} + f_y^2
+f_{xx} - 2 f_x f_y f_{xyy}$, which we saw earlier as an invariant of
+$A(2)$, which is a subgroup of $\mathrm{PSL}(3,\R)$. Note that $D$ and
+$\bar f_{\bar y \bar y}$ have the same sign. If $D < 0$, we choose the
+frame $\bar{f}_{\bar y \bar y} = -1$ and if $D \ge 0$ we choose $\bar
+f_{\bar y \bar y} = 1$. Then $d = f_x/|D|^{1/2}.$
 
@@
 Having determined the frame, any function of the remaining derivatives $\bar f_{ \bar x \bar x \bar x}$, $\bar f_{ \bar x \bar x \bar y}$, and $\bar f_{ \bar y \bar y \bar y}$, as given in Equation~(\ref{eq:prolong}), provides invariants.
-We choose: $$ (f_{xxx}, f_{xxy}^2, f_{xyy})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right)\:,$$ where (with $P_n$ denoting a polynomial of degree $n$):
-$$ J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5.$$
+We choose:
+\begin{equation*}
+ (\bar f_{\bar x\bar x\bar x}, \bar f_{\bar x\bar x\bar y}^2, \bar f_{\bar
+ x\bar y\bar
+ y})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right).
+\end{equation*} 
+\todo[inline]{Check J2 has squared or not}
+The terms $J_1, J_2, J_3$ can be written in terms of $D$ and $E$, together
+with a polynomial of degree $n$ denoted by $P_n$. 
+\begin{equation*}
+    J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5.
+\end{equation*}
 

### 2020-11-17 paper/newpaper.tex
updates'

--- 2020-11-17 paper/newpaper.tex
@@
 \begin{abstract}
-Object recognition, planar transformation, invariants, differential invariant signature, demo of 3 methods with examples for planar Lie groups, discussion of utility
+Camera motion imposes transformations on the objects in an image, and these transformations will differ for objects at different positions relativele to the camera.
+Typically these transformations will be elements of planar Lie groups.
+While there have been significant advances in object recognition using machine learning in recent years, the question of how to recognise an object in an image as its appearance varies through camera motion and similar effects remains open.
+We consider how differential invariant signatures can be derived for each of the transformation groups, and how the underlying invariances reflect the group-subgroup structure of the transformation groups.
+
+There are a variety of methods that can be used to identify differential invariants, and we provide examples of three of them: tensor contraction, transvectants, and the method of moving frames.
+We use the resulting invariants to construct practical sets to form three-dimensional invariant signatures.
+These signatures are not necessarily complete: the image cannot always be reconstructed uniquely up to transformation, but they are plottable, and depend at worst on third derivatives, although more channels of information, such as colour images, can reduce the highest order to derivate needed in some cases.
+We demonstrate the invariant signatures for each transformation group based on a simple smooth image.
+A full consideration of how these signatures could be used in practice will require effective methods to numerically approximate derivatives effectively for images.
 \end{abstract}
@@
 \begin{keywords}
-Object recognition, planar transformation, invariants, differential invariant signature
+Object recognition, planar transformation, planar Lie groups, invariants, differential invariant signature
 \end{keywords}
@@
 \todo[inline]{
-Abstract
 Literature
+Discussion -- syzygies
 
@@
 Check signatures for Mobius etc.
-
-Discussion
 }
@@
 In order for the invariant signatures to be useful to identify similarity in images, there are two key considerations: they must vary continuously with respect to the image, either for all smooth images or for all except a set of sufficiently high codimension, and they must be robust with respect to occlusions, where one object obscures some part of another.
-These constraints lead one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology.
+Thse constraints are essential if the signature is to be used to detect similarity of images, but the first fails for the rational invariants found in the literature.
+Such considerations lead one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology.
 This is sufficient to compute, e.g., derivatives of an object.
@@
 
-\subsection{Relevant Literature}
-
-Classical invariants
-
-The theory of invariants has a rich mathematical history, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview. Polynomials, then geometry.
-
-Lie
-
-\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872,Lie1884}
-
-A variety of function spaces have allowed for the creation of different sets of invariants for particular groups.
-For the Euclidean group, the Fourier transform provides a useful tool, and this can be extended to the affine group using the Fourier-Mellin transform and the bispectrum.
-Alternatively, integral invariants and moments can be computed.
-For the similarity group applied to images the seminal reference is \cite{Hu1962}, but see also~\cite{}.
-\cite{Hickman2011,Abu-Mostafa1984,Kakarala2010,Flusser2009,Papakostas2013}
-\cite{Manay2006,Negrinho2013,Ghorbel1994,Turski2006}
-\cite{Reddy1996,Gauthier2008,Kakarala2011,Smach2007}
-
-The other group that has been of particular interest for image analysis is the projective group, because of its ubiquity in images from cameras. Summarise these...
-\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}
-
-Diff invs and sigs
-
-An algorithm to compute differential and joint invariants and determine complete signature sets is described in \cite{Olver2005}.
-The entire set of invariants is computed using the method of moving frames (see Section~\ref{sec:MF}) and then the signature set of a maximal set of functionally independent invariants is identified.
-A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
-
-Joint sigs
-\cite{Fels1997,Olver2013,Arora2009}
-An intermediary role is played by the “semi-differential invariants” (or, as we would
-prefer they be known, “joint differential invariants”) introduced into vision by Van Gool et. al., [34],
-
-Diff Invs
-\cite{Florack1993,Olver2007,Bouton1898}
-
-This is essential if the
-signature is to be used to detect similarity of images, but it fails for the rational
-invariants found in the literature.
-
-not intensity transforms
-
-** FIX FAUGERAS
-
-There has been a long-standing interest in constructing invariants for image recognition. 
-\cite{VanGool1995,Wood1996,Zhang2019,Faugeras1994,Gros1992,Taubin1992,Lenz1990,Florack1993}
-
-\cite{SURF}
-
-SURF and that kind of crap
-
 %Groups we've done:
@@
 Figure~\ref{fig:T2} shows (a) the original image, (b) the translated image by $x,y$, (c) the signature of one of them, (d) the superimposed pair of signatures. Now explain the missing bits.
+
+\subsection{Relevant Literature}
+
+Classical invariants
+
+The theory of invariants has a rich mathematical history, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview. Polynomials, then geometry.
+
+Lie
+
+\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872,Lie1884}
+\cite{VanGool1995}
+
+\kakarala2011
+
+There has been a long-standing interest in constructing invariants for image recognition.
+Wood1996,
+Taubin1992
+A variety of function spaces have allowed for the creation of different sets of invariants for particular groups.
+For the Euclidean group, the Fourier transform provides a useful tool~\cite{Ghorbel1994,Turski2006,Smach2007,Gauthier2008}, and this can be extended to the affine group using the Fourier-Mellin transform~\cite{Reddy1996,Zhang2019} and the bispectrum~\cite{Kakarala2009,Negrinho2013}.
+Alternatively, integral invariants~\cite{Manay2006,Feng2010} and moments can be computed.
+For the similarity group applied to images the original reference is \cite{Hu1962}, but see also~\cite{Hickman2011} for affine transformations, \cite{Flusser2009} for an implicit representation, and \cite{Papakostas2013} for their use in a binary pattern for image recognition.
+
+The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models. Summarise these...
+\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}
+\cite{Gros1992,Hubert2007}
+
+Although there are computational challenges regarding the numerical approximation of derivatives on images, the fact that differential invariants are robust to occlusion, cheap to compute, and well-behaved with respect to small changes in the image, has made them popular for researchers in image analysis.
+Diff invs and sigs
+
+An algorithm to compute differential and joint invariants and determine complete signature sets is described in \cite{Olver2005}.
+The entire set of invariants is computed using the method of moving frames (see Section~\ref{sec:movingframes}) and then the signature set of a maximal set of functionally independent invariants is identified.
+A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
+
+\cite{Faugeras1994}
+
+Joint sigs
+\cite{Fels1997,Olver2013,Arora2009}
+An intermediary role is played by the “semi-differential invariants” (or, as we would
+prefer they be known, “joint differential invariants”) introduced into vision by Van Gool et. al., [34],
+
+Diff Invs
+\cite{Florack1993,Olver2007,Bouton1898}
+
+** FIX FAUGERAS
+
+\cite{SURF}
+
+SURF and that kind of crap
 
@@
 
+not intensity transforms
+
 \bibliographystyle{plainnat}

### 2020-11-17 paper/newpaper.tex

@@
 
-\kakarala2011
+\cite{Kakarala2011}
 
@@
 
+%Groups we've done:
+%translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
 \section{Differential invariants through tensor contraction}
@@
 
-Olver uses the group $SE(2)$ on curves as an example~\cite{Olver}, recovering the Euclidean curvature as a second-order invariant.
+Olver uses the group $SE(2)$ on curves as an example~\cite{OlverCIT}, recovering the Euclidean curvature as a second-order invariant.
 We continue this example to compute invariants to $SE(2)$ for images, before moving on to other planar Lie group examples: $E(2)$, the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).

### 2020-11-17 paper/newpaper.tex
missed one
Similarity and E(2) done

@@
 
-In this paper our aim is develop the mathematical underpinnings of constructing differential invariant signatures for images under the action of planar Lie groups.
-However, as we develop the signature for each group, we will provide an example of the type of surface that the signature defines.
-Note that these will generally be three-dimensional representation of the planar image.
+In this paper our aim is develop the mathematical underpinnings of
+constructing differential invariant signatures for images under the action
+of planar Lie groups. However, as we develop the signature for each group,
+we will provide an example of the type of surface that the signature
+defines. Note that these will generally be three-dimensional representation
+of the planar image.
 
@@
 On the left the image itself is shown, while on the right a version with a
-regular grid superimposed is given. This is useful for visualising both the
-transformation and how the image is mapped into the three-dimensional
-signature surface.
+regular grid superimposed is given. We will use this function throughout,
+using the grid to help visualise both the transformation and how the image
+is mapped into the three-dimensional signature surface.
 
@@
 three-dimensional space, and the two images will produce the same surface,
-which we call the signature.
+which we call the signature, $\mathcal{I}(f)(x, y) = \left(I_1, I_2,
+I_3\right)$ where $I_1 = f, I_2 = f_x, I_3 = f_y$.
 
@@
 yellow lines in (c) correspond to where the yellow grid from (a) has been
-mapped to on the signature surface. In (d), notice that as some of the
-image has moved out of frame, there are parts of the signature near its
-boundary that do not overlap.
+mapped to on the signature surface. The parts of the surface where the mesh
+gets close together are where the function and its derivatives are tending
+towards zero. This occurs around the boundary of our test image and so all
+of these points are close together in the signature space. In (d), notice
+that as some of the image has moved out of frame, there are parts of the
+signature surfaces of the two images that do not overlap.
 
@@
 The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models. Summarise these...
-\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}
+\cite{Suk2000,Suk2004,Hann2002a,Kogan2014,Li19}
 \cite{Gros1992,Hubert2007}
@@
 
-While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$.
-In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance as they are equivalent.
-We therefore use subscript indices exclusively.
+While we avoid the use of tensors in most of this study, there is a notable
+exception to be made for the Euclidean transformation group $E(2)$. In this
+setting we can restrict ourselves to \emph{Cartesian tensors}, where we
+need make no distinction between covariance and contravariance as they are
+equivalent. We therefore use subscript indices exclusively.
 
@@
 \end{equation*}
-using the Einstein summation convention. The orthogonality condition is that $a_{ik}a_{jk} = a_{ki}a_{kj} = \delta_{ij}$.
+using the Einstein summation convention. The orthogonality condition is
+that $a_{ik}a_{jk} = a_{ki}a_{kj} = \delta_{ij}$. A Euclidean
+transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$ can also be
+written in matrix form as $\bar{\mathbf{x}} = \varphi(\mathbf{x}) =
+U\mathbf{x} + \mathbf{t}$ where the matrix $U$ satisfies $U^TU = I$ and
+$\mathbf{t} \in \mathbb{R}^2$.
 
@@
 
-The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}}\cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor~\cite{Florack1993}.
+The main observation is that in this setting, the $n^\text{th}$ order
+partial derivative operator $\partial^n / \partial_{x_{i_1}}\cdots
+\partial_{x_{i_n}}$ formally transforms as an $n$-tensor, \citep{Florack1993}.
 Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial^p f / \partial_{x_{i_1}} \cdots \partial_{x_{i_p}}$ will give a Euclidean invariant.
@@
 For example, up to second derivatives, we have the following Euclidean invariants, expressed as tensor contractions:
-\begin{align*}
-  f &= f \\
-  f_if_i &= f_x^2 + f_y^2 \\
-  f_{ii} &= f_{xx} + f_{yy} \\
-  f_{ij} f_{ij} &= f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
-  f_i f_j f_{ij} &= f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}
-\label{eq:se2}
-\end{align*}
-
-While we can construct any number of invariants this way, there is no guarantee of functional independence between them.
-We will address this issue in Section~\ref{sec:movingframes} when we construct invariants of $E(2)$ and other groups using the method of moving frames.
-
-SE(2): rotation, Sim(2): zooming.
-
-\begin{figure}
-\centering
-\includegraphics[width=.45\textwidth]{Figs/f_transformed_SE2.png}
-\includegraphics[width=.45\textwidth]{Figs/SE2_signature.png}
-\caption{A sample $SE(2)$ Transform and 3D signature.}
-\label{fig:SE2}
-\end{figure}
-
+\begin{equation}
+\label{eq:e2tensor}
+\begin{aligned}
+  I_0 &= f = f \\
+  I_1 &= f_if_i = f_x^2 + f_y^2 \\
+  I_2 &= f_{ii} = f_{xx} + f_{yy} \\
+  I_3 &= f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
+  I_4 &= f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}
+\end{aligned}
+\end{equation}
+
+While we can construct any number of invariants this way, there is no
+guarantee of functional independence between them. We will address this
+issue in Section~\ref{sec:movingframes} when we construct invariants of
+$E(2)$ and other groups using the method of moving frames. We can form a
+signature from any three of these invariants \eqref{eq:e2tensor}, we choose for
+simplicity our signature to be 
+\begin{equation}
+    \label{eq:e2signature}
+    \mathcal{I}_{E(2)} = (I_0, I_1, I_2)
+\end{equation}.  
+A sample $E(2)$ transformation is depicted in Fig.~\ref{fig:E2} with its corresponding
+signature.
 \begin{figure}
@@
 \label{fig:E2}
+\end{figure}
+We will defer discussion of the Special Euclidean group (which excludes
+reflections) until Section~\ref{sec:SE2} where invariants naturally arise
+from the method of moving frames.
+
+\subsection{The similarity group}
+\label{sec:Sim2}
+The similarity group $\text{Sim}(2)$ consists transformations of the form
+$\bar{\mathbf{x}} = \varphi(\mathbf{x}) = sU\mathbf{x} + \mathbf{t}$, where $U^TU = I$ and $s
+\in \mathbb{R}\setminus\{0\}$. It is like the Euclidean group except it
+also allows for isotropic scaling. In image applications, similarity
+transformations arise from operations like zooming.
+
+Under similarity transformations, the Euclidean invariants become
+/emph{relative invariants}. Each derivative introduces a multiple of $s$ to
+each invariant. For example, $\bar{f}_{\bar x}^2 + \bar{f}_{\bar y}^2 =
+s^2(f_x^2 + f_y^2)$ and $\bar{f}_{\bar x \bar x}^2 + 2\bar{f}_{\bar x \bar
+y}^2 + \bar{f}_{\bar y \bar y} = s^4 (f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2$). We
+refer to the power of $s$ as the weight of the transformation.
+
+One way to produce similarity invariants would be to take ratios of powers
+of the Euclidean invariants \eqref{eq:e2tensor} so that the multiples of
+$s$ cancel. For example $\frac{f_x^2 + f_y^2}{f_{xx} + f_{yy}}$ is the
+ratio of two weight-2 relative invariants and is hence a similarity
+invariant. However this invariant is singular whenever $f_{xx} + f_{yy} =
+0$ which is a codimension-0 phenomenon for images.
+
+A better approach is to take three invariants of the same weight, we'll
+take $I_1^2$, $I_2^2$, and $I_3$ from \eqref{eq:e2tensor}, all of which are
+weight $4$, and project them onto the unit sphere. This can then be
+multiplied by $I_0 = f$ to form a signature surface. So our signature is
+defined by
+\begin{equation}
+    \label{eq:sim2signature}
+\mathcal{I}_{\text{Sim(2)}}(f) = \frac{f}{\sqrt{I_1^4 + I_2^4 + I_3^2}}(I_1^2, I_2^2,
+        I_3)
+\end{equation}
+This signature is only singular when $f_x = f_y = f_{xx} = f_{yy} = f_{xy}
+= 0$. A sample similarity transformation and computed signature is shown in
+Fig.~\ref{fig:Sim2}
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_Sim2.png}
+\includegraphics[width=.45\textwidth]{Figs/Sim2_signature.png}
+\caption{A sample $\text{Sim}(2)$ Transform and 3D signature.}
+\label{fig:Sim2}
 \end{figure}
@@
 \subsection{The Special Euclidean Group SE(2)}
+\label{sec:SE2}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_SE2.png}
+\includegraphics[width=.45\textwidth]{Figs/SE2_signature.png}
+\caption{A sample $SE(2)$ Transform and 3D signature.}
+\label{fig:SE2}
+\end{figure}
 \subsection{The Euclidean Group E(2)}

### 2020-11-17 paper/newpaper.tex
A2 and SA2 done

@@
 
+Some of these partial transvectants appear in signatures
+from other transformation groups, so for future reference, let
+\begin{equation}
+    \label{eq:cde}
+    \begin{aligned}
+        C &= f_{xx}f_{yy}-f_{xy}^2, \\
+        D &= f_x^2f_{yy} - 2f_xf_yf_{xy} + f_{xx}f_y^2, \\
+        E &= f_{xxx}f_y^3 - 3f_{xxy}f_xf_y^2 + 3f_{xyy}f_x^2f_y -
+        f_{yyy}f_x^3.
+    \end{aligned}
+\end{equation}
+
 \subsection{Signatures of $SA(2)$ and $A(2)$}
 
-The action of the affine group $A(2)$ arises as the motions of planar objects far from a camera.
-Recall that invariants of a supergroup are automatically invariants of any of its subgroups.
-For example, invariants of $A(2)$ are automatically invariants of $SA(2)$, but not necessarily vice versa.
-Any of the partial transvectants found in Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} are invariants of $SA(2)$ (as the determinant is $1$), but only up to scale factor ($\det A^{-r}$) of $A(2)$.
-
-Hence, we can form a signature for $SA(2)$ by choosing any combination of partial transvectants.
-We choose a signature with three components so that it can be visualised as a three-dimensional surface; note that this will not be complete and may well have a very large bad set.
-For example, we can choose the function value together with the first two partial transvectants to form the signature:
-\begin{equation*}
-    \left(f, f_{xx}f_{yy}-f_{xy}^2, f_x^2f_{yy} - 2f_xf_yf_{xy} + f_{xx}f_y^2\right).
-\end{equation*}
-
+The action of the affine group $A(2)$ arises in images as the motion of
+planar objects in images taken from a distant camera. Recall that
+invariants of a supergroup are automatically invariants of any of its
+subgroups. For example, invariants of $A(2)$ are automatically invariants
+of $SA(2)$, but not necessarily vice versa. Any of the partial
+transvectants found in Tables~\ref{tab:transvectants1}
+and~\ref{tab:transvectants2} are invariants of $SA(2)$ (as the determinant
+is $1$), but only up to scale factor ($\det A^{-r}$) of $A(2)$.
+
+Hence, we can form a signature for $SA(2)$ by choosing any combination of
+partial transvectants. We choose a signature with three components so that
+it can be visualised as a three-dimensional surface; note that this will
+not be complete and may well have a very large bad set. For example, we can
+choose the function value together with the $C, D$ from \eqref{eq:cde}
+to form the signature.
+
+\begin{equation}
+    \label{eq:SA2signature}
+    \mathcal{I}_{SA(2)}(f) = \left(f, C, D \right).
+\end{equation}
 We will subject our test image to the special affine transformation:
 \begin{equation*}
-\mathbf{x} \mapsto \frac{1}{1.1}\begin{bmatrix} 0.6875 & 1.1 \\ -0.6 & 0.8 \end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
+\mathbf{x} \mapsto \frac{1}{1.22}\begin{bmatrix} 0.7 & 1.1 \\ -0.6 & 0.8 \end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
 \end{equation*}
-
 Fig.~\ref{fig:SA2} shows the signature of our test image under this transformation.
@@
 \subsubsection{Moving on to A(2), \ldots}
-Using the same function as an example, 
+
+For $A(2)$ the weight of the partial transvectants prevents them from being
+invariants. There are two options to create a signature. One is to select
+ratios of partial transvectants, similar to as discussed in
+Section~\ref{sec:Sim2}. It is then beneficial to choose the
+numerator and denominator so that they have different critical points,
+which can be achieved by adding together partial transvectants of the same
+weight as appropriate. Instead, we employ the same normalisation strategy
+as previously, projecting the weight four relative invariants $(C^2, D^2,
+E)$ onto the unit hypersphere and multiplying by $f$. In this way, our
+signature is
+\begin{equation}
+    \label{eq:A2signature}
+    \mathcal{I}_{A(2)} = \frac{f}{\sqrt{C^4 + D^4 + E^2}}(C^2, D^2, E)
+\end{equation}
+
+We will subject our test image to the special affine transformation:
+\begin{equation*}
+\mathbf{x} \mapsto \begin{bmatrix} 0.7 & 1.1 \\ -0.6 & 0.8
+\end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
+\end{equation*}
+Fig.~\ref{fig:A2} shows the signature of our test image under this transformation.
 \begin{figure}
@@
 \end{figure}
-
-For $A(2)$ the weight of the partial transvectants prevents them from being invariants.
-There are two options to create a signature.
-One is to select ratios of partial transvectants.
-It is then beneficial to choose the numerator and denominator so that they have different critical points, which can be achieved by adding together partial transvectants of the same weight as appropriate.
-Instead, we normalise the partial transvectants by choosing only those where all components have the same weight and projecting them onto the unit hypersphere.
-By multiplying these by the function (which takes values between 0 and 1) we create a signature enclosed by the unit hypersphere.
-An example is shown in Figure~\ref{fig:A2}.
 

### 2020-11-17 paper/newpaper.tex
conformal and mobius signatures updated

@@
 \def\R{\mathbb{R}}
+\usepackage{mathtools}
 \usepackage{xcolor}
@@
 locally free (away from critical points) when prolonged to $J^1$, however
-we prolonged to $J^2$ in order to compute invariants. points. The moving
+we prolonged to $J^2$ in order to compute invariants. The moving
 frame is then given by the prolonged Euclidean transformation that maps an
@@
 \begin{aligned}
-  I_0 &= f \\
-  I_1 &= f_x^2 + f_y^2 & &(= \bar{f}_{\bar{x}}^2)\\
-  I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= I_1\bar{f}_{\bar{x}\bar{x}}) \\
-  I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) &&(= I_1\bar{f}_{\bar{x}\bar{y}})\\
-  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}}).
+  K_0 &= f \\
+  K_1 &= f_x^2 + f_y^2 & &(= \bar{f}_{\bar{x}}^2)\\
+  K_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= K_1\bar{f}_{\bar{x}\bar{x}}) \\
+  K_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) &&(= K_1\bar{f}_{\bar{x}\bar{y}})\\
+  K_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= K_1\bar{f}_{\bar{y}\bar{y}}).
 \end{aligned}
 \end{equation}
-Note that we multiplied each of the second derivative invariants by $I_1$
-so that they would decay smoothly to zero at critical points.
-
+Note that we multiplied each of the second derivative invariants by the
+invariant $K_1$ so that they would decay smoothly to zero at critical
+points.  Interestingly, $K_4$ is the affine invariant $D$ from
+\eqref{eq:cde} and $K_1, K_2$ are also Euclidean invariants, so we need to
+include $K_3$ in our signature. We choose our signature to be
+\begin{equation}
+    \label{eq:SE2signature}
+    I_{SE(2)}(f) = (f, K_1, K_3)
+\end{equation}
+Fig.~\ref{fig:SE2} shows the signature of our test image under a sample
+transformation of $SE(2)$:
 \begin{figure}
@@
 \end{figure}
+
 \subsection{The Euclidean Group E(2)}
@@
 This suggests choosing $\varepsilon$ to make $\bar{f}_{\bar{x}\bar{y}} \ge
-0$. We can then list the invariants:
+0$. The moving frame is then fully specified, and the remaining derivatives
+give the same invariants $K_0, K_1, K_2, K_4$ as for $SE(2)$,
+\eqref{eq:se2invariants}, the one difference being $\hat{K}_3$:
 \begin{equation}\label{eq:e2invariants}
-\begin{aligned}
-  I_0 &= f \\
-  I_1 &= f_x^2 + f_y^2 & &(= \bar{f}_{\bar{x}}^2)\\
-  I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} &&(= I_1\bar{f}_{\bar{x}\bar{x}}) \\
-  I_3 &= \lvert f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2)\rvert
-  &&(= I_1\lvert \bar{f}_{\bar{x}\bar{y}}\rvert)\\
-  I_4 &= f_y^2 f_{xx} - 2 f_x f_y f_{xy} + f_x^2 f_{yy} &&(= I_1\bar{f}_{\bar{y}\bar{y}}).
-\end{aligned}
-\end{equation}
-Notice that most, but not all of the $SE(2)$ invariants
-\eqref{eq:se2invariants} are also $E(2)$ invariants. We again multiply
-through the invariants by $I_1$ so that they decay smoothly at critical
-points.
-
-These invariants are a functionally independent, complete, set of polynomial differential invariants up to second derivatives.
-Note that the invariants found previously by tensor contraction Eq.
-(\ref{eq:se2}) in Section~\ref{sec:contraction} can be expressed in terms of these:
+    \hat{K}_3 = \lvert f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2)\rvert
+\end{equation}
+
+These invariants are a functionally independent, complete, set of
+polynomial differential invariants up to second derivatives. Note that the
+invariants found previously by tensor contraction Eq. (\ref{eq:e2tensor}) in
+Section~\ref{sec:contraction} can be expressed in terms of these:
 \begin{align*}
-  f = f &= I_0 \\
-  f_if_i = f_x^2 + f_y^2 &= I_1 \\
-  f_{ii} = f_{xx} + f_{yy} &= \frac{I_2 + I_4}{I_1} \\
-  f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 &= \frac{I_2^2 + I_4^2 + 2I_3^2}{I_1^2} \\
-  f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy} &= I_2.
+  f = f &= K_0 \\
+  f_if_i = f_x^2 + f_y^2 &= K_1 \\
+  f_{ii} = f_{xx} + f_{yy} &= \frac{K_2 + K_4}{K_1} \\
+  f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 &= \frac{K_2^2 + K_4^2 + 2K_3^2}{K_1^2} \\
+  f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy} &= K_2.
 \end{align*}
@@
 
-The four third-order invariants can be deduced from the moving frame.
-They are rational functions with numerators of degree 6 and denominators $(f_x^2 + f_y^2)^4$, and are relative invariants of weight 8.
-Clearing denominators so as to work with polynomials, we choose $M_1 = (f_{xx} + f_{yy})^4$ and two of the four third-order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where:
-\begin{align} M_2&=
+The four third-order invariants can be deduced from the moving frame. They
+are rational functions with numerators of degree 6 and denominators $(f_x^2
++ f_y^2)^4$, and are relative invariants of weight 8.  Clearing
+denominators so as to work with polynomials, we choose $M_1 = (f_{xx} +
+f_{yy})^4$ and two of the four third-order invariants $M_2$ and $M_3$:
+\begin{align*} M_2&=
 f_y ^5 f_{yyy} + \frac{9}{2} f_y ^2 f_{yy}^2 f_x ^2 + 
@@
  f_x ^5 f_{xxx}, 
-\end{align}
-
-\begin{align}
+\end{align*}
+
+\begin{align*}
 M_3&=-3 f_y  f_{yy}^2 f_x ^3 + 
@@
  f_y ^3 f_x ^2 f_{xxx}.
-\end{align}
-
-The image $f$ and these 3 relative invariants of weight 8 provide a three-dimensional signature; an example is shown in Figure~\ref{fig:mobius}, although note that it is singular when $f_x=f_y=f_{xx}+f_{yy}=0$, a codimension 1 phenomenon for images.
+\end{align*}
+We then form a signature by our usual projection method from the image $f$
+and these three weight $8$ relative invariants:
+\begin{equation}
+    \label{eq:mobiussignature}
+    \mathcal{I}_{\text{M\"obius}}(f) = \frac{f}{\sqrt{M_1^2 + M_2^2 +
+    M_3^2}} (M_1, M_2, M_3)
+\end{equation}
+An example is shown in Figure~\ref{fig:mobius}, although note that the
+signature is singular when $f_x=f_y=f_{xx}+f_{yy}=0$, a codimension 1
+phenomenon for images. 
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_Mobius.png}
+\includegraphics[width=.45\textwidth]{Figs/Mobius_signature.png}
+\caption{A sample M\"obius Transform and 3D signature.}
+\label{fig:mobius}
+\end{figure}
 
@@
 %Any such signature that includes $J_1$ and $J_2$ is
-
-\begin{figure}
-\centering
-\includegraphics[width=.45\textwidth]{Figs/f_transformed_Mobius.png}
-\includegraphics[width=.45\textwidth]{Figs/Mobius_signature.png}
-\caption{A sample M\"obius Transform and 3D signature.}
-\label{fig:mobius}
-\end{figure}
 
@@
 \begin{equation}
-    \bar{f}_{\bar{y}\bar{y}} = \frac{f_{xx} + f_{yy}}{f_x^2 + f_y^2}.
+    \bar{f}_{\bar{y}\bar{y}} = \frac{f_{xx} + f_{yy}}{f_x^2 + f_y^2} =
+    \frac{C_1}{f_x^2 + f_y^2}.
 \label{eqn:C1}
@@
 \begin{align}
-    \bar{f}_{\bar{x}\bar{y}\bar{y}} &= \frac{1}{(f_x^2 + f_y^2)^3} \left[
+    \bar{f}_{\bar{x}\bar{y}\bar{y}} &= 
+    \begin{multlined}[t]
+        \frac{1}{(f_x^2 + f_y^2)^3} \left[
 f_y^3f_{yyy} + f_x^2f_yf_{yyy}
             -2f_y^2f_{yy}^2 - 2f_{xx}f_y^2f_{yy} -
-            4f_xf_{xy}f_yf_{yy} - 2f_x^2 f_{xx}f_{yy} \right. \\ \nonumber
-&+ \left. f_{xxy}f_y^3 +
+            4f_xf_{xy}f_yf_{yy} - 2f_x^2 f_{xx}f_{yy} \right. \\ 
++ \left. f_{xxy}f_y^3 +
             f_x^2 f_{xxy}f_y - 4 f_x f_{xy} f_{xx} f_y + f_x^3 f_{xxx} -
     2f_x^2 f_{xx}^2 + f_x^3 f_{xyy} \right]
-\\ \label{eqn:C2}
-        \bar{f}_{\bar{y}\bar{y}\bar{y}} &= \frac{1}{(f_x^2 + f_y^2)^3} \left[
+    = \frac{C_2}{(f_x^2 +
+f_y^2)^3}\end{multlined} \\
+    \bar{f}_{\bar{y}\bar{y}\bar{y}} &= 
+    \begin{multlined}[t]
+        \frac{1}{(f_x^2 + f_y^2)^3} \left[
 f_xf_y^2f_{yyy} +
         f_x^3f_{yyy} - 2f_x f_y f_{yy}^2 + 2f_{xy}f_y^2f_{yy} -
-    2f_x^2f_{xy}f_{yy} - f_{xxx}f_y^3 \right. \\ \nonumber
-&- \left. f_{xyy}f_y^3 + f_xf_{xxy}f_y^2 +
+    2f_x^2f_{xy}f_{yy} - f_{xxx}f_y^3 \right. \\ 
+-  f_{xyy}f_y^3 + f_xf_{xxy}f_y^2 +
 2f_{xy}f_{xx}f_y^2 - f_x^2 f_{xxx} f_y + 2f_xf_{xx}^2 f_y - f_x^2 f_{xyy}
-f_y + f_x^3 f_{xxy} - 2f_x^2 f_{xy} f_{xx} \right] \label{eqn:C3}
+f_y \\\left.+ f_x^3 f_{xxy} - 2f_x^2 f_{xy} f_{xx}\right]
+= \frac{C_3}{(f_x^2 + f_y^2)^3}
+\end{multlined}\label{eqn:C3}
 \end{align}
-
-Note that the denominators of all three of these equations are the same up to index.
-We therefore clear denominators as usual and form the three-dimensional signature ((\ref{eqn:C1})$^3$,(\ref{eqn:C2}),(\ref{eqn:C3})).
-We then project them into the unit sphere and multiply by $f$ to constrain them.
-This signature is continuous at all $(x,y)$ such that the three quantities are not simultaneously equal to zero, which occurs when $f_x = f_y = f_{xx} = f_{yy} = 0$, which is a codimension-1 phenomenon for images.
+Note that the denominators of all three of these equations are the same up
+to index. We therefore clear denominators as usual and form the
+signature using our usual projection technique:
+\begin{equation}
+    \label{eq:conformalsignature}
+\mathcal{I}_{\text{Diff}_\text{con}}(f) = \frac{f}{\sqrt{C_1^6 + C_2^2 +
+C_3^2}}(C_1^3, C_2, C_3)
+\end{equation}
+This signature is continuous at all $(x,y)$ such that the three quantities
+are not simultaneously equal to zero, which occurs when $f_x = f_y = f_{xx}
+= f_{yy} = 0$, which is a codimension-1 phenomenon for images.
+
+An example for the conformal map $\varphi$ defined through $\varphi^{-1}$ by
+$\varphi^{-1}(z) = \frac{3}{8}(z - 2)^2 - \frac{3}{2}$ is shown in
+Figure~\ref{fig:Diffcon}.
+\begin{figure}
+\centering 
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_Diffcon.png}
+\includegraphics[width=.45\textwidth]{Figs/Diffcon_signature.png}
+\caption{A sample $\text{Diff}_{con}$ Transform and 3D signature.}
+\label{fig:Diffcon}
+\end{figure}
 

### 2020-11-18 paper/newpaper.tex
Projective stuff

@@
 
-\todo[inline]{Problem here? fyyy is in MF and an invariant...}
-The frame $\bar f_{ \bar y \bar y \bar y} = 0$ determines the group parameter $ h = \frac{d(f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2 f_{xxy} - f_y^3 f_{xxx})}{6 f_x D},$ while $\bar f_{ \bar x \bar y \bar y}=0$ provides $ c = \frac{h f_x^2}{d D} - \frac{f_x f_{xy} - f_y f_{xx}}{D}$, and $\bar f_{ \bar x \bar x}=0$ gives $ g = \frac{1}{2 f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$ In fact, the denominator of the expression for $h$ was another invariant of $A(2)$; we label it $E$ for convenience.
+The frame $\bar f_{ \bar y \bar y \bar y} = 0$ determines the group
+parameter $ h = \frac{f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2
+f_{xxy} - f_y^3 f_{xxx}}{6|D|^{3/2}},$ while $\bar f_{ \bar x \bar y 
+y}=0$ provides $ c = \frac{h f_x^2}{d D} - \frac{f_x f_{xy} - f_y
+f_{xx}}{D}$, and $\bar f_{ \bar x \bar x}=0$ gives $ g = \frac{1}{2
+f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$ In fact, the
+numerator of the expression for $h$ was another invariant of $A(2)$; we
+label it $E$ for convenience.
 
@@
 \end{equation*} 
-\todo[inline]{Check J2 has squared or not}
 The terms $J_1, J_2, J_3$ can be written in terms of $D$ and $E$, together

### 2020-11-18 paper/newpaper.tex
lit

--- 2020-11-17 paper/newpaper.tex
@@
 \begin{abstract}
-Camera motion imposes transformations on the objects in an image, and these transformations will differ for objects at different positions relativele to the camera.
+Changes in viewpoint, such as camera motion, impose transformations on the objects in an image, and these transformations will differ for objects at different positions relativele to the camera.
 Typically these transformations will be elements of planar Lie groups.
@@
 
-An alternative option is to seek $\mathcal{G}$-invariant functions on $M$, which is what we consider here.
-In this case, rather than considering the image of the object, one constructs an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group.
+An alternative option is to seek $\mathcal{G}$-invariant functions on $M$.
+Mathematical invariants provide a useful way to identify sets of objects that are the same up to some equivalence relation, since the functions are constant for objects in the same equivalence class.
+For a group $\mathcal{G}$, orbits of the group form the equivalence classes.
+For images, rather than considering the image of the object, one constructs an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group.
 This has been considered extensively by Olver and co-authors for the case of outlines of objects~\cite{Calabi1998,Hoff2013}.
-In this paper we consider the case of signatures for images rather than outlines of curves.
+In this paper we consider the case of signatures for images rather than outlines of curves under a variety of transformation groups.
 
@@
 
-In this paper our aim is develop the mathematical underpinnings of
-constructing differential invariant signatures for images under the action
-of planar Lie groups. However, as we develop the signature for each group,
-we will provide an example of the type of surface that the signature
-defines. Note that these will generally be three-dimensional representation
-of the planar image.
+In this paper our aim is develop the mathematical underpinnings of constructing differential invariant signatures for images under the action of planar Lie groups.
+However, as we develop the signature for each group, we will provide an example of the type of surface that the signature defines.
+Note that these will generally be three-dimensional representation of the planar image.
 
@@
 On the left the image itself is shown, while on the right a version with a
-regular grid superimposed is given. We will use this function throughout,
-using the grid to help visualise both the transformation and how the image
-is mapped into the three-dimensional signature surface.
+regular grid superimposed is given. This is useful for visualising both the
+transformation and how the image is mapped into the three-dimensional
+signature surface.
 
@@
 three-dimensional space, and the two images will produce the same surface,
-which we call the signature, $\mathcal{I}(f)(x, y) = \left(I_1, I_2,
-I_3\right)$ where $I_1 = f, I_2 = f_x, I_3 = f_y$.
+which we call the signature.
 
@@
 yellow lines in (c) correspond to where the yellow grid from (a) has been
-mapped to on the signature surface. The parts of the surface where the mesh
-gets close together are where the function and its derivatives are tending
-towards zero. This occurs around the boundary of our test image and so all
-of these points are close together in the signature space. In (d), notice
-that as some of the image has moved out of frame, there are parts of the
-signature surfaces of the two images that do not overlap.
+mapped to on the signature surface. In (d), notice that as some of the
+image has moved out of frame, there are parts of the signature near its
+boundary that do not overlap.
 
@@
 
-The theory of invariants has a rich mathematical history, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview. Polynomials, then geometry.
-
-Lie
-
-\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872,Lie1884}
-\cite{VanGool1995}
-
-\cite{Kakarala2011}
-
-There has been a long-standing interest in constructing invariants for image recognition.
-Wood1996,
-Taubin1992
+The theory of invariants has a rich mathematical history, starting from invariants of forms~\cite{Cayley}, where the invariants are polynomials in the coefficients of the forms, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview.
+Geometric considerations and differential invariants followed fairly quickly~\cite{Veblen1872,Tresse1894,Bouton1898,Patterson1928}, particularly because they enabled the classification of differential equations into equivalence classes~\cite{Lie1884,Littlewood44, Cartan52}.
+More recently, this has extended, primarily by Olver and collaborators, see e.g.,~\cite{OlverCIT} and~\cite{OlverEIS} for summaries.
+
+There has been a long-standing interest in constructing invariants for image recognition and pattern analysis, see e.g.,~\cite{Mundy1992} and~\cite{Wood1996}.
+This was set in the context of Lie's invariants in~\cite{VanGool1995}, where the concept of a joint (or semi-) differential invariant (an invariant that acts on the joint action of the transformation group, see~\cite{Fels1997,Olver2013}) was introduced~\cite{VanGool1992}; see also~\cite{Hubert2009}.
+
 A variety of function spaces have allowed for the creation of different sets of invariants for particular groups.
 For the Euclidean group, the Fourier transform provides a useful tool~\cite{Ghorbel1994,Turski2006,Smach2007,Gauthier2008}, and this can be extended to the affine group using the Fourier-Mellin transform~\cite{Reddy1996,Zhang2019} and the bispectrum~\cite{Kakarala2009,Negrinho2013}.
-Alternatively, integral invariants~\cite{Manay2006,Feng2010} and moments can be computed.
-For the similarity group applied to images the original reference is \cite{Hu1962}, but see also~\cite{Hickman2011} for affine transformations, \cite{Flusser2009} for an implicit representation, and \cite{Papakostas2013} for their use in a binary pattern for image recognition.
-
-The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models. Summarise these...
-\cite{Suk2000,Suk2004,Hann2002a,Kogan2014,Li19}
-\cite{Gros1992,Hubert2007}
-
-Although there are computational challenges regarding the numerical approximation of derivatives on images, the fact that differential invariants are robust to occlusion, cheap to compute, and well-behaved with respect to small changes in the image, has made them popular for researchers in image analysis.
-Diff invs and sigs
-
-An algorithm to compute differential and joint invariants and determine complete signature sets is described in \cite{Olver2005}.
-The entire set of invariants is computed using the method of moving frames (see Section~\ref{sec:movingframes}) and then the signature set of a maximal set of functionally independent invariants is identified.
+Alternatively, integral invariants~\cite{Manay2006,Feng2010} and geometric moments can be computed.
+For the similarity group applied to images the original reference is \cite{Hu1962}, but see also~\cite{Hickman2011} for affine transformations, \cite{Flusser2009} for an implicit representation, and \cite{Papakostas2013} for their use in a binary pattern for image recognition, which is somewhat related to the invariant features such as SURF~\cite{SURF}.
+
+The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models.
+Invariants for this group have been computing using points~\cite{Gros1992,Suk2000}, geometric moments~\cite{Suk2004}, curvature~\cite{Hann2002a}, and differential and joint invariants~\cite{Hubert2007,Arora2009,Kogan2014,Li19}.
+
+Although there are computational challenges regarding the numerical approximation of derivatives on images, the fact that differential invariants are robust to occlusion, cheap to compute, and well-behaved with respect to small changes in the image, has made them popular for researchers in image analysis~\cite{Florack1993}.
+Two particular tools have been key to this: Cartan's moving frame~\cite{Cartan35} (see Section~\ref{sec:movingframes}), and which was used to construct image invariants as early as 1994 in \cite{Faugeras1994}, and the concept of an image signature built from a set of invariants~\cite{Calabi1998}.
+An algorithm to compute differential and joint invariants and determine complete signature sets is described in \cite{Olver2005,Olver2007}.
+The entire set of invariants is computed using the method of moving frames and then the signature set of a maximal set of functionally independent invariants is identified.
 A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
-
-\cite{Faugeras1994}
-
-Joint sigs
-\cite{Fels1997,Olver2013,Arora2009}
-An intermediary role is played by the “semi-differential invariants” (or, as we would
-prefer they be known, “joint differential invariants”) introduced into vision by Van Gool et. al., [34],
-
-Diff Invs
-\cite{Florack1993,Olver2007,Bouton1898}
-
-** FIX FAUGERAS
-
-\cite{SURF}
-
-SURF and that kind of crap
 
@@
 
-While we avoid the use of tensors in most of this study, there is a notable
-exception to be made for the Euclidean transformation group $E(2)$. In this
-setting we can restrict ourselves to \emph{Cartesian tensors}, where we
-need make no distinction between covariance and contravariance as they are
-equivalent. We therefore use subscript indices exclusively.
+While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$.
+In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance as they are equivalent.
+We therefore use subscript indices exclusively.
 
@@
 \end{equation*}
-using the Einstein summation convention. The orthogonality condition is
-that $a_{ik}a_{jk} = a_{ki}a_{kj} = \delta_{ij}$. A Euclidean
-transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$ can also be
-written in matrix form as $\bar{\mathbf{x}} = \varphi(\mathbf{x}) =
-U\mathbf{x} + \mathbf{t}$ where the matrix $U$ satisfies $U^TU = I$ and
-$\mathbf{t} \in \mathbb{R}^2$.
+using the Einstein summation convention. The orthogonality condition is that $a_{ik}a_{jk} = a_{ki}a_{kj} = \delta_{ij}$.
 
@@
 
-The main observation is that in this setting, the $n^\text{th}$ order
-partial derivative operator $\partial^n / \partial_{x_{i_1}}\cdots
-\partial_{x_{i_n}}$ formally transforms as an $n$-tensor, \citep{Florack1993}.
+The main observation is that in this setting, the $n^\text{th}$ order partial derivative operator $\partial^n / \partial_{x_{i_1}}\cdots \partial_{x_{i_n}}$ formally transforms as an $n$-tensor~\cite{Florack1993}.
 Because the product of a $p$-tensor and a $q$-tensor gives a $(p+q)$-tensor and contraction of a $p$-tensor yields a $(p-2)$-tensor, a complete contraction of a tensor of even rank formed as a product of terms of the form $\partial^p f / \partial_{x_{i_1}} \cdots \partial_{x_{i_p}}$ will give a Euclidean invariant.
@@
 For example, up to second derivatives, we have the following Euclidean invariants, expressed as tensor contractions:
-\begin{equation}
-\label{eq:e2tensor}
-\begin{aligned}
-  I_0 &= f = f \\
-  I_1 &= f_if_i = f_x^2 + f_y^2 \\
-  I_2 &= f_{ii} = f_{xx} + f_{yy} \\
-  I_3 &= f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
-  I_4 &= f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}
-\end{aligned}
-\end{equation}
-
-While we can construct any number of invariants this way, there is no
-guarantee of functional independence between them. We will address this
-issue in Section~\ref{sec:movingframes} when we construct invariants of
-$E(2)$ and other groups using the method of moving frames. We can form a
-signature from any three of these invariants \eqref{eq:e2tensor}, we choose for
-simplicity our signature to be 
-\begin{equation}
-    \label{eq:e2signature}
-    \mathcal{I}_{E(2)} = (I_0, I_1, I_2)
-\end{equation}.  
-A sample $E(2)$ transformation is depicted in Fig.~\ref{fig:E2} with its corresponding
-signature.
+\begin{align*}
+  f &= f \\
+  f_if_i &= f_x^2 + f_y^2 \\
+  f_{ii} &= f_{xx} + f_{yy} \\
+  f_{ij} f_{ij} &= f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
+  f_i f_j f_{ij} &= f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}
+\label{eq:se2}
+\end{align*}
+
+While we can construct any number of invariants this way, there is no guarantee of functional independence between them.
+We will address this issue in Section~\ref{sec:movingframes} when we construct invariants of $E(2)$ and other groups using the method of moving frames.
+
+SE(2): rotation, Sim(2): zooming.
+
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{Figs/f_transformed_SE2.png}
+\includegraphics[width=.45\textwidth]{Figs/SE2_signature.png}
+\caption{A sample $SE(2)$ Transform and 3D signature.}
+\label{fig:SE2}
+\end{figure}
+
 \begin{figure}
@@
 \label{fig:E2}
-\end{figure}
-We will defer discussion of the Special Euclidean group (which excludes
-reflections) until Section~\ref{sec:SE2} where invariants naturally arise
-from the method of moving frames.
-
-\subsection{The similarity group}
-\label{sec:Sim2}
-The similarity group $\text{Sim}(2)$ consists transformations of the form
-$\bar{\mathbf{x}} = \varphi(\mathbf{x}) = sU\mathbf{x} + \mathbf{t}$, where $U^TU = I$ and $s
-\in \mathbb{R}\setminus\{0\}$. It is like the Euclidean group except it
-also allows for isotropic scaling. In image applications, similarity
-transformations arise from operations like zooming.
-
-Under similarity transformations, the Euclidean invariants become
-/emph{relative invariants}. Each derivative introduces a multiple of $s$ to
-each invariant. For example, $\bar{f}_{\bar x}^2 + \bar{f}_{\bar y}^2 =
-s^2(f_x^2 + f_y^2)$ and $\bar{f}_{\bar x \bar x}^2 + 2\bar{f}_{\bar x \bar
-y}^2 + \bar{f}_{\bar y \bar y} = s^4 (f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2$). We
-refer to the power of $s$ as the weight of the transformation.
-
-One way to produce similarity invariants would be to take ratios of powers
-of the Euclidean invariants \eqref{eq:e2tensor} so that the multiples of
-$s$ cancel. For example $\frac{f_x^2 + f_y^2}{f_{xx} + f_{yy}}$ is the
-ratio of two weight-2 relative invariants and is hence a similarity
-invariant. However this invariant is singular whenever $f_{xx} + f_{yy} =
-0$ which is a codimension-0 phenomenon for images.
-
-A better approach is to take three invariants of the same weight, we'll
-take $I_1^2$, $I_2^2$, and $I_3$ from \eqref{eq:e2tensor}, all of which are
-weight $4$, and project them onto the unit sphere. This can then be
-multiplied by $I_0 = f$ to form a signature surface. So our signature is
-defined by
-\begin{equation}
-    \label{eq:sim2signature}
-\mathcal{I}_{\text{Sim(2)}}(f) = \frac{f}{\sqrt{I_1^4 + I_2^4 + I_3^2}}(I_1^2, I_2^2,
-        I_3)
-\end{equation}
-This signature is only singular when $f_x = f_y = f_{xx} = f_{yy} = f_{xy}
-= 0$. A sample similarity transformation and computed signature is shown in
-Fig.~\ref{fig:Sim2}
-\begin{figure}
-\centering
-\includegraphics[width=.45\textwidth]{Figs/f_transformed_Sim2.png}
-\includegraphics[width=.45\textwidth]{Figs/Sim2_signature.png}
-\caption{A sample $\text{Sim}(2)$ Transform and 3D signature.}
-\label{fig:Sim2}
 \end{figure}
@@
 
-Some of these partial transvectants appear in signatures
-from other transformation groups, so for future reference, let
-\begin{equation}
-    \label{eq:cde}
-    \begin{aligned}
-        C &= f_{xx}f_{yy}-f_{xy}^2, \\
-        D &= f_x^2f_{yy} - 2f_xf_yf_{xy} + f_{xx}f_y^2, \\
-        E &= f_{xxx}f_y^3 - 3f_{xxy}f_xf_y^2 + 3f_{xyy}f_x^2f_y -
-        f_{yyy}f_x^3.
-    \end{aligned}
-\end{equation}
-
 \subsection{Signatures of $SA(2)$ and $A(2)$}
 
-The action of the affine group $A(2)$ arises in images as the motion of
-planar objects in images taken from a distant camera. Recall that
-invariants of a supergroup are automatically invariants of any of its
-subgroups. For example, invariants of $A(2)$ are automatically invariants
-of $SA(2)$, but not necessarily vice versa. Any of the partial
-transvectants found in Tables~\ref{tab:transvectants1}
-and~\ref{tab:transvectants2} are invariants of $SA(2)$ (as the determinant
-is $1$), but only up to scale factor ($\det A^{-r}$) of $A(2)$.
-
-Hence, we can form a signature for $SA(2)$ by choosing any combination of
-partial transvectants. We choose a signature with three components so that
-it can be visualised as a three-dimensional surface; note that this will
-not be complete and may well have a very large bad set. For example, we can
-choose the function value together with the $C, D$ from \eqref{eq:cde}
-to form the signature.
-
-\begin{equation}
-    \label{eq:SA2signature}
-    \mathcal{I}_{SA(2)}(f) = \left(f, C, D \right).
-\end{equation}
+The action of the affine group $A(2)$ arises as the motions of planar objects far from a camera.
+Recall that invariants of a supergroup are automatically invariants of any of its subgroups.
+For example, invariants of $A(2)$ are automatically invariants of $SA(2)$, but not necessarily vice versa.
+Any of the partial transvectants found in Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} are invariants of $SA(2)$ (as the determinant is $1$), but only up to scale factor ($\det A^{-r}$) of $A(2)$.
+
+Hence, we can form a signature for $SA(2)$ by choosing any combination of partial transvectants.
+We choose a signature with three components so that it can be visualised as a three-dimensional surface; note that this will not be complete and may well have a very large bad set.
+For example, we can choose the function value together with the first two partial transvectants to form the signature:
+\begin{equation*}
+    \left(f, f_{xx}f_{yy}-f_{xy}^2, f_x^2f_{yy} - 2f_xf_yf_{xy} + f_{xx}f_y^2\right).
+\end{equation*}
+
 We will subject our test image to the special affine transformation:
 \begin{equation*}
-\mathbf{x} \mapsto \frac{1}{1.22}\begin{bmatrix} 0.7 & 1.1 \\ -0.6 & 0.8 \end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
+\mathbf{x} \mapsto \frac{1}{1.1}\begin{bmatrix} 0.6875 & 1.1 \\ -0.6 & 0.8 \end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
 \end{equation*}
+
 Fig.~\ref{fig:SA2} shows the signature of our test image under this transformation.
@@
 \subsubsection{Moving on to A(2), \ldots}
-
-For $A(2)$ the weight of the partial transvectants prevents them from being
-invariants. There are two options to create a signature. One is to select
-ratios of partial transvectants, similar to as discussed in
-Section~\ref{sec:Sim2}. It is then beneficial to choose the
-numerator and denominator so that they have different critical points,
-which can be achieved by adding together partial transvectants of the same
-weight as appropriate. Instead, we employ the same normalisation strategy
-as previously, projecting the weight four relative invariants $(C^2, D^2,
-E)$ onto the unit hypersphere and multiplying by $f$. In this way, our
-signature is
-\begin{equation}
-    \label{eq:A2signature}
-    \mathcal{I}_{A(2)} = \frac{f}{\sqrt{C^4 + D^4 + E^2}}(C^2, D^2, E)
-\end{equation}
-
-We will subject our test image to the special affine transformation:
-\begin{equation*}
-\mathbf{x} \mapsto \begin{bmatrix} 0.7 & 1.1 \\ -0.6 & 0.8
-\end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
-\end{equation*}
-Fig.~\ref{fig:A2} shows the signature of our test image under this transformation.
+Using the same function as an example, 
 \begin{figure}
@@
 \end{figure}
+
+For $A(2)$ the weight of the partial transvectants prevents them from being invariants.
+There are two options to create a signature.
+One is to select ratios of partial transvectants.
+It is then beneficial to choose the numerator and denominator so that they have different critical points, which can be achieved by adding together partial transvectants of the same weight as appropriate.
+Instead, we normalise the partial transvectants by choosing only those where all components have the same weight and projecting them onto the unit hypersphere.
+By multiplying these by the function (which takes values between 0 and 1) we create a signature enclosed by the unit hypersphere.
+An example is shown in Figure~\ref{fig:A2}.
 
@@
 \subsection{The Special Euclidean Group SE(2)}
-\label{sec:SE2}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=.45\textwidth]{Figs/f_transformed_SE2.png}
-\includegraphics[width=.45\textwidth]{Figs/SE2_signature.png}
-\caption{A sample $SE(2)$ Transform and 3D signature.}
-\label{fig:SE2}
-\end{figure}
 \subsection{The Euclidean Group E(2)}
@@
 
-Functions of these invariants are invariants or relative invariants for many groups that contain $E(2)$, such as those that we have considered in this paper. Syzygies.
-
-not intensity transforms
+Functions of these invariants are invariants or relative invariants for many groups that contain $E(2)$, such as those that we have considered in this paper.
 

### 2020-11-18 paper/newpaper.tex
All lit

@@
 \section{Introduction}
-\todo[inline]{
-Literature
-Discussion -- syzygies
-
-Sim(2) by contraction
-A(2) by transvectant
-Check signatures for Mobius etc.
-}
-
 The appearance of a fixed object in a set of images can vary markedly depending upon such variables as pose and position relative to the camera, even though the object itself does not change.
@@
 \subsection{Relevant Literature}
-
-Classical invariants
 

### 2021-02-10 paper/newpaper.tex
Some more intro material on signatures etc, 3D, and why we can't do completeness

@@
 We use the resulting invariants to construct practical sets to form three-dimensional invariant signatures.
-These signatures are not necessarily complete: the image cannot always be reconstructed uniquely up to transformation, but they are plottable, and depend at worst on third derivatives, although more channels of information, such as colour images, can reduce the highest order to derivate needed in some cases.
+These signatures are not necessarily complete: the image cannot always be reconstructed uniquely up to transformation, but they are plottable, and depend at worst on third derivatives, although more channels of information, such as colour images, can reduce the highest order of derivative needed in some cases.
 We demonstrate the invariant signatures for each transformation group based on a simple smooth image.
@@
 
-The introduction of an invariant signature reduces the recognition problem to one of comparing the higher-dimensional signatures (typically the signatures need to be at least three dimensional for planar images) that encode the desired self-equivalences.
-In this paper we introduce the mathematical considerations necessary to construct invariant signatures to the planar Lie groups (and some infinite-dimensional, pseudo-Lie groups too) that can transform 2D images.
-As we shall show, the lattice structure of the set of groups influences the relationship between the sets of invariants for the different groups.
-We provide sample signature sets for the various groups we consider, and examples of the appearance of those signatures for transformations of a simple, smooth image, but do not consider the question of a complete practical implementation.
-We do not consider the classification of the signatures, for which either a standard image recognition algorithm can be used (see, e.g.,~\cite{Zhang20} for a survey), or a matching method such as~\cite{UsCurrents} can be used.
+A greyscale image can be viewed as a two-dimensional manifold embedded in a
+three dimensional ambient space, with coordinates $(x, y, f(x,y))$. A
+signature has coordinates $\mathcal{I}(f) = (I_1, I_2, \ldots, I_m)$ which
+are functions of the derivatives of $f(x, y))$, and will therefore be a
+two-dimensional manifold embedded in $\mathbb{R}^m$. Under a change of
+coordinates $(x, y) \mapsto (\bar{x}, \bar{y})$ induced by a group action,
+the signature of the corresponding image $\bar{f}(\bar{x}, \bar{y}) = f(x, y)$
+will have the same signature.
+
+The introduction of an invariant signature reduces the recognition problem to
+one of comparing the signatures in a higher-dimensional space that encode the
+desired self-equivalences. For greyscale images, it is natural to seek
+signatures with three coordinates as $\mathbb{R}^3$ is the smallest space in
+which the signature surfaces can reside. In this paper we introduce the
+mathematical considerations necessary to construct invariant signatures to
+the planar Lie groups (and some infinite-dimensional, pseudo-Lie groups too)
+that can transform 2D images. As we shall show, the lattice structure of the
+set of groups influences the relationship between the sets of invariants for
+the different groups. We provide sample signature sets for the various groups
+we consider, and examples of the appearance of those signatures for
+transformations of a simple, smooth image, but do not consider the question
+of a complete practical implementation. We do not consider the classification
+of the signatures, for which either a standard image recognition algorithm
+can be used (see, e.g.,~\cite{Zhang20} for a survey), or a matching method
+such as~\cite{UsCurrents} can be used.
 
 In order for the invariant signatures to be useful to identify similarity in images, there are two key considerations: they must vary continuously with respect to the image, either for all smooth images or for all except a set of sufficiently high codimension, and they must be robust with respect to occlusions, where one object obscures some part of another.
-Thse constraints are essential if the signature is to be used to detect similarity of images, but the first fails for the rational invariants found in the literature.
+These constraints are essential if the signature is to be used to detect similarity of images, but the first fails for the rational invariants found in the literature.
 Such considerations lead one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology.
@@
 Ideally, an invariant signature would be complete, so that the image is exactly determined by the signature up to a transformation, and two objects share a signature if and only if they differ only by a transformation from $\mathcal{G}$.
-However, this often requires signatures in many dimensions, and potentially also more derivatives of the image.
-For many applications an incomplete signature is sufficient, and is what we consider here.
+However there are some pathological scenarios that occur regularly in images, particularly that flat regions of images collapse down to single points in the signature as all of the derivatives are zero in these regions.
+So images that are otherwise similar apart from the size of one of these regions cannot be distinguished between.
+For this reason, we do not pursue complete signatures, for many applications an incomplete signature is sufficient, and is what we consider here.
 See, e.g.,~\cite{UsMobius} and references therein for more discussion about the desirable properties of a set of invariants for image and curve analysis.
@@
 
-An $m$-dimensional signature set is the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e., the set $\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$.
-See Section~\ref{sec:T2} for a basic example.
-A signature set is complete for $f$ if it determines $f$ up to transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.
-If the signature is not complete, then there will be a \emph{bad set} of images that cannot be differentiated between.
+An signature set is the image of $m$ invariants
+$\mathcal{I}=(I_1,I_2,\dots,I_m)$. For simplicity of notation we will write
+$\mathcal{I}(f)$ with the understanding that each signature component is
+actually acting on the jet space $J^d(f, \Omega, k)$. The signature
+$\mathcal{I}(f) \subset \mathbb{R}^m$. See Section~\ref{sec:T2} for a basic
+example. A signature set is complete for $f$ if it determines $f$ up to
+transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde
+f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a
+transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$
+and $\tilde \Omega = \varphi(\Omega)$. If the signature is not complete, then
+there will be a \emph{bad set} of images that cannot be differentiated
+between.
 
@@
 %translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
-\subsection{Example signatures}
-
+\subsection{Test image}
 In this paper our aim is develop the mathematical underpinnings of

### 2021-02-16 paper/newpaper.tex
Updates

@@
 \begin{abstract}
-Changes in viewpoint, such as camera motion, impose transformations on the objects in an image, and these transformations will differ for objects at different positions relativele to the camera.
+Changes in viewpoint, such as camera motion, impose transformations on the objects in an image, and these transformations will differ for objects at different positions relative to the camera.
 Typically these transformations will be elements of planar Lie groups.
 While there have been significant advances in object recognition using machine learning in recent years, the question of how to recognise an object in an image as its appearance varies through camera motion and similar effects remains open.
-We consider how differential invariant signatures can be derived for each of the transformation groups, and how the underlying invariances reflect the group-subgroup structure of the transformation groups.
+We demonstrate how differential invariant signatures can be derived for each of the transformation groups, and how the underlying invariances reflect the group-subgroup structure of the transformation groups.
 
@@
 We demonstrate the invariant signatures for each transformation group based on a simple smooth image.
-A full consideration of how these signatures could be used in practice will require effective methods to numerically approximate derivatives effectively for images.
+A full consideration of how these signatures could be used in practice will require effective methods to numerically approximate derivatives for images.
 \end{abstract}
@@
 \begin{AMS}
-
+65D18, 53A55, 68U10
 \end{AMS}
@@
 The appearance of a fixed object in a set of images can vary markedly depending upon such variables as pose and position relative to the camera, even though the object itself does not change.
-This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera and any fixed background.
+This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera against a fixed background.
 The appearance of each individual object will then vary independently as a constant camera motion or other such transformation is applied.
@@
 If the space of objects is denoted $M$ and the appearance transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$.
-One way to achieve this is by transforming all objects to match a chosen target object by registration (the transformation of the appearance of one shape to match another, typically by gradient descent on a matching function, see e.g.~\cite{Modersitzki03}).
-Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{Kendall1989} will place all of the shapes into the reference frame of one template example.
-However, analysis on these quotient spaces is rarely simple (see e.g.,~\cite{RiemannianStats} for a basic primer), and if one is interested in the object, and not the transformation, then it necessitates a lot of computational work for relatively little benefit.
+One way to achieve this is by transforming all objects to match a chosen target object by registration (the transformation of the appearance of one shape to match another, typically by gradient descent on a matching function, see e.g.,~\citep{Modersitzki03}).
+For example, for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\citep{Kendall1989} will place all of the shapes into the reference frame of one template example.
+However, analysis on these quotient spaces is rarely simple (see e.g.,~\citet{RiemannianStats} for a basic primer), and if one is interested in the object, and not the transformation, then it necessitates a lot of computational work for relatively little benefit.
+The alternative approach, of showing examples of each object after applying sufficiently many transformations that the classifier can learn to recognise the object after any group transformation, inevitably scales extremely badly.
 
 An alternative option is to seek $\mathcal{G}$-invariant functions on $M$.
-Mathematical invariants provide a useful way to identify sets of objects that are the same up to some equivalence relation, since the functions are constant for objects in the same equivalence class.
-For a group $\mathcal{G}$, orbits of the group form the equivalence classes.
+Mathematical invariants provide a useful way to identify sets of objects that are the same up to some equivalence relation, since the functions are constant for objects in the same equivalence class (orbits of the group).
 For images, rather than considering the image of the object, one constructs an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group.
-This has been considered extensively by Olver and co-authors for the case of outlines of objects~\cite{Calabi1998,Hoff2013}.
-In this paper we consider the case of signatures for images rather than outlines of curves under a variety of transformation groups.
-
-A greyscale image can be viewed as a two-dimensional manifold embedded in a
-three dimensional ambient space, with coordinates $(x, y, f(x,y))$. A
-signature has coordinates $\mathcal{I}(f) = (I_1, I_2, \ldots, I_m)$ which
-are functions of the derivatives of $f(x, y))$, and will therefore be a
-two-dimensional manifold embedded in $\mathbb{R}^m$. Under a change of
-coordinates $(x, y) \mapsto (\bar{x}, \bar{y})$ induced by a group action,
-the signature of the corresponding image $\bar{f}(\bar{x}, \bar{y}) = f(x, y)$
-will have the same signature.
-
-The introduction of an invariant signature reduces the recognition problem to
-one of comparing the signatures in a higher-dimensional space that encode the
-desired self-equivalences. For greyscale images, it is natural to seek
-signatures with three coordinates as $\mathbb{R}^3$ is the smallest space in
-which the signature surfaces can reside. In this paper we introduce the
-mathematical considerations necessary to construct invariant signatures to
-the planar Lie groups (and some infinite-dimensional, pseudo-Lie groups too)
-that can transform 2D images. As we shall show, the lattice structure of the
-set of groups influences the relationship between the sets of invariants for
-the different groups. We provide sample signature sets for the various groups
-we consider, and examples of the appearance of those signatures for
-transformations of a simple, smooth image, but do not consider the question
-of a complete practical implementation. We do not consider the classification
-of the signatures, for which either a standard image recognition algorithm
-can be used (see, e.g.,~\cite{Zhang20} for a survey), or a matching method
-such as~\cite{UsCurrents} can be used.
-
-In order for the invariant signatures to be useful to identify similarity in images, there are two key considerations: they must vary continuously with respect to the image, either for all smooth images or for all except a set of sufficiently high codimension, and they must be robust with respect to occlusions, where one object obscures some part of another.
+This has been considered extensively by Olver and co-authors for the case of outlines of objects~\citep{Calabi1998,Hoff2013}.
+We extend this by considering the case of signatures for images rather than outlines of curves under a variety of transformation groups of relevance to image analysis.
+
+A greyscale image can be viewed as a two-dimensional manifold embedded in a three dimensional ambient space, with coordinates $(x, y, f(x,y))$.
+A signature $\mathcal{I}(f) \in \mathbb{R}^m$ has coordinates $\mathcal{I}(f) = (I_1, I_2, \ldots, I_m)$, where each $I_i$ is a function of $f(x, y))$ and its derivatives, and will therefore be a two-dimensional manifold embedded in $\mathbb{R}^m$.
+Under a change of coordinates $(x, y) \mapsto (\bar{x}, \bar{y})$ induced by a group action, the signatures of the original image and transformed version $\bar{f}(\bar{x}, \bar{y}) = f(x, y)$ will be the same.
+The introduction of an invariant signature reduces the object recognition problem modulo some transformation group to one of comparing the signatures of the objects, rather than the images themselves.
+We do not consider the question of classification further in this paper; a standard image recognition algorithm can be used (see, e.g.,~\citet{Zhang20} for a survey), or a matching method such as~\citet{UsCurrents} can be used.
+
+Ideally, an invariant signature would be complete, so that the image is exactly determined by the signature up to a transformation, and two objects share a signature if and only if they differ only by a transformation from $\mathcal{G}$.
+However, there are some pathological scenarios that occur regularly in images, particularly that flat regions of images collapse down to single points in the signature (as all of the derivatives are zero in these regions).
+Then images that are otherwise similar (apart from the size of one of these regions) cannot be distinguished.
+However, the number of dimensions $m$ of the ambient manifold can increase markedly for complete signatures, increasing the computational cost and making it impossible to visualise the signature surface.
+For many applications an incomplete signature is sufficient, and is what we consider here, favouring signatures in three coordinates, since for greyscale images, $\mathbb{R}^3$ is the smallest space in which the signature surfaces can reside.
+If the signature is not complete, then there will be a `bad set' of images that cannot be distinguished from each other.
+The codimension of the bad set is defined as the difference between the dimensionalities of the whole space and of the bad set.
+The codimension should ideally be large, meaning that the dimension of the bad set would be small.
+
+In addition to a bad set of high codimension, in order for the invariant signatures to be useful to identify similarity in images, there are two other key considerations: they must vary continuously with respect to the image, and they must be robust with respect to occlusions, where one object obscures some part of another.
 These constraints are essential if the signature is to be used to detect similarity of images, but the first fails for the rational invariants found in the literature.
@@
 The disadvantage of such invariants, as we shall discuss, is the need to compute several orders of spatial derivative of the image.
-
-Ideally, an invariant signature would be complete, so that the image is exactly determined by the signature up to a transformation, and two objects share a signature if and only if they differ only by a transformation from $\mathcal{G}$.
-However there are some pathological scenarios that occur regularly in images, particularly that flat regions of images collapse down to single points in the signature as all of the derivatives are zero in these regions.
-So images that are otherwise similar apart from the size of one of these regions cannot be distinguished between.
-For this reason, we do not pursue complete signatures, for many applications an incomplete signature is sufficient, and is what we consider here.
-See, e.g.,~\cite{UsMobius} and references therein for more discussion about the desirable properties of a set of invariants for image and curve analysis.
-
-In this paper we investigate differential invariant signatures for images and parts of images under planar spatial transformations, primarily Lie groups, for both greyscale and colour images.
-The set of groups that we consider are shown as a lattice in Figure~\ref{fig:lattice}, where the size of the groups decrease as down the page, and the arrows denote the subgroup relationship.
+See~\citet{UsMobius} and references therein for more discussion about the desirable properties of a set of invariants for image and curve analysis.
+
+In this paper our aim is develop the mathematical underpinnings of constructing differential invariant signatures for images under the action of planar Lie groups, and to summarise the impediments to a practical implementation, including the number of derivatives required.
+We demonstrate three distinct methods of computing differential invariants: by tensor contraction, using the theory of transvectants, and via the method of moving frames, applying the methods to a variety of the planar Lie groups, providing sample signature sets for the various groups we consider, together with an example of a sample signature surface based on a random transformation of a simple, smooth image.
+
+The set of groups that we consider are shown as a lattice in Fig.~\ref{fig:lattice}, where the size of the groups decrease down the page, and the arrows denote the subgroup relationship.
 There is an important relationship between a group and its subgroups for invariants, which is that invariants of a group are automatically invariants of its subgroups.
-This means that differentiating between them requires care.
-
-The remainder of this introductory section provides a description of the notation that we use in this paper, followed by a summary of relevant work on invariants.
+This means that care is needed to distinguish between the two, with further invariants that are known not to be invariant in the supergroup included.
+The finite-dimensional groups in this lattice were chosen because they are the only planar Lie groups that include translation and have locally primitive algebras (that is, for any open subset of the plane, there is no one-dimensional foliation that is left invariant by the action of the corresponding group~\citep{Gonzalez-Lopez90}).
+This makes them the groups most directly relevant to image transformations.
+The infinite-dimensional examples are likewise those most likely to be of interest for image transformation, in particular the full diffeomorphism group, which is commonly used for image registration for medical images, see e.g.,~\citet{YounesBook}.
+
+%We next provide a description of the notation that we use in this paper, followed by a summary of relevant work on invariants.
 We also introduce the way that we will present examples of the signatures for the various groups we consider.
 Following this, in the next three sections we describe three distinct methods of computing differential invariants: by tensor contraction, using the theory of transvectants, and via the method of moving frames, applying the methods to a variety of the planar Lie groups.
-We consider the difference that colour images make in Section~\ref{sec:colour}, and then discuss the number of derivatives required and the effect this has on the practicality of the method.
+We conclude by considering the practical issues of implementation, including the number of derivatives required and the effect this has on the practicality of the method.
 
@@
 \begin{tikzpicture}[node distance=2cm]
-\node(C1) [] {Diff};
+\node(C1) [] {$\mathrm{Diff}$};
 \node(C2) [below left of=C1] {$\mathrm{Diff}_{\mathrm{vol}}$};
@@
 
+\section{Preliminaries}
+
 \subsection{Concepts and Notation}
@@
 A transformation $\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) = (f\circ\varphi^{-1},\varphi(\Omega),k)$.
-For many of our examples we consider greyscale images, so $k=1$, although we will discuss colour images in Section~\ref{sec:colour}.
+We mostly consider greyscale images, so $k=1$.
 Also, since we work locally, we will usually omit the domain $\Omega$.
 
-In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$ via the jet space~\cite{OlverEIS}.
+In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$ via the jet space~\citep{OlverEIS}.
 The $d$-th order jet space $J^d$ consists of the function itself and the set of all partial derivatives of the function up to order $d$.
@@
 $\mathcal{I}=(I_1,I_2,\dots,I_m)$. For simplicity of notation we will write
-$\mathcal{I}(f)$ with the understanding that each signature component is
-actually acting on the jet space $J^d(f, \Omega, k)$. The signature
-$\mathcal{I}(f) \subset \mathbb{R}^m$. See Section~\ref{sec:T2} for a basic
+$\mathcal{I}(f) \subset \mathbb{R}^m$ with the understanding that each signature component is
+actually acting on the jet space $J^d(f, \Omega, k)$. See Section~\ref{sec:T2} for a basic
 example. A signature set is complete for $f$ if it determines $f$ up to
@@
 transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$
-and $\tilde \Omega = \varphi(\Omega)$. If the signature is not complete, then
-there will be a \emph{bad set} of images that cannot be differentiated
-between.
-
-The methods we use to construct the invariants, particularly the moving frames, produces invariants that, when considered alone, are singular at certain points (for example, critical points).
+and $\tilde \Omega = \varphi(\Omega)$.
+
+The methods we use to construct the invariants, particularly the moving frames, produces invariants that, when considered alone, are singular at points (such as critical points).
 However, in all groups considered the invariants are rational functions of the derivatives of the function.
-Moreover, the denominators of these functions are powers of each other, and so it is possible to clear them, thus removing these singular points by a projection technique that will be introduced in Section~\ref{sec:Sim2}.
+Moreover, the denominators of these functions are powers of each other, and so it is possible to clear them by a projection technique that will be introduced in Section~\ref{sec:Sim2}.
 
 For the case of two-dimensional greyscale images it is often convenient to work in coordinates.
-In this case the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$ is given by:
+In this case the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$ is given by (where $f$ and $\mathbf{x}$ denote the original image and coordinates, and $\bar{f}$ and $\bar{\mathbf{x}}$ the transformed versions):
 \begin{equation}\label{eq:transformation}
@@
 \subsection{Test image}
-In this paper our aim is develop the mathematical underpinnings of
-constructing differential invariant signatures for images under the action
-of planar Lie groups. However, as we develop the signature for each group,
-we will provide an example of the type of surface that the signature
-defines. Note that these will generally be three-dimensional representation
-of the planar image.
-
-The image we use is defined on $[-1,1] \times [-1,1]$ to be:
+
+For each signature set that we derive, it is informative to see an example signature of the kind of surface that is defined, 
+normally a two-dimensional surface in three-dimensions.  We will apply a small random transformation from 
+the relevant group to a single continuous image and plot the signature before and after this transformation has been applied.
+This is an aid to understanding rather than any form of demonstration of the robustness of our signature sets.
+
+The image we use is a continuous function (thus avoiding numerical issues in the approximation 
+of derivatives) defined on $[-1,1] \times [-1,1]$ as:
 
@@
 
-The function is depicted as a greyscale image in Figure~\ref{fig:function}.
-On the left the image itself is shown, while on the right a version with a
-regular grid superimposed is given. We will use this function throughout,
-using the grid to help visualise both the transformation and how the image
+The function is depicted as a greyscale image in Fig.~\ref{fig:function}.
+We will use this function throughout, using the grid on the right of the figure to help visualise both the transformation and how the image
 is mapped into the three-dimensional signature surface.
@@
   \includegraphics[width=.45\textwidth]{Figs/function_scanlines}
-  \caption{The test function used in this document, from
-  Eq.~\eqref{eq:function}.}\label{fig:function}
+  \caption{The test function used as an image, defined in Eq.~\eqref{eq:function}.
+On the left the image itself is shown, while on the right a version with a
+regular grid superimposed is given. 
+}\label{fig:function}
 \end{figure}
@@
 three-dimensional space, and the two images will produce the same surface,
-which we call the signature, $\mathcal{I}(f)(x, y) = \left(I_1, I_2,
+the signature, $\mathcal{I}(f)(x, y) = \left(I_1, I_2,
 I_3\right)$ where $I_1 = f, I_2 = f_x, I_3 = f_y$.
 
-Figure~\ref{fig:T2} shows (a) the original image, (b) the translated image
+Fig.~\ref{fig:T2} shows (a) the original image, (b) the translated image
 under the transformation $(x,y) \mapsto (x + 0.1, y - 0.2)$, (c) the
 signature of one of them, (d) the superimposed pair of signatures. The
-yellow lines in (c) correspond to where the yellow grid from (a) has been
+yellow lines in (c) correspond to places where the yellow grid from (a) has been
 mapped to on the signature surface. The parts of the surface where the mesh
@@
   \end{tabular}
-  \caption{(a), (b) The image before and after the T(2) transformation $(x,
+  \caption{(a), (b) The image before and after the $T(2)$ transformation $(x,
   y) \mapsto (x + 0.1, y - 0.2)$. (c) the signature of the
-  image (before translation). (d) the signature after the
+  image (before translation). (d) the signatures before and after the
   translation superimposed.}\label{fig:T2}
@@
 
-The theory of invariants has a rich mathematical history, starting from invariants of forms~\cite{Cayley}, where the invariants are polynomials in the coefficients of the forms, see e.g.,~\cite{OlverCIT,Kraft2002} for an overview.
-Geometric considerations and differential invariants followed fairly quickly~\cite{Veblen1872,Tresse1894,Bouton1898,Patterson1928}, particularly because they enabled the classification of differential equations into equivalence classes~\cite{Lie1884,Littlewood44, Cartan52}.
-More recently, this has extended, primarily by Olver and collaborators, see e.g.,~\cite{OlverCIT} and~\cite{OlverEIS} for summaries.
-
-There has been a long-standing interest in constructing invariants for image recognition and pattern analysis, see e.g.,~\cite{Mundy1992} and~\cite{Wood1996}.
-This was set in the context of Lie's invariants in~\cite{VanGool1995}, where the concept of a joint (or semi-) differential invariant (an invariant that acts on the joint action of the transformation group, see~\cite{Fels1997,Olver2013}) was introduced~\cite{VanGool1992}; see also~\cite{Hubert2009}.
+The theory of invariants has a rich mathematical history, starting from invariants of forms~\citep{Cayley}, where the invariants are polynomials in the coefficients of the forms, see e.g.,~\citet{OlverCIT,Kraft2002} for an overview.
+Geometric considerations and differential invariants followed fairly quickly~\citep{Veblen1872,Tresse1894,Bouton1898,Patterson1928}, particularly because they enabled the classification of differential equations into equivalence classes~\citep{Lie1884,Littlewood44, Cartan52}.
+More recently, this has been extended, primarily by Olver and collaborators, see e.g.,~\citet{OlverCIT} and~\citet{OlverEIS} for summaries.
+
+There has been a long-standing interest in constructing invariants for image recognition and pattern analysis, see e.g.,~\citet{Mundy1992} and~\citet{Wood1996}.
+This was set in the context of Lie's invariants by~\citet{VanGool1995}, where the concept of a joint (or semi-) differential invariant (an invariant that acts on the joint action of the transformation group, see~\citet{Fels1997,Olver2013}) was introduced~\citep{VanGool1992}; see also~\citet{Hubert2009}.
 
 A variety of function spaces have allowed for the creation of different sets of invariants for particular groups.
-For the Euclidean group, the Fourier transform provides a useful tool~\cite{Ghorbel1994,Turski2006,Smach2007,Gauthier2008}, and this can be extended to the affine group using the Fourier-Mellin transform~\cite{Reddy1996,Zhang2019} and the bispectrum~\cite{Kakarala2009,Negrinho2013}.
-Alternatively, integral invariants~\cite{Manay2006,Feng2010} and geometric moments can be computed.
-For the similarity group applied to images the original reference is \cite{Hu1962}, but see also~\cite{Hickman2011} for affine transformations, \cite{Flusser2009} for an implicit representation, and \cite{Papakostas2013} for their use in a binary pattern for image recognition, which is somewhat related to the invariant features such as SURF~\cite{SURF}.
+For the Euclidean group, the Fourier transform provides a useful tool~\citep{Ghorbel1994,Turski2006,Smach2007,Gauthier2008}, and this can be extended to the affine group using the Fourier-Mellin transform~\citep{Reddy1996,Zhang2019} and the bispectrum~\citep{Kakarala2009,Negrinho2013}.
+Alternatively, integral invariants~\citep{Manay2006,Feng2010} and geometric moments can be computed.
+For the similarity group applied to images the original reference is \citet{Hu1962}, but see also~\citet{Hickman2011} for affine transformations, \citet{Flusser2009} for an implicit representation, and \citet{Papakostas2013} for their use in a binary pattern for image recognition, which is somewhat related to the invariant features such as SURF~\citep{SURF}.
 
 The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models.
-Invariants for this group have been computing using points~\cite{Gros1992,Suk2000}, geometric moments~\cite{Suk2004}, curvature~\cite{Hann2002a}, and differential and joint invariants~\cite{Hubert2007,Arora2009,Kogan2014,Li19}.
-
-Although there are computational challenges regarding the numerical approximation of derivatives on images, the fact that differential invariants are robust to occlusion, cheap to compute, and well-behaved with respect to small changes in the image, has made them popular for researchers in image analysis~\cite{Florack1993}.
-Two particular tools have been key to this: Cartan's moving frame~\cite{Cartan35} (see Section~\ref{sec:movingframes}), and which was used to construct image invariants as early as 1994 in \cite{Faugeras1994}, and the concept of an image signature built from a set of invariants~\cite{Calabi1998}.
-An algorithm to compute differential and joint invariants and determine complete signature sets is described in \cite{Olver2005,Olver2007}.
+Invariants for this group have been computing using points~\citep{Gros1992,Suk2000}, geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and differential and joint invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19}.
+
+Although there are computational challenges regarding the numerical approximation of derivatives on images, the fact that differential invariants are robust to occlusion, cheap to compute, and well-behaved with respect to small changes in the image, has made them popular for researchers in image analysis~\citep{Florack1993}.
+Two particular tools have been key to this: Cartan's moving frame~\citep{Cartan35} (see Section~\ref{sec:movingframes}), and which was used to construct image invariants as early as 1994 by \citet{Faugeras1994}, and the concept of an image signature built from a set of invariants~\citep{Calabi1998}.
+An algorithm to compute differential and joint invariants and determine complete signature sets is described by \citet{Olver2005,Olver2007}.
 The entire set of invariants is computed using the method of moving frames and then the signature set of a maximal set of functionally independent invariants is identified.
@@
   I_3 &= f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
-  I_4 &= f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}
+  I_4 &= f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}.
 \end{aligned}
@@
 $E(2)$ and other groups using the method of moving frames. We can form a
-signature from any three of these invariants \eqref{eq:e2tensor}, we choose for
-simplicity our signature to be 
+signature from any three of the invariants in Eq.~\eqref{eq:e2tensor}, for simplicity we choose 
+our signature to be:
 \begin{equation}
     \label{eq:e2signature}
-    \mathcal{I}_{E(2)} = (I_0, I_1, I_2)
-\end{equation}.  
+    \mathcal{I}_{E(2)} = (I_0, I_1, I_2) .
+\end{equation}  
 A sample $E(2)$ transformation is depicted in Fig.~\ref{fig:E2} with its corresponding
@@
 We will defer discussion of the Special Euclidean group (which excludes
-reflections) until Section~\ref{sec:SE2} where invariants naturally arise
+reflections) until Section~\ref{sec:SE2}, where suitable invariants naturally arise
 from the method of moving frames.
@@
 \label{sec:Sim2}
-The similarity group $\text{Sim}(2)$ consists transformations of the form
+The similarity group $\text{Sim}(2)$ consists of transformations of the form
 $\bar{\mathbf{x}} = \varphi(\mathbf{x}) = sU\mathbf{x} + \mathbf{t}$, where $U^TU = I$ and $s
@@
 Under similarity transformations, the Euclidean invariants become
-/emph{relative invariants}. Each derivative introduces a multiple of $s$ to
+\emph{relative invariants}, i.e., each derivative introduces a multiple of $s$ to
 each invariant. For example, $\bar{f}_{\bar x}^2 + \bar{f}_{\bar y}^2 =
@@
 y}^2 + \bar{f}_{\bar y \bar y} = s^4 (f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2$). We
-refer to the power of $s$ as the weight of the transformation.
+refer to the power of $s$ as the weight of the transformation. The concept of a 
+relative invariant will be important in the rest of this paper. It follows the 
+definition given here, except that the function weighting the invariant is more 
+general, see~\citet{Fels1997} for more details. In contrast to that paper, 
+we will continue to use the term weight to represent the power to which the function is raised.
 
@@
 ratio of two weight-2 relative invariants and is hence a similarity
-invariant. However this invariant is singular whenever $f_{xx} + f_{yy} =
-0$ which is a codimension-0 phenomenon for images.
-
-A better approach is to take three invariants of the same weight, we'll
-take $I_1^2$, $I_2^2$, and $I_3$ from \eqref{eq:e2tensor}, all of which are
-weight $4$, and project them onto the unit sphere. This can then be
-multiplied by $I_0 = f$ to form a signature surface. So our signature is
-defined by
+invariant. However, this invariant is singular whenever $f_{xx} + f_{yy} =
+0$, which is a codimension 0 phenomenon for images.
+
+A better approach is to take three invariants of the same weight.
+Taking $I_1^2$, $I_2^2$, and $I_3$ from \eqref{eq:e2tensor}, all of which are
+weight $4$, they can be projected on to the unit sphere, which can be
+multiplied by $I_0 = f$ to form a signature surface. This signature is
+defined by:
 \begin{equation}
@@
 \mathcal{I}_{\text{Sim(2)}}(f) = \frac{f}{\sqrt{I_1^4 + I_2^4 + I_3^2}}(I_1^2, I_2^2,
-        I_3)
+        I_3) .
 \end{equation}
@@
 = 0$. A sample similarity transformation and computed signature is shown in
-Fig.~\ref{fig:Sim2}
+Fig.~\ref{fig:Sim2}.
+
 \begin{figure}
@@
 
-Another way to compute invariants is to compare the simultaneous action of a group element on separate copies of the underlying space (here, $\mathbb{R}^2$).
-By identifying these spaces with each other it is possible to construct a function known as a transvectant that is invariant up to a scale factor (a \emph{relative invariant}) to that group action.
+Another way to compute invariants is to compare the simultaneous action of a group element on separate copies of the underlying space (for planar images, $\mathbb{R}^2$).
+By identifying these spaces with each other it is possible to construct a function known as a transvectant that is a relative invariant to that group action.
 
 We will demonstrate this for the affine group $A(2)$ and its subgroup
-$SA(2)$ where, following the treatment in~\cite{OlverCIT}, this leads to
-Cayley's Omega Process~\cite{Cayley1846}.
+$SA(2)$ where, following the treatment by~\citet{OlverCIT}, this leads to
+Cayley's Omega Process~\citep{Cayley1846}.
 
@@
 Under the above affine transformation, $\Omega_{ij} \mapsto (\det A)^{-1}
-\Omega_{ij}$, and is thus a relative invariant. Note that $(\det A)^{-1}$ has no dependence on the coordinates.
+\Omega_{ij}$, and is therefore a relative invariant. Note that $(\det A)^{-1}$ has no dependence on the coordinates.
 The Omega Process can be applied to products of pairs of smooth functions as follows,
@@
 
-Identifying $x_i = x_j = x, y_i = y_j = y$ gives us functions of $x$ and $y$
+Identifying $x_i = x_j = x, y_i = y_j = y$ gives functions of $x$ and $y$
 that only vary by a scaling factor of $(\det A)^{-1}$ when $\mathbf{x}$ is
@@
 
-This can be generalised to $n$ functions $f^{(1)}(x_1, y_1), \ldots, f^{(n)}(x_n, y_n)$ and $r$-th order~\cite{OlverEIS} to define a partial transvectant as:
+This can be generalised to $n$ functions $f^{(1)}(x_1, y_1), \ldots, f^{(n)}(x_n, y_n)$ and $r$-th order~\citep{OlverEIS} to define a partial transvectant as:
 
@@
 
-Under this formula we end with a factor $(\det A)^{-r}$ in place of $(\det
+Under this formula there is a factor $(\det A)^{-r}$ in place of $(\det
 A)^{-1}$ that we saw previously, when all $n$ copies of $\mathbb{R}^2$ are
 transformed by the same affine function $\mathbf{x} \mapsto A\mathbf{x} +
-\mathbf{b}$. $r$ is referred to as the weight of the partial
-transvectant. Note that the individual pairwise Omega processes commute.
-
-The concept of a relative invariant will be important in the rest of this paper.
-It follows the definition given here, except that the function weighting the invariant is more general, see~\cite{Fels1997} for more details.
-In contrast to that paper, we will continue to use the term weight to represent the power to which the function is raised.
+\mathbf{b}$. Note that the individual pairwise Omega processes commute.
 
 For the current case it is sufficient to consider $n$ copies of the same
-function $f$. If we represent each copy of $\mathbb{R}^2$ as a node on a
+function $f$. If we represent each copy of $\mathbb{R}^2$ as a node in an
 undirected graph, and each Omega process $\Omega_{ij}$ as an edge joining
 nodes $i$ and $j$, a partial transvectant can be compactly represented in a
-graphical form.
-
-For example, consider a weight $2$ transvectant defined as:
+graphical form. For example, consider a weight $2$ transvectant defined as:
 \begin{align*}
@@
 \end{center}
-where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$ (the names are purely for convenience).
-
-Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} shows all possible nonzero partial
+where the double edge corresponds to the two copies of $\Omega_{12}$ (the names are purely for convenience), i.e.,
+the weight is the number of edges in the graph.
+
+Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} shows all possible non-zero partial
 transvectants of $A_2$ up to weight $4$ that can be generated in this way.
-Note that the weight is the number of edges in the graph.
 
@@
 
-Some of these partial transvectants appear in signatures
-from other transformation groups, so for future reference, let
+Owing to the group-subgroup structure some of these partial transvectants appear in signatures
+from other transformation groups, so for future reference, we define:
 \begin{equation}
@@
 planar objects in images taken from a distant camera. Recall that
-invariants of a supergroup are automatically invariants of any of its
-subgroups. For example, invariants of $A(2)$ are automatically invariants
+because of the subgroup relationship, invariants of $A(2)$ are automatically invariants
 of $SA(2)$, but not necessarily vice versa. Any of the partial
 transvectants found in Tables~\ref{tab:transvectants1}
-and~\ref{tab:transvectants2} are invariants of $SA(2)$ (as the determinant
-is $1$), but only up to scale factor ($\det A^{-r}$) of $A(2)$.
-
-Hence, we can form a signature for $SA(2)$ by choosing any combination of
+and~\ref{tab:transvectants2} are relative invariants of $SA(2)$ (as the determinant
+is $1$). Hence, we can form a signature for $SA(2)$ by choosing any combination of
 partial transvectants. We choose a signature with three components so that
@@
 not be complete and may well have a very large bad set. For example, we can
-choose the function value together with the $C, D$ from \eqref{eq:cde}
-to form the signature.
+choose the function value together with $C$ and $D$ from Eq.~\eqref{eq:cde}
+to form the signature:
 
@@
 \end{equation}
-We will subject our test image to the special affine transformation:
-\begin{equation*}
-\mathbf{x} \mapsto \frac{1}{1.22}\begin{bmatrix} 0.7 & 1.1 \\ -0.6 & 0.8 \end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
-\end{equation*}
-Fig.~\ref{fig:SA2} shows the signature of our test image under this transformation.
+
+Fig.~\ref{fig:SA2} shows the signature of our test image under an $SA(2)$ transformation.
 
@@
 \includegraphics[width=.45\textwidth]{Figs/SA2_signature.png}
-\caption{A sample $SA(2)$ transformation and 3D signature.}
+\caption{A sample $SA(2)$ transformation applied to our test function, and the corresponding signature.}
+%\begin{equation*}
+%\mathbf{x} \mapsto \frac{1}{1.22}\begin{bmatrix} 0.7 & 1.1 \\ -0.6 & 0.8 \end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
+%\end{equation*}
 \label{fig:SA2}
@@
 
-\subsubsection{Moving on to A(2), \ldots}
-
 For $A(2)$ the weight of the partial transvectants prevents them from being
 invariants. There are two options to create a signature. One is to select
-ratios of partial transvectants, similar to as discussed in
+ratios of partial transvectants, as discussed in
 Section~\ref{sec:Sim2}. It is then beneficial to choose the
@@
 E)$ onto the unit hypersphere and multiplying by $f$. In this way, our
-signature is
+signature is:
 \begin{equation}
@@
 We will subject our test image to the special affine transformation:
-\begin{equation*}
-\mathbf{x} \mapsto \begin{bmatrix} 0.7 & 1.1 \\ -0.6 & 0.8
-\end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
-\end{equation*}
 Fig.~\ref{fig:A2} shows the signature of our test image under this transformation.
@@
 \includegraphics[width=.45\textwidth]{Figs/A2_signature.png}
-\caption{A sample $A(2)$ transformation and 3D signature.}
+\caption{A sample $A(2)$ transformation applied to our test function, and the corresponding signature.}
+%\begin{equation*}
+%\mathbf{x} \mapsto \begin{bmatrix} 0.7 & 1.1 \\ -0.6 & 0.8
+%\end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
+%\end{equation*}
 \label{fig:A2}
@@
 
-So far the methods that we have seen to construct differential invariants for particular groups are not directly generalisable.
+So far, the methods that we have seen to construct differential invariants for particular groups are not directly generalisable.
 It is natural to ask if there is an algorithmic approach that will yield invariants more directly.
@@
 There is a general method, based on Cartan's method of moving frames, that is generally applicable, but finding good solutions with it still requires some ingenuity in general.
-We introduce the method here and then demonstrate its use to find invariants to further groups.
+Olver and co-authors have popularised the approach and made it applicable to object recognition based on outline curves, see~\citet{Olver2005} for an overview, and note particularly the original application paper~\citep{Calabi1998}.
+We introduce the method here and then demonstrate its use to find invariants to further groups, but for further technical details see~\citet{OlverCIT}.
 
 A moving frame is a mapping into a group $\mathcal{G}$ that provides a frame of reference along a manifold.
-It was extended by Cartan~\cite{Cartan35} to the `method of moving frames'.
+It was extended by~\citet{Cartan35} to the `method of moving frames'.
 If the group $\mathcal{G}$ is a Lie group then it has a homogeneous space and a frame of reference can be applied on the manifold structure of the group.
-Considering the actions of such a transformation group it can enable the identification of invariants to that group since it defines a $\mathcal{G}$-equivariant mapping.
+Considering the actions of such a transformation group enables the identification of invariants to that group since it defines a $\mathcal{G}$-equivariant mapping.
 A (right-) moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$, where $z \in J^d$.
-It is necessary~\cite{Olver2013} for the group act freely.
+It is necessary~\citep{Olver2013} for the group act freely.
 This means that the group action needs to be extended to the entire jet space of derivatives up to order $d$ by implicit differentiation of the group action, a process known as prolongation.
-
-Olver and co-authors, in particular, have popularised the approach and made it applicable to object recognition, see~\cite{Olver2005} for an overview, and note particularly the original application paper~\cite{Calabi1998}.
-The method is described in detail in~\cite{OlverCIT}.
 
@@
 
-Olver uses the group $SE(2)$ on curves as an example~\cite{OlverCIT}, recovering the Euclidean curvature as a second-order invariant.
+\citet{OlverCIT} uses the group $SE(2)$ on curves as an example, recovering the Euclidean curvature as a second-order invariant.
 We continue this example to compute invariants to $SE(2)$ for images, before moving on to other planar Lie group examples: $E(2)$, the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).
@@
 where $c = \cos \theta$ and $s = \sin \theta$. Because the group has three
-parameters, we choose the cross section of the group orbits to be $\bar{x}
-= 0, \bar{y} = 0, \bar{f}_{\bar{y}} = 0$. We also require that $\bar{f}_{x}
+parameters, we choose the cross-section of the group orbits to be $\bar{x}
+= 0, \bar{y} = 0, \bar{f}_{\bar{y}} = 0$. We also require that $\bar{f}_{\bar{x}}
 > 0$ to uniquely define the moving frame. Note that the group action is
 locally free (away from critical points) when prolonged to $J^1$, however
-we prolonged to $J^2$ in order to compute invariants. The moving
+we prolong to $J^2$ in order to compute invariants. The moving
 frame is then given by the prolonged Euclidean transformation that maps an
-element of  $J^2$ to this cross section. It can be thought of as rotating
+element of  $J^2$ to this cross-section. It can be thought of as rotating
 the image about that point so that its gradient is pointing in the positive
@@
 
-The remaining elements not fixed by the cross section, $\bar{f}$,
+The remaining elements not fixed by the cross-section, $\bar{f}$,
 $\bar{f}_{\bar{x}}$, $\bar{f}_{\bar{x}\bar{x}}$,
-$\bar{f}_{\bar{x}\bar{y}}$, and $\bar{f}_{\bar{y}\bar{y}}$ are therefore
+$\bar{f}_{\bar{x}\bar{y}}$, and $\bar{f}_{\bar{y}\bar{y}}$, are therefore
 all invariant. This gives the following set of invariants:
@@
 \end{equation}
-Note that we multiplied each of the second derivative invariants by the
-invariant $K_1$ so that they would decay smoothly to zero at critical
+Note that we have multiplied each of the second derivative invariants by the
+invariant $K_1$ so that they decay smoothly to zero at critical
 points.  Interestingly, $K_4$ is the affine invariant $D$ from
-\eqref{eq:cde} and $K_1, K_2$ are also Euclidean invariants, so we need to
-include $K_3$ in our signature. We choose our signature to be
+Eq.~\eqref{eq:cde} and $K_1$ and $K_2$ are also Euclidean invariants, so we need to
+include $K_3$ in our signature: 
 \begin{equation}
     \label{eq:SE2signature}
-    I_{SE(2)}(f) = (f, K_1, K_3)
+    I_{SE(2)}(f) = (f, K_1, K_3).
 \end{equation}
 Fig.~\ref{fig:SE2} shows the signature of our test image under a sample
-transformation of $SE(2)$:
+transformation of $SE(2)$.
 \begin{figure}
@@
 \includegraphics[width=.45\textwidth]{Figs/SE2_signature.png}
-\caption{A sample $SE(2)$ Transform and 3D signature.}
+\caption{A sample $SE(2)$ transform and 3D signature.}
 \label{fig:SE2}
@@
 $(x, y, f, f_x, f_y)$) away from critical points because there are two
-possible transformations that map to the cross section $(0, 0, \bar{f},
+possible transformations that map to the cross-section $(0, 0, \bar{f},
 \bar{f}_{\bar{x}}, 0)$ where $\bar{f}_{\bar{x}} > 0$, one that reflects the
@@
 
-We begin by choosing the same cross section as for $SE(2)$, namely $\bar{x} = 0,
+We begin by choosing the same cross-section as for $SE(2)$, namely $\bar{x} = 0,
 \bar{y} = 0, \bar{f}_{\bar{y}} = 0, \bar{f}_{\bar{x}} > 0$. This gives
@@
 regardless of whether $\varepsilon = 1$ or $\varepsilon = -1$, the
-derivative $\bar{f}_{\bar{x}} = \lVert \nabla f \rVert$. We need a second
-derivative term to resolve the choice of $\varepsilon$ for the moving
-frame. The only second derivative term in which $\varepsilon$ appears is
-the $\bar{f}_{\bar{x}\bar{y}}$ term. Substituting in for $\cos\theta,
+derivative $\bar{f}_{\bar{x}} = \lVert \nabla f \rVert$. 
+The only second derivative term in which $\varepsilon$ appears is
+the $\bar{f}_{\bar{x}\bar{y}}$ term, so we use this to resolve the sign. Substituting in for $\cos\theta,
 \sin\theta$, we see that:
@@
 give the same invariants $K_0, K_1, K_2, K_4$ as for $SE(2)$,
-\eqref{eq:se2invariants}, the one difference being $\hat{K}_3$:
+\eqref{eq:se2invariants}, the one difference being:
 \begin{equation}\label{eq:e2invariants}
@@
 invariants found previously by tensor contraction Eq. (\ref{eq:e2tensor}) in
-Section~\ref{sec:contraction} can be expressed in terms of these:
+Section~\ref{sec:contraction} can be expressed in terms of them:
 \begin{align*}
@@
 
-The M\"obius group $\mathrm{PSL}(2,\mathbb{C})$ acts on the Riemann sphere $\overline{\mathbb{C}} = \mathbb{C}\cup\infty$ by:
+The M\"obius group $PSL(2,\mathbb{C})$ acts on the Riemann sphere $\overline{\mathbb{C}} = \mathbb{C}\cup\infty$ by:
 \begin{equation} 
@@
 Identifying $\R^2$ with $\mathbb{C}$, the M\"obius group is a real 6-dimensional local Lie group acting on $\mathbb{R}^2$. 
-It is the smallest nonlinear planar group that contains $SE(2)$, and it also has direct applications in image processing since it arises in the {\em conformal camera} model of vision, in which scenes are projected radially onto a sphere \cite{Lenz1990,Turski2004}; it is also the set of biholomorphic maps of the Riemann sphere.
+It is the smallest nonlinear planar group that contains $SE(2)$, and it also has direct applications in image processing since it arises in the {\em conformal camera} model of vision, in which scenes are projected radially onto a sphere \citep{Lenz1990,Turski2004}; it is also the set of biholomorphic maps of the Riemann sphere.
 %Different shapes may be related by M\"obius transformations, as is explored by Petukhov \cite{petukhov1989non} for biological objects: in one example, the human skull grows approximately by M\"obius transformations.
@@
 In order to find further invariants the prolongation to 3rd derivatives is required, which will result in at least another four invariants.
-This simple counting arguments works because the group acts freely on the prolongation.
+This simple counting argument works because the group acts freely on the prolongation.
 %There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 5 invariants.
@@
 \begin{enumerate}
-\item The frame $\bar f_{\bar x}=1$, $\bar f_{\bar y}=0$ determines the group parameters:
+\item The frame $\bar f_{\bar x}=1$, $\bar f_{\bar y}=0$ determines two group parameters:
 $$ a = f_x/(f_x^2 + f_y^2),\quad b = f_y/(f_x^2 f_y^2).$$
@@
 
-\item The second-order invariant is then given by $\bar f_{\bar x \bar x}$ using Equation~(\ref{eqn:mobius}); it is:
+\item The second-order invariant is then given by $\bar f_{\bar x \bar x}$ using Eq.~(\ref{eqn:mobius}):
 $$\bar f_{\bar x \bar x} = \frac{f_{xx}+f_{yy}}{f_x^2 + f_y^2}.$$
@@
 \end{equation}
-An example is shown in Figure~\ref{fig:mobius}, although note that the
+An example is shown in Fig.~\ref{fig:mobius}, although note that the
 signature is singular when $f_x=f_y=f_{xx}+f_{yy}=0$, a codimension 1
@@
 \includegraphics[width=.45\textwidth]{Figs/Mobius_signature.png}
-\caption{A sample M\"obius Transform and 3D signature.}
+\caption{A sample M\"obius transform and 3D signature.}
 \label{fig:mobius}
@@
 
-The action of the projective group arises naturally through the movements of the camera watching planar objects.
-We consider the eight-dimensional group $\mathrm{PSL}(3,\R)$ acting on $\R^2$ by projective transformations, i.e., 
+The action of the projective group arises naturally through the movements of the camera viewing planar objects.
+We consider the eight-dimensional group $PSL(3,\R)$ acting on $\R^2$ by projective transformations, i.e., 
 \begin{equation}
@@
 We begin the construction of the moving frame by choosing $\bar f_{\bar x}
-= 1$ and $\bar f_{\bar y}=  0$, which determine the group parameters $a =
+= 1$ and $\bar f_{\bar y}=  0$, which determines the group parameters $a =
 (1-c f_y)/f_x.$ and $b = -d f_y/f_x$. Direction substition then shows that
 $\bar f_{\bar y \bar y} = D d^2 / f_x^2$, where $D = f_{x}^2 f_{yy} + f_y^2
-f_{xx} - 2 f_x f_y f_{xyy}$, which we saw earlier as an invariant of
-$A(2)$, which is a subgroup of $\mathrm{PSL}(3,\R)$. Note that $D$ and
+f_{xx} - 2 f_x f_y f_{xyy}$ was listed in Eq.~\eqref{eq:cde} as an invariant of
+$A(2)$, which is a subgroup of $PSL(3,\R)$. Note that $D$ and
 $\bar f_{\bar y \bar y}$ have the same sign. If $D < 0$, we choose the
@@
 f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$ In fact, the
-numerator of the expression for $h$ was another invariant of $A(2)$; we
-label it $E$ for convenience.
+numerator of the expression for $h$ was another invariant of $A(2)$ labelled as
+$E$ in Eq.~\eqref{eq:cde}.
 
@@
 
-Having determined the frame, any function of the remaining derivatives $\bar f_{ \bar x \bar x \bar x}$, $\bar f_{ \bar x \bar x \bar y}$, and $\bar f_{ \bar y \bar y \bar y}$, as given in Equation~(\ref{eq:prolong}), provides invariants.
+Having determined the frame, any function of the remaining derivatives $\bar f_{ \bar x \bar x \bar x}$, $\bar f_{ \bar x \bar x \bar y}$, and $\bar f_{ \bar y \bar y \bar y}$, as given in Eq.~(\ref{eq:prolong}), provides invariants.
 We choose:
@@
 They do have one benefit, though, which is that they  all have denominators given by integer powers of $D$, resolving the ambiguity caused by the sign of $D$.
-Therefore, $$ (D^{18}, J_1^3, J_2^2, J_3^6)$$ are all relative invariants of weight 36, and so projecting any subset of them of them to a sphere yields a third-order invariant signature.
+Therefore, $ (D^{18}, J_1^3, J_2^2, J_3^6)$ are all relative invariants of weight 36, and so projecting any subset of them of them to a sphere yields a third-order invariant signature.
 
@@
 $$P_4 = -4(\det f_{ij})^2 + Q_4,$$
-where $Q_4$ is a polynomial of degree 4 that vanishes when $f_x=f_y=0$. Hence, the relative invariant of weight 12:
-$$ (D^6, P_4^3, (E^2-12D P_5)^2)$$
-can be projected to $S^2$, yielding a projective invariant of images that is singular only when $D=E=P_4=0$, which is a codimension 1 phenomenon, since  $D=E=0\Rightarrow P_4=0$.
-In particular, at critical points it tends to:
-$(0, (2\det f_{ij})^6, 0),$ and hence critical points with $\det f_{ij}\ne 0$ have signature value $(0,1,0)$.
-Including $J_2$ provides a 4-dimensional signature set, but does not increase the codimension of the set of bad images.
-
-\todo[inline]{Is this useful? Is it what we actually use? If so, fix the names...}
-For completeness we write out the invariant signature we use explicitly:
-
-$Q_4=4 f_x  f_{xy} ^2 f_{xyy}  - 
-f_x ^2 f_{xyy} ^2 - 
- 2 f_{yyy}  f_x  f_{xy}  f_{xx}  + 
- 2 f_{yy}  f_x  f_{xyy}  f_{xx}  - 
- 6 f_{y}  f_{xy}  f_{xyy}  f_{xx}  + 
- 2 f_{y}  f_{yyy}  f_{xx} ^2 + 
- f_{yyy}  f_x ^2 f_{xxy}  - 
- 6 f_{yy}  f_x  f_{xy}  f_{xxy}  + 
- 4 f_{y}  f_{xy} ^2 f_{xxy}  + 
- f_{y}  f_x  f_{xyy}  f_{xxy}  + 
- 2 f_{y}  f_{yy}  f_{xx}  f_{xxy}  - 
- f_{y} ^2 f_{xxy} ^2 + 
- 2 f_{yy} ^2 f_x  f_{xxx}  - 
- f_{y}  f_{yyy}  f_x  f_{xxx}  - 
- 2 f_{y}  f_{yy}  f_{xy}  f_{xxx}  + f_{y} ^2 f_{xyy}  f_{xxx}, $
-
-$P_5=f_{yyy}  f_{x} ^3 f_{xy}  - 
-f_{yy}  f_{x} ^2 f_{xy} ^2 + 
- 2 f_{y}  f_{x}  f_{xy} ^3 - 
- f_{yy}  f_{x} ^3 f_{xyy}  - 
- f_{y}  f_{x} ^2 f_{xy}  f_{xyy}  + 
- f_{yy} ^2 f_{x} ^2 f_{xx}  - 
- f_{y}  f_{yyy}  f_{x} ^2 f_{xx}  - 
- 2 f_{y}  f_{yy}  f_{x}  f_{xy}  f_{xx}  - 
- f_{y} ^2 f_{xy} ^2 f_{xx}  + 
- 2 f_{y} ^2 f_{x}  f_{xyy}  f_{xx}  + 
- f_{y} ^2 f_{yy}  f_{xx} ^2 + 
- 2 f_{y}  f_{yy}  f_{x} ^2 f_{xxy}  - 
- f_{y} ^2 f_{x}  f_{xy}  f_{xxy}  - 
- f_{y} ^3 f_{xx}  f_{xxy}  - 
- f_{y} ^2 f_{yy}  f_{x}  f_{xxx}  + 
- f_{y} ^3 f_{xy}  f_{xxx}. $
-
-Further invariants can be found by noting that, for any planar transformation group and any two invariants
-$I^1$ and $I^2$, $\nabla I^1 \times \nabla I^2$ is a relative invariant of weight 1; that is:
-$$\nabla I^1 \times \nabla I^2\mapsto (\det \phi')(\nabla I^1 \times \nabla I^2).$$
-Applying this operation to $f$ and the four third-order invariants yields $5\cdot4/2=10$ fourth-order invariants.
+where $Q_4$ is a polynomial of degree 4 that vanishes when $f_x=f_y=0$.
+Hence, the relative invariant signature of weight 12 $ (D^6, P_4^3, (E^2-12D P_5)^2)$ can be projected to $S^2$, yielding a projective invariant of images that is singular only when $D=E=P_4=0$, which is a codimension 1 phenomenon, since  $D=E=0\Rightarrow P_4=0$.
+In particular, at critical points it tends to $(0, (2\det f_{ij})^6, 0),$ and hence critical points with $\det f_{ij}\ne 0$ have signature value $(0,1,0)$.
+Including $J_2$ provides a 4-dimensional signature set, but does not change the codimension of the set of bad images.
+
+%For completeness we write out the invariant signature we use explicitly:
+
+%$Q_4=4 f_x  f_{xy} ^2 f_{xyy}  - 
+%f_x ^2 f_{xyy} ^2 - 
+ %2 f_{yyy}  f_x  f_{xy}  f_{xx}  + 
+ %2 f_{yy}  f_x  f_{xyy}  f_{xx}  - 
+ %6 f_{y}  f_{xy}  f_{xyy}  f_{xx}  + 
+ %2 f_{y}  f_{yyy}  f_{xx} ^2 + 
+ %f_{yyy}  f_x ^2 f_{xxy}  - 
+ %6 f_{yy}  f_x  f_{xy}  f_{xxy}  + 
+ %4 f_{y}  f_{xy} ^2 f_{xxy}  + 
+ %f_{y}  f_x  f_{xyy}  f_{xxy}  + 
+ %2 f_{y}  f_{yy}  f_{xx}  f_{xxy}  - 
+ %f_{y} ^2 f_{xxy} ^2 + 
+ %2 f_{yy} ^2 f_x  f_{xxx}  - 
+ %f_{y}  f_{yyy}  f_x  f_{xxx}  - 
+ %2 f_{y}  f_{yy}  f_{xy}  f_{xxx}  + f_{y} ^2 f_{xyy}  f_{xxx}, $
+
+%$P_5=f_{yyy}  f_{x} ^3 f_{xy}  - 
+%f_{yy}  f_{x} ^2 f_{xy} ^2 + 
+ %2 f_{y}  f_{x}  f_{xy} ^3 - 
+ %f_{yy}  f_{x} ^3 f_{xyy}  - 
+ %f_{y}  f_{x} ^2 f_{xy}  f_{xyy}  + 
+ %f_{yy} ^2 f_{x} ^2 f_{xx}  - 
+ %f_{y}  f_{yyy}  f_{x} ^2 f_{xx}  - 
+ %2 f_{y}  f_{yy}  f_{x}  f_{xy}  f_{xx}  - 
+ %f_{y} ^2 f_{xy} ^2 f_{xx}  + 
+ %2 f_{y} ^2 f_{x}  f_{xyy}  f_{xx}  + 
+ %f_{y} ^2 f_{yy}  f_{xx} ^2 + 
+ %2 f_{y}  f_{yy}  f_{x} ^2 f_{xxy}  - 
+ %f_{y} ^2 f_{x}  f_{xy}  f_{xxy}  - 
+ %f_{y} ^3 f_{xx}  f_{xxy}  - 
+ %f_{y} ^2 f_{yy}  f_{x}  f_{xxx}  + 
+ %f_{y} ^3 f_{xy}  f_{xxx}. $
+
+%Further invariants can be found by noting that, for any planar transformation group and any two invariants
+%$I^1$ and $I^2$, $\nabla I^1 \times \nabla I^2$ is a relative invariant of weight 1; that is:
+%$$\nabla I^1 \times \nabla I^2\mapsto (\det \phi')(\nabla I^1 \times \nabla I^2).$$
+%Applying this operation to $f$ and the four third-order invariants yields $5\cdot4/2=10$ fourth-order invariants.
 
@@
 \includegraphics[width=.45\textwidth]{Figs/PSL3R_signature.png}
-\caption{A sample $PSL(3,\mathbb{R})$ Transform and 3D signature.}
+\caption{A sample $PSL(3,\mathbb{R})$ transform and 3D signature.}
 \label{fig:PSL3R}
@@
 
-The conformal camera model is well known. The group of conformal diffeomorphisms is the subgroup of diffeomorphisms that are angle-preserving, i.e.,:
-
-\begin{equation}
-\angle (u,v) = \angle (D \phi(x) . u, D \phi(x).v)
+The conformal camera model is well known. The group of conformal diffeomorphisms is the subgroup of diffeomorphisms (i.e., smooth functions with smooth inverses) that are angle-preserving:
+
+\begin{equation}
+\angle (u,v) = \angle (D \phi(x) . u, D \phi(x).v),
 \end{equation}
@@
 elements of the form $(x, y, f, f_x, f_y, f_{xx}, f_{xy}, f_{yy}, \ldots)$.
-Recall the moving frame produces a conformal map $\psi$ for each element of
-$J^\infty$ that maps it to a suitably chosen cross section.
+%Recall the moving frame produces a conformal map $\psi$ for each element of
+%$J^\infty$ that maps it to a suitably chosen cross-section.
 
@@
 generality, we can assume $x = y = 0$. We begin the construction of our
-cross section by choosing $\bar{x} = \bar{y} = 0$. Then, $\psi^{-1}$ 
+cross-section by choosing $\bar{x} = \bar{y} = 0$. Then $\psi^{-1}$ 
 can be represented locally by a Taylor series of the form:
@@
 Differentiating $f(x, y) = \bar{f}(\bar{x}, \bar{y})$ and substituting in
-our existing cross section constraints $\bar{x} = \bar{y} = 0$ gives:
+our existing cross-section constraints $\bar{x} = \bar{y} = 0$ gives:
 \begin{align*}
@@
 Note that $\bar{x} = \bar{y} = 0$ removes all higher order derivatives from
-the cross section equation. Adding two extra constraints to the cross
+the cross-section equation. Adding two extra constraints to the cross
 section, $\bar{f}_{\bar{x}} = 1, \bar{f}_{\bar{y}} = 0$, this system is readily
-solved to give :
+solved to give:
 \begin{equation*}
@@
 We then repeat the process, this time using the second derivative
-computations. This time, there are two new parameters, $a_2, b_2$, to solve
-for, but there are three derivatives. We use the cross section equations
+computations. There are two new parameters, $a_2, b_2$, to solve
+for, but there are three derivatives. We use the cross-section equations
 $\bar{f}_{\bar{x}\bar{x}} = 0, \bar{f}_{\bar{x}\bar{y}} = 0$ to solve for
@@
 are not simultaneously equal to zero, which occurs when $f_x = f_y = f_{xx}
-= f_{yy} = 0$, which is a codimension-1 phenomenon for images.
+= f_{yy} = 0$, which is a codimension 1 phenomenon for images.
 
@@
 $\varphi^{-1}(z) = \frac{3}{8}(z - 2)^2 - \frac{3}{2}$ is shown in
-Figure~\ref{fig:Diffcon}.
+Fig.~\ref{fig:Diffcon}.
 \begin{figure}
@@
 
-\section{Colour Images}\label{sec:colour}
-
-The formulation we provided in the introduction considered $k$ channels of information.
-So far we have considered only greyscale images ($k=1$), but most real images are three-channel colour (RBG), and multi-spectral images can have hundreds of channels of measurement.
-It is therefore natural to consider whether this information is useful for the computation of invariants.
-
-The hope is that by constructing invariants using different colour channels, fewer derivatives are needed: for $k$ colours, signature sets of dimension up to $k + k(k+1)/2$ can be chosen from the invariants $f^i$ and $f^i_m f^j_m$ for $i,j=1,\dots, k$.
-However, the situation is more complicated that it first appears because the information in the channels is not independent: colour is built by the intensities in the three channels, and so there is correlation between them.
-We briefly sketch some possibilities for some of the groups that we have considered earlier, but note that the correlation means that the invariant signatures identified next are na\"ive, and should be viewed as best-case scenarios.
-
-\begin{description}
-\item[$E(2)$]
-Considering $E(2)$, for $k\ge 2$, first derivatives suffice.
-However, note that for $k\ge 3$ the three-dimensional signature $(f^1,f^2,f^3)$ is invariant under all local planar diffeomorphisms and so a higher-dimensional signature, involving at least first derivatives, is required.
-\item[$SA(2)$]
-For $SA(2)$, one can take transvectants of any components of $f$ to get invariants.
-For $k=2$ colours, there is only one  invariant formed from first derivatives, namely $((f^1)',(f^2)')_x = f^1_x f^2_y - f^1_y f^2_x$ (the Poisson bracket $\{f^1,f^2\}$).
-So again two derivatives are necessary, even for a 3-dimensional signature.
-
-For $k\ge 3$ colours there are plenty of invariants formed from first derivatives, namely $\nabla f^i \times \nabla f^j$ for $i<j$.
-However, these are all invariant under the bigger group $\mathrm{Diff}_{\mathrm{vol}}$ of local volume-preserving diffeomorphisms, and so the Poisson brackets cannot form a complete invariant for $SA(2)$: two derivatives are always needed no matter how many colours we have.
-The relation $SA(2)\subset \mathrm{Diff}_{\mathrm{vol}}$ acts an obstruction to $SA(2)$, an instance of the phenomenon of hidden symmetry.
-\item[$A(2)$]
-The same problem occurs with $A(2)$.
-There are plenty of invariants formed from two derivatives: already 9 when $k=2$.
-However, as with $SA(2)$, we can never get away with one derivative because all the first-derivative invariants, such as $\{f^1,f^2\}/\{f^1,f^3\}$, are also invariant under $\mathrm{Diff}_{\mathrm{vol}}$ (even though $A(2)$ is not even a subgroup of $\mathrm{Diff}_{\mathrm{vo}l}$).
-\item[$PSL(2,\mathbb{C})$]
-Recall that M\"obius and conformal transformations cannot be distinguished by their action on second derivatives.
-Therefore at least three derivatives are needed, no matter how many colours we have.
-We can use, for example, the invariants arising from the curvature of the level sets of each colour.
-Replacing the relative invariant $\|\nabla f\|^2$ by $\sum_{j=1}^k \|\nabla f^j\|^2$, and $f_{ii}$ by $\sum_{j=1}^k (f^j_{ii})^2$, increases the codimension of the singular images from 1 to $3k-2$.
-\item[$PSL(3,\mathbb{R})$]
-In $PSL(3, \mathbb{R})$ for $2$-colour images, there are three second-order relative invariants of weight 2, namely $(D_1,D_2,(\nabla f^1\times \nabla f^2)^2)$.
-Together with $(f^1,f^2)$, these yield a 4-dimensional $\mathbb{R}^2\times S^2$-valued signature using only second derivatives.
-With $k>2$ colours there are many more second-order invariants; however, as the action of the projective group on first derivatives is indistinguishable from that of the full diffeomorphism group, it is not possible to have a first-order signature that distinguishes projectively-related images from diffeomorphically-related ones.
-\item[$\mathrm{Diff}_{\mathrm{con}}$]
-For the infinite-dimensional group $\mathrm{Diff}_{\mathrm{con}}$, first-order signature sets are possible for $k \ge 2$ colours.
-They are formed from the relative invariants $(f^j_1 + i f^j_2)(f^m_1 - i f^m_2)$ of weight 2.
-We illustrate this using the Hopf fibration for $k=2$.
-The weight 2 relative invariant $$J = (2(f^1_1 + i f^1_2)(f^2_1 - i f^2_2), ||\nabla f^1\|^2 - \|\nabla f^2\|^2)$$ obeys $\|J\|^2 = \|\nabla f^1\|^2 + \|\nabla f^2\|^2$, hence projecting to the unit sphere shows that $(f^1,f^2,J/\|J\|)$ provides a 4-dimensional signature set that is singular only when $\nabla f^1 = \nabla f^2 = 0$, a codimension 2 phenomenon for images.
-\end{description}
-
-\subsection{Infinite-dimensional groups of diffeomorphisms}
-
-We have already seen one example of an infinite-dimensional group, the 2D conformal diffeomorphisms.
-We here briefly consider two other groups: the volume-preserving diffeomorphisms, which act as the space of transformations of an incompressible fluid, and then the full group of planar diffeomorphisms, which are widely used in image registration~\cite{YounesBook}.
+\subsection{$\mathrm{Diff}_{\mathrm{vol}}$ and $\mathrm{Diff}$}
+
+Two other infinite-dimensional groups are of interest: the volume-preserving diffeomorphisms, which act as the space of transformations of an incompressible fluid, and the full group of planar diffeomorphisms, which are widely-used in image registration~\citep{YounesBook}.
+However, in these cases there are no differential invariant signatures of greyscale images.
 
 The volume-preserving diffeomorphisms $\mathrm{Diff}_{\mathrm{vol}}$ are those diffeomorphisms that preserve the volume form (area form in 2D).
-They can be defined by one function of two variables, the generating function $S$; one possibility is $S(x,y')$ where $(x,y)\mapsto(x',y')$ according to:
+They can be defined by one function of two variables, the generating function $S$; one possibility is $S(x',y')$ where $(x,y)\mapsto(x',y')$ according to:
 $$ x'=\frac{\partial S}{\partial y'},\quad y = \frac{\partial S}{\partial x}.$$
@@
 The image $f$ transforms to $x + \varepsilon \psi_y(x,y)$ which (by choosing $\psi$ appropriately) can be any function close to $x$.
-
 At nongeneric points, there can be invariants.
@@
 
-When considering colour images, for $k\ge 2$ in $\mathrm{Diff}_{\mathrm{vol}}$ there are $k(k-1)/2$ first-order invariants $ \nabla f^i \times \nabla f^j$.
+In the full diffeomorphism group $\mathrm{Diff}$ there are no differential invariants using 1 or even 2 colours (colour will be discussed in the Section~\ref{sec:colour}).
+For example, with $k=2$, for generic $f^1$, $f^2$ we can choose a diffeomorphism (i.e., choose local coordinates) so that $f^1=x$ and $f^2=y$.
+
+\section{Discussion}\label{sec:colour}
+
+%\todo[inline]{Number of derivatives}
+%\todo[inline]{Noise; integral invariants, Fourier}
+%\todo[inline]{Is there a general theory - syzygy??}
+%\todo[inline]{Difficulties of a practical implementation}
+
+The recognition of objects within images as their appearance changes based on camera motion remains an unsolved problem.
+In this paper we have used three different methods of computing differential invariant signatures to identify appropriate signatures for images transformed under the planar Lie groups that are of interest for this question.
+The resulting three-dimensional signatures are not always complete, but they are relatively fast to compute.
+However, there are some issues that arise with turning this into a practical method.
+
+The first is a standard issue for images: producing a computationally robust method of numerically approximating derivatives and hence invariants is not trivial, particularly for the higher-orders, where noise and rounding errors can dominate.
+There are three primary considerations: noise and texture; flat areas, where the derivatives are all identically zero; and the fact that conventional numerical differentiation is not well-posed~\citep{Florack1993}.
+Some considerations of these points and some potential approaches to solving them for practical implementations are considered by~\citet{Calabi1998} and~\citet{Florack1993}, but the question of how to create a full and effective method of computing numerical derivatives for images remains open.
+Practical approaches to using the signatures identified in this paper for real-world images will be considered in future work.
+
+The second problem is that there are hidden symmetries within the lattice of groups we consider.
+For example, the relation $SA(2)\subset \mathrm{Diff}_{\mathrm{vol}}$ acts an obstruction to $SA(2)$, since many of the invariants of $SA(2)$ are also invariant under the larger group.
+While there will be more invariants for the smaller group, care needs to be taken to check that the set chosen are unique to that group.
+The same issue arises with $A(2)$, even though $A(2)$ is not even a subgroup of $\mathrm{Diff}_{\mathrm{vol}}$.
+
+It might be hoped that colour information can help.
+The formulation we provided in the introduction considered $k$ channels of information, but so far we have considered only greyscale images ($k=1$).
+Most real images are three-channel colour (RBG), and multi-spectral images can have hundreds of channels of measurement.
+It is therefore natural to consider whether this information is useful for the computation of invariants, in particular by allowing lower-order derivatives to form a suitable signatures.
+However, in practice the situation is more complicated that it first appears because the information in the channels is not independent: colour is built by the intensities in the three channels, and so there is correlation between them.
+%We briefly sketch some possibilities for some of the groups that we have considered earlier, but note that the correlation means that the invariant signatures identified next are na\"ive, and should be viewed as best-case scenarios.
+%for $k$ colours, signature sets of dimension up to $k + k(k+1)/2$ can be chosen from the invariants $f^i$ and $f^i_m f^j_m$ for $i,j=1,\dots, k$.
+
+For $E(2)$, for $k\ge 2$, first derivatives suffice, but for both $SA(2)$ and $A(2)$ the hidden symmetry noted above mean that there are no signatures with only first derivatives.
+
+The picture is more positive for the infinite-dimensional groups.
+For $\mathrm{Diff}_{\mathrm{con}}$, first-order signature sets are possible for $k \ge 2$ colours.
+They are formed from the relative invariants $(f^j_x + i f^j_y)(f^m_x - i f^m_y)$ of weight 2 (where $f^j$ is the $j$the colour channel).
+We illustrate this using the Hopf fibration for $k=2$.
+The weight 2 relative invariant $$J = (2(f^1_x + i f^1_y)(f^2_x - i f^2_y), ||\nabla f^1\|^2 - \|\nabla f^2\|^2)$$ obeys $\|J\|^2 = \|\nabla f^1\|^2 + \|\nabla f^2\|^2$, hence projecting to the unit sphere shows that $(f^1,f^2,J/\|J\|)$ provides a 4-dimensional signature set that is singular only when $\nabla f^1 = \nabla f^2 = 0$, a codimension 2 phenomenon for images.
+For $\mathrm{Diff}_{\mathrm{vol}}$ extra channels mean that different invariants now exist: there are $k(k-1)/2$ first-order invariants $ \nabla f^i \times \nabla f^j$.
+Then the three-dimensional signature $ (f^1,f^2, \nabla f^1 \times \nabla f^2)$ determines (generically and locally) the image up to an area-preserving map.
+We can choose the area-preserving map so that $f^1=x$.
+The remaining freedom is of the area-preserving maps that preserve $x$: these are the shears $y\mapsto y + g(x)$.
+The signature for each fixed $x$ now gives $(f^2,f^2_y)$.
+This is the standard signature curve for the group of translations in $y$.
+Thus, $f^2$ is determined by the signature up to a translation in $y$, i.e., an area-preserving map.
+
+In the full diffeomorphism group $\mathrm{Diff}$ there are no differential invariants using 1 or 2 colours.
+For example, with $k=2$, for generic $f^1$, $f^2$ we can choose a diffeomorphism (i.e., choose local coordinates) so that $f^1=x$ and $f^2=y$.
+We therefore take $k\ge 3$.
+This provides the first-order relative invariants of weight 1 $\nabla f^i\times \nabla f^j$, and hence a first-order signature.
+However, a zeroth-order signature set is possible: $(f^1,\dots,f^k)$, the image of the image.
+It is (locally and generically) complete.
+We can choose coordinates so that $f^1=x$ and $f^2=y$; then the signature locally determines $f^3,\dots,f^k$ as functions of $f^1$ and $f^2$, i.e., the image.
+
+%\begin{description}
+%\item[$E(2)$]
+%Considering $E(2)$, for $k\ge 2$, first derivatives suffice.
+However, note that for $k\ge 3$ the three-dimensional signature $(f^1,f^2,f^3)$ is invariant under all local planar diffeomorphisms and so a higher-dimensional signature, involving at least first derivatives, is required.
+%\item[$SA(2)$]
+%For $SA(2)$, one can take transvectants of any components of $f$ to get invariants.
+For $k=2$ colours, there is only one  invariant formed from first derivatives, namely $((f^1)',(f^2)')_x = f^1_x f^2_y - f^1_y f^2_x$ (the Poisson bracket $\{f^1,f^2\}$).
+So again two derivatives are necessary, even for a 3-dimensional signature.
+
+%For $k\ge 3$ colours there are plenty of invariants formed from first derivatives, namely $\nabla f^i \times \nabla f^j$ for $i<j$.
+However, these are all invariant under the bigger group $\mathrm{Diff}_{\mathrm{vol}}$ of local volume-preserving diffeomorphisms, and so the Poisson brackets cannot form a complete invariant for $SA(2)$: two derivatives are always needed no matter how many colours we have.
+%The relation $SA(2)\subset \mathrm{Diff}_{\mathrm{vol}}$ acts an obstruction to $SA(2)$, an instance of the phenomenon of hidden symmetry.
+%\item[$A(2)$]
+%The same problem occurs with $A(2)$.
+There are plenty of invariants formed from two derivatives: already 9 when $k=2$.
+However, as with $SA(2)$, we can never get away with one derivative because all the first-derivative invariants, such as $\{f^1,f^2\}/\{f^1,f^3\}$, are also invariant under $\mathrm{Diff}_{\mathrm{vol}}$ (even though $A(2)$ is not even a subgroup of $\mathrm{Diff}_{\mathrm{vo}l}$).
+%\item[$PSL(2,\mathbb{C})$]
+%Recall that M\"obius and conformal transformations cannot be distinguished by their action on second derivatives.
+Therefore at least three derivatives are needed, no matter how many colours we have.
+We can use, for example, the invariants arising from the curvature of the level sets of each colour.
+Replacing the relative invariant $\|\nabla f\|^2$ by $\sum_{j=1}^k \|\nabla f^j\|^2$, and $f_{ii}$ by $\sum_{j=1}^k (f^j_{ii})^2$, increases the codimension of the singular images from 1 to $3k-2$.
+%\item[$PSL(3,\mathbb{R})$]
+%In $PSL(3, \mathbb{R})$ for $2$-colour images, there are three second-order relative invariants of weight 2, namely $(D_1,D_2,(\nabla f^1\times \nabla f^2)^2)$.
+Together with $(f^1,f^2)$, these yield a 4-dimensional $\mathbb{R}^2\times S^2$-valued signature using only second derivatives.
+With $k>2$ colours there are many more second-order invariants; however, as the action of the projective group on first derivatives is indistinguishable from that of the full diffeomorphism group, it is not possible to have a first-order signature that distinguishes projectively-related images from diffeomorphically-related ones.
+%\item[$\mathrm{Diff}_{\mathrm{con}}$]
+%For the infinite-dimensional group $\mathrm{Diff}_{\mathrm{con}}$, first-order signature sets are possible for $k \ge 2$ colours.
+They are formed from the relative invariants $(f^j_1 + i f^j_2)(f^m_1 - i f^m_2)$ of weight 2.
+We illustrate this using the Hopf fibration for $k=2$.
+The weight 2 relative invariant $$J = (2(f^1_1 + i f^1_2)(f^2_1 - i f^2_2), ||\nabla f^1\|^2 - \|\nabla f^2\|^2)$$ obeys $\|J\|^2 = \|\nabla f^1\|^2 + \|\nabla f^2\|^2$, hence projecting to the unit sphere shows that $(f^1,f^2,J/\|J\|)$ provides a 4-dimensional signature set that is singular only when $\nabla f^1 = \nabla f^2 = 0$, a codimension 2 phenomenon for images.
+%\end{description}
+%When considering colour images, for $k\ge 2$ in $\mathrm{Diff}_{\mathrm{vol}}$ there are $k(k-1)/2$ first-order invariants $ \nabla f^i \times \nabla f^j$.
 We consider the case $k=2$ and the 3-dimensional signature $$ (f^1,f^2, \nabla f^1 \times \nabla f^2).$$ This signature determines (generically and locally) the image up to an area-preserving map.
@@
 Thus, $f^2$ is determined by the signature up to a translation in $y$, i.e., an area-preserving map.
-
-In the full diffeomorphism group $\mathrm{Diff}$ there are no differential invariants using 1 or 2 colours.
+%In the full diffeomorphism group $\mathrm{Diff}$ there are no differential invariants using 1 or 2 colours.
 For example, with $k=2$, for generic $f^1$, $f^2$ we can choose a diffeomorphism (i.e., choose local coordinates) so that $f^1=x$ and $f^2=y$.
@@
 
-\section{Discussion}
-
-%\todo[inline]{Number of derivatives}
-%\todo[inline]{Noise; integral invariants, Fourier}
-%\todo[inline]{Is there a general theory - syzygy??}
-%\todo[inline]{Difficulties of a practical implementation}
-
-The recognition of objects within images as their appearance changes based on camera motion remains an unsolved problem.
-In this paper we have used three different methods of computing differential invariant signatures to identify appropriate signatures for images transformed under the planar Lie groups that are of interest for this question.
-The resulting three-dimensional signatures are not always complete, but they are relatively fast to compute.
-
-Table~\ref{tab:derivs} summarises one of the most important parameters of differential invariant signatures for the transformation groups that we have considered, namely the highest order of derivative of the image that is needed.
-While none of the groups need more than third-order differentiation, and usually less (especially for colour images), even this can be problematic for real images.
-Our aim in this paper has been to explore the mathematical theory required to compute the invariants.
+Putting all of this information together, Table~\ref{tab:derivs} summarises one of the most important parameters of differential invariant signatures for the transformation groups that we have considered, namely the highest order of derivative of the image that is needed.
+None of the groups need more than third-order differentiation, and usually less, especially for colour images.
+
+%even this can be problematic for real images. %Our aim in this paper has been to explore the mathematical theory required to compute the invariants.
 
@@
 \hline
-SE(2) & 2 &1 & 1 \\
-E(2) & 2 & 1 & 1 \\
-Sim(2) & 2 & 1 & 1 \\
-SA(2) & 2 & 2 & 2 \\
-A(2) & 3 & 2 & 2 \\
-$\mathrm{PSL}(2,\mathbb{C})$ & 3 & 3 & 3 \\
-$\mathrm{PSL}(3,\R)$ & 3 & 2 & 2 \\
+$SE(2)$ & 2 &1 & 1 \\
+$E(2)$ & 2 & 1 & 1 \\
+$Sim(2)$ & 2 & 1 & 1 \\
+$SA(2)$ & 2 & 2 & 2 \\
+$A(2)$ & 3 & 2 & 2 \\
+$PSL(2,\mathbb{C})$ & 3 & 3 & 3 \\
+$PSL(3,\R)$ & 3 & 2 & 2 \\
 $\mathrm{Diff}_{\mathrm{vol}}$ & -- & 1 & 1 \\
@@
 
-Producing a computationally robust method of numerically approximating derivatives and hence invariants is not trivial, particularly for the higher-orders, where noise and rounding errors can dominate.
-There are three primary considerations: noise and texture; flat areas, where the derivatives are all identically zero; and the fact that conventional numerical differentiation is not well-posed~\cite{Florack1993}.
-Some considerations of these points and some potential approaches to solving them for practical implementations are considered in~\cite{Calabi1998} and~\cite{Florack1993}.
-However, the question of how to create a full and effective implementation remains an open problem.
-
-Finally, we note that there is underlying mathematical structure that we have not fully exposed.
+In future work we will seek the underlying mathematical structure that we have not fully exposed.
 For example, all of the second-order differential invariants of $E(2)$ play known roles in geometric analysis:
@@
 
+Function $D$ from Eq.~\eqref{eq:cde}, which appeared in $SE(2)$, $SA(2)$ and $PSL(3,\mathbb{R})$, is also known as the Bateman equation~\citep{Andriopoulos}, and is linked to the Hodograph transformation~\citep{Rosenhaus}.
+
 \bibliographystyle{plainnat}

### 2021-03-02 paper/letter.tex
As submitted

\documentclass[12pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
%\usepackage[a4paper,left=2.5cm, right=2.5cm, top=2cm, bottom=2.5cm]{geometry}
\usepackage[a4paper,left=2cm, right=2cm,height=26cm]{geometry}
\usepackage{graphicx}
\usepackage{url}

\begin{document}
\thispagestyle{empty}

\textbf{To}
\\
The Editor
\\
SIAM Journal on Imaging Sciences
\\

{\bf Subject}:  Submission of Manuscript

Manuscript title: Differential invariant signatures for planar Lie group transformations of images \\
Authors: Richard Brown, Stephen Marsland, and Robert McLachlan

\vspace{2em}

Dear Editor,

we write to submit the above research paper for consideration by your journal. The paper considers the practicality of differential invariant signatures for image recognition under different transformations, some of which relate to camera models. It extends the mathematical research on invariant signatures for Lie groups, provides a tutorial example of how to use methods such as moving frames to derive invariants, provides examples for a series of important groups, and considers the practical questions that would need to be answered to make a fully useful application. We believe that readers of SIIMS would find it of interest.

Please note that to get the full pdf under 5MB in size we have had to shrink the images. Higher-quality versions of them are available.

Some possible referees that we believe are knowledgeable about this area include:

\begin{itemize}
\item Peter Olver, U Minnesota,  \url{olver@umn.edu}
\item Cheri Shakiban, University of St Thomas, St Paul, \url{cshakiban@stthomas.edu}
\item Alain Trouv\'{e}, ENS-Cachan \url{ trouve@cmla.ens-cachan.fr}
\item Irina Kogan, North Carloin State University, \url{iakogan@math.ncsu.edu}
\item Allen Tannenbaum, Stony Brook University, \url{arobertan@cs.stonybrook.edu}
\end{itemize}

\closing{We look forward to hearing from you,
\\ Professor Stephen Marsland\\Victoria University of Wellington, New Zealand\\ \url{stephen.marsland@vuw.ac.nz}}

\end{document}

### 2021-08-04 paper/newpaper.tex
As submitted
Some progress on ref reports

@@
 
-The methods we use to construct the invariants, particularly the moving frames, produces invariants that, when considered alone, are singular at points (such as critical points).
-However, in all groups considered the invariants are rational functions of the derivatives of the function.
-Moreover, the denominators of these functions are powers of each other, and so it is possible to clear them by a projection technique that will be introduced in Section~\ref{sec:Sim2}.
+The methods we use to construct the invariants, particularly the moving frames, produce invariants that are singular at points such as critical points.
+In all groups considered the invariants are rational functions of the derivatives of the function.
+Moreover, the denominators of these functions are powers of each other, and so it is possible to clear the denominators, thereby removing the singularity, by a projection technique that will be introduced in Section~\ref{sec:Sim2}.
 
@@
   y) \mapsto (x + 0.1, y - 0.2)$. (c) the signature of the
-  image (before translation). (d) the signatures before and after the
-  translation superimposed.}\label{fig:T2}
+  image (before translation). (d) the signatures before (blue) and after (red)
+  the translation superimposed, showing that the signature surface is invariant.}\label{fig:T2}
 \end{figure}
@@
 The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models.
-Invariants for this group have been computing using points~\citep{Gros1992,Suk2000}, geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and differential and joint invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19}.
+Invariants for this group have been computed using points~\citep{Gros1992,Suk2000}, geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and differential and joint invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19}.
 
@@
 \begin{aligned}
-  I_0 &= f = f \\
-  I_1 &= f_if_i = f_x^2 + f_y^2 \\
-  I_2 &= f_{ii} = f_{xx} + f_{yy} \\
-  I_3 &= f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \\
-  I_4 &= f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}.
+  I_0 &= f = f \,,\\
+  I_1 &= f_if_i = f_x^2 + f_y^2  \,,\\
+  I_2 &= f_{ii} = f_{xx} + f_{yy} \,,\\
+  I_3 &= f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 \,,\\
+  I_4 &= f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy}\,.
 \end{aligned}
@@
 
-Under similarity transformations, the Euclidean invariants become
-\emph{relative invariants}, i.e., each derivative introduces a multiple of $s$ to
+Under transformations by $\text{Sim}(2)$, the Euclidean invariants become
+\emph{relative} invariants, i.e., each derivative introduces a multiple of $s$ to
 each invariant. For example, $\bar{f}_{\bar x}^2 + \bar{f}_{\bar y}^2 =
@@
 Functions of these invariants are invariants or relative invariants for many groups that contain $E(2)$, such as those that we have considered in this paper.
+We will consider this further in future work.
 

### 2021-08-09 paper/newpaper.tex
Started on revisions

@@
 This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera against a fixed background.
-The appearance of each individual object will then vary independently as a constant camera motion or other such transformation is applied.
+The appearance of each individual object will then chnge in different ways as a constant camera motion or other such transformation is applied.
 Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.
@@
 
-Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} shows all possible non-zero partial
+Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} show all possible non-zero partial
 transvectants of $A_2$ up to weight $4$ that can be generated in this way.
@@
 
-The action of the affine group $A(2)$ arises in images as the motion of
-planar objects in images taken from a distant camera. Recall that
-because of the subgroup relationship, invariants of $A(2)$ are automatically invariants
-of $SA(2)$, but not necessarily vice versa. Any of the partial
-transvectants found in Tables~\ref{tab:transvectants1}
-and~\ref{tab:transvectants2} are relative invariants of $SA(2)$ (as the determinant
-is $1$). Hence, we can form a signature for $SA(2)$ by choosing any combination of
-partial transvectants. We choose a signature with three components so that
-it can be visualised as a three-dimensional surface; note that this will
-not be complete and may well have a very large bad set. For example, we can
-choose the function value together with $C$ and $D$ from Eq.~\eqref{eq:cde}
-to form the signature:
+The action of the affine group $A(2)$ arises in images as the motion of planar objects in images taken from a distant camera.
+Because $SA(2)$ is a subgroup of $A(2)$, any invariant of $A(2)$ is also an invariant of $SA(2)$, but not necessarily vice-versa.
+Any of the partial transvectants found in Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} are invariants of $SA(2)$ as the determinant is $1$.
+Hence, we can form a signature for $SA(2)$ by choosing any combination of partial transvectants.
+We choose a signature with three components so that it can be visualised as a three-dimensional surface; note that this will not be complete and may well have a very large bad set.
+For example, we can choose the function value together with $C$ and $D$ from Eq.~\eqref{eq:cde} to form the signature:
 
@@
 Considering the actions of such a transformation group enables the identification of invariants to that group since it defines a $\mathcal{G}$-equivariant mapping.
-A (right-) moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$, where $z \in J^d$.
-It is necessary~\citep{Olver2013} for the group act freely.
+A (right-) moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$, where $z \in J^d$ and where $\cdot$ denotes the group operation of $\mathcal{G}$.
+It is necessary~\citep{Olver2013} for the group to act freely.
 This means that the group action needs to be extended to the entire jet space of derivatives up to order $d$ by implicit differentiation of the group action, a process known as prolongation.

### 2021-08-25 paper/newerpaper.tex
Some updates

--- 2021-08-09 paper/newpaper.tex
@@
 \date{\today}
-\title{Differential invariant signatures for planar Lie group transformations of images}
+\title{Differential invariant signatures for planar Lie group transformations with application to images}
 \author{Richard Brown, Stephen Marsland, and Robert McLachlan}
@@
 \begin{abstract}
-Changes in viewpoint, such as camera motion, impose transformations on the objects in an image, and these transformations will differ for objects at different positions relative to the camera.
-Typically these transformations will be elements of planar Lie groups.
+The actions of different various Lie groups underlie the change of appearance of objects in images as the viewpoint changes, e.g., through camera motion.
 While there have been significant advances in object recognition using machine learning in recent years, the question of how to recognise an object in an image as its appearance varies through camera motion and similar effects remains open.
-We demonstrate how differential invariant signatures can be derived for each of the transformation groups, and how the underlying invariances reflect the group-subgroup structure of the transformation groups.
+We demonstrate how differential invariant signatures can be derived for each of the transformation groups, and how the underlying invariances reflect the group-subgroup structure of the relevant Lie groups.
 
@@
 This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera against a fixed background.
-The appearance of each individual object will then chnge in different ways as a constant camera motion or other such transformation is applied.
-Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.
-
-For image recognition it is then natural to seek representations of objects that do not change as these various transformation groups act.
-If the space of objects is denoted $M$ and the appearance transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$.
-One way to achieve this is by transforming all objects to match a chosen target object by registration (the transformation of the appearance of one shape to match another, typically by gradient descent on a matching function, see e.g.,~\citep{Modersitzki03}).
+The appearance of each individual object will then chnnge in different ways as a constant camera motion or other such transformation is applied.
+The individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.
+
+It is then natural to seek representations of objects that do not change as these various transformation groups act.
+If the space of objects is denoted $M$ and the transformations form a Lie group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$.
+One way to achieve this is to seek $\mathcal{G}$-invariant functions on $M$.
+Mathematical invariants provide a useful way to identify sets of objects that are the same up to some equivalence relation, since the functions are constant for objects in the same equivalence class (orbits of the group).
+For images, rather than considering the image of the object, one constructs an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group.
+This has been considered extensively by Olver and co-authors for the case of outlines of objects~\citep{Calabi1998,Hoff2013}.
+We extend this by considering the case of signatures for images rather than outlines of curves under a variety of planar Lie transformation groups, particularly those of relevance to image analysis.
+
+In this paper our aim is to follow the mathematical underpinnings of constructing differential invariant signatures for images under the action of (nested) planar Lie groups, and to summarise the impediments to a practical implementation, including the number of derivatives required.
+We demonstrate three distinct methods of computing differential invariants: by tensor contraction, using the theory of transvectants, and via the method of moving frames, applying the methods to a variety of the planar Lie groups, providing sample signature sets for the various groups we consider, together with an example of a sample signature surface based on a random transformation of a simple, smooth image.
+
+%An alternative option is by transforming all objects to match a chosen target object by registration (the transformation of the appearance of one shape to match another, typically by gradient descent on a matching function, see e.g.,~\citep{Modersitzki03}).
 For example, for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\citep{Kendall1989} will place all of the shapes into the reference frame of one template example.
@@
 
-An alternative option is to seek $\mathcal{G}$-invariant functions on $M$.
-Mathematical invariants provide a useful way to identify sets of objects that are the same up to some equivalence relation, since the functions are constant for objects in the same equivalence class (orbits of the group).
-For images, rather than considering the image of the object, one constructs an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group.
-This has been considered extensively by Olver and co-authors for the case of outlines of objects~\citep{Calabi1998,Hoff2013}.
-We extend this by considering the case of signatures for images rather than outlines of curves under a variety of transformation groups of relevance to image analysis.
+\subsection{Invariant signatures of images}
 
@@
 We do not consider the question of classification further in this paper; a standard image recognition algorithm can be used (see, e.g.,~\citet{Zhang20} for a survey), or a matching method such as~\citet{UsCurrents} can be used.
+
+We define a {\em $k$-colour image} as a triple $(f,\Omega,k)$ where $\Omega\subset\R^n$ (typically, images are planar, so $n=2$), $1\le k\in\mathbb{Z}$ is the number of colour channels, and $f\colon\Omega\to\R^k$.
+The function $f$ will be taken to be as smooth as necessary.
+Consider a (finite or infinite-dimensional) local transformation group $\mathcal{G}$.
+A transformation $\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) = (f\circ\varphi^{-1},\varphi(\Omega),k)$.
+We mostly consider greyscale images, so $k=1$.
+Also, since we work locally, we will usually omit the domain $\Omega$.
+
+In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$ via the jet space~\citep{OlverEIS}.
+The $d$-th order jet space $J^d$ consists of the function itself and the set of all partial derivatives of the function up to order $d$.
+(Note that there are $\left( \begin{array}{c} d+k-1 \\ k \end{array} \right)$ partial derivatives of order $d$.) As the group $\mathcal{G}$ is local, it acts naturally on derivatives of the transformation, and so each individual transformation $\varphi \in \mathcal{G}$ can be prolonged to act on the jet space $J^d$.
+We can thus prolong the action of the group and consider the action of $\mathcal{G}$ on not just $f$, but all derivatives of $f$ up to order $d$.
+A $d$-th order differential invariant is then a local scalar function $I: J^{d} (f,\Omega, k) \to \mathbb{R}$ that is invariant under the action of $\mathcal{G}$, i.e., $I(\varphi(f,\Omega, k)) = I(f, \Omega, k) \forall \varphi \in \mathcal{G}$.
+It can also be useful to consider the maximum order of derivative in the invariant, which we term degree, e.g., $f_{xy}^2 f_x f_y$ has degree 2.
+
+The methods we use to construct the invariants, particularly the moving frames, produce invariants that are singular at points such as critical points.
+In all groups considered the invariants are rational functions of the derivatives of the function.
+Moreover, the denominators of these functions are powers of each other, and so it is possible to clear the denominators, thereby removing the singularity, by a projection technique that will be introduced in Section~\ref{sec:Sim2}.
+
+For the case of two-dimensional greyscale images it is often convenient to work in coordinates.
+In this case the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$ is given by (where $f$ and $\mathbf{x}$ denote the original image and coordinates, and $\bar{f}$ and $\bar{\mathbf{x}}$ the transformed versions):
+\begin{equation}\label{eq:transformation}
+  \mathbf{x} \mapsto \bar{\mathbf{x}} = \varphi(\mathbf{x}).
+\end{equation}
+The transformed image is then defined to be:
+\begin{equation}\label{eq:fbarequalsf}
+  \bar{f}(\bar{\mathbf{x}}) = (f\circ\varphi^{-1})(\bar{\mathbf{x}}) = f(\mathbf{x}).
+\end{equation}
+
+Derivatives of $\bar{f}$ and $f$ can be related by the chain rule, for example the first order derivatives are given by:
+\begin{equation}\label{eq:prolongation}
+  \begin{aligned}
+    f_x &= \bar{f}_{\bar{x}} \bar{x}_x + \bar{f}_{\bar{y}}\bar{y}_x \\
+    f_y &= \bar{f}_{\bar{x}} \bar{x}_y + \bar{f}_{\bar{y}}\bar{y}_y \\
+  \end{aligned}
+\end{equation}
+where $\bar{x}_x = \frac{\partial \varphi_1}{\partial x}(x, y)$, et cetera. %It is often convenient to work with $\varphi^{-1}$ instead, as in \S\ref{sec:movingframes}.
+
+A signature set is the image of $m$ invariants
+$\mathcal{I}=(I_1,I_2,\dots,I_m)$. For simplicity of notation we will write
+$\mathcal{I}(f) \subset \mathbb{R}^m$ with the understanding that each signature component is
+actually acting on the jet space $J^d(f, \Omega, k)$. See Section~\ref{sec:T2} for a basic
+example. A signature set is complete for $f$ if it determines $f$ up to
+transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde
+f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a
+transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$
+and $\tilde \Omega = \varphi(\Omega)$.
 
@@
 
-In this paper our aim is develop the mathematical underpinnings of constructing differential invariant signatures for images under the action of planar Lie groups, and to summarise the impediments to a practical implementation, including the number of derivatives required.
-We demonstrate three distinct methods of computing differential invariants: by tensor contraction, using the theory of transvectants, and via the method of moving frames, applying the methods to a variety of the planar Lie groups, providing sample signature sets for the various groups we consider, together with an example of a sample signature surface based on a random transformation of a simple, smooth image.
+\subsection{Relevant groups}
 
@@
 This makes them the groups most directly relevant to image transformations.
-The infinite-dimensional examples are likewise those most likely to be of interest for image transformation, in particular the full diffeomorphism group, which is commonly used for image registration for medical images, see e.g.,~\citet{YounesBook}.
+The infinite-dimensional (pseudo-Lie) examples are likewise those most likely to be of interest for image transformation, in particular the full diffeomorphism group, which is commonly used for image registration for medical images, see e.g.,~\citet{YounesBook}.
 
@@
 
-\section{Preliminaries}
-
-\subsection{Concepts and Notation}
-
-We define a {\em $k$-colour image} as a triple $(f,\Omega,k)$ where $\Omega\subset\R^n$ (typically, images are planar, so $n=2$), $1\le k\in\mathbb{Z}$ is the number of colour channels, and $f\colon\Omega\to\R^k$.
-The function $f$ will be taken to be as smooth as necessary.
-Consider a (finite or infinite-dimensional) local transformation group $\mathcal{G}$.
-A transformation $\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) = (f\circ\varphi^{-1},\varphi(\Omega),k)$.
-We mostly consider greyscale images, so $k=1$.
-Also, since we work locally, we will usually omit the domain $\Omega$.
-
-In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$ via the jet space~\citep{OlverEIS}.
-The $d$-th order jet space $J^d$ consists of the function itself and the set of all partial derivatives of the function up to order $d$.
-(Note that there are $\left( \begin{array}{c} d+k-1 \\ k \end{array} \right)$ partial derivatives of order $d$.) As the group $\mathcal{G}$ is local, it acts naturally on derivatives of the transformation, and so each individual transformation $\varphi \in \mathcal{G}$ can be prolonged to act on the jet space $J^d$.
-We can thus prolong the action of the group and consider the action of $\mathcal{G}$ on not just $f$, but all derivatives of $f$ up to order $d$.
-A $d$-th order differential invariant is then a local scalar function $I: J^{d} (f,\Omega, k) \to \mathbb{R}$ that is invariant under the action of $\mathcal{G}$, i.e., $I(\varphi(f,\Omega, k)) = I(f, \Omega, k) \forall \varphi \in \mathcal{G}$.
-It can also be useful to consider the maximum order of derivative in the invariant, which we term degree, e.g., $f_{xy}^2 f_x f_y$ has degree 2.
-
-An signature set is the image of $m$ invariants
-$\mathcal{I}=(I_1,I_2,\dots,I_m)$. For simplicity of notation we will write
-$\mathcal{I}(f) \subset \mathbb{R}^m$ with the understanding that each signature component is
-actually acting on the jet space $J^d(f, \Omega, k)$. See Section~\ref{sec:T2} for a basic
-example. A signature set is complete for $f$ if it determines $f$ up to
-transformations from $\mathcal{G}$, i.e., if $\mathcal{I}(\tilde
-f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies that there exists a
-transformation $\varphi\in \mathcal{G}$ such that $\tilde f = \varphi\cdot f$
-and $\tilde \Omega = \varphi(\Omega)$.
-
-The methods we use to construct the invariants, particularly the moving frames, produce invariants that are singular at points such as critical points.
-In all groups considered the invariants are rational functions of the derivatives of the function.
-Moreover, the denominators of these functions are powers of each other, and so it is possible to clear the denominators, thereby removing the singularity, by a projection technique that will be introduced in Section~\ref{sec:Sim2}.
-
-For the case of two-dimensional greyscale images it is often convenient to work in coordinates.
-In this case the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$ is given by (where $f$ and $\mathbf{x}$ denote the original image and coordinates, and $\bar{f}$ and $\bar{\mathbf{x}}$ the transformed versions):
-\begin{equation}\label{eq:transformation}
-  \mathbf{x} \mapsto \bar{\mathbf{x}} = \varphi(\mathbf{x}).
-\end{equation}
-The transformed image is then defined to be:
-\begin{equation}\label{eq:fbarequalsf}
-  \bar{f}(\bar{\mathbf{x}}) = (f\circ\varphi^{-1})(\bar{\mathbf{x}}) = f(\mathbf{x}).
-\end{equation}
-
-Derivatives of $\bar{f}$ and $f$ can be related by the chain rule, for example the first order derivatives are given by:
-\begin{equation}\label{eq:prolongation}
-  \begin{aligned}
-    f_x &= \bar{f}_{\bar{x}} \bar{x}_x + \bar{f}_{\bar{y}}\bar{y}_x \\
-    f_y &= \bar{f}_{\bar{x}} \bar{x}_y + \bar{f}_{\bar{y}}\bar{y}_y \\
-  \end{aligned}
-\end{equation}
-where $\bar{x}_x = \frac{\partial \varphi_1}{\partial x}(x, y)$, et cetera. %It is often convenient to work with $\varphi^{-1}$ instead, as in \S\ref{sec:movingframes}.
+\subsection{Relevant Literature}
+
+The theory of invariants has a rich mathematical history, starting from invariants of forms~\citep{Cayley}, where the invariants are polynomials in the coefficients of the forms, see e.g.,~\citet{OlverCIT,Kraft2002} for an overview.
+Geometric considerations and differential invariants followed fairly quickly~\citep{Veblen1872,Tresse1894,Bouton1898,Patterson1928}, particularly because they enabled the classification of differential equations into equivalence classes~\citep{Lie1884,Littlewood44, Cartan52}.
+More recently, this has been extended, primarily by Olver and collaborators, see e.g.,~\citet{OlverCIT} and~\citet{OlverEIS} for summaries.
+
+There has been a long-standing interest in constructing invariants for image recognition and pattern analysis, see e.g.,~\citet{Mundy1992} and~\citet{Wood1996}.
+This was set in the context of Lie's invariants by~\citet{VanGool1995}, where the concept of a joint (or semi-) differential invariant (an invariant that acts on the joint action of the transformation group, see~\citet{Fels1997,Olver2013}) was introduced~\citep{VanGool1992}; see also~\citet{Hubert2009}.
+
+A variety of function spaces have allowed for the creation of different sets of invariants for particular groups.
+For the Euclidean group, the Fourier transform provides a useful tool~\citep{Ghorbel1994,Turski2006,Smach2007,Gauthier2008}, and this can be extended to the affine group using the Fourier-Mellin transform~\citep{Reddy1996,Zhang2019} and the bispectrum~\citep{Kakarala2009,Negrinho2013}.
+Alternatively, integral invariants~\citep{Manay2006,Feng2010} and geometric moments can be computed.
+For the similarity group applied to images the original reference is \citet{Hu1962}, but see also~\citet{Hickman2011} for affine transformations, \citet{Flusser2009} for an implicit representation, and \citet{Papakostas2013} for their use in a binary pattern for image recognition, which is somewhat related to the invariant features such as SURF~\citep{SURF}.
+
+The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models.
+Invariants for this group have been computed using points~\citep{Gros1992,Suk2000}, geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and differential and joint invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19}.
+
+Although there are computational challenges regarding the numerical approximation of derivatives on images, the fact that differential invariants are robust to occlusion, cheap to compute, and well-behaved with respect to small changes in the image, has made them popular for researchers in image analysis~\citep{Florack1993}.
+Two particular tools have been key to this: Cartan's moving frame~\citep{Cartan35} (see Section~\ref{sec:movingframes}), and which was used to construct image invariants as early as 1994 by \citet{Faugeras1994}, and the concept of an image signature built from a set of invariants~\citep{Calabi1998}.
+An algorithm to compute differential and joint invariants and determine complete signature sets is described by \citet{Olver2005,Olver2007}.
+The entire set of invariants is computed using the method of moving frames and then the signature set of a maximal set of functionally independent invariants is identified.
+A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
 
@@
 %translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
-\subsection{Test image}
-
-For each signature set that we derive, it is informative to see an example signature of the kind of surface that is defined, 
-normally a two-dimensional surface in three-dimensions.  We will apply a small random transformation from 
-the relevant group to a single continuous image and plot the signature before and after this transformation has been applied.
-This is an aid to understanding rather than any form of demonstration of the robustness of our signature sets.
-
-The image we use is a continuous function (thus avoiding numerical issues in the approximation 
-of derivatives) defined on $[-1,1] \times [-1,1]$ as:
-
-\begin{equation}\label{eq:function}
-f(x, y) = \exp(-2x^2 - 4\sin^2(y + 0.5x^2))
-\end{equation}
-
-The function is depicted as a greyscale image in Fig.~\ref{fig:function}.
-We will use this function throughout, using the grid on the right of the figure to help visualise both the transformation and how the image
-is mapped into the three-dimensional signature surface.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=.45\textwidth]{Figs/function}
-  \includegraphics[width=.45\textwidth]{Figs/function_scanlines}
-  \caption{The test function used as an image, defined in Eq.~\eqref{eq:function}.
-On the left the image itself is shown, while on the right a version with a
-regular grid superimposed is given. 
-}\label{fig:function}
-\end{figure}
-
-\subsection{Getting Started: Translations}
+
+%Groups we've done:
+%translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
+\section{Differential Invariants By Direct Computation}
+
+\subsection{Translations}
 \label{sec:T2}
@@
 I_3\right)$ where $I_1 = f, I_2 = f_x, I_3 = f_y$.
+
+For each signature set that we derive, it is informative to see an example signature of the kind of surface that is defined, 
+normally a two-dimensional surface in three-dimensions.  We will apply a small random transformation from 
+the relevant group to a single continuous image and plot the signature before and after this transformation has been applied.
+This is an aid to understanding rather than any form of demonstration of the robustness of our signature sets.
+
+The image we use is a continuous function (thus avoiding numerical issues in the approximation 
+of derivatives) defined on $[-1,1] \times [-1,1]$ as:
+
+\begin{equation}\label{eq:function}
+f(x, y) = \exp(-2x^2 - 4\sin^2(y + 0.5x^2))
+\end{equation}
+
+The function is depicted as a greyscale image in Fig.~\ref{fig:function}.
+We will use this function throughout, using the grid on the right of the figure to help visualise both the transformation and how the image
+is mapped into the three-dimensional signature surface.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.45\textwidth]{Figs/function}
+  \includegraphics[width=.45\textwidth]{Figs/function_scanlines}
+  \caption{The test function used as an image, defined in Eq.~\eqref{eq:function}.
+On the left the image itself is shown, while on the right a version with a
+regular grid superimposed is given. 
+}\label{fig:function}
+\end{figure}
 
@@
 
-\subsection{Relevant Literature}
-
-The theory of invariants has a rich mathematical history, starting from invariants of forms~\citep{Cayley}, where the invariants are polynomials in the coefficients of the forms, see e.g.,~\citet{OlverCIT,Kraft2002} for an overview.
-Geometric considerations and differential invariants followed fairly quickly~\citep{Veblen1872,Tresse1894,Bouton1898,Patterson1928}, particularly because they enabled the classification of differential equations into equivalence classes~\citep{Lie1884,Littlewood44, Cartan52}.
-More recently, this has been extended, primarily by Olver and collaborators, see e.g.,~\citet{OlverCIT} and~\citet{OlverEIS} for summaries.
-
-There has been a long-standing interest in constructing invariants for image recognition and pattern analysis, see e.g.,~\citet{Mundy1992} and~\citet{Wood1996}.
-This was set in the context of Lie's invariants by~\citet{VanGool1995}, where the concept of a joint (or semi-) differential invariant (an invariant that acts on the joint action of the transformation group, see~\citet{Fels1997,Olver2013}) was introduced~\citep{VanGool1992}; see also~\citet{Hubert2009}.
-
-A variety of function spaces have allowed for the creation of different sets of invariants for particular groups.
-For the Euclidean group, the Fourier transform provides a useful tool~\citep{Ghorbel1994,Turski2006,Smach2007,Gauthier2008}, and this can be extended to the affine group using the Fourier-Mellin transform~\citep{Reddy1996,Zhang2019} and the bispectrum~\citep{Kakarala2009,Negrinho2013}.
-Alternatively, integral invariants~\citep{Manay2006,Feng2010} and geometric moments can be computed.
-For the similarity group applied to images the original reference is \citet{Hu1962}, but see also~\citet{Hickman2011} for affine transformations, \citet{Flusser2009} for an implicit representation, and \citet{Papakostas2013} for their use in a binary pattern for image recognition, which is somewhat related to the invariant features such as SURF~\citep{SURF}.
-
-The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models.
-Invariants for this group have been computed using points~\citep{Gros1992,Suk2000}, geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and differential and joint invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19}.
-
-Although there are computational challenges regarding the numerical approximation of derivatives on images, the fact that differential invariants are robust to occlusion, cheap to compute, and well-behaved with respect to small changes in the image, has made them popular for researchers in image analysis~\citep{Florack1993}.
-Two particular tools have been key to this: Cartan's moving frame~\citep{Cartan35} (see Section~\ref{sec:movingframes}), and which was used to construct image invariants as early as 1994 by \citet{Faugeras1994}, and the concept of an image signature built from a set of invariants~\citep{Calabi1998}.
-An algorithm to compute differential and joint invariants and determine complete signature sets is described by \citet{Olver2005,Olver2007}.
-The entire set of invariants is computed using the method of moving frames and then the signature set of a maximal set of functionally independent invariants is identified.
-A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
-
-%Groups we've done:
-%translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff
-\section{Differential invariants through tensor contraction}
+\subsection{Differential invariants through tensor contraction}
 \label{sec:contraction}
@@
 It was extended by~\citet{Cartan35} to the `method of moving frames'.
-If the group $\mathcal{G}$ is a Lie group then it has a homogeneous space and a frame of reference can be applied on the manifold structure of the group.
-Considering the actions of such a transformation group enables the identification of invariants to that group since it defines a $\mathcal{G}$-equivariant mapping.
+The actions of a Lie group $\mathcal{G}$ enables the identification of invariants to that group through the definition of a $\mathcal{G}$-equivariant mapping.
 A (right-) moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$, where $z \in J^d$ and where $\cdot$ denotes the group operation of $\mathcal{G}$.
@@
 \begin{enumerate}
-\item Prolong the group action to the jet space of $d$-th order derivatives: $F: J^d \to \mathbb{R}$. 
+\item Prolong the group action to the jet space of $d$-th order derivatives $J^d$.
 \item Apply Cartan normalisation:
@@
     \end{enumerate}
-\item The differential invariants are not affected by the action of the group: $I(g \cdot z) = I(z) \: \forall z \in \mathrm{dom} I$, or equivalently, if it is constant on the orbits. 
-\item Hence $F$ is made invariant by transforming it with a group action: $I(z) = F(g \cdot z) |_{g=\rho(z)}$.  
+\item The differential invariants are not affected by the action of the group: $I(g \cdot z) = I(z) \: \forall z \in \mathrm{dom} I$, or equivalently, are constant on the orbits. 
 \end{enumerate}

### 2021-09-14 paper/newerpaper.tex
More minor increments

@@
 
-In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$ via the jet space~\citep{OlverEIS}.
+In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$ via the jet space~\citep{Kruglikov2011,OlverEIS}.
 The $d$-th order jet space $J^d$ consists of the function itself and the set of all partial derivatives of the function up to order $d$.
@@
 Two particular tools have been key to this: Cartan's moving frame~\citep{Cartan35} (see Section~\ref{sec:movingframes}), and which was used to construct image invariants as early as 1994 by \citet{Faugeras1994}, and the concept of an image signature built from a set of invariants~\citep{Calabi1998}.
-An algorithm to compute differential and joint invariants and determine complete signature sets is described by \citet{Olver2005,Olver2007}.
+An algorithm to compute differential and joint invariants and determine complete signature sets is described by \citet{Olver2005,Olver2007}
 The entire set of invariants is computed using the method of moving frames and then the signature set of a maximal set of functionally independent invariants is identified.
 A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.
+Further work, including applications to ODEs and the Calculus of Variations can be found in~\cite{Mansfield}.
 
@@
 There is a general method, based on Cartan's method of moving frames, that is generally applicable, but finding good solutions with it still requires some ingenuity in general.
-Olver and co-authors have popularised the approach and made it applicable to object recognition based on outline curves, see~\citet{Olver2005} for an overview, and note particularly the original application paper~\citep{Calabi1998}.
+Olver and co-authors have developed~\cite{Fels1999} and popularised the approach, and made it applicable to object recognition based on outline curves, see~\citet{Olver2005} for an overview, and note particularly the original application paper~\citep{Calabi1998}.
 We introduce the method here and then demonstrate its use to find invariants to further groups, but for further technical details see~\citet{OlverCIT}.

### 2021-09-14 paper/newpaper.tex
Added reference to Olver

@@
 \section{Introduction}
-The appearance of a fixed object in a set of images can vary markedly depending upon such variables as pose and position relative to the camera, even though the object itself does not change.
-This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera against a fixed background.
-The appearance of each individual object will then chnge in different ways as a constant camera motion or other such transformation is applied.
-Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.
+The appearance of a fixed object in a set of images can vary markedly
+depending upon such variables as pose and position relative to the camera,
+even though the object itself does not change. This is even more marked in
+scenes that consist of multiple objects at different distances and
+orientations to the camera against a fixed background. The appearance of
+each individual object will then change in different ways as a constant
+camera motion or other such transformation is applied. Typically the
+individual transformations will appear as the action of an element of a
+planar Lie group, for example the affine, or projective groups, or an
+angle-preserving transformation from the conformal group, depending upon
+the camera model.
 
@@
 
-The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models.
-Invariants for this group have been computed using points~\citep{Gros1992,Suk2000}, geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and differential and joint invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19}.
+The group that has been of particular interest for image analysis is the
+projective group, because of its ubiquity in camera models. Invariants for
+this group have been computed using points~\citep{Gros1992,Suk2000},
+geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and
+differential and joint
+invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19, Olver2020}. In
+particular Olver, in \citet{Olver2020}, uses the same approach as we do in
+\S\ref{sec:projective}, but with a different moving frame normalization to
+produce a different set of projective image invariants.
 
@@
 
-\subsection{The Projective Group}
+\subsection{The Projective Group}\label{sec:projective}
 

### 2021-09-28 paper/newerpaper.tex
Ported accidental changes to newpaper into newerpaper. Next up nuevapapel.tex
Typos, JLT format

@@
-\documentclass[review,onefignum,onetabnum]{siamonline190516}
+\documentclass{artjlt}
+
+% Load whatever packages you need
 \usepackage{amsmath,amsfonts,graphicx}
@@
 
-\date{\today}
+% Make sure to set *all* of the following
 \title{Differential invariant signatures for planar Lie group transformations with application to images}
 \author{Richard Brown, Stephen Marsland, and Robert McLachlan}
+\lastname{Brown, Marsland, McLachlan}  %<-------------------
+
+% Mathematics Subject Classification 2000
+\msc{65D18, 53A55, 68U10}
+
+% Keywords and phrases
+\keywords{ Object recognition, planar transformation, planar Lie groups, invariants, differential invariant signature}
+
+% For each author, add one of the following
+\address{%
+Richard Brown \\               %<-------------------
+School of Information and Mathematical Sciences, Massey University, Palmerston North, New Zealand\\            %<-------------------
+r.g.brown@massey.ac.nz                %<-------------------
+}
+\address{%
+Stephen Marsland \\               %<-------------------
+School of Mathematics and Statistics, Victoria University of Wellington, Wellington, New Zealand\\            %<-------------------
+stephen.marsland@vuw.ac.nz                %<-------------------
+}
+\address{%
+Robert McLachlan \\               %<-------------------
+School of Information and Mathematical Sciences, Massey University, Palmerston North, New Zealand\\            %<-------------------
+r.mclachlan@massey.ac.nz                %<-------------------
+}
+
+%
+% The following are for editors only.
+%
+%\volume{VOLUME}
+%\annum{YEAR}
+%\issue{ISSUE}
+%\editor{NAME OF EDITOR}
+%\received{Date article was first received} 
+%\final{Date final version was received}
 
@@
 The actions of different various Lie groups underlie the change of appearance of objects in images as the viewpoint changes, e.g., through camera motion.
-While there have been significant advances in object recognition using machine learning in recent years, the question of how to recognise an object in an image as its appearance varies through camera motion and similar effects remains open.
+Despite significant advances in object recognition using machine learning in recent years, the question of how to recognise an object in an image as its appearance varies through camera motion and similar effects remains open.
 We demonstrate how differential invariant signatures can be derived for each of the transformation groups, and how the underlying invariances reflect the group-subgroup structure of the relevant Lie groups.
@@
 
-% REQUIRED
-\begin{keywords}
-Object recognition, planar transformation, planar Lie groups, invariants, differential invariant signature
-\end{keywords}
-
-% REQUIRED
-\begin{AMS}
-65D18, 53A55, 68U10
-\end{AMS}
-
 \section{Introduction}
@@
 This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera against a fixed background.
-The appearance of each individual object will then chnnge in different ways as a constant camera motion or other such transformation is applied.
+The appearance of each individual object will then change in different ways as a constant camera motion or other such transformation is applied.
 The individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.
 
-It is then natural to seek representations of objects that do not change as these various transformation groups act.
-If the space of objects is denoted $M$ and the transformations form a Lie group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$.
-One way to achieve this is to seek $\mathcal{G}$-invariant functions on $M$.
+It is therefore natural to seek representations of objects that do not change as these various transformation groups act.
+If the space of objects is denoted $M$ and the transformations form a Lie group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$, such as by seeking $\mathcal{G}$-invariant functions on $M$.
 Mathematical invariants provide a useful way to identify sets of objects that are the same up to some equivalence relation, since the functions are constant for objects in the same equivalence class (orbits of the group).
@@
 In this paper our aim is to follow the mathematical underpinnings of constructing differential invariant signatures for images under the action of (nested) planar Lie groups, and to summarise the impediments to a practical implementation, including the number of derivatives required.
-We demonstrate three distinct methods of computing differential invariants: by tensor contraction, using the theory of transvectants, and via the method of moving frames, applying the methods to a variety of the planar Lie groups, providing sample signature sets for the various groups we consider, together with an example of a sample signature surface based on a random transformation of a simple, smooth image.
+We demonstrate three distinct methods of computing differential invariants: by tensor contraction, using the theory of transvectants, and via the method of moving frames, applying the methods to a variety of the planar Lie groups, and providing sample signature sets for the various groups we consider, together with an example of a sample signature surface based on a random transformation of a simple, smooth image.
 
@@
 
-The methods we use to construct the invariants, particularly the moving frames, produce invariants that are singular at points such as critical points.
+The methods we use to construct the invariants, particularly the moving frame, produce invariants that are singular at points such as critical points.
 In all groups considered the invariants are rational functions of the derivatives of the function.
@@
 $\mathcal{I}(f) \subset \mathbb{R}^m$ with the understanding that each signature component is
-actually acting on the jet space $J^d(f, \Omega, k)$. See Section~\ref{sec:T2} for a basic
+actually acting on the jet space $J^d(f, \Omega, k)$; see Section~\ref{sec:T2} for a basic
 example. A signature set is complete for $f$ if it determines $f$ up to
@@
 Although there are computational challenges regarding the numerical approximation of derivatives on images, the fact that differential invariants are robust to occlusion, cheap to compute, and well-behaved with respect to small changes in the image, has made them popular for researchers in image analysis~\citep{Florack1993}.
-Two particular tools have been key to this: Cartan's moving frame~\citep{Cartan35} (see Section~\ref{sec:movingframes}), and which was used to construct image invariants as early as 1994 by \citet{Faugeras1994}, and the concept of an image signature built from a set of invariants~\citep{Calabi1998}.
+Two particular tools have been key to this: Cartan's moving frame~\citep{Cartan35} (see Section~\ref{sec:movingframes}), which was used to construct image invariants as early as 1994 by \citet{Faugeras1994}, and the concept of an image signature built from a set of invariants~\citep{Calabi1998}.
 An algorithm to compute differential and joint invariants and determine complete signature sets is described by \citet{Olver2005,Olver2007}

### 2022-03-09 paper/newerpaper.tex
And one more..
revisions for referee

@@
 \usepackage{natbib}
+\usepackage{url}
 
@@
 \begin{abstract}
-The actions of different various Lie groups underlie the change of appearance of objects in images as the viewpoint changes, e.g., through camera motion.
+The actions of various Lie groups underlie the change of appearance of objects in images as the viewpoint changes, e.g., through camera motion.
 Despite significant advances in object recognition using machine learning in recent years, the question of how to recognise an object in an image as its appearance varies through camera motion and similar effects remains open.
@@
 In order to define differential invariants, it is necessary to identify how the group transformation $\varphi$ acts on derivatives of the function $f$ via the jet space~\citep{Kruglikov2011,OlverEIS}.
-The $d$-th order jet space $J^d$ consists of the function itself and the set of all partial derivatives of the function up to order $d$.
+The $d$-th order jet space $J^d$ is coordinatised by the function itself and the set of all partial derivatives of the function up to order $d$.
 (Note that there are $\left( \begin{array}{c} d+k-1 \\ k \end{array} \right)$ partial derivatives of order $d$.) As the group $\mathcal{G}$ is local, it acts naturally on derivatives of the transformation, and so each individual transformation $\varphi \in \mathcal{G}$ can be prolonged to act on the jet space $J^d$.
@@
 A $d$-th order differential invariant is then a local scalar function $I: J^{d} (f,\Omega, k) \to \mathbb{R}$ that is invariant under the action of $\mathcal{G}$, i.e., $I(\varphi(f,\Omega, k)) = I(f, \Omega, k) \forall \varphi \in \mathcal{G}$.
-It can also be useful to consider the maximum order of derivative in the invariant, which we term degree, e.g., $f_{xy}^2 f_x f_y$ has degree 2.
+It can also be useful to consider the maximum order of derivative in the invariant, which we term the degree, e.g., $f_{xy}^2 f_x f_y$ has degree 2.
 
@@
 
-The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models.
-Invariants for this group have been computed using points~\citep{Gros1992,Suk2000}, geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and differential and joint invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19}.
-
-Although there are computational challenges regarding the numerical approximation of derivatives on images, the fact that differential invariants are robust to occlusion, cheap to compute, and well-behaved with respect to small changes in the image, has made them popular for researchers in image analysis~\citep{Florack1993}.
+The group that has been of particular interest for image analysis is the
+projective group, because of its ubiquity in camera models. Invariants for
+this group have been computed using points~\citep{Gros1992,Suk2000},
+geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and
+differential and joint
+invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19}.  In particular
+Olver, in \citet{Olver2020}, uses the same approach as we do in
+\S\ref{sec:projective}, but with a different moving frame normalization to
+produce a different set of projective image invariants.
+
+Although there are computational challenges regarding the numerical approximation of derivatives on images, the fact that differential invariants are robust to occlusion, cheap to compute, and are based on local computations, has made them popular for researchers in image analysis~\citep{Florack1993}.
 Two particular tools have been key to this: Cartan's moving frame~\citep{Cartan35} (see Section~\ref{sec:movingframes}), which was used to construct image invariants as early as 1994 by \citet{Faugeras1994}, and the concept of an image signature built from a set of invariants~\citep{Calabi1998}.
@@
 We will use this function throughout, using the grid on the right of the figure to help visualise both the transformation and how the image
-is mapped into the three-dimensional signature surface.
+is mapped into the three-dimensional signature surface. Note that there is nothing particularly special about this particular function; it has relatively 
+well-behaved derivatives, includes a critical point, and decays towards the boundary of the image.
 
@@
 Taking $I_1^2$, $I_2^2$, and $I_3$ from \eqref{eq:e2tensor}, all of which are
-weight $4$, they can be projected on to the unit sphere, which can be
-multiplied by $I_0 = f$ to form a signature surface. This signature is
-defined by:
+weight $4$, defines a surface up to scale, and so they can be projected on to the unit sphere. 
+We therefore multiply by another invariant to form the signature surface; an appropriate choice 
+is $I_0 = f$. This signature is defined by:
 \begin{equation}
@@
 \end{equation}
-This signature is only singular when $f_x = f_y = f_{xx} = f_{yy} = f_{xy}
+It is only singular when $f_x = f_y = f_{xx} = f_{yy} = f_{xy}
 = 0$. A sample similarity transformation and computed signature is shown in
@@
 A moving frame is a mapping into a group $\mathcal{G}$ that provides a frame of reference along a manifold.
-It was extended by~\citet{Cartan35} to the `method of moving frames'.
-The actions of a Lie group $\mathcal{G}$ enables the identification of invariants to that group through the definition of a $\mathcal{G}$-equivariant mapping.
+It was used by~\citet{Cartan35} as the basis for his `method of moving frames', which uses Cartan equivalence to identify the set of structural invariants of a manifold.
+\cite{Fels1998,Fels1999} showed that the actions of a Lie group $\mathcal{G}$ enable the identification of invariants to that group through the definition of a $\mathcal{G}$-equivariant mapping.
 A (right-) moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$, where $z \in J^d$ and where $\cdot$ denotes the group operation of $\mathcal{G}$.
@@
 invariants found previously by tensor contraction Eq. (\ref{eq:e2tensor}) in
-Section~\ref{sec:contraction} can be expressed in terms of them:
+Section~\ref{sec:contraction} can be expressed in terms of them (see the replacement theorem in \cite{Fels1999} for a justification of this):
 \begin{align*}
@@
 \begin{enumerate}
-\item The frame $\bar f_{\bar x}=1$, $\bar f_{\bar y}=0$ determines two group parameters:
+\item The partial cross-section $\bar f_{\bar x}=1$, $\bar f_{\bar y}=0$ determines two group parameters:
 $$ a = f_x/(f_x^2 + f_y^2),\quad b = f_y/(f_x^2 f_y^2).$$
 
-\item The frame $\bar f_{\bar x \bar y}=\bar f_{\bar y \bar y}=0$ determines the next group parameters:
+\item The partial cross-section $\bar f_{\bar x \bar y}=\bar f_{\bar y \bar y}=0$ determines the next group parameters:
 $$ c = (2 f_xf_yf_{xyy} - f_{xx}f_y^2 - f_{yy}f_x^2)/(2 f_x^2 + f_y^2)^2$$
@@
 = 1$ and $\bar f_{\bar y}=  0$, which determines the group parameters $a =
-(1-c f_y)/f_x.$ and $b = -d f_y/f_x$. Direction substition then shows that
+(1-c f_y)/f_x.$ and $b = -d f_y/f_x$. Direct substition then shows that
 $\bar f_{\bar y \bar y} = D d^2 / f_x^2$, where $D = f_{x}^2 f_{yy} + f_y^2
@@
 
-The frame $\bar f_{ \bar y \bar y \bar y} = 0$ determines the group
+The partial cross-section $\bar f_{ \bar y \bar y \bar y} = 0$ determines the group
 parameter $ h = \frac{f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2
